### 2012-11-30 protein.tex
first commit

\documentclass[pdftex,10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{wrapfig}
\begin{document}
\bibliographystyle{unsrt}

It is vital during the process of bacterial cell division for proper nucleiod occlusion that the FtsZ polymer chain develop on the cell wall in the center of the cell.  Huang et all have shown in simulation that a system of Min protein interaction within the cell will lead to a natural oscillation of the MinC protein from one cell end to the other that will leave the center free of any build up of MinC.  This will allow for the PtsZ chain to develop in the center and not at the ends, where the two nucleiods are housed.  The cell has a built in method of ensuring that minicelling during cell division deos not occur.  The interaction takes place between MinE,MinD, and MinC, which naturally associates with MinD.  During an oscillation period, MinD accumulates at the end of the cell in a polar zone.  It is membrane-associated in its ATP bound form, and while membrane associated it recruits MinC to the cell wall (blocking FtsZ formation).  Meanwhile the MinE forms a cytoplasmic ring at the edge of the MinD polar zone with some MinE in the zone itself.  The MinD zone shrinks and builds up on the other side of the cell.  Huang's simulation involves basic interactions between the MinD, MinE, and ATP.  MinD:ATP builds up on the membrane, where it interacts with cytoplasmic MinE that activates hydrolisis and MinE and MinD:ADP enter back into the cell.

Mannik et all have shown that the formation of irregular cell shapes adversly effects the Min system's ability to maintain their regular oscillatory behavior, while the accuracy of daughter cell size in cell division is much more stable.  This shows the importance of the other regulating factor in cell division - nucleiod occlusion.  They use microfabricated silicon chips that have etched microchambers and shallow channels.  The debth of the chambers is 1.8$\mu$m and squeezes the bacteria into channels of .25$\mu$m.  Upon entering the channels, the cells quickly widen along their short axis by 30-40 percent and then slow remodeling of the cell wall with the mechanical stress, broadens the cells so that they can reach diameters of 5 $\mu$m.  Daighter cell size after division is recorded and the data is evaluated in histograms against the ratio of volume between the two cells.  Suprisingly, the central peak around a .5 division - so equal sizes between them, is largely not affected by the flattening of cells.  99 percent of the unflattened cells and 90 percent of the flattened ones fall in limits of .375 and .625, and the standard deviation of the peaks themselves are very similar.  With the flattened cells, the the ones that fall outside of this mid range create small spikes at .25 and .75, correspnding to daughter cells that have a 1:3 ratio.

They gneetically mutate the bacterial cells in order to eliminate certain proteins from them.  They eliminate MinC and SlmA.  SlmA deletion has very little effect accept for some assymetry in cell division area.  The MinC deletion shows a difference in volume division.  Only 73 percent divide with the approximate 1:1 ratio while for un deleted 99 percent do.  This effect is seen in both flattened and unflattened cells, and its very similar in both, which is suprising.
In the flattened cells, there is still MinD maxima of localization, but these will sometimes split into multiple maxima as opposed to just the the usual back and forth single maxima.  This causes the usual polarized time averages to be more uniform, which will cause the min protein system to have less of an effect on the cell division process.  
The nuclioed occlusion process works as, the nucleioeds seperate into the different poles, and the FtsZ begins to set up where the nuclioeds are not -into the gap in the center.  Mannik shows with time-lapse imaging that the gap between develops first and then the FtsZ.  Even in flattened and abberent shaped cells, there's a strong anti-correlation between FtsZ and chromosomes in the nucleioeds.  Most of this is about the occlusion of the nuclioeds by analyzing the anticorrelation between the FtsZ and the chromosomal mass.  So these anticorrelations are not effected by the deletion of MinC or slmA except for the FtsZ formation that leads to minicells.  In these cases, the anticorreltion is not strong, so the nucleiods seem to be closer and no occlusion (this is not totally it, it's top of pg 5 in this paper).

Hello cruel, cruel world. \cite{huang2003dynamic} \cite{mannik2012robustness}
\cite{huang2006curvature}
\bibliography{protein}
\end{document}

### 2012-11-30 protein.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+pdflatex protein.tex
+bibtex protein
+pdflatex protein.tex
+pdflatex protein.tex
+evince protein.pdf

### 2012-11-30 protein.tex
second commit

@@
 
+Bump.fdsfdsfds
 It is vital during the process of bacterial cell division for proper nucleiod occlusion that the FtsZ polymer chain develop on the cell wall in the center of the cell.

### 2012-11-30 protein.tex
stufftwo

--- 2012-11-30 protein.tex
@@
 
+Bump.fdsfdsfdsoblem  Hello cruel cruel World!  The other thing
 It is vital during the process of bacterial cell division for proper nucleiod occlusion that the FtsZ polymer chain develop on the cell wall in the center of the cell.

### 2013-06-26 protein.cpp
includes catalog.txt change

@@ -349,6 +349,38 @@ int main (int argc, char *argv[]) {
     Ny = ceil(2*A/dx) + 4;
     Nz = ceil(2*B/dx) + 4;
   }
+
+  //printing to a catalog for each directory so we know what we've run.
+
+  char *fname = new char[1024];
+  sprintf(fname,"data/shape-%s/catalog.txt",mem_f_shape.c_str());
+  FILE * catalog;
+  int catalog_exists;
+
+  time_t rawtime;
+  struct tm * timeinfo;
+
+  time (&rawtime);
+  timeinfo = localtime (&rawtime);
+
+  catalog = fopen(fname,"r");
+  if (catalog==NULL) {
+    catalog_exists=0;
+  }
+  else {
+    catalog_exists=1;
+    fclose(catalog);
+  }
+  if (catalog_exists==1) {
+    catalog=fopen(fname,"a+b");
+  }
+  else { 
+    catalog=fopen(fname,"w+b");
+  }
+  if (catalog!=NULL) {
+    fprintf(catalog," %s %1.2f %1.2f %1.2f %1.2f %1.2f\n", mem_f_shape.c_str(),A,B,C,D,density_factor);
+    fclose(catalog);
+  }
   char * out_file_name = new char[1024];
   sprintf(out_file_name,"data/shape-%s/out_files/%s-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.out",mem_f_shape.c_str(),mem_f_shape.c_str(),A,B,C,D,density_factor);
   FILE * out_file = fopen((const char *)out_file_name,"w");
@@ -478,7 +510,7 @@ int main (int argc, char *argv[]) {
           if (insideArr[i*Ny*Nz+j*Nz+k]==true){
             double area_rating = 0;
             double area_rating_two = 0;
-            for (int i2=0;i2<Nx;i2++){ // possible source of membrane.dat problem?
+            for (int i2=0;i2<Nx;i2++){
               for (int j2=0;j2<Ny;j2++){
                 for (int k2=0;k2<Nz;k2++){
                   if(i2!=i && j2!=j && k2!=k){

### 2013-06-26 pyplots/extrema.py

@@ -82,7 +82,7 @@ def maxvectorplot(dataset):
     X,Y,U,V = zip(*displacements)
     figure()
     ax = plt.gca()
-    ax.quiver(X,Y,U,V,angles='xy',scale_units='xy',scale=1)
+    ax.quiver(X,Y,U,V,scale_units='xy',angles='xy',scale=1)
     xlim((0,data_shape[0]))
     ylim((0,data_shape[1]))
     scatter(unzip_membrane(cell_membrane)[0],unzip_membrane(cell_membrane)[1])

### 2013-07-11 protein_microscopy.cpp
changed two elifs to ifs

@@ -306,11 +306,11 @@ int main (int argc, char *argv[]) {
       area_rating_flag = 1;
       printf("Area rating printout.\n");
     }
-    else if (strcmp(argv[i],"-hires")==0) {
+    if (strcmp(argv[i],"-hires")==0) {
       dx=.05;
       printf("Using high resolution.\n");
     }
-    else if (strcmp(argv[i],"-slice")==0) {
+    if (strcmp(argv[i],"-slice")==0) {
       slice_flag = 1;
       printf("Printing middle slice data.\n");
     }

### 2013-07-11 paper/paper.tex
includes catalog.txt change
paper outline

--- 2012-11-30 protein.tex
@@
-\documentclass[pdftex,10pt,a4paper]{article}
-\usepackage[latin1]{inputenc}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{fullpage}
-\usepackage{graphicx}
-\usepackage{wrapfig}
+\documentclass[letterpaper,twocolumn,amsmath,amssymb,pre]{revtex4-1}
+\usepackage{graphicx}% Include figure files
+\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
+\usepackage{color}
+\usepackage{breqn}
+
+\newcommand{\red}[1]{{\bf \color{red} #1}}
+\newcommand{\blue}[1]{{\bf \color{blue} #1}}
+\newcommand{\green}[1]{{\bf \color{green} #1}}
+\newcommand{\rr}{\textbf{r}}
+\newcommand{\refnote}{\red{[ref]}}
+
+\newcommand{\fixme}[1]{\red{[#1]}}
+
+%\newcommand{\derivation}[1]{#1} % Use this to show all derivations in detail
+\newcommand{\derivation}[1]{} % Use this for nice pegagogical paper...
+
+% needsworklater is used to annotate bits that need work, but that we
+% can postpone for a while.
+\newcommand{\needsworklater}[1]{\emph{[#1]}}
+% needsworknow is intended to prioritize stuff that needs fixing.
+\newcommand{\needsworknow}[1]{\textcolor{red}{[\emph{#1}]}}
+
 \begin{document}
-\bibliographystyle{unsrt}
+\title{E Coli project paper}
 
-It is vital during the process of bacterial cell division for proper nucleiod occlusion that the FtsZ polymer chain develop on the cell wall in the center of the cell.
-Huang et all have shown in simulation that a system of Min protein interaction within the cell will lead to a natural oscillation of the MinC protein from one cell end to the other that will leave the center free of any build up of MinC.
-This will allow for the PtsZ chain to develop in the center and not at the ends, where the two nucleiods are housed.
-The cell has a built in method of ensuring that minicelling during cell division deos not occur.
-The interaction takes place between MinE,MinD, and MinC, which naturally associates with MinD.
-During an oscillation period, MinD accumulates at the end of the cell in a polar zone.
-It is membrane-associated in its ATP bound form, and while membrane associated it recruits MinC to the cell wall (blocking FtsZ formation).
-Meanwhile the MinE forms a cytoplasmic ring at the edge of the MinD polar zone with some MinE in the zone itself.
-The MinD zone shrinks and builds up on the other side of the cell.
-Huang's simulation involves basic interactions between the MinD, MinE, and ATP.
-MinD:ATP builds up on the membrane, where it interacts with cytoplasmic MinE that activates hydrolisis and MinE and MinD:ADP enter back into the cell.
+%\pacs{61.20.Ne, 61.20.Gy, 61.20.Ja}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{abstract}
+  This paper is about science.
+\end{abstract}
 
-Mannik et all have shown that the formation of irregular cell shapes adversly effects the Min system's ability to maintain their regular oscillatory behavior, while the accuracy of daughter cell size in cell division is much more stable.
-This shows the importance of the other regulating factor in cell division - nucleiod occlusion.
-They use microfabricated silicon chips that have etched microchambers and shallow channels.
-The debth of the chambers is 1.8$\mu$m and squeezes the bacteria into channels of .25$\mu$m.
-Upon entering the channels, the cells quickly widen along their short axis by 30-40 percent and then slow remodeling of the cell wall with the mechanical stress, broadens the cells so that they can reach diameters of 5 $\mu$m.
-Daighter cell size after division is recorded and the data is evaluated in histograms against the ratio of volume between the two cells.
-Suprisingly, the central peak around a .5 division - so equal sizes between them, is largely not affected by the flattening of cells.
-99 percent of the unflattened cells and 90 percent of the flattened ones fall in limits of .375 and .625, and the standard deviation of the peaks themselves are very similar.
-With the flattened cells, the the ones that fall outside of this mid range create small spikes at .25 and .75, correspnding to daughter cells that have a 1:3 ratio.
+\section{Why does the E. Coli distribution matter?}
+\subsection{E. Coli are important}
+\subsection{E. Coli theory enables treatment of inhomogeneous systems}
+\subsection{E. Coli distribution function is key input in thermodynamic perturbation theory}
+\subsection{Explain what the $a_1$ in thermodynamic E. Coli theory is}
 
-They gneetically mutate the bacterial cells in order to eliminate certain proteins from them.
-They eliminate MinC and SlmA.
-SlmA deletion has very little effect accept for some assymetry in cell division area.
-The MinC deletion shows a difference in volume division.
-Only 73 percent divide with the approximate 1:1 ratio while for un deleted 99 percent do.
-This effect is seen in both flattened and unflattened cells, and its very similar in both, which is suprising.
-In the flattened cells, there is still MinD maxima of localization, but these will sometimes split into multiple maxima as opposed to just the the usual back and forth single maxima.
-This causes the usual polarized time averages to be more uniform, which will cause the min protein system to have less of an effect on the cell division process.
-The nuclioed occlusion process works as, the nucleioeds seperate into the different poles, and the FtsZ begins to set up where the nuclioeds are not -into the gap in the center.
-Mannik shows with time-lapse imaging that the gap between develops first and then the FtsZ.
-Even in flattened and abberent shaped cells, there's a strong anti-correlation between FtsZ and chromosomes in the nucleioeds.
-Most of this is about the occlusion of the nuclioeds by analyzing the anticorrelation between the FtsZ and the chromosomal mass.
-So these anticorrelations are not effected by the deletion of MinC or slmA except for the FtsZ formation that leads to minicells.
-In these cases, the anticorreltion is not strong, so the nucleiods seem to be closer and no occlusion (this is not totally it, it's top of pg 5 in this paper).
+\section{What E. Coli has been done before?}
+\subsection{Gloor simple method, problematic E. Coli}
 
-Hello cruel, cruel world. \cite{huang2003dynamic} \cite{mannik2012robustness}
-\cite{huang2006curvature}
-\bibliography{protein}
+\subsection{Fischer accurate but E. Coli}
+
+\section{Triplet E. Coli correlation function?}
+
+\section{What is our new E. Coli?}
+
+\section{What does E. Coli look like (graphs that show the E. Coli itself)?}
+\subsection{Fit to radial E. Coli function}
+
+\section{How well does E. Coli work?}
+
+\section{THE END OF THE E. COLI}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction to E. Coli}
+
+\section{Previous E. Coli}
+
+\section{Pair distribution function with E. Coli}
+
+\section{Goals of this E. Coli (to be integrated into rest of paper)}
+
+\section{Theoretical E. Coli}
+
+\section{Comparison with e. coli}\label{sec:comparison}
+
+\section{Conclusion}
+
+\appendix
+
+\section*{Appendix}
+%\cite{jin2011perturbative} Combines hard sphere (white bear) with attraction that is not mean field but rather uses two other correltation expressions given in  -\cite{tang2008accurate} and \cite{hlushak2009direct}
+
+%Tang \cite{tang2008accurate}Derives the direct correltation for a SW and Yukawa and LJ potentials by first getting the radial distribution function through a method I don't really understand.
+Composes fourier transforms $c(k)$ and $h(k)$ of these complicated functions that depend on filling fraction and the potential in an integral.
+Uses first order mean spherical approximation.
+This is just square potential well around particle but the radial distribution function takes only the first order in an expansion in...
+(high temp?).
+
+%\bibliography{paper}% Produces the bibliography via BibTeX.
+
 \end{document}

### 2013-07-12 paper/paper.tex
started outline of paper

@@
 
-\section{Why does the E. Coli distribution matter?}
-\subsection{E. Coli are important}
-\subsection{E. Coli theory enables treatment of inhomogeneous systems}
-\subsection{E. Coli distribution function is key input in thermodynamic perturbation theory}
-\subsection{Explain what the $a_1$ in thermodynamic E. Coli theory is}
+\section{Introduction}
+\subsection{What is the MinD system and why is it important?}
+-Systm of proteins in E.Coli and other cells.
+-Theorized to be instrumental in cell citokenisis. Reference experiments
+\subsection{How proteins move in cell}
+-Reference experimental showing proteins oscillating
+-Reference theory showing difEQ model shows oscillations
+-Reference Mannik shoving into crevices.
+-Worthwhile studying effect of walls shape on the movement of cells
+(Sign post of what to expect from this paper)
 
-\section{What E. Coli has been done before?}
-\subsection{Gloor simple method, problematic E. Coli}
+\section{Methods and Initial Conditions}
 
-\subsection{Fischer accurate but E. Coli}
+\section{Specific Results}
+-Data and plots that show concrete results.
 
-\section{Triplet E. Coli correlation function?}
-
-\section{What is our new E. Coli?}
-
-\section{What does E. Coli look like (graphs that show the E. Coli itself)?}
-\subsection{Fit to radial E. Coli function}
-
-\section{How well does E. Coli work?}
-
-\section{THE END OF THE E. COLI}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction to E. Coli}
-
-\section{Previous E. Coli}
-
-\section{Pair distribution function with E. Coli}
-
-\section{Goals of this E. Coli (to be integrated into rest of paper)}
-
-\section{Theoretical E. Coli}
-
-\section{Comparison with e. coli}\label{sec:comparison}
+\section{Interpretation of Data}
+-Discussion of conceptual reasons of why we see what we see
+-Plots that are more interpretive (area-rating)
+-Some sort of predictive claim?
 
@@
 \section*{Appendix}
-%\cite{jin2011perturbative} Combines hard sphere (white bear) with attraction that is not mean field but rather uses two other correltation expressions given in  -\cite{tang2008accurate} and \cite{hlushak2009direct}
-
-%Tang \cite{tang2008accurate}Derives the direct correltation for a SW and Yukawa and LJ potentials by first getting the radial distribution function through a method I don't really understand.
-Composes fourier transforms $c(k)$ and $h(k)$ of these complicated functions that depend on filling fraction and the potential in an integral.
-Uses first order mean spherical approximation.
-This is just square potential well around particle but the radial distribution function takes only the first order in an expansion in...
-(high temp?).
-
-%\bibliography{paper}% Produces the bibliography via BibTeX.
 

### 2013-07-12 paper/protein_paper.sh

@@ -1,6 +1,6 @@
 #!/bin/bash
-pdflatex protein.tex
-bibtex protein
-pdflatex protein.tex
-pdflatex protein.tex
-evince protein.pdf
+pdflatex paper.tex
+#bibtex paper
+pdflatex paper.tex
+pdflatex paper.tex
+evince paper.pdf

### 2013-07-12 protein_microscopy.cpp

@@ -42,7 +42,7 @@ double *nATP; //min D bound to an ATP
 double *nADP; //min D bound to an ADP
 double *nE; //loose min E in cytoplasm
 double *Nd; //min D bound to ATP on the wall
-double *Nde; //min D bound to ATP and min E on the wall 
+double *Nde; //min D bound to ATP and min E on the wall
 double *f_mem;
 
 const int starting_num_guassians=20;

### 2013-07-12 paper/paper.tex
first draft of methodology section

--- 2013-07-11 paper/paper.tex
@@
 
+\section{Methodology}
+\subsection{Mathematical Model} %shouldn't be a scripty mu
+The model for the behavio r of the MinD and MinE proteins inside the cell
+implemented the same set of 5 reaction-diffusion equations described in the paper
+by Huang et al (equations 1, 2, 3, 4, and 5). A 3d grid was constructed in
+cartesian coordinates with a grid spacing of .05 $\mu$m. From there, we
+were able to define a cell shape on the grid, and solve the
+reaction-diffusion equations numerically to observe the time evolution of
+the MinD and MinE concentrations inside the cell.
+
+Our simulation used the same diffusion constants and reaction rates as
+Huang et al, which are
+
+\begin{align*} %format better
+  \mathcal{D}_D = \mathcal{D}_{E}  = 2.5 \mu \textrm{m$^2$ / sec}, \\
+  \sigma_D^{\textrm{ADP $\rightarrow$ ATP}} = 1/\textrm{sec},  \sigma_D = 0.025 \mu \textrm{m/sec}, \\
+  \sigma_{dD} = 0.0015 \mu \textrm{m$^3$/sec}, \\
+  \sigma_{de} = 0.7/\textrm{sec}, \sigma_E = 0.093 \mu \textrm{$m^3$/sec}.
+\end{align*}
+
+To test our computational model, we implemented a pill shaped cell, and
+tested using the same cell parameters as Huang et al, which were a radius
+of 0.5 $\mu$m in the middle and at the spherical endcaps, and two different
+cell lengths of 4 $\mu$m and 10 $\mu$m. We found the same type of
+oscillations as in their paper using these initial conditions, verifying
+that our model works as intended. Below are snapshots of MinD and MinE
+concentrations at 5 second timestamps in the 4 $\mu$m cell:
+\newline
+\newline
+[insert 5 second time stamps of 4 $\mu$m sim]
+\newline
+\newline
+We then began to define other, non-traditional cell shapes for the purpose of
+modeling squished and perturbed E. coli cells, which were created
+experimentally in Mannick et al. To achieve this, we went with a
+cartesian lattice rather than the cylindrical lattice used in Huang et 
+al's simulations, as it allows for more flexibility in defining the 
+cell shape. Some of the cell shape models included a flattened pill
+(stadium shape), an ellipsoid, a spherical cell, and various randomly
+generated smooth shapes, such as those in the figures below. 
+\newline
+\newline
+[insert memf print of 2-3 cell shapes]
+\newline
+\newline
+To interpret the results, we generated several different plot views of
+the printed simulation data. These plots included a time averaged view
+of the protein densities in the cell; a plot tracking the location of
+protein concentrations that were global maxima in space and local maxima in 
+time; and an animated view that showed the actual dispersion of
+protein concentrations in the cell over time. 
 \section{Why does the E. Coli distribution matter?}

### 2013-07-12 batchloader.py
batchloader and todo and bugs

@@ -8,43 +8,36 @@ import time
 #set up simulations to be run:
 batch_randst_simulations = []
 i=1
-while i<7:
-    a = abs(i/2)
-    b = abs(5-i/2)
-    c = 2.00
-    if ([a, b] not in batch_randst_simulations) and ([b, a] not in batch_randst_simulations):
-        for d in [96.00, 97.00, 98.00, 99.00]:
-            batch_randst_simulations+=[[a,b,c,d]]
-    i+=1
 
-batch_pill_simulations = [ [0.50, 3.50], \
-                               [1.00, 4.00], \
-                               [2.00, 3.00], \
-                               [2.00, 3.00], \
-                               [2.50, 2.50], \
-                               [7.00, 2.00], \
-                               [7.50, 2.50], \
-                               [8.00, 3.00], \
-                               [8.50, 3.50], \
-                               [9.00, 4.00] ]
+batch_pill_simulations = [
+    [10.00, 0.50], \
+        [4.00, 0.50], \
+        [4.00, 2.00], \
+        [4.00, 3.00] ]
+
+batch_randst_simulations = [
+    [1.00,6.00,6.00,99.00], \
+    [1.00,8.00,6.00,98.00], \
+    [1.00,6.00,8.00,98.00], \
+    [1.00,6.00,6.00,97.00], \
+    [1.00,6.00,6.00,96.00]
+    ]
 
 #simulation subprocess management:
 if '-sim' in sys.argv:
     processes = set()
-    max_processes = 7
+    max_processes = 100
     if 'p' in sys.argv:
         for job in batch_pill_simulations:
-            processes.add(subprocess.Popen(['./protein_microscopy','p',str(job[0]),str(job[1]),'0.00','0.00','15.00']))
+            processes.add(subprocess.Popen(['srun','./protein_microscopy','p',str(job[0]),str(job[1]),'0.00','0.00','15.00']))
             if len(processes) >= max_processes:
                 os.wait()
                 processes.difference_update(p for p in processes if p.poll() is not None)
     if 'randst' in sys.argv:
         for job in batch_randst_simulations:
-            processes.add(subprocess.Popen(['./protein_microscopy','randst',str(job[0]),str(job[1]),str(job[2]),str(job[3]),'15.00']))
-            if len(processes) >= max_processes:
-                os.wait()
-                processes.difference_update(p for p in processes if p.poll() is not None)
[…]

### 2013-07-12 paper/paper.tex
centered ic

--- 2013-07-12 paper/paper.tex
@@
 \section{Methods and Initial Conditions}
+\subsection{Mathematical Model} %shouldn't be a scripty mu
+The model for the behavior of the MinD and MinE proteins inside the cell
+implemented the same set of 5 reaction-diffusion equations described in the paper
+by Huang et al (equations 1, 2, 3, 4, and 5). A 3d grid was constructed in
+cartesian coordinates with a grid spacing of .05 $\mu$m. From there, we
+were able to define a cell shape on the grid, and solve the
+reaction-diffusion equations numerically to observe the time evolution of
+the MinD and MinE concentrations inside the cell.
 
+Our simulation used the same diffusion constants and reaction rates as
+Huang et al, which are
+
+\begin{gather*} %format better
+  \mathcal{D}_D = \mathcal{D}_{E}  = 2.5 \mu \textrm{m$^2$ / sec}, \\
+  \sigma_D^{\textrm{ADP $\rightarrow$ ATP}}  = 1/\textrm{sec},  \sigma_D = 0.025 \mu \textrm{m/sec}, \\
+  \sigma_{dD}  = 0.0015 \mu \textrm{m$^3$/sec}, \\
+  \sigma_{de}  = 0.7/\textrm{sec}, \sigma_E = 0.093 \mu \textrm{m$^3$/sec}.
+\end{gather*}
+
+To test our computational model, we implemented a pill shaped cell, and
+tested using the same cell parameters as Huang et al, which were a radius
+of 0.5 $\mu$m in the middle and at the spherical endcaps, and two different
+cell lengths of 4 $\mu$m and 10 $\mu$m. We found the same type of
+oscillations as in their paper using these initial conditions, verifying
+that our model works as intended. Below are snapshots of MinD and MinE
+concentrations at 5 second timestamps in the 4 $\mu$m cell:
+\newline
+\newline
+[insert 5 second time stamps of 4 $\mu$m sim]
+\newline
+\newline
+We then began to define other, non-traditional cell shapes for the purpose of
+modeling squished and perturbed E. coli cells, which were created
+experimentally in Mannick et al. To achieve this, we went with a
+cartesian lattice rather than the cylindrical lattice used in Huang et 
+al's simulations, as it allows for more flexibility in defining the 
+cell shape. Some of the cell shape models included a flattened pill
+(stadium shape), an ellipsoid, a spherical cell, and various randomly
+generated smooth shapes, such as those in the figures below. 
+\newline
+\newline
+[insert memf print of 2-3 cell shapes]
+\newline
+\newline
+To interpret the results, we generated several different plot views of
+the printed simulation data. These plots included a time averaged view
+of the protein densities in the cell; a plot tracking the location of
+protein concentrations that were global maxima in space and local maxima in 
+time; and an animated view that showed the actual dispersion of
+protein concentrations in the cell over time. 
 \section{Specific Results}

### 2013-07-12 protein_microscopy.cpp
disabled area rating for now.

@@ -315,6 +315,7 @@ int main (int argc, char *argv[]) {
       printf("Printing middle slice data.\n");
     }
   }
+  printf("%f",dx);
 
   //compute grid size based on cell parameters
   if (mem_f_shape=="p") {
@@ -467,82 +468,82 @@ int main (int argc, char *argv[]) {
     fprintf (out_file,"\nFinished with set_membrane function. Now we have a mem_A.");
   }
 
-  //begin area rating
-  char *area_rating_out = new char[1024];
-  if (dx==.05) {
-    sprintf(area_rating_out, "data/shape-%s/hires-area_rating-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),A,B,C,D,density_factor);
-  }
-  else {
-    sprintf(area_rating_out, "data/shape-%s/area_rating-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),A,B,C,D,density_factor);
-  }
-  FILE *area_rating_file = fopen((const char *)area_rating_out,"w");
-  if (area_rating_file == NULL){
-    printf("Error: area_rating_file == null \n");
-  }
+  // //begin area rating
+  // char *area_rating_out = new char[1024];
+  // if (dx==.05) {
+  //   sprintf(area_rating_out, "data/shape-%s/hires-area_rating-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),A,B,C,D,density_factor);
+  // }
+  // else {
+  //   sprintf(area_rating_out, "data/shape-%s/area_rating-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),A,B,C,D,density_factor);
+  // }
+  // FILE *area_rating_file = fopen((const char *)area_rating_out,"w");
+  // if (area_rating_file == NULL){
+  //   printf("Error: area_rating_file == null \n");
+  // }
 
-  char * area_rating_out_two = new char[1024];
-  if (dx==.05) {
-    sprintf(area_rating_out_two, "data/shape-%s/hires-area_rating_two-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),A,B,C,D,density_factor);
-  }
-  else {
[…]

### 2013-07-12 pyplots/time_map.py
added to Makefile and paper a time_map figure

@@ -12,11 +12,11 @@ nADP = load.data(protein="nADP")
 Nd = load.data(protein="Nd")
 
 f_shape = sys.argv[1]
-f_param1 = sys.argv[2]
-f_param2 = sys.argv[3]
-f_param3 = sys.argv[4]
-f_param4 = sys.argv[5]
-f_param5 = sys.argv[6]
+f_param1 = int(10*(float(sys.argv[2])))
+f_param2 = int(10*(float(sys.argv[3])))
+f_param3 = int(10*(float(sys.argv[4])))
+f_param4 = int(10*(float(sys.argv[5])))
+f_param5 = int(10*(float(sys.argv[6])))
 
 def average_location(dataset):
     tsum = np.zeros_like(dataset[0])
@@ -27,17 +27,21 @@ def average_location(dataset):
 plt.figure(1)
 plt.subplot(221)
 plt.contourf(nATP.axes[1],nATP.axes[0],average_location(nATP.dataset),500)
+plt.title('nATP', fontsize=20)
 
 plt.subplot(222)
 plt.contourf(nE.axes[1],nE.axes[0],average_location(nE.dataset),500)
+plt.title('nE', fontsize=20)
 
 plt.subplot(223)
 plt.contourf(nADP.axes[1],nADP.axes[0],average_location(nADP.dataset),500)
+plt.title('nADP', fontsize=20)
 
 plt.subplot(224)
 plt.contourf(Nd.axes[1],Nd.axes[0],average_location(Nd.dataset),500)
+plt.title('Nd', fontsize=20)
 #plt.show(1)
-plt.savefig('./data/shape-'+f_shape+'/plots/time_map_compare-'+f_shape+'-'+f_param1+'-'+f_param2+'-'+f_param3+'-'+f_param4+'-'+f_param5+'.pdf')
+plt.savefig('./data/shape-'+f_shape+'/plots/time-map-compare-'+f_shape+'-'+str(f_param1)+'-'+str(f_param2)+'-'+str(f_param3)+'-'+str(f_param4)+'-'+str(f_param5)+'.pdf')
 print "time_map plot generated: subplot comparison"
 
 for p in [nflE, nflD, nATP, nE, nADP, Nd]:
@@ -45,5 +49,10 @@ for p in [nflE, nflD, nATP, nE, nADP, Nd]:
     plt.contourf(p.axes[1],p.axes[0],average_location(p.dataset),500)
[…]

### 2013-07-12 protein_microscopy.cpp
area rating commented

@@ -216,10 +216,10 @@ double mem_f(double x, double y, double z) {
     double Z = Nz*dx;
     if ( (x >= (X-A)/2) && (x <= A+(X-A)/2) && (z >= (Z-B)/2) && (z <= B+(Z-B)/2) && (y >= (Y-C)/2) && (y <= C+(Y-C)/2)) {
       f = -1;
-      }
+    }
     else {
       f = 1;
-      }
+    }
     return f;
   }
 
@@ -234,11 +234,11 @@ double mem_f(double x, double y, double z) {
     double z1=(Z-A)/2;
     double z2=(A+(Z-A)/2);
     if ((z > z1) && (z < z2)){
-    	f = sqrt((x-x1)*(x-x1) + (y-y1)*(y-y1))/(z-z1) - B/(z2-z1);
+      f = sqrt((x-x1)*(x-x1) + (y-y1)*(y-y1))/(z-z1) - B/(z2-z1);
     }
     else { f = 1; }
     return f;
-	}
+  }
 
   if (mem_f_shape=="st"){
     //A = length, B = x axis radius radius, C = y axis radius radius, D = z axis radius radius
@@ -258,7 +258,7 @@ double mem_f(double x, double y, double z) {
       f = sqrt((x-x1)*(x-x1)/(B*B)+(y-y1)*(y-y1)/(C*C)+(z-z2)*(z-z2)/(D*D))-1;
     }
     return f;
-	}
+  }
 
   if (mem_f_shape=="sp"){
     // A = radius
@@ -267,7 +267,7 @@ double mem_f(double x, double y, double z) {
     double Z = Nz*dx;
     double x1 = X/2;
     double y1 = Y/2;
-		double z1 = Z/2;
+    double z1 = Z/2;
     double f;
     f = sqrt((x-x1)*(x-x1) + (y-y1)*(y-y1) + (z-z1)*(z-z1)) - A;
     return f;
@@ -422,7 +422,7 @@ int main (int argc, char *argv[]) {
   Nde = new double[Nx*Ny*Nz];
   f_mem = new double[Nx*Ny*Nz];
   fprintf(out_file,"For this simulation,\ndx = %f\ntot_time = %f\ntimestep = %f\ntotal iterations = %d\niter at five sec = %d\n",
-         dx, tot_time, time_step, iter, iter_at_half_sec);
+          dx, tot_time, time_step, iter, iter_at_half_sec);
   double *JxATP = new double[Nx*Ny*Nz];
[…]

### 2013-07-12 paper/paper.tex

@@
 \section{Specific Results}
--Data and plots that show concrete results.
+-Datahjhuj and plots that show concrete results. Pill normal is for the establishing that we have what works, reference other paper, then modify, is the idea.
+Pill Normal -
+
+Pill Short -
+     -Know how short is too short
+
+Randst 99 -
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{data/shape-randst/plots/time-map-compare-randst-10-60-60-990-150.pdf}
+  \caption{Pretty plot of the pair distribution function near a hard wall.}
+  \label{fig:pair-distribution-3}
+\end{figure}
+
+Randst 98 -
+
+Randst 97 -
+
+Randst 96 -
+
+Triangle -
 

### 2013-07-12 pyplots/showatp.py
changed Makefile and showatp and batchloader

@@ -54,7 +54,7 @@ def contourplt(protein):
     maxval = timemax(protein)
     minval = timemin(protein)
     plt.figure(1)
-    os.system("rm -f ./data/shape-"+f_shape+"/plots/tmp_*.png")
+    os.system("rm -f ./data/shape-"+f_shape+"/plots/"+str(protein.protein)+"-tmp_*.png")
     Z, Y = np.meshgrid(np.arange(0,protein.datashape[1],1), np.arange(0,protein.datashape[0],1))
     for k in range(len(protein.dataset)): #fig.dpi method
         page = protein.dataset[k]
@@ -67,20 +67,20 @@ def contourplt(protein):
         plt.xlabel("Z position")
         plt.ylabel("Y position")
         if k<10:
-            plt.savefig('./data/shape-'+f_shape+'/plots/tmp_00'+str(k)+'-'+str(protein.protein)+ \
+            plt.savefig('./data/shape-'+f_shape+'/plots/'+str(protein.protein)+'-tmp_00'+str(k)+'-'+str(protein.protein)+ \
                             '-'+f_shape+'-'+f_param1+'-'+f_param2+'-'+f_param3+'-'+f_param4+'-'+f_param5+'.png',dpi=50)
         elif k<100:
-            plt.savefig('./data/shape-'+f_shape+'/plots/tmp_0'+str(k)+'-'+str(protein.protein)+ \
+            plt.savefig('./data/shape-'+f_shape+'/plots/'+str(protein.protein)+'-tmp_0'+str(k)+'-'+str(protein.protein)+ \
                             '-'+f_shape+'-'+f_param1+'-'+f_param2+'-'+f_param3+'-'+f_param4+'-'+f_param5+'.png',dpi=50)
         else:
-            plt.savefig('./data/shape-'+f_shape+'/plots/tmp_'+str(k)+'-'+str(protein.protein)+ \
+            plt.savefig('./data/shape-'+f_shape+'/plots/'+str(protein.protein)+'-tmp_'+str(k)+'-'+str(protein.protein)+ \
                             '-'+f_shape+'-'+f_param1+'-'+f_param2+'-'+f_param3+'-'+f_param4+'-'+f_param5+'.png',dpi=50)
-    os.system("convert -delay 8 ./data/shape-"+f_shape+"/plots/tmp_*" \
[…]

### 2013-07-12 paper/paper.tex

@@
   \includegraphics[width=\columnwidth]{data/shape-randst/plots/time-map-compare-randst-10-60-60-990-150.pdf}
-  \caption{Pretty plot of the pair distribution function near a hard wall.}
-  \label{fig:pair-distribution-3}
+  \caption{randst 99}
+  %\label{}
+\end{figure}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{data/shape-randst/plots/time-map-compare-randst-10-80-60-980-150.pdf}
+  \caption{randst 98}
+  %\label{fig:pair-distribution-3}
+\end{figure}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{data/shape-randst/plots/time-map-compare-randst-10-60-60-970-150.pdf}
+  \caption{randst 97}
+  %\label{fig:pair-distribution-3}
+\end{figure}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{data/shape-randst/plots/time-map-compare-randst-10-60-60-960-150.pdf}
+  \caption{randst 96}
+  %\label{fig:pair-distribution-3}
 \end{figure}

### 2013-07-12 batchloader.py
batchloader plotting updated

@@ -36,9 +36,9 @@ if '-sim' in sys.argv:
     if 'randst' in sys.argv:
         for job in batch_randst_simulations:
             processes.add(subprocess.Popen(['srun','./protein_microscopy','randst',str(job[0]),str(job[1]),str(job[2]),str(job[3]),'15.00']))
-
-
-
+        if len(processes) >= max_processes:
+            os.wait()
+            processes.difference_update(p for p in processes if p.poll() is not None)
 
 #plots the recent simulations:
 if '-plot' in sys.argv:
@@ -48,7 +48,7 @@ if '-plot' in sys.argv:
         for job in batch_pill_simulations:
             #processes.add(subprocess.Popen(['python','pyplots/extrema.py','p',str(job[0]),str(job[1]),'0.00','0.00','15.00']))
             #processes.add(subprocess.Popen(['python','pyplots/time_map.py','p',str(job[0]),str(job[1]),'0.00','0.00','15.00']))
-            processes.add(subprocess.Popen(['python','pyplots/showatp.py','p',str(job[0])+'0',str(job[1])+'0','0.00','0.00','15.00']))
+            processes.add(subprocess.Popen(['srun''python','pyplots/showatp.py','p',str(job[0]),str(job[1]),'0.00','0.00','15.00']))
             if len(processes) >= max_processes:
                 os.wait()
                 processes.difference_update(p for p in processes if p.poll() is not None)
@@ -56,7 +56,7 @@ if '-plot' in sys.argv:
         for job in batch_randst_simulations:
 #            processes.add(subprocess.Popen(['python','pyplots/extrema.py','p',str(job[0]),str(job[1]),'0.00','0.00','15.00']))
 #            processes.add(subprocess.Popen(['python','pyplots/time_map.py','randst',str(job[0]),str(job[1]),str(job[2]),str(job[3]),'15.00']))
-            processes.add(subprocess.Popen(['python','pyplots/showatp.py','randst',str(job[0])+'0',str(job[1])+'0',str(job[2])+'0',str(job[3])+'0','15.00']))
+            processes.add(subprocess.Popen(['srun''python','pyplots/showatp.py','randst',str(job[0]),str(job[1]),str(job[2]),str(job[3]),'15.00']))
             if len(processes) >= max_processes:
                 os.wait()
                 processes.difference_update(p for p in processes if p.poll() is not None)

### 2013-07-12 paper/paper.tex

--- 2013-07-12 paper/paper.tex
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{data/shape-randst/plots/time-map-compare-randst-10-60-60-990-150.pdf}
-  \caption{Pretty plot of the pair distribution function near a hard wall.}
-  \label{fig:pair-distribution-3}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-990-150.pdf}
+  \caption{randst 99}
+  %\label{}
+\end{figure}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-80-60-980-150.pdf}
+  \caption{randst 98}
+  %\label{fig:pair-distribution-3}
+\end{figure}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-970-150.pdf}
+  \caption{randst 97}
+  %\label{fig:pair-distribution-3}
+\end{figure}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-960-150.pdf}
+  \caption{randst 96}
+  %\label{fig:pair-distribution-3}
 \end{figure}

### 2013-07-12 batchloader.py
sync

@@ -29,13 +29,13 @@ if '-sim' in sys.argv:
     max_processes = 100
     if 'p' in sys.argv:
         for job in batch_pill_simulations:
-            processes.add(subprocess.Popen(['srun','./protein_microscopy','p',str(job[0]),str(job[1]),'0.00','0.00','15.00']))
+            processes.add(subprocess.Popen(['srun','./protein_microscopy','p','%.2f'%job[0],'%.2f'%job[1],'0.00','0.00','15.00']))
             if len(processes) >= max_processes:
                 os.wait()
                 processes.difference_update(p for p in processes if p.poll() is not None)
     if 'randst' in sys.argv:
         for job in batch_randst_simulations:
-            processes.add(subprocess.Popen(['srun','./protein_microscopy','randst',str(job[0]),str(job[1]),str(job[2]),str(job[3]),'15.00']))
+            processes.add(subprocess.Popen(['srun','./protein_microscopy','randst','%.2f'%job[0],'%.2f'%job[1],'%.2f'%job[2],'%.2f'%job[3],'15.00']))
         if len(processes) >= max_processes:
             os.wait()
             processes.difference_update(p for p in processes if p.poll() is not None)
@@ -46,17 +46,17 @@ if '-plot' in sys.argv:
     max_processes = 100
     if 'p' in sys.argv:
         for job in batch_pill_simulations:
-            #processes.add(subprocess.Popen(['python','pyplots/extrema.py','p',str(job[0]),str(job[1]),'0.00','0.00','15.00']))
-            #processes.add(subprocess.Popen(['python','pyplots/time_map.py','p',str(job[0]),str(job[1]),'0.00','0.00','15.00']))
-            processes.add(subprocess.Popen(['srun''python','pyplots/showatp.py','p',str(job[0]),str(job[1]),'0.00','0.00','15.00']))
+            #processes.add(subprocess.Popen(['python','pyplots/extrema.py','p','%.2f'%job[0],'%.2f'%job[1],'0.00','0.00','15.00']))
+            #processes.add(subprocess.Popen(['python','pyplots/time_map.py','p','%.2f'%job[0],'%.2f'%job[1],'0.00','0.00','15.00']))
+            processes.add(subprocess.Popen(['srun','python','pyplots/showatp.py','p','%.2f'%job[0],'%.2f'%job[1],'0.00','0.00','15.00']))
             if len(processes) >= max_processes:
                 os.wait()
[…]

### 2013-07-12 pyplots/showatp.py

@@ -1,5 +1,7 @@
 from __future__ import division
 import numpy as np
+import matplotlib
+matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 import os
 import sys
@@ -75,7 +77,7 @@ def contourplt(protein):
         else:
             plt.savefig('./data/shape-'+f_shape+'/plots/'+str(protein.protein)+'-tmp_'+str(k)+'-'+str(protein.protein)+ \
                             '-'+f_shape+'-'+f_param1+'-'+f_param2+'-'+f_param3+'-'+f_param4+'-'+f_param5+'.png',dpi=50)
-    os.system("convert -delay 8 ./data/shape-"+f_shape+"/plots/-tmp_*" \
+    os.system("convert -delay 8 ./data/shape-"+f_shape+"/plots/"+str(protein.protein)+"-tmp_*" \
     +"-"+str(protein.protein)+"-"+f_shape+"-"+f_param1+"-"+f_param2 \
     +"-"+f_param3+"-"+f_param4+"-"+f_param5+".png ./data/shape-"+f_shape \
     +"/plots/density_movie-"+str(protein.protein)+"-"+f_shape \

### 2013-07-13 protein_microscopy.cpp
update from work

@@ -27,6 +27,7 @@ int area_rating_flag = 0;
 int slice_flag = 0;
 
 double dx=0.15;
+
 const double tot_time = 62;
 const double time_step = .1*dx*dx/difD; // = .0009 s if dx=.15
 const int iter = int(tot_time/time_step)+3;
@@ -151,6 +152,7 @@ double mem_f(double x, double y, double z) {
         f = abs(2*(x-(X/2))/A) - 1;
         return f;
       }
+      fflush(stdout);
       if (f>0) {
         double closest_y0 = -100.0;
         double closest_z0 = -100.0;
@@ -161,8 +163,6 @@ double mem_f(double x, double y, double z) {
             if(mem_f_shape=="TIE_fighter") f0 = f_2D_TIE_fighter(y0,z0);
             if(mem_f_shape=="triangle") f0 = f_2D_triangle(y0,z0);
             if (f0 <= 0) {
-              //printf("f0 = %g\n",f0);
-              fflush(stdout);
               //there_is_closest_point = 1; unused
               if ( (y-y0)*(y-y0)+(z-z0)*(z-z0) < (y-closest_y0)*(y-closest_y0)+(z-closest_z0)*(z-closest_z0) ) {
                 closest_y0 = y0;
@@ -307,7 +307,7 @@ int main (int argc, char *argv[]) {
       printf("Area rating printout.\n");
     }
     if (strcmp(argv[i],"-hires")==0) {
-      dx=.05;
+      //dx=.05;
       printf("Using high resolution.\n");
     }
     if (strcmp(argv[i],"-slice")==0) {
@@ -369,104 +369,104 @@ int main (int argc, char *argv[]) {
   }
 
   //open out file to begin recording info about simulation
-  char * out_file_name = new char[1024];
-  sprintf(out_file_name,"data/shape-%s/out_files/%s-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.out",mem_f_shape.c_str(),mem_f_shape.c_str(),A,B,C,D,density_factor);
-  FILE * out_file = fopen((const char *)out_file_name,"w");
+  // char * out_file_name = new char[1024];
[…]

### 2013-07-14 protein_microscopy.cpp
working on new area rating

@@ -433,6 +433,10 @@ int main (int argc, char *argv[]) {
   double *JyE = new double[Nx*Ny*Nz];
   double *JzE = new double[Nx*Ny*Nz];
   double *mem_A = new double[Nx*Ny*Nz];
+  double *normals_x = new double[Nx*Ny*Nz];
+  double *normals_y = new double[Nx*Ny*Nz];
+  double *normals_z = new double[Nx*Ny*Nz];
+  double *curvature = new double[Nx*Ny*Nz];
   bool *insideArr = new bool[Nx*Ny*Nz];
   for (int i=0;i<Nx*Ny*Nz;i++){mem_A[i] = 0;}
   bool force_to_generate_new_memA = true;
@@ -443,7 +447,8 @@ int main (int argc, char *argv[]) {
     if (!memAin || force_to_generate_new_memA) {
       if (memAin && force_to_generate_new_memA) fclose(memAin);
       fprintf(out_file,"There is evidently no file called %s,\n so we're going to create one and fill it with memA information for future use.\n",memA_name);
-      set_membrane(out_file, mem_f, mem_A);
+      set_membrane(out_file, mem_f, mem_A, normals_x, normals_y, normals_z);
+      set_curvature(mem_A, normals_x, normals_y, normals_z, curvature);
       fprintf (out_file,"\nFinished with set_membrane function. Now we have a mem_A.\n");
       char* memA_out = new char[1024];
       sprintf(memA_out,"data/shape-randst/membrane_files/memA-%4.02f-%4.02f-%4.02f-%4.02f-%4.0f.dat",A,B,C,D,density_factor);
@@ -464,101 +469,104 @@ int main (int argc, char *argv[]) {
       }
     }
   } else {
-    set_membrane(out_file, mem_f, mem_A);
+    set_membrane(out_file, mem_f, mem_A, normals_x, normals_y, normals_z);
+    set_curvature(mem_A, normals_x, normals_y, normals_z, curvature);
     fprintf (out_file,"\nFinished with set_membrane function. Now we have a mem_A.");
   }
 
   // //begin area rating
-  // char *area_rating_out = new char[1024];
-  // if (dx==.05) {
[…]

### 2013-07-14 paper/paper.tex

@@
 \section{Specific Results}
--Datahjhuj and plots that show concrete results. Pill normal is for the establishing that we have what works, reference other paper, then modify, is the idea.
-Pill Normal -
+%-Datahjhuj and plots that show concrete results. Pill normal is for the establishing that we have what works, reference  other paper, then modify, is the idea.
+Pill Normal section - 
+Our goal with this project was to test whether or not the computational model developed by
+Huang et al was consistent with the newer experimental results (squishing E
+Coli) produced by Mannick et al. We generally see that:
+
+- Protein concentrations bounce around to areas with high curvature.
+- - example: nflD randst 1 6 6 99 tri-polar zones with tri-polar concentrations
+- - nflE the same
+- There is some time delay between where different protein types appear.
+-
 

### 2013-07-14 protein_microscopy.cpp
debugging wip

@@ -478,6 +478,7 @@ int main (int argc, char *argv[]) {
   // }
 
     //  else {
+  printf("starting to set membrane");
   set_membrane(out_file, mem_f, mem_A);
   printf("membrane set");
   fprintf (out_file,"\nFinished with set_membrane function. Now we have a mem_A.");

### 2013-07-15 paper/paper.tex

@@
 %-Datahjhuj and plots that show concrete results. Pill normal is for the establishing that we have what works, reference  other paper, then modify, is the idea.
+\section{Pill Shape}
 Pill Normal section - 
@@
 - There is some time delay between where different protein types appear.
--
+
+The pills with larger cylindrical widths, 4.00 3.00 (the wider pill shapes)
+exhibit oscillations with maxima reached on either side (half period
+times) 30s, 70s, 110s, so first half oscillation occured in 30s, the
+next two in 40s
+
+The 4.00 2.00 pills exhibit a similar pattern, but max out at times
+25s,55s,85s,115s, so thirty seconds each half period.  Seemed once again that
+the first oscillation had a higher max density, then settled down.  I
+wonder if extremely increasing the starting condition density
+lopsidedness will still yield a settle down pattern with the same max
+densities?  Is this dependent on shape/size?
+
+The 4.00 0.50 pill seemed to show oscillations of 20 second half
+periods very consistently.  Density maximum did not seem to lose
+intensity.  Seemed to be the same each oscillation.
+
+The difference between the center and max pole densities of the nflD
+do not seem to be very extreme.  Wonder if you do a comparison of the
+max density versus center density somehow.  Really ask how it would
+effect the polymer that's supposed to build.  Are there definded
+limits on how extreme this difference can be?  If the oscillations
+settle down into the same density difference for each cell shape, how
+can polymer build?  Also with this, when look at the periods and max
+denisty/min density ratio, consider the size dimensions of the pill
+shape and see if can see a mathematical relation.
+
+The nflE 4.00 0.50 shows a very large difference in center highest density
+versus pole highest density (during a maxima).  Is this perhaps the
+protein that's more important.
+
+Looking at the extrema plots - one very interesting thing is the 4.00
+2.00 ATP extrema, which shows the extrema only in the center of the
+cell.  The other proteins for this shape show the extrema to be at the
+ends.  Also, it seems the 4.00 3.00 cell shapes for these plots are
+missing.  Very interesting to see if there is a certain protein that
+has its maxima in the center of the cell, while the others have maxima
+elsewhere.  Tells a story that could maybe relate to the other shapes.
+
+Also, try starting the cells with density only in the corner.  Now the
+extrema go down the center of the cell, see if there would remain a
+lopsided nature of the oscillations if you started it like this instead.
+
+The very long cells have very long periods
+
+The time map plots seem inconsistent in that some show the highest
+densities on the poles, some in the centers, some on just one pole.
+For these want to run starting from a time when the proteins are
+evenly spread out (so between two maxima) and stop at a similar pointe
+at the end.
+
+The time map plots that I believe though sometimes show that the max
+density time-wise is actually in the middle of the cell!  Make sure we
+have a good, longer view of this being true.
+
+Important
 
@@
 Randst 99 -
+
+\section{Randst shape}
+There are sudden bursts in the nflE protein plots, at the poles. Their
+density maxima build very quickly then diffuse more slowly.
 

### 2013-07-15 pyplots/file_loader.py
file loader updated

@@ -9,13 +9,20 @@ f_param3 = sys.argv[4]
 f_param4 = sys.argv[5]
 f_param5 = sys.argv[6]
 
-#get_filenames method sloppy but it works.
+dx=.15
 
+#initialize as empty lists incase arguments not present in sys.argv
+hires_str=''
+m_str=''
+
+#change them to print the correct file names if arguments present
 if "-hires" in sys.argv:
     dx=.05
-else:
-    dx=.15
+    hires_str='hires-'
+if "-slice" not in sys.argv:
+    m_str='m-'
 
+#data object, to create in another plot: proteinname=data(protein="proteinname")
 class data(object):
     def __init__(self,protein):
         self.protein = protein
@@ -26,31 +33,19 @@ class data(object):
         self.datasize = [self.datashape[n]*dx for n in range(len(self.datashape))]
         self.axes = [np.arange(0,self.datasize[n],dx) for n in range(len(self.datashape))]
 
+#loads the files for creating the data object.
     @staticmethod
     def get_filenames(protein):
         dat_filenames = []
-        if "-hires" in sys.argv:
-            if "-slice" in sys.argv:
-                for fn in glob.iglob('./data/shape-'+f_shape+'/hires-'+protein+'-'+f_shape+'-'+f_param1+'-'+f_param2+'-'+f_param3+'-'+f_param4+'-'+f_param5+'*.dat'):
-                    dat_filenames.append(fn)
-            else:
-                for fn in glob.iglob('./data/shape-'+f_shape+'/hires-m-'+protein+'-'+f_shape+'-'+f_param1+'-'+f_param2+'-'+f_param3+'-'+f_param4+'-'+f_param5+'*.dat'):
-                    dat_filenames.append(fn)
-        else:
-            if "-slice" in sys.argv:
-                for fn in glob.iglob('./data/shape-'+f_shape+'/'+protein+'-'+f_shape+'-'+f_param1+'-'+f_param2+'-'+f_param3+'-'+f_param4+'-'+f_param5+'*.dat'):
-                    dat_filenames.append(fn)
-            else:
-                for fn in glob.iglob('./data/shape-'+f_shape+'/m-'+protein+'-'+f_shape+'-'+f_param1+'-'+f_param2+'-'+f_param3+'-'+f_param4+'-'+f_param5+'*.dat'):
-                    dat_filenames.append(fn)
[…]

### 2013-07-15 pyplots/time_map.py

@@ -1,9 +1,12 @@
 from __future__ import division
+import matplotlib
+matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 import numpy as np
 import file_loader as load
 import sys
 
+#create protein data objects (see file_loader.py)
 nflE = load.data(protein="nflE")
 nflD = load.data(protein="nflD")
 nATP = load.data(protein="nATP")
@@ -18,12 +21,15 @@ f_param3 = int(10*(float(sys.argv[4])))
 f_param4 = int(10*(float(sys.argv[5])))
 f_param5 = int(10*(float(sys.argv[6])))
 
+#compute time average (removing first 10% happens in file loading)
 def average_location(dataset):
     tsum = np.zeros_like(dataset[0])
     for t in range(nATP.tsteps):
             tsum += dataset[t]
     return tsum/(nATP.tsteps)
 
+print './data/shape-'+f_shape+'/plots/'+load.hires_str+load.m_str+'time-map-compare-'+f_shape+'-'+str(f_param1)+'-'+str(f_param2)+'-'+str(f_param3)+'-'+str(f_param4)+'-'+str(f_param5)+'.pdf'
+#create comparison subplots and print them to one file. 
 plt.figure(1)
 plt.subplot(221)
 plt.contourf(nATP.axes[1],nATP.axes[0],average_location(nATP.dataset),500)
@@ -39,20 +45,15 @@ plt.title('nADP', fontsize=20)
 
 plt.subplot(224)
 plt.contourf(Nd.axes[1],Nd.axes[0],average_location(Nd.dataset),500)
-plt.title('Nd', fontsize=20)
-#plt.show(1)
-plt.savefig('./data/shape-'+f_shape+'/plots/time-map-compare-'+f_shape+'-'+str(f_param1)+'-'+str(f_param2)+'-'+str(f_param3)+'-'+str(f_param4)+'-'+str(f_param5)+'.pdf')
+plt.title('Nd', fontsize=20) #load.hires_str and load.m_str are empty strings unless -hires and -slice are in the sys.argv list. see file_loader.py
+plt.savefig('./data/shape-'+f_shape+'/plots/'+load.hires_str+load.m_str+'time-map-compare-'+f_shape+'-'+str(f_param1)+'-'+str(f_param2)+'-'+str(f_param3)+'-'+str(f_param4)+'-'+str(f_param5)+'.pdf')
[…]

### 2013-07-15 protein_microscopy.cpp
paper and something the the area_rating loop

@@ -307,7 +307,7 @@ int main (int argc, char *argv[]) {
       printf("Area rating printout.\n");
     }
     if (strcmp(argv[i],"-hires")==0) {
-      //dx=.05;
+      dx=.05;
       printf("Using high resolution.\n");
     }
     if (strcmp(argv[i],"-slice")==0) {
@@ -523,37 +523,39 @@ int main (int argc, char *argv[]) {
     }
   }
   int i=int(Nx/2);
-    for (int j=0;j<Ny;j++){
-      for (int k=0;k<Nz;k++){
-        double area_rating_two = curvature[i*Ny*Nz+j*Nz+k];
-        total_cell_area += mem_A[i*Ny*Nz+j*Nz+k];
-        double area_rating = 0;
-        double area_rating_three = 0;
-        if (insideArr[i*Ny*Nz+j*Nz+k]==true){
-          for (int i2=0;i2<Nx;i2++){
-            for (int j2=0;j2<Ny;j2++){
-              for (int k2=0;k2<Nz;k2++){
-                if(i2!=i && j2!=j && k2!=k){
-                  //double dis = dx*sqrt((i-i2)*(i-i2)+(j-j2)*(j-j2)+(k-k2)*(k-k2));
-                  area_rating += curvature[i2*Ny*Nz+j2*Nz+k2];
-                  // if (dis<1.5*A){
-                  //   area_rating_two += mem_A[i2*Ny*Nz+j2*Nz+k2]/(dis*dis);
-                  //   area_rating_three += mem_A[i2*Ny*Nz+j2*Nz+k2];
-                  //}
-                }
+  printf("Hello!!!Nx=%d, x=%g, Nx/2=%d, x/2=%g\n",Nx,Nx*dx,i,Nx*dx/2.0);
+  fflush(stdout);
+  for (int j=0;j<Ny;j++){
+    for (int k=0;k<Nz;k++){
+      double area_rating_two = curvature[i*Ny*Nz+j*Nz+k];
+      total_cell_area += mem_A[i*Ny*Nz+j*Nz+k];
+      double area_rating = 0;
+      double area_rating_three = 0;
[…]

### 2013-07-15 protein_microscopy.cpp
y points added

@@ -1438,9 +1438,9 @@ int set_density(double *nATP, double *nE, double *mem_A){
   //  printf("Total inside = %d\nTotal nATP should be = %f\n NE per cell = %f\n", count_inside,count_inside*NE_per_cell, NE_per_cell);
   //.
   //double r2,U,V; unused
-  int right_most_point_z=0;
+  int right_most_point_z=0; //left and right most points for z
   int left_most_point_z=Nz;
-  int right_most_point_y=0;
+  int right_most_point_y=0; //"left" and "right" most points for y, in terms of magnitude (right = larger y value)
   int left_most_point_y=Ny;
   for (int i=0;i<Nx;i++){
     for (int j=0;j<Ny;j++){
@@ -1464,6 +1464,7 @@ int set_density(double *nATP, double *nE, double *mem_A){
   }
 
   int density_divider_z = int(right_most_point_z - (right_most_point_z - left_most_point_z)/3);
+  int density_divider_y = int(right_most_point_y - (right_most_point_y - left_most_point_y)/3);
 
   //get total gridpoints, gridpoints left of divide, gridpoints right of divide for protein count
   int gridpoints_left = 0;

### 2013-07-15 paper/paper.tex

@@
 
+The star shape (randst-96) Shows oscillations in nflD horizontally, two poles to two
+poles.  There is sometimes a small amount of lag between the upper
+maxima moving horizontally and the lower.  Half periods take roughly
+25s. Dimensions are roughly 5.00 by 5.00?  Check this.
+
+Randst (sort of triangle) is roughly dimensions of 3.5 by 3.5?
+nflD oscillations appear to be half periods of 25s as well.  Maxima appear
+at the poles and in the interim there are weak maxima in center pole.
+
+Funny randst shape 98 shows nflD oscillations of about 30s or so.
+
 \begin{figure}

### 2013-07-15 protein_microscopy.cpp
changed line 1505 for protein_microscopy randst sim

@@ -316,7 +316,7 @@ int main (int argc, char *argv[]) {
   }
 
   //these had to be moved inside int main if we're to change dx
-  tot_time = 124;
+  tot_time = 248; //4 periods ish
   time_step = .1*dx*dx/difD;
   iter = int(tot_time/time_step)+3;
   iter_at_half_sec = int(0.5/time_step)+1; //# of iteratings at a half second = 55
@@ -1438,6 +1438,7 @@ int set_density(double *nATP, double *nE, double *mem_A){
   //  printf("Total inside = %d\nTotal nATP should be = %f\n NE per cell = %f\n", count_inside,count_inside*NE_per_cell, NE_per_cell);
   //.
   //double r2,U,V; unused
+
   int right_most_point_z=0; //left and right most points for z
   int left_most_point_z=Nz;
   int right_most_point_y=0; //"left" and "right" most points for y, in terms of magnitude (right = larger y value)
@@ -1501,28 +1502,28 @@ int set_density(double *nATP, double *nE, double *mem_A){
     for (int j=0;j<Ny;j++){
       for (int k=0;k<Nz;k++){
         if (inside(i,j,k)){
-          if(k>density_divider_z){
+          if(j>density_divider_y && k>density_divider_z){
             nATP[i*Ny*Nz+j*Nz+k] = nATP_starting_density*density_factor_right;
             nE[i*Ny*Nz+j*Nz+k] = nE_starting_density*density_factor_right;
-	    nADP[i*Ny*Nz+j*Nz+k] =0;
-	    Nd[i*Ny*Nz+j*Nz+k] =0;
-	    Nde[i*Ny*Nz+j*Nz+k] = 0;
+            nADP[i*Ny*Nz+j*Nz+k] =0;
+            Nd[i*Ny*Nz+j*Nz+k] =0;
+            Nde[i*Ny*Nz+j*Nz+k] = 0;
           }
           else {
             nATP[i*Ny*Nz+j*Nz+k] = nATP_starting_density*density_factor_left;
             nE[i*Ny*Nz+j*Nz+k] = nE_starting_density*density_factor_left;
[…]

### 2013-07-15 paper/paper.tex
small changes to paper

@@
 
-The star shape (randst-96) Shows oscillations in nflD horizontally, two poles to two
-poles.  There is sometimes a small amount of lag between the upper
-maxima moving horizontally and the lower.  Half periods take roughly
-25s. Dimensions are roughly 5.00 by 5.00?  Check this.
+The star shape (randst-96) Shows oscillations in nflD horizontally,
+two poles to two poles.  There is sometimes a small amount of lag
+between the upper maxima moving horizontally and the lower.  Half
+periods take roughly 25s. Dimensions are roughly 5.00 by 5.00?  Check
+this.  The nflE short bursts do develop lag between when the top and
+the bottom go off.  Should coordinate this with the nflD lag.
 
-Randst (sort of triangle) is roughly dimensions of 3.5 by 3.5?
+Randst 97 nflE starts with small maxima, not much difference at all,
+then actually builds to high maxima at the poles.
+
+Randst 99 (sort of triangle) is roughly dimensions of 3.5 by 3.5?
 nflD oscillations appear to be half periods of 25s as well.  Maxima appear
@@
 Funny randst shape 98 shows nflD oscillations of about 30s or so.
+
+Randst nflD doesn't show much oscillation at all, but we start it so
+that the density is not max at the pole.
 

### 2013-07-15 batchloader.py
printing Nde now too

@@ -9,18 +9,20 @@ import time
 batch_randst_simulations = []
 i=1
 
-batch_pill_simulations = [
-    [10.00, 0.50], \
-        [4.00, 0.50], \
-        [4.00, 2.00], \
-        [4.00, 3.00] ]
+# batch_pill_simulations = [
+#     [10.00, 0.50], \
+#         [4.00, 0.50], \
+#         [4.00, 2.00], \
+#         [4.00, 3.00] ]
 
-batch_randst_simulations = [
-    [1.00,6.00,6.00,99.00], \
-    [1.00,8.00,6.00,98.00], \
-    [1.00,6.00,8.00,98.00], \
-    [1.00,6.00,6.00,97.00], \
-    [1.00,6.00,6.00,96.00]
+batch_pill_simulations = [
+    [4.00,3.75,0.00,0.00,15.00], \
+    [4.00,3.50,0.00,0.00,15.00], \
+    [4.00,3.00,0.00,0.00,15.00], \
+    [4.00,2.00,0.00,0.00,15.00], \
+    [4.00,0.50,0.00,0.00,15.00], \
+    [4.00,2.00,0.00,0.00,500.00], \
+    [4.00,0.50,0.00,0.00,500.00], \
     ]
 
 #simulation subprocess management:
@@ -29,13 +31,13 @@ if '-sim' in sys.argv:
     max_processes = 100
     if 'p' in sys.argv:
         for job in batch_pill_simulations:
-            processes.add(subprocess.Popen(['srun','./protein_microscopy','p','%.2f'%job[0],'%.2f'%job[1],'0.00','0.00','15.00']))
+            processes.add(subprocess.Popen(['srun','./protein_microscopy','p','%.2f'%job[0],'%.2f'%job[1],'%.2f'%job[2],'%.2f'%job[3],'%.2f'%job[4]]))
             if len(processes) >= max_processes:
                 os.wait()
                 processes.difference_update(p for p in processes if p.poll() is not None)
     if 'randst' in sys.argv:
         for job in batch_randst_simulations:
-            processes.add(subprocess.Popen(['srun','./protein_microscopy','randst','%.2f'%job[0],'%.2f'%job[1],'%.2f'%job[2],'%.2f'%job[3],'15.00']))
+            processes.add(subprocess.Popen(['srun','./protein_microscopy','randst','%.2f'%job[0],'%.2f'%job[1],'%.2f'%job[2],'%.2f'%job[3],'%.2f'%job[4]]))
             if len(processes) >= max_processes:
[…]

### 2013-07-15 protein_microscopy.cpp

@@ -297,7 +297,7 @@ int main (int argc, char *argv[]) {
   C = atof(argv[4]);
   D = atof(argv[5]);
   density_factor = atof(argv[6]);
-
+  dx=.15;
   //flags I want: -area, -hires, -slice
 
   for (int i=0; i<argc; i++) {
@@ -443,108 +443,108 @@ int main (int argc, char *argv[]) {
   double *JyE = new double[Nx*Ny*Nz];
   double *JzE = new double[Nx*Ny*Nz];
   double *mem_A = new double[Nx*Ny*Nz];
-  double *normals_x = new double[Nx*Ny*Nz];
-  double *normals_y = new double[Nx*Ny*Nz];
-  double *normals_z = new double[Nx*Ny*Nz];
-  double *curvature = new double[Nx*Ny*Nz];
+  // double *normals_x = new double[Nx*Ny*Nz];
+  // double *normals_y = new double[Nx*Ny*Nz];
+  // double *normals_z = new double[Nx*Ny*Nz];
+  // double *curvature = new double[Nx*Ny*Nz];
   bool *insideArr = new bool[Nx*Ny*Nz];
   for (int i=0;i<Nx*Ny*Nz;i++){mem_A[i] = 0;}
 
-  ////begin area rating
-  char *area_rating_out = new char[1024];
-  if (dx==.05) {
-    sprintf(area_rating_out, "data/shape-%s/hires-area_rating-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),A,B,C,D,density_factor);
-  }
-  else {
-    sprintf(area_rating_out, "data/shape-%s/area_rating-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),A,B,C,D,density_factor);
-  }
-  FILE *area_rating_file = fopen((const char *)area_rating_out,"w");
-  if (area_rating_file == NULL){
-    printf("Error: area_rating_file == null \n");
-  }
+  //begin area rating
+  // char *area_rating_out = new char[1024];
+  // if (dx==.05) {
+  //   sprintf(area_rating_out, "data/shape-%s/hires-area_rating-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),A,B,C,D,density_factor);
+  // }
+  // else {
[…]

### 2013-07-15 paper/paper.tex
paper changes

@@
 \usepackage{graphicx}% Include figure files
+\usepackage{animate}
 \usepackage{dcolumn}% Align table columns on decimal point
@@
 \section{Randst shape}
+whats the difference between the extremes in density at different
+places (like the density max at the poles and at the rims in the
+center).  Still need to do this.
+
 There are sudden bursts in the nflE protein plots, at the poles. Their
@@
 
+\subsection{randst-96}
 The star shape (randst-96) Shows oscillations in nflD horizontally,
@@
 
+Tried to see if there is a time correlation between nflE and nflD but
+the maxima seem to appear in the poles at roughly the same time.
+
+Watched Nd and nE simulations next to each other at same time.  Both
+have maxima that build up right at the walls (in the corners) and then
+subside.  It's clear that the nE density bursts appear directly after
+the Nd bursts.  The Nd bursts are subsiding as the nE bursts are
+rising up.  The Nd reaches a time maxima just before the nE.  This is
+true in each corner, so that when the maxima are lopsided top to
+bottom - when the top right corner maximizes first, say, the interplay
+between nE and Nd remains very clear in those corners where and when
+maxima occur.
+
+Watched nATP and nADP together.  nATP maxima seem to follow slightly
+after nADP maxima.  This is not surprising since in rotation nATP
+follows after nADP.  nATP maxima is more spread out - inbetween pole
+maxima there is more spread out maxima in the center.  This should
+show itself in the time map plotting.  About this - the percentage
+difference seem to be the same between the non-max places and max
+places, roughly, its just that the nATP seems to have a max region
+that covers a wider area throughout the oscillation (or at least in
+between the maxima points in the oscillation).
+
+Also watched the Nd next to the nATP.  The Nd maximize more extreme in
+the corners up against the walls.  The nATP density follows the Nd
+maxima, it looks like the nATP maxima follows the Nd.  So if the Nd
+appears somewhere (in a corner) then the nATP will travel there to
+follow.
+
+\subsection{randst-97}
 Randst 97 nflE starts with small maxima, not much difference at all,
 then actually builds to high maxima at the poles.
-
+\subsection{randst-99}
 Randst 99 (sort of triangle) is roughly dimensions of 3.5 by 3.5?
@@
 at the poles and in the interim there are weak maxima in center pole.
+\subsection{randst-98}
+Funny randst shape 98 shows nflD oscillations of about 30s or so.
 
-Funny randst shape 98 shows nflD oscillations of about 30s or so.
+nADP and nATP side by side.  nADP maximizes in the corners right
+before the nATP maxima follows.  Makes sense looking at equations.
+Once again the nATP maxima is more spread out, where maxima in nADP
+appear more just at walls.
+
+Nd and nATP side by side.  Nd maximizes at walls and the nATP moves in
+to follow it
+
+Nd and nE side by side.  Nd maximizes in corners and then the nE also
+maximizes in the corners.  The nE maxima appear in these sort of quick
+bursts in the corners, along with a slower broader movements away from
+that corner after the burst and into the next, where another sharp
+burst occurs.  The Nd bursts occurs after the Nd as subsided in that
+corner, and really by the time the burst maximizes, the Nd is already
+on its way over and starting to build on the otehr side.
 
@@
 
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-990-150.pdf}
-  \caption{randst 99}
-  %\label{}
-\end{figure}
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-80-60-980-150.pdf}
-  \caption{randst 98}
-  %\label{fig:pair-distribution-3}
-\end{figure}
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-970-150.pdf}
-  \caption{randst 97}
-  %\label{fig:pair-distribution-3}
-\end{figure}
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-960-150.pdf}
-  \caption{randst 96}
-  %\label{fig:pair-distribution-3}
-\end{figure}
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-990-150.pdf}
+%%   \caption{randst 99}
+%%   %\label{}
+%% \end{figure}
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-80-60-980-150.pdf}
+%%   \caption{randst 98}
+%%   %\label{fig:pair-distribution-3}
+%% \end{figure}
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-970-150.pdf}
+%%   \caption{randst 97}
+%%   %\label{fig:pair-distribution-3}
+%% \end{figure}
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-960-150.pdf}
+%%   \caption{randst 96}
+%%   %\label{fig:pair-distribution-3}
+%% \end{figure}
 
@@
 
+\section{animate?}
+\animategraphics[height=2.8in,autoplay,controls]{12}{../data/shape-randst/plots/movie-density-Nd-96/animate_}{0}{120}
+
 \section{Conclusion}

### 2013-07-15 protein_microscopy.cpp
fixed sly bug in set density

@@ -1511,7 +1511,7 @@ int set_density(double *nATP, double *nE, double *mem_A){
   }
 
   int density_divider_z = int(right_most_point_z - (right_most_point_z - left_most_point_z)/3);
-  int density_divider_y = int(right_most_point_y - (right_most_point_y - left_most_point_y)/3);
+  //int density_divider_y = int(right_most_point_y - (right_most_point_y - left_most_point_y)/3);
 
   //get total gridpoints, gridpoints left of divide, gridpoints right of divide for protein count
   int gridpoints_left = 0;
@@ -1522,7 +1522,7 @@ int set_density(double *nATP, double *nE, double *mem_A){
       for (int k=0;k<Nz;k++){
         if (inside(i,j,k)){
           gridpoints_total++;
-          if (k<density_divider_z) {
+          if (k<=density_divider_z) {
             gridpoints_left++;
           }
           else {
@@ -1548,7 +1548,7 @@ int set_density(double *nATP, double *nE, double *mem_A){
     for (int j=0;j<Ny;j++){
       for (int k=0;k<Nz;k++){
         if (inside(i,j,k)){
-          if(j>density_divider_y && k>density_divider_z){
+          if(k>density_divider_z){
             nATP[i*Ny*Nz+j*Nz+k] = nATP_starting_density*density_factor_right;
             nE[i*Ny*Nz+j*Nz+k] = nE_starting_density*density_factor_right;
             nADP[i*Ny*Nz+j*Nz+k] =0;

### 2013-07-18 pyplots/frequency_plot.py
modified frequency plotting

@@ -3,6 +3,7 @@ import numpy as np
 import matplotlib
 matplotlib.use('Agg')
 import matplotlib.pyplot as plt
+import pylab
 import os
 import sys
 import time
@@ -55,36 +56,64 @@ nATP = load.data(protein="nATP")
 nE = load.data(protein="nE")
 nADP = load.data(protein="nADP")
 Nd = load.data(protein="Nd")
+Nde = load.data(protein="Nde")
 
-for p in [nflE, nflD, nATP, nE, nADP, Nd]:
+proteins = [nflE, nflD, nATP, nE, nADP, Nd, Nde]
+proteins_strings = ["nflE", "nflD", "nATP", "nE", "nADP", "Nd", "Nde"]
+
+for p in proteins:
     for i in p.dataset:
         if (globalmax(i) != "empty"):
             p.pointInfo = (globalmax(i)[0][0], globalmax(i)[0][1])
             break
     print p.pointInfo
 
-z = 2 + round((float(f_param1)-.15)/dx)
-y = 2 + round((float(f_param2)-.15)/dx)
-print z*dx
-print y*dx
-print "Hello"
-print z
-print y
-pointB = ()
+mid_z = 2 + round((float(f_param1)-.15)/dx)
+mid_y = 2 + round((float(f_param2)-.15)/dx)
 
-for p in [nflE, nflD, nATP, nE, nADP, Nd]:
+
+for p in proteins:
     p.densityInfo = []
     p.densityInfoTwo = []
-    print p.pointInfo[0]
-    print p.pointInfo[1]
     for file in p.dataset:
         p.densityInfo += [ file[p.pointInfo[0]][p.pointInfo[1]] ]
-        p.densityInfoTwo += [ file[y][z] ]
+        p.densityInfoTwo += [ file[mid_y][mid_z] ]
     time = np.arange(0,len(p.densityInfo)/2,.5)
     plt.figure()
     plt.plot(time,p.densityInfo)
     plt.plot(time,p.densityInfoTwo)
     plt.title('Max point = '+str(p.pointInfo[0]*dx)+','+str(p.pointInfo[0]*dx)
-              +'   Middle point = '+str(y*dx)+','+str(z*dx))
+              +'   Middle point = '+str(mid_y*dx)+','+str(mid_z*dx))
[…]

### 2013-07-18 pyplots/frequency_plot.py
bug!

@@ -116,4 +116,4 @@ plt.legend(proteins_strings,loc='best')
 if norm:
     plt.savefig('./data/shape-'+f_shape+'/plots/'+load.hires_str+load.m_str+'frequency_plot_all_norm-'+f_shape+'-'+str(f_param1)+'-'+str(f_param2)+'-'+str(f_param3)+'-'+str(f_param4)+'-'+str(f_param5)+'.pdf')
 else:
-        plt.savefig('./data/shape-'+f_shape+'/plots/'+load.hires_str+load.m_str+'frequency_plot_all-'+f_shape+'-'+str(f_param1)+'-'+str(f_param2)+'-'+str(f_param3)+'-'+str(f_param4)+'-'+str(f_param5)+'.pdf')
+    plt.savefig('./data/shape-'+f_shape+'/plots/'+load.hires_str+load.m_str+'frequency_plot_all-'+f_shape+'-'+str(f_param1)+'-'+str(f_param2)+'-'+str(f_param3)+'-'+str(f_param4)+'-'+str(f_param5)+'.pdf')

### 2013-07-18 paper/paper.tex
more changes to paper.tex

@@
 \end{abstract}
+\section{Introduction}
+\subsection{What is the MinD system and why is it important?}
+\subsection{How proteins move in cell}
+\section{Methods and Initial Conditions}
+The model for the behavior of the MinD and MinE proteins inside the cell
+implemented the same set of 5 reaction-diffusion equations described in the paper
+by Huang et al (equations 1, 2, 3, 4, and 5). A 3d grid was constructed in
+cartesian coordinates with a grid spacing of .05 $\mu$m. From there, we
+were able to define a cell shape on the grid, and solve the
+reaction-diffusion equations numerically to observe the time evolution of
+the MinD and MinE concentrations inside the cell.
+
+Our simulation used the same diffusion constants and reaction rates as
+Huang et al, which are
+
+\begin{gather*} %format better
+  \mathcal{D}_D = \mathcal{D}_{E}  = 2.5 \mu \textrm{m$^2$ / sec}, \\
+  \sigma_D^{\textrm{ADP $\rightarrow$ ATP}}  = 1/\textrm{sec},  \sigma_D = 0.025 \mu \textrm{m/sec}, \\
+  \sigma_{dD}  = 0.0015 \mu \textrm{m$^3$/sec}, \\
+  \sigma_{de}  = 0.7/\textrm{sec}, \sigma_E = 0.093 \mu \textrm{m$^3$/sec}.
+\end{gather*}
+
+To test our computational model, we implemented a pill shaped cell, and
+tested using the same cell parameters as Huang et al, which were a radius
+of 0.5 $\mu$m in the middle and at the spherical endcaps, and two different
+cell lengths of 4 $\mu$m and 10 $\mu$m. We found the same type of
+oscillations as in their paper using these initial conditions, verifying
+that our model works as intended. Below are snapshots of MinD and MinE
+concentrations at 5 second timestamps in the 4 $\mu$m cell:
+\newline
+\newline
+[insert 5 second time stamps of 4 $\mu$m sim]
+\newline
+\newline
+We then began to define other, non-traditional cell shapes for the purpose of
+modeling squished and perturbed E. coli cells, which were created
+experimentally in Mannick et al. To achieve this, we went with a
+cartesian lattice rather than the cylindrical lattice used in Huang et 
+al's simulations, as it allows for more flexibility in defining the 
+cell shape. Some of the cell shape models included a flattened pill
+(stadium shape), an ellipsoid, a spherical cell, and various randomly
+generated smooth shapes, such as those in the figures below. 
+\newline
+\newline
+[insert memf print of 2-3 cell shapes]
+\newline
+\newline
+To interpret the results, we generated several different plot views of
+the printed simulation data. These plots included a time averaged view
+of the protein densities in the cell; a plot tracking the location of
+protein concentrations that were global maxima in space and local maxima in 
+time; and an animated view that showed the actual dispersion of
+protein concentrations in the cell over time. 
+\subsection{Mathematical Model}
+\section{Specific Results}
+\subsection{Pill Shape}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-p/plots/frequency_plot_all_norm-p-40-20-0-0-150.pdf}
+  \caption{Protein density fluctuation with time against the polar
+    wall in a 4$\mu m$ by 2$\mu m$ pill shaped cell.  The wall-bound
+    proteins are shown at a point that is on the wall and the
+    cytoplasm densities are shown at a point immediately adjecent.
+    This plot is normalized so that every protein density peaks at 1}
+  \label{frequency-plot-40-20-0-0-150}
+\end{figure}
+
+\fixme{Be more exact about what exactly Nd is versus nATP, in terms of
+  the unit and dimensions.  The plotting may need to be changed}
+Figure \ref{frequency-plot-40-20-0-0-150} shows the protein density
+fluctuations at a point in space adjecent to a polar wall.  At each
+collection of peaks the proteins reach their zenith in an order that
+agrees with the qualitative picture described by
+Huang\cite{huang2003dynamic}, except for nADP peak.  The peaks start
+with a maxima of ATP-MinD accumulating at the walls \fixme{Need a
+  better way to refer to compounds}. This peak is followed by a peak
+in Nde, or ATP-MinD-MinE, as the cell is converted on the wall from
+the former to the latter compound.  As this compound splits apart and
+leaves the wall we see a peak in nE, or MinE in the cytoplasm.  This
+is then followed by a broader peak in nATP, or the MinD-ATP compound,
+as minD-ADP is (changed but I forgot the name for it) into minD-ATP in
+the cytoplasm.  The minD-ATP naturally diffuses away from the pole,
+which is shown by the broad nature of this peak.  All of these peaks
+fit the qualitative picture except for the sharp MinD-ADP peak.  One
+could except it to be a sharp peak, meaning that the MinD-ADP proteins
+do not last in the cytoplasm for very long before they are converted
+(once again forgot the name) into MinD-ATP.  The location of the peak
+in the time dimension is troubling, however, since that we would
+expect it to occur just after the peak in Nde, since the wall-bound
+MinD-ATP-MinE proteins are the ones that split up and leave the wall,
+creating both the MinE and the MinD-ADP.  One would expect to see the
+minD-ADP peak to coincide in time with the minE peak, but it instead
+coincides with the wall-bound MinD-ATP-MinE peak. (Although you can
+maybe sort of convince yourself otherwiase, really looking at it).
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-p/plots/frequency_plot_all_middle-p-40-20-0-0-150.pdf}
+  \caption{A comparison of protein density fluctuation with time
+    against the polar wall and at a point in the center of the
+    z-length and adjacent to the wall, in the cytoplasm.  The cell is
+    pill shaped and has dimensions of 4$\mu m$ by 2$\mu m$.  }
+  \label{frequency-plot-40-20-0-0-150}
+\end{figure}
+
+The theory states that the aversion of the (forgot name of polymer) to
+the MinD system is responsible for the polymer setting up in the
+center of the cell as opposed to at the cellular poles.\fixme{look
+  this up and write this section up properly} The theory is dependent
+on there being a significant difference in protein density between the
+center and polar regions. It is worthwhile examining this difference
+in detail.  Figure \ref{frequency-plot-40-20-0-0-150} shows a
+comparison of density fluctuation over time at a point adjacent to the
+polar cell wall and at a point adjacent to the cell wall in the center
+region of the cell.  The different proteins show different
+relationships between their maxima and minima.  The MinD-ADP show
+sharp spikes at the poles and much smaller oscillations at in the
+middle.  The values at the poles are always greater than those in the
+middle, and the polar peaks exhibit densities that are roughly 2.5
+times greater than the maxima in the center (\fixme{this factor and
+  the following factor will be put into a table of comparisons for
+  each protein and for the different cell sizes}).  The MinD-ATP
+densities show a very different trend.  For these it is the center
+density that is almost always greater than the polar density.  The
+difference in density at the pole versus the middle is a factor of
+roughly .85 (once again we'll do this more officially in a table).
+The MinE is similar to the MinD-ADP comparison.  It shows a difference
+in maxima by a factor of roughly 2.  It seems that the MinD-ATP is not
+a good candidate for polymer aversion while the MinD-ADP and MinE
+are. \fixme{I know that the idea here is wrong since I'm pretty
+  sure there's an entirely different Min system protein that is averse
+  to the polymer (minC?).  We need to look this up again and be very
+  specific about testing the idea properly.  If the MinC is attached
+  to the minD and that's the idea, then we need to plot the nflD (total
+  D) along with these other proteins, to give an idea of the density
+  of total minD (and perhaps MinC)}
+
+Figure \ref{frequency-plot-40-20-0-0-150} also shows that the middle density oscillates at a frequency that is
+twice that of the polar regions, which is to be expected considering
+the symmetry of the center compared to the that of the polar regions.
+Also, the difference between density maxima and minima each
+oscillation is smaller for the middle points than for the polar
+points.  This is evident from simply watching the simulation movies -
+the fluctulations are more extreme in the polar regions.
+
+We see as well
+
+The difference between the center and max pole densities of the nflD
+do not seem to be very extreme.  Wonder if you do a comparison of the
+max density versus center density somehow.  Really ask how it would
+effect the polymer that's supposed to build.  Are there definded
+limits on how extreme this difference can be?  If the oscillations
+settle down into the same density difference for each cell shape, how
+can polymer build?
+\subsection{Randst shape}
+\subsubsection{Randst-96-Star}
+\subsubsection{Randst-97-}
+\subsubsection{Randst-98-Actually Random}
+\subsubsection{Randst-99}
+\section{Interpretation of Data}
+\section{Conclusion}
+\section*{Appendix}
+\bibliography{paper}
+
+%%Below are NOTES for the Writing
 
@@
 
-The difference between the center and max pole densities of the nflD
-do not seem to be very extreme.  Wonder if you do a comparison of the
-max density versus center density somehow.  Really ask how it would
-effect the polymer that's supposed to build.  Are there definded
-limits on how extreme this difference can be?  If the oscillations
-settle down into the same density difference for each cell shape, how
-can polymer build?  Also with this, when look at the periods and max
+ Also with this, when look at the periods and max
 denisty/min density ratio, consider the size dimensions of the pill
@@
 
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-990-150.pdf}
-%%   \caption{randst 99}
-%%   %\label{}
-%% \end{figure}
-%% \begin{figure}
+%%\begin{figure}
 %%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-80-60-980-150.pdf}
@@
 
-\appendix
-
-\section*{Appendix}
-
 \end{document}

### 2013-07-18 pyplots/frequency_plot.py

@@ -10,7 +10,7 @@ import time
 import file_loader as load
 
 
-dx = .15
+dx = load.dx
 #wip
 
 #function to compute the local maxima of a 2 dimensional array (used for local maxima in space)
@@ -50,6 +50,13 @@ f_param3 = sys.argv[4]
 f_param4 = sys.argv[5]
 f_param5 = sys.argv[6]
 
+par1 = str(int(10*(float(f_param1))))
+par2 = str(int(10*(float(f_param2))))
+par3 = str(int(10*(float(f_param3))))
+par4 = str(int(10*(float(f_param4))))
+par5 = str(int(10*(float(f_param5))))
+
+
 nflE = load.data(protein="nflE")
 nflD = load.data(protein="nflD")
 nATP = load.data(protein="nATP")
@@ -58,8 +65,23 @@ nADP = load.data(protein="nADP")
 Nd = load.data(protein="Nd")
 Nde = load.data(protein="Nde")
 
-proteins = [nflE, nflD, nATP, nE, nADP, Nd, Nde]
-proteins_strings = ["nflE", "nflD", "nATP", "nE", "nADP", "Nd", "Nde"]
+mid = False
+if "-mid" in sys.argv:
+    mid = True
+    print "The -mid flag was set so we'll add the middle point data to the plot"
+
+norm = False
+if "-norm" in sys.argv:
+    norm = True
+    print "We are normalizing the plots so the highest density for each protein will be one"
+
+
+proteins = [nATP, nE, nADP, Nd, Nde]#normally have nflD and nflE too
+proteins_strings = ["nATP", "nE", "nADP", "Nd", "Nde"] #normally "nflD" and "nflE"
+if mid:
+    proteins_strings = ["nATP", "middle-nATP","nE", "middle-nE","nADP", "middle-nADP"] #normally "nflD" and "nflE"
+
+
 
 for p in proteins:
     for i in p.dataset:
@@ -68,8 +90,8 @@ for p in proteins:
             break
     print p.pointInfo
 
-mid_z = 2 + round((float(f_param1)-.15)/dx)
-mid_y = 2 + round((float(f_param2)-.15)/dx)
+mid_z = 2 + round((float(f_param1)-dx)/dx)
+mid_y = 2 + round((float(f_param2)-dx)/dx)
 
 
 for p in proteins:
[…]

### 2013-07-18 paper/paper.tex
more paper

@@
 fit the qualitative picture except for the sharp MinD-ADP peak.  One
-could except it to be a sharp peak, meaning that the MinD-ADP proteins
+could except that it is a sharp peak, meaning that the MinD-ADP proteins
 do not last in the cytoplasm for very long before they are converted
@@
 a good candidate for polymer aversion while the MinD-ADP and MinE
-are. \fixme{I know that the idea here is wrong since I'm pretty
-  sure there's an entirely different Min system protein that is averse
-  to the polymer (minC?).  We need to look this up again and be very
+are. \fixme{I know that the idea here is wrong since I'm pretty sure
+  there's an entirely different Min system protein that is averse to
+  the polymer (minC?).  We need to look this up again and be very
   specific about testing the idea properly.  If the MinC is attached
-  to the minD and that's the idea, then we need to plot the nflD (total
-  D) along with these other proteins, to give an idea of the density
-  of total minD (and perhaps MinC)}
+  to the minD and that's the idea, then we need to plot the nflD
+  (total D) along with these other proteins, to give an idea of the
+  density of total minD (and perhaps MinC).  It really would be good
+  to do a more extensive analysis here, referencing what other papers
+  say about this.}
 
-Figure \ref{frequency-plot-40-20-0-0-150} also shows that the middle density oscillates at a frequency that is
-twice that of the polar regions, which is to be expected considering
-the symmetry of the center compared to the that of the polar regions.
-Also, the difference between density maxima and minima each
-oscillation is smaller for the middle points than for the polar
-points.  This is evident from simply watching the simulation movies -
-the fluctulations are more extreme in the polar regions.
+It would be good here to add the time map plots and discuss the idea
+about the proteins spending most of their time in the center of the
+cell.
 
-We see as well
+Figure \ref{frequency-plot-40-20-0-0-150} also shows that the middle
+density oscillates at a frequency that is twice that of the polar
+regions, which is to be expected considering the symmetry of the
+center compared to the that of the polar regions.  Also, the
+difference between density maxima and minima each oscillation is
+smaller for the middle points than for the polar points.  This is
+evident from simply watching the simulation movies - the fluctulations
+are more extreme in the polar regions.
 
-The difference between the center and max pole densities of the nflD
-do not seem to be very extreme.  Wonder if you do a comparison of the
-max density versus center density somehow.  Really ask how it would
-effect the polymer that's supposed to build.  Are there definded
-limits on how extreme this difference can be?  If the oscillations
-settle down into the same density difference for each cell shape, how
-can polymer build?
+Add a table here that shows the period of oscillations versus the cell
+dimensions.  Do the mathematical solution of the differential
+equations for an infinite long cylinder with different widths to see
+how fast the mxima move and compare (Dr. Roundy says that making the
+radial speed infinite would help.
+
 \subsection{Randst shape}

### 2013-07-18 paper/paper.tex
more paper changes

@@
 
-The theory states that the aversion of the (forgot name of polymer) to
-the MinD system is responsible for the polymer setting up in the
-center of the cell as opposed to at the cellular poles.\fixme{look
-  this up and write this section up properly} The theory is dependent
-on there being a significant difference in protein density between the
-center and polar regions. It is worthwhile examining this difference
-in detail.  Figure \ref{frequency-plot-40-20-0-0-150} shows a
-comparison of density fluctuation over time at a point adjacent to the
-polar cell wall and at a point adjacent to the cell wall in the center
-region of the cell.  The different proteins show different
-relationships between their maxima and minima.  The MinD-ADP show
-sharp spikes at the poles and much smaller oscillations at in the
-middle.  The values at the poles are always greater than those in the
-middle, and the polar peaks exhibit densities that are roughly 2.5
-times greater than the maxima in the center (\fixme{this factor and
-  the following factor will be put into a table of comparisons for
-  each protein and for the different cell sizes}).  The MinD-ATP
-densities show a very different trend.  For these it is the center
-density that is almost always greater than the polar density.  The
-difference in density at the pole versus the middle is a factor of
-roughly .85 (once again we'll do this more officially in a table).
-The MinE is similar to the MinD-ADP comparison.  It shows a difference
-in maxima by a factor of roughly 2.  It seems that the MinD-ATP is not
-a good candidate for polymer aversion while the MinD-ADP and MinE
-are. \fixme{I know that the idea here is wrong since I'm pretty sure
-  there's an entirely different Min system protein that is averse to
-  the polymer (minC?).  We need to look this up again and be very
-  specific about testing the idea properly.  If the MinC is attached
-  to the minD and that's the idea, then we need to plot the nflD
-  (total D) along with these other proteins, to give an idea of the
-  density of total minD (and perhaps MinC).  It really would be good
-  to do a more extensive analysis here, referencing what other papers
-  say about this.}
+The theory states that the aversion of the FtsZ polymer to the MinC
+protein is responsible for the FtsZ polymer setting up in the center
+of the cell as opposed to at the cellular poles.  The MinC protein in
+turn natrually associates with the minD protein that is modelled in
+Huang's differential equations.  \fixme{look this up and write this
+  again} The theory is dependent on there being a significant
+difference in protein density between the center and polar regions. It
+is worthwhile examining this difference in detail.  Figure
+\ref{frequency-plot-40-20-0-0-150} shows a comparison of density
+fluctuation over time at a point adjacent to the polar cell wall and
+at a point adjacent to the cell wall in the center region of the cell.
+The different proteins show different relationships between their
+maxima and minima.  The MinD-ADP show sharp spikes at the poles and
+much smaller oscillations at in the middle.  The values at the poles
+are always greater than those in the middle, and the polar peaks
+exhibit densities that are roughly 2.5 times greater than the maxima
+in the center (\fixme{this factor and the following factor will be put
+  into a table of comparisons for each protein and for the different
+  cell sizes}).  The MinD-ATP densities show a very different trend.
+For these it is the center density that is almost always greater than
+the polar density.  The difference in density at the pole versus the
+middle is a factor of roughly .85 (once again we'll do this more
+officially in a table).  The MinE is similar to the MinD-ADP
+comparison.  It shows a difference in maxima by a factor of roughly 2.
+The MinC protein is associated with the minD protein, so perhaps the
+most important camparison is between the nfl-MinD (MinD protein in all
+its forms) at the ends and in the center of the pill.  This shows
+sharp spikes at the pills and a maxima difference factor of roughly
+1.25. \fixme{I'd like to analyze further what this means for the FtZ
+  polymer.  Would a difference like this really have a big effect?
+  What sort of effect should it have, looking at experimental data?
+  One thing is that Mannik (is it Mannik?) genetically deletes the
+  MinC protein and they get 73 percent proper cell division.  It
+  really would be good to do a more extensive analysis here,
+  referencing what other papers say about this.}
 
@@
 \section{Introduction}
+It is vital during the process of bacterial cell division for proper nucleiod occlusion that the FtsZ polymer chain develop on the cell wall in the center of the cell.
+Huang et all have shown in simulation that a system of Min protein interaction within the cell will lead to a natural oscillation of the MinC protein from one cell end to the other that will leave the center free of any build up of MinC.
+This will allow for the PtsZ chain to develop in the center and not at the ends, where the two nucleiods are housed.
+The interaction takes place between MinE,MinD, and MinC, which naturally associates with MinD.
+They gneetically mutate the bacterial cells in order to eliminate certain proteins from them.
+They eliminate MinC and SlmA.
+SlmA deletion has very little effect accept for some assymetry in cell division area.
+The MinC deletion shows a difference in volume division.
+Only 73 percent divide with the approximate 1:1 ratio while for un deleted 99 percent do.This effect is seen in both flattened and unflattened cells, and its very similar in both, which is suprising.
+Mannik et all have shown that the formation of irregular cell shapes adversly effects the Min system's ability to maintain their regular oscillatory behavior.
+They use microfabricated silicon chips that have etched microchambers and shallow channels.
+
 \subsection{What is the MinD system and why is it important?}
+
 -Systm of proteins in E.Coli and other cells.

### 2013-07-18 pyplots/frequency_plot.py

@@ -76,10 +76,10 @@ if "-norm" in sys.argv:
     print "We are normalizing the plots so the highest density for each protein will be one"
 
 
-proteins = [nATP, nE, nADP, Nd, Nde]#normally have nflD and nflE too
+proteins = [nflD, nATP, nE, nADP, Nd, Nde]#normally have nflD and nflE too
 proteins_strings = ["nATP", "nE", "nADP", "Nd", "Nde"] #normally "nflD" and "nflE"
 if mid:
-    proteins_strings = ["nATP", "middle-nATP","nE", "middle-nE","nADP", "middle-nADP"] #normally "nflD" and "nflE"
+    proteins_strings = ["nflD", "middle-nflD", "nATP", "middle-nATP","nE", "middle-nE","nADP", "middle-nADP"] #normally "nflD" and "nflE"
 
 
 

### 2013-07-18 paper/paper.tex
even more!

@@
 exhibit densities that are roughly 2.5 times greater than the maxima
-in the center (\fixme{this factor and the following factor will be put
+in the center (\fixme{this factor and the following factors will be put
   into a table of comparisons for each protein and for the different

### 2013-07-19 paper/paper.tex
more changes (these are not very good I need to go home)

@@
 \begin{document}
-\title{E Coli project paper}
+\title{E Coli Project Paper Incredibly Rough Draft}
 
@@
 \section{Introduction}
+\fixme{I need a lot of references here!!!  (And the writing is just terrible)}
+It is vital that the process of bacterial cell division result in a single nucleiod in each daughter cell.
+The cell must avoid minicelling, or splitting into daughter cells with lopsided volumes.
+One of the mechanisms the cell employs in order to avoid this is to allow a long FtsZ polymer chain to develop on the cell wall in the center of the cell.
+This chain acts as a guide for the cell splitting process.
+Huang et all have shown in simulation that a system of Min protein interaction within the cell will lead to a natural oscillation of the MinC protein, which exhibits an aversion to the FtsZ polymer, from one cell end to the other that will leave the center free of any build up of MinC.
+This will allow for the PtsZ chain to develop in the center and not at the ends, where the two nucleiods are housed.
+The interaction takes place between MinE,MinD, and MinC, which naturally associates with MinD.
+
+Mannik et all have shown that the formation of irregular cell shapes adversly effects the Min system's ability to maintain their regular oscillatory behavior (cramming into spaces).
+
 \subsection{What is the MinD system and why is it important?}
@@
 
-%%Below are NOTES for the Writing
+\section{Below are NOTES for the Writing}
 
 \section{Introduction}
-It is vital during the process of bacterial cell division for proper nucleiod occlusion that the FtsZ polymer chain develop on the cell wall in the center of the cell.
-Huang et all have shown in simulation that a system of Min protein interaction within the cell will lead to a natural oscillation of the MinC protein from one cell end to the other that will leave the center free of any build up of MinC.
+\fixme{I need a lot of references here!!!}
+It is vital that the process of bacterial cell division result in a single nucleiod in each daughter cell.
+The cell must avoid minicelling, or splitting into daughter cells with lopsided volumes.
+One of the mechanisms the cell employs in order to avoid this is to allow a long FtsZ polymer chain to develop on the cell wall in the center of the cell.
+This chain acts as a guide for the cell splitting process.
+Huang et all have shown in simulation that a system of Min protein interaction within the cell will lead to a natural oscillation of the MinC protein, which exhibits an aversion to the FtsZ polymer, from one cell end to the other that will leave the center free of any build up of MinC.
 This will allow for the PtsZ chain to develop in the center and not at the ends, where the two nucleiods are housed.
 The interaction takes place between MinE,MinD, and MinC, which naturally associates with MinD.
-They gneetically mutate the bacterial cells in order to eliminate certain proteins from them.
-They eliminate MinC and SlmA.
-SlmA deletion has very little effect accept for some assymetry in cell division area.
-The MinC deletion shows a difference in volume division.
-Only 73 percent divide with the approximate 1:1 ratio while for un deleted 99 percent do.This effect is seen in both flattened and unflattened cells, and its very similar in both, which is suprising.
-Mannik et all have shown that the formation of irregular cell shapes adversly effects the Min system's ability to maintain their regular oscillatory behavior.
-They use microfabricated silicon chips that have etched microchambers and shallow channels.
+
+Mannik et all have shown that the formation of irregular cell shapes adversly effects the Min system's ability to maintain their regular oscillatory behavior (cramming into spaces).
 

### 2013-07-29 pyplots/file_loader.py
.

@@ -51,6 +51,7 @@ class data(object):
         else:
             return dat_filenames
 
+#function for easier plot name printing. probably should be renamed itself.
 def print_string(plot_name,p):
     arg = [str(int(100*(float(i)))) for i in sys.argv[2:7]]
     filename = "./data/shape-%s/plots/%s%s%s-%s-%s-%s-%s-%s-%s-%s.pdf"%(f_shape, hires_str, m_str, plot_name, p.protein, f_shape, arg[0], arg[1], arg[2], arg[3], arg[4])

### 2013-07-29 paper/protein_paper.sh
added a lot of stuff after coming back before pulling Renes changes.  Nothing very major except the bug fix in protein_microscopy

@@ -1,6 +1,6 @@
 #!/bin/bash
 pdflatex paper/paper.tex
-#bibtex paper
+bibtex paper/paper
 pdflatex paper/paper.tex
 pdflatex paper/paper.tex
 

### 2013-07-29 protein_microscopy.cpp

@@ -971,46 +971,48 @@ int main (int argc, char *argv[]) {
       char *outfilenameflE = new char[1000];
       if (dx==.05) {
         if (slice_flag==1) {
-          sprintf(outfilenameflE, "data/shape-%s/hires-nflE-%s-%03.2f-%03.2f-%03.2f-%03.2f-%03.2f-%03d.dat", argv[1],argv[1],A,B,C,D,density_factor,k);
+          sprintf(outfilenameflE, "data/shape-%s/hires-NflE-%s-%03.2f-%03.2f-%03.2f-%03.2f-%03.2f-%03d.dat", argv[1],argv[1],A,B,C,D,density_factor,k);
         }
         else {
-          sprintf(outfilenameflE, "data/shape-%s/hires-m-nflE-%s-%03.2f-%03.2f-%03.2f-%03.2f-%03.2f-%03d.dat", argv[1],argv[1],A,B,C,D,density_factor,k);
+          sprintf(outfilenameflE, "data/shape-%s/hires-m-NflE-%s-%03.2f-%03.2f-%03.2f-%03.2f-%03.2f-%03d.dat", argv[1],argv[1],A,B,C,D,density_factor,k);
         }
       }
       else {
         if (slice_flag==1) {
-          sprintf(outfilenameflE, "data/shape-%s/nflE-%s-%03.2f-%03.2f-%03.2f-%03.2f-%03.2f-%03d.dat", argv[1],argv[1],A,B,C,D,density_factor,k);
+          sprintf(outfilenameflE, "data/shape-%s/NflE-%s-%03.2f-%03.2f-%03.2f-%03.2f-%03.2f-%03d.dat", argv[1],argv[1],A,B,C,D,density_factor,k);
         }
         else {
-          sprintf(outfilenameflE, "data/shape-%s/m-nflE-%s-%03.2f-%03.2f-%03.2f-%03.2f-%03.2f-%03d.dat", argv[1],argv[1],A,B,C,D,density_factor,k);
+          sprintf(outfilenameflE, "data/shape-%s/m-NflE-%s-%03.2f-%03.2f-%03.2f-%03.2f-%03.2f-%03d.dat", argv[1],argv[1],A,B,C,D,density_factor,k);
         }
       }
 
-      FILE *nflEfile = fopen((const char *)outfilenameflE,"w");
+      FILE *NflEfile = fopen((const char *)outfilenameflE,"w");
[…]

### 2013-07-29 pyplots/showatp.py

@@ -15,6 +15,7 @@ nATP = load.data(protein="nATP")
 nE = load.data(protein="nE")
 nADP = load.data(protein="nADP")
 Nd = load.data(protein="Nd")
+Nde = load.data(protein="Nde")
 
 f_shape = sys.argv[1]
 f_param1 = sys.argv[2]
@@ -97,16 +98,18 @@ def contourplt(protein):
     +"-"+f_param3+"-"+f_param4+"-"+f_param5+".png")
     return 0
 
-print "Generating flourescent Min D tagging plot:"
-contourplt(nflD)
-print "Done! Generating flourescent Min E tagging plot:"
-contourplt(nflE)
-print "Generating nATP plot:"
-contourplt(nATP)
-print "Done! Generating nE plot:"
-contourplt(nE)
-print "Done! Generating nADP plot:"
-contourplt(nADP)
-print "Done! Generating nD plot:"
-contourplt(Nd)
+# print "Generating flourescent Min D tagging plot:"
+# contourplt(nflD)
+# print "Done! Generating flourescent Min E tagging plot:"
+# contourplt(nflE)
+# print "Generating nATP plot:"
+# contourplt(nATP)
+# print "Done! Generating nE plot:"
+# contourplt(nE)
+# print "Done! Generating nADP plot:"
+# contourplt(nADP)
+# print "Done! Generating nD plot:"
+# contourplt(Nd)
+# print "Finished generating plots."
+contourplt(Nde)
 print "Finished generating plots."

### 2013-07-29 protein.h
sync;

@@ -1,22 +1,3 @@
-
-
-/* struct densities { */
-/* public: */
-/*   densities(int xnum, int ynum, int znum, double mydx); // allocates the arrays */
-/*   //densities(double size, double mydx); // allocates the arrays */
-/*   ~densities(); // free all the arrays */
-/*   int Nx, Ny, Nz; */
-/*   double dx; */
-/*   double *Nd, *Nde, *nATP; */
-/* private: */
-/*   density(const density &); */
-/*   void operator=(const density &); */
-/* }; */
-/*
-extern const int Nx;
-extern const int Ny;
-extern const int Nz;
-*/
 extern double *nATP;
 extern double *nADP;
 extern double *nE;

### 2013-07-29 paper/paper.tex
took figures from paper

@@
 \fixme{I need a lot of references here!!!  (And the writing is just terrible)}
-It is vital that the process of bacterial cell division result in a single nucleiod in each daughter cell.
-The cell must avoid minicelling, or splitting into daughter cells with lopsided volumes.
-One of the mechanisms the cell employs in order to avoid this is to allow a long FtsZ polymer chain to develop on the cell wall in the center of the cell.
-This chain acts as a guide for the cell splitting process.
-Huang et all have shown in simulation that a system of Min protein interaction within the cell will lead to a natural oscillation of the MinC protein, which exhibits an aversion to the FtsZ polymer, from one cell end to the other that will leave the center free of any build up of MinC.
-This will allow for the PtsZ chain to develop in the center and not at the ends, where the two nucleiods are housed.
-The interaction takes place between MinE,MinD, and MinC, which naturally associates with MinD.
+It is vital that the process of bacterial cell division result in a single
+nucleiod in each daughter cell.  The cell must avoid minicelling, or
+splitting into daughter cells with lopsided volumes.  One of the mechanisms
+the cell employs in order to avoid this is to allow a long FtsZ polymer
+chain to develop on the cell wall in the center of the cell.  This chain
+acts as a guide for the cell splitting process.  Huang et all have shown in
+simulation that a system of Min protein interaction within the cell will
+lead to a natural oscillation of the MinC protein, which exhibits an
+aversion to the FtsZ polymer, from one cell end to the other that will
+leave the center free of any build up of MinC.  This will allow for the
+PtsZ chain to develop in the center and not at the ends, where the two
+nucleiods are housed.  The interaction takes place between MinE,MinD, and
+MinC, which naturally associates with MinD.
 
-Mannik et all have shown that the formation of irregular cell shapes adversly effects the Min system's ability to maintain their regular oscillatory behavior (cramming into spaces).
+Mannik et all have shown that the formation of irregular cell shapes
+adversly effects the Min system's ability to maintain their regular
+oscillatory behavior (cramming into spaces).
 
@@
 \subsection{Pill Shape}
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-p/plots/frequency_plot_all_norm-p-40-20-0-0-150.pdf}
-  \caption{Protein density fluctuation with time against the polar
-    wall in a 4$\mu m$ by 2$\mu m$ pill shaped cell.  The wall-bound
-    proteins are shown at a point that is on the wall and the
-    cytoplasm densities are shown at a point immediately adjecent.
-    This plot is normalized so that every protein density peaks at 1}
-  \label{frequency-plot-40-20-0-0-150}
-\end{figure}
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-p/plots/frequency-plot-all-NflD-p-40-20-0-0-150.pdf}
+%%   \caption{Protein density fluctuation with time against the polar
+%%     wall in a 4$\mu m$ by 2$\mu m$ pill shaped cell.  The wall-bound
+%%     proteins are shown at a point that is on the wall and the
+%%     cytoplasm densities are shown at a point immediately adjecent.
+%%     This plot is normalized so that every protein density peaks at 1}
+%%   \label{frequency-plot-40-20-0-0-150}
+%% \end{figure}
 
@@
   the unit and dimensions.  The plotting may need to be changed}
-Figure \ref{frequency-plot-40-20-0-0-150} shows the protein density
+Figure %%\ref{frequency-plot-40-20-0-0-150} shows the protein density
 fluctuations at a point in space adjecent to a polar wall.  At each
@@
 
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-p/plots/frequency_plot_all_middle-p-40-20-0-0-150.pdf}
-  \caption{A comparison of protein density fluctuation with time
-    against the polar wall and at a point in the center of the
-    z-length and adjacent to the wall, in the cytoplasm.  The cell is
-    pill shaped and has dimensions of 4$\mu m$ by 2$\mu m$.  }
-  \label{frequency-plot-40-20-0-0-150}
-\end{figure}
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-p/plots/frequency_plot_all_middle-p-40-20-0-0-150.pdf}
+%%   \caption{A comparison of protein density fluctuation with time
+%%     against the polar wall and at a point in the center of the
+%%     z-length and adjacent to the wall, in the cytoplasm.  The cell is
+%%     pill shaped and has dimensions of 4$\mu m$ by 2$\mu m$.  }
+%%   \label{frequency-plot-40-20-0-0-150}
+%% \end{figure}
 
@@
 is worthwhile examining this difference in detail.  Figure
-\ref{frequency-plot-40-20-0-0-150} shows a comparison of density
+%%\ref{frequency-plot-40-20-0-0-150} shows a comparison of density
 fluctuation over time at a point adjacent to the polar cell wall and
@@
 \fixme{I need a lot of references here!!!}
-It is vital that the process of bacterial cell division result in a single nucleiod in each daughter cell.
-The cell must avoid minicelling, or splitting into daughter cells with lopsided volumes.
-One of the mechanisms the cell employs in order to avoid this is to allow a long FtsZ polymer chain to develop on the cell wall in the center of the cell.
-This chain acts as a guide for the cell splitting process.
-Huang et all have shown in simulation that a system of Min protein interaction within the cell will lead to a natural oscillation of the MinC protein, which exhibits an aversion to the FtsZ polymer, from one cell end to the other that will leave the center free of any build up of MinC.
-This will allow for the PtsZ chain to develop in the center and not at the ends, where the two nucleiods are housed.
-The interaction takes place between MinE,MinD, and MinC, which naturally associates with MinD.
+It is vital that the process of bacterial cell division result in a single
+nucleiod in each daughter cell.  The cell must avoid minicelling, or
+splitting into daughter cells with lopsided volumes.  One of the mechanisms
+the cell employs in order to avoid this is to allow a long FtsZ polymer
+chain to develop on the cell wall in the center of the cell.  This chain
+acts as a guide for the cell splitting process.  Huang et all have shown in
+simulation that a system of Min protein interaction within the cell will
+lead to a natural oscillation of the MinC protein, which exhibits an
+aversion to the FtsZ polymer, from one cell end to the other that will
+leave the center free of any build up of MinC.  This will allow for the
+PtsZ chain to develop in the center and not at the ends, where the two
+nucleiods are housed.  The interaction takes place between MinE,MinD, and
+MinC, which naturally associates with MinD.
 
-Mannik et all have shown that the formation of irregular cell shapes adversly effects the Min system's ability to maintain their regular oscillatory behavior (cramming into spaces).
+Mannik et all have shown that the formation of irregular cell shapes
+adversly effects the Min system's ability to maintain their regular
+oscillatory behavior (cramming into spaces).
 
@@
 Pill Normal section -
-Our goal with this project was to test whether or not the computational model developed by
-Huang et al was consistent with the newer experimental results (squishing E
-Coli) produced by Mannick et al. We generally see that:
+Our goal with this project was to test whether or not the computational
+model developed by Huang et al was consistent with the newer experimental
+results (squishing E Coli) produced by Mannick et al. We generally see
+that:
 
@@
 \section{animate?}
-\animategraphics[height=2.8in,autoplay,controls]{12}{../data/shape-randst/plots/movie-density-Nd-96/animate_}{0}{120}
+%%\animategraphics[height=2.8in,autoplay,controls]{12}{../data/shape-randst/plots/movie-density-Nd-96/animate_}{0}{120}
 

### 2013-07-31 pyplots/box_plot.py
fixed typo bug

@@ -154,6 +154,9 @@ for p in proteins:
 
     #matplotlib method for filling in color between two lines. left = blue, mid = green, right = red.
     if "-all" not in sys.argv:
+        plt.plot(time_axis[start:end],lowest_line[start:end],color="blue",linewidth=0.5)
+        plt.plot(time_axis[start:end],middle_line[start:end],color="green",linewidth=0.5)
+        plt.plot(time_axis[start:end],top_line[start:end],color="red",linewidth=0.5)
         plt.fill_between(time_axis[start:end],0,lowest_line[start:end],alpha=0.5)
         plt.fill_between(time_axis[start:end],lowest_line[start:end],middle_line[start:end],alpha=0.5,facecolor="green")
         plt.fill_between(time_axis[start:end],middle_line[start:end],top_line[start:end],alpha=0.5,facecolor="red")
@@ -163,26 +166,29 @@ for p in proteins:
         plt.fill_between(time_axis[start:end],plot_lines[0][start:end],plot_lines[1][start:end],alpha=0.5,facecolor="blue")
         plt.fill_between(time_axis[start:end],plot_lines[1][start:end],plot_lines[2][start:end],alpha=0.75,facecolor="blue")
         plt.fill_between(time_axis[start:end],plot_lines[2][start:end],plot_lines[3][start:end],alpha=1.0,facecolor="blue")
+
         plt.fill_between(time_axis[start:end],plot_lines[3][start:end],plot_lines[4][start:end],alpha=0.25,facecolor="red")
         plt.fill_between(time_axis[start:end],plot_lines[4][start:end],plot_lines[5][start:end],alpha=0.5,facecolor="red")
         plt.fill_between(time_axis[start:end],plot_lines[5][start:end],plot_lines[6][start:end],alpha=0.75,facecolor="red")
         plt.fill_between(time_axis[start:end],plot_lines[6][start:end],plot_lines[7][start:end],alpha=1.0,facecolor="red")
+
         plt.fill_between(time_axis[start:end],plot_lines[7][start:end],plot_lines[8][start:end],alpha=0.25,facecolor="green")
         plt.fill_between(time_axis[start:end],plot_lines[8][start:end],plot_lines[9][start:end],alpha=0.5,facecolor="green")
         plt.fill_between(time_axis[start:end],plot_lines[9][start:end],plot_lines[10][start:end],alpha=0.75,facecolor="green")
[…]

### 2013-07-31 pyplots/box_plot.py
legends box moved

@@ -181,38 +181,45 @@ for p in proteins:
         plt.plot(time_axis[start:end],plot_lines[1][start:end],alpha=0.5,color="blue",linewidth=0.5)
         plt.plot(time_axis[start:end],plot_lines[2][start:end],alpha=0.75,color="blue",linewidth=0.5)
         plt.plot(time_axis[start:end],plot_lines[3][start:end],alpha=1.0,color="blue",linewidth=0.5)
+
         plt.plot(time_axis[start:end],plot_lines[4][start:end],alpha=0.25,color="red",linewidth=0.5)
         plt.plot(time_axis[start:end],plot_lines[5][start:end],alpha=0.5,color="red",linewidth=0.5)
         plt.plot(time_axis[start:end],plot_lines[6][start:end],alpha=0.75,color="red",linewidth=0.5)
         plt.plot(time_axis[start:end],plot_lines[7][start:end],alpha=1.0,color="red",linewidth=0.5)
+
         plt.plot(time_axis[start:end],plot_lines[8][start:end],alpha=0.25,color="green",linewidth=0.5)
         plt.plot(time_axis[start:end],plot_lines[9][start:end],alpha=0.5,color="green",linewidth=0.5)
         plt.plot(time_axis[start:end],plot_lines[10][start:end],alpha=0.75,color="green",linewidth=0.5)
         plt.plot(time_axis[start:end],plot_lines[11][start:end],alpha=1.0,color="green",linewidth=0.5)
+
         plt.legend(["nATP proteins left", "nADP proteins left", "Nd proteins left", "Nde proteins left", \
                           "nATP proteins mid", "nADP proteins mid", "Nd proteins mid", "Nde proteins mid", \
-                          "nATP proteins right", "nADP proteins right", "Nd proteins right", "Nde proteins right"],loc="best")
+                          "nATP proteins right", "nADP proteins right", "Nd proteins right", "Nde proteins right"],loc=9,ncol=2)
 
     if ("-all" in sys.argv) and (p==NflE):
         plt.fill_between(time_axis[start:end],[0]*(end-start),plot_lines[0][start:end],alpha=0.3,facecolor="blue")
         plt.fill_between(time_axis[start:end],plot_lines[0][start:end],plot_lines[1][start:end],alpha=1.0,facecolor="blue")
+
         plt.fill_between(time_axis[start:end],plot_lines[1][start:end],plot_lines[2][start:end],alpha=0.3,facecolor="red")
[…]

### 2013-07-31 pyplots/box_plot.py
boxPlot before pulling from Rene

@@ -183,9 +183,9 @@ for p in proteins:
         plt.plot(time_axis[start:end],plot_lines[0][start:end],alpha=0.5,color="green",linewidth=0.5)
         plt.plot(time_axis[start:end],plot_lines[0][start:end],alpha=0.75,color="green",linewidth=0.5)
         plt.plot(time_axis[start:end],plot_lines[0][start:end],alpha=1.0,color="green",linewidth=0.5)
-        plt.legend(["nATP proteins left", "nADP proteins left", "Nd proteins left", "Nde proteins left", \
-                          "nATP proteins mid", "nADP proteins mid", "Nd proteins mid", "Nde proteins mid", \
-                          "nATP proteins right", "nADP proteins right", "Nd proteins right", "Nde proteins right"],loc="best")
+        # plt.legend(["nATP proteins left", "nADP proteins left", "Nd proteins left", "Nde proteins left", \
+        #                   "nATP proteins mid", "nADP proteins mid", "Nd proteins mid", "Nde proteins mid", \
+        #                   "nATP proteins right", "nADP proteins right", "Nd proteins right", "Nde proteins right"],loc="best")
 
     if ("-all" in sys.argv) and (p==NflE):
         plt.fill_between(time_axis[start:end],[0]*(end-start),plot_lines[0][start:end],alpha=0.3,facecolor="blue")
@@ -223,3 +223,41 @@ for p in proteins:
     if "-all" not in sys.argv:
         plt.legend(["left density", "middle density", "right density"],loc="best")
     plt.savefig(load.print_string("box-plot"+short_string+all_string,p))
+
+    plt.figure()
+    plt.xlabel("Time")
+    plt.ylabel("%s count"%p.protein)
+    plt.title("%s count vs time at end caps of cell"%p.protein)
+
+    if ("-all" in sys.argv) and (p==NflD):
+        plt.fill_between(time_axis[start:end],[0]*(end-start),plot_lines[0][start:end],alpha=1.0,facecolor="blue")
+        plt.fill_between(time_axis[start:end],plot_lines[0][start:end],plot_lines[1][start:end],alpha=1.0,facecolor="red")
+        plt.fill_between(time_axis[start:end],plot_lines[1][start:end],plot_lines[2][start:end],alpha=1.0,facecolor="green")
[…]

### 2013-07-31 pyplots/box_plot.py
switched ADP and ATP in box_plots

@@ -33,7 +33,7 @@ Nde = load.data(protein="Nde")
 proteins = [NflE, NflD]
 
 #sub proteins are the individual, optionally-plotted proteins.
-sub_proteins_D = [nATP, nADP, Nd, Nde]
+sub_proteins_D = [nADP, nATP, Nd, Nde]
 sub_proteins_E = [nE, Nde]
 
 for p in proteins:
@@ -119,9 +119,9 @@ for p in proteins:
                 individual_proteins.proteins_right += [right_sum*dV]
         #store them in one big list for plotting purposes later. the order is important, since we will be
         #adding each element in this list to the one before it, starting with the first one (for the stacked plot)
-        NflD.lines = [nATP.proteins_left, nADP.proteins_left, Nd.proteins_left, Nde.proteins_left, \
-                          nATP.proteins_mid, nADP.proteins_mid, Nd.proteins_mid, Nde.proteins_mid, \
-                          nATP.proteins_right, nADP.proteins_right, Nd.proteins_right, Nde.proteins_right]
+        NflD.lines = [nADP.proteins_left, nATP.proteins_left, Nd.proteins_left, Nde.proteins_left, \
+                          nADP.proteins_mid, nATP.proteins_mid, Nd.proteins_mid, Nde.proteins_mid, \
+                          nADP.proteins_right, nATP.proteins_right, Nd.proteins_right, Nde.proteins_right]
 
     #calculate the indicies of the first period or so
     #if -all and -short are both not present in the system arguments,
@@ -192,9 +192,9 @@ for p in proteins:
         plt.plot(time_axis[start:end],plot_lines[10][start:end],alpha=0.75,color="green",linewidth=0.5)
         plt.plot(time_axis[start:end],plot_lines[11][start:end],alpha=1.0,color="green",linewidth=0.5)
 
-        plt.legend(["nATP proteins left", "nADP proteins left", "Nd proteins left", "Nde proteins left", \
-                          "nATP proteins mid", "nADP proteins mid", "Nd proteins mid", "Nde proteins mid", \
-                          "nATP proteins right", "nADP proteins right", "Nd proteins right", "Nde proteins right"],loc=9,ncol=2)
+        plt.legend(["nADP proteins left", "nATP proteins left", "Nd proteins left", "Nde proteins left", \
[…]

### 2013-07-31 pyplots/box_plot.py
updated box plot to have dividers at the endcaps

@@ -14,11 +14,11 @@ import file_loader as load
 #returns the indicies of the first two peaks.
 def oscillation_period(density_list):
     peaklist = []
-    index_position_pairs = list(enumerate(density_list))
-    for i in index_position_pairs:
-        if (abs(i[1]-max(density_list)) < .01*max(density_list)):
-            peaklist += [i[0]]
-    return (peaklist[0], peaklist[1])
+    index_position = list(enumerate(density_list))
+    for i in range(1,len(index_position)-1):
+        if (index_position[i][1]>index_position[i-1][1]) and (index_position[i][1]>index_position[i+1][1]):
+            peaklist += [index_position[i][0]]
+    return (peaklist[0], peaklist[2])
 
 #load protein data.
 NflE = load.data(protein="NflE")
@@ -38,8 +38,12 @@ sub_proteins_E = [nE, Nde]
 
 for p in proteins:
     #pick a relatively arbitrary box divider
-    divider_left = round(p.datashape[1]/3)
-    divider_right = round(p.datashape[1]*2/3)
+    divider_left = round(p.datashape[0]/2)-1
+    divider_right = p.datashape[1] - (round(p.datashape[0]/2)-1)
+    print "Here!"
+    print p.datashape[1]
+    print divider_right
+    print divider_left
     p.proteins_left = []
     p.proteins_mid = []
     p.proteins_right = []
@@ -128,7 +132,8 @@ for p in proteins:
     #plot all of the data.
     (start, end) = (0, -1)
     if ("-all" in sys.argv) or ("-short" in sys.argv):
-        (start, end) = oscillation_period(p.proteins_mid)
+        (start, end) = oscillation_period(proteins[0].proteins_mid)
+        print oscillation_period(proteins[0].proteins_mid)
 
     #plot them and save the figures.
     plt.figure()

### 2013-08-15 protein_microscopy.cpp
updated file name printing (we werent printing shape names) and the plots to reflect that change

@@ -326,7 +326,7 @@ struct protein {
 
 char* print_filename(const char* plotname, const char* proteinname) {
   char* filename = new char[1024];
-  sprintf(filename,"data/shape-%s/%s%s%s-%s-%1.2f-%1.2f-%1.2f-%1.2f-%1.2f.dat",mem_f_shape.c_str(),hires_flag_str,slice_flag_str,plotname,proteinname,A,B,C,D,density_factor);
+  sprintf(filename,"data/shape-%s/%s%s%s-%s-%s-%1.2f-%1.2f-%1.2f-%1.2f-%1.2f.dat",mem_f_shape.c_str(),hires_flag_str,slice_flag_str,plotname,proteinname,mem_f_shape.c_str(),A,B,C,D,density_factor);
   return filename;
 }
 
@@ -800,28 +800,28 @@ int main (int argc, char *argv[]) {
 
       //box plot ...
       if (i%print_denominator==0) {
-	if ((strcmp(proteinList[pNum]->name,"D_nATP")==0) || (strcmp(proteinList[pNum]->name,"E_nE")==0) || (strcmp(proteinList[pNum]->name,"D_nADP")==0)) {
-	  dV = dx*dx*dx;
-	}
-	else {
-	  dV = 1;
-	}
+        if ((strcmp(proteinList[pNum]->name,"D_nATP")==0) || (strcmp(proteinList[pNum]->name,"E_nE")==0) || (strcmp(proteinList[pNum]->name,"D_nADP")==0)) {
+          dV = dx*dx*dx;
+        }
+        else {
+          dV = 1;
+        }
         int i_dat = i/print_denominator;
         for (int a=0; a<Ny; a++) {
           for (int b=0; b<Nz; b++) {
             for (int c=0; c<Nx; c++) {
               if (mem_f_shape == "p") {
-		if (b < box_divider_left) {
+                if (b < box_divider_left) {
                   proteinList[pNum]->numLeft[i_dat] += accessGlobals[pNum][c*Ny*Nz+a*Nz+b]*dV;
                 }
                 if (b > box_divider_right) {
                   proteinList[pNum]->numRight[i_dat] += accessGlobals[pNum][c*Ny*Nz+a*Nz+b]*dV;
[…]

### 2013-08-15 pyplots/box_plot.py

@@ -26,7 +26,7 @@ import file_loader_dump as load
 def returnData(boxName,proteinType):
 
     #open the data file, grab the line with the correct protein type and box partition, load it as a [string] (so we can use list comprehensions)
-    with open("./data/shape-%s/box-plot--%s-%s-%s-%s-%s.dat"%(load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5),"r") as boxData:
+    with open("./data/shape-%s/box-plot--%s-%s-%s-%s-%s-%s.dat"%(load.f_shape,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5),"r") as boxData:
         proteinsOverTime = [line for line in boxData if (proteinType in line) and (boxName in line)]
 
 
@@ -137,7 +137,7 @@ def main():
     plt.xlabel("Time (s)")
     plt.ylabel("Number of proteins")
     plt.legend(plotNameList_D,loc="best",prop={'size':10})
-    plt.savefig("./data/shape-%s/plots/box-plot_D--%s-%s-%s-%s-%s.pdf"%(load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5))
+    plt.savefig("./data/shape-%s/plots/box-plot_D--%s-%s-%s-%s-%s-%s.pdf"%(load.f_shape,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5))
 
     plt.figure()
     j=0
@@ -160,7 +160,7 @@ def main():
     plt.xlabel("Time (s)")
     plt.ylabel("Number of proteins")
     plt.legend(plotNameList_E,loc="best",prop={'size':10})
-    plt.savefig("./data/shape-%s/plots/box-plot_E--%s-%s-%s-%s-%s.pdf"%(load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5))
+    plt.savefig("./data/shape-%s/plots/box-plot_E--%s-%s-%s-%s-%s-%s.pdf"%(load.f_shape,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5))
 
     return 0
 

### 2013-08-15 pyplots/time_map.py

@@ -9,7 +9,7 @@ import sys
 # WIP
 
 for protein in load.proteinList:
-    file = np.loadtxt("./data/shape-%s/time-map-%s-%s-%s-%s-%s-%s.dat"%(load.f_shape,protein,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5))
+    file = np.loadtxt("./data/shape-%s/time-map-%s-%s-%s-%s-%s-%s-%s.dat"%(load.f_shape,protein,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5))
     plt.figure()
     plt.pcolor(file)
     plt.xlim(0,file.shape[1])
@@ -18,4 +18,4 @@ for protein in load.proteinList:
     plt.ylabel("Y grid position")
     plt.title("Time averaged view of %s"%(protein))
     plt.colorbar()
-    plt.savefig("./data/shape-%s/plots/time-map-%s-%s-%s-%s-%s-%s.pdf"%(load.f_shape,protein,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5))
+    plt.savefig("./data/shape-%s/plots/time-map-%s-%s-%s-%s-%s-%s-%s.pdf"%(load.f_shape,protein,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5))

### 2013-08-15 batchloader.py
updated batch loader but it could use a rewrite

@@ -9,12 +9,8 @@ import time
 batch_randst_simulations = []
 i=1
 
-# batch_pill_simulations = [
-#     [10.00, 0.50], \
-#         [4.00, 0.50], \
-#         [4.00, 2.00], \
-#         [4.00, 3.00] ]
-
+batch_triangle_simulations = [
+    [1.00,4.00,4.00,4.00,15.00] ]
 batch_pill_simulations = [
     [4.00,3.75,0.00,0.00,15.00], \
     [4.00,3.50,0.00,0.00,15.00], \
@@ -32,6 +28,12 @@ if '-sim' in sys.argv:
     if 'p' in sys.argv:
         for job in batch_pill_simulations:
             processes.add(subprocess.Popen(['srun','./protein_microscopy','p','%.2f'%job[0],'%.2f'%job[1],'%.2f'%job[2],'%.2f'%job[3],'%.2f'%job[4],'-slice']))
+            if len(processes) >= max_processes:
+                os.wait()
+                processes.difference_update(p for p in processes if p.poll() is not None)
+    if 'triangle' in sys.argv:
+        for job in batch_triangle_simulations:
+            processes.add(subprocess.Popen(['srun','./protein_microscopy','triangle','%.2f'%job[0],'%.2f'%job[1],'%.2f'%job[2],'%.2f'%job[3],'%.2f'%job[4],'-slice']))
             if len(processes) >= max_processes:
                 os.wait()
                 processes.difference_update(p for p in processes if p.poll() is not None)

### 2013-08-15 protein_microscopy.cpp
Added volume printout

@@ -655,6 +655,8 @@ int main (int argc, char *argv[]) {
       total_cell_volume += dx*dx*dx;
     }
   }
+  printf("total_cell_volume = %g\n",total_cell_volume);
+  fprintf(out_file, "total_cell_volume = %g\n",total_cell_volume);
 
   //add cell params file
 

### 2013-08-15 batchloader.py
rewriting batch loader so figures are ready for the paper.

@@ -1,3 +1,4 @@
+#!/usr/bin/python
 from __future__ import division
 import numpy as np
 import sys
@@ -5,79 +6,15 @@ import os
 import subprocess
 import time
 
-#set up simulations to be run:
-batch_randst_simulations = []
-i=1
+#parses sys.argv for key=value arguments
+def parseKwargs(stringList):
+    stringDict = {}
+    for arg in stringList:
+        if "=" in arg:
+            (key,value) = arg.split("=")
+            stringDict[key]=value
+    return stringDict
 
-batch_triangle_simulations = [
-    [1.00,4.00,4.00,4.00,15.00] ]
-batch_pill_simulations = [
-    [4.00,3.75,0.00,0.00,15.00], \
-    [4.00,3.50,0.00,0.00,15.00], \
-    [4.00,3.00,0.00,0.00,15.00], \
-    [4.00,2.00,0.00,0.00,15.00], \
-    [4.00,0.50,0.00,0.00,15.00], \
-    [4.00,2.00,0.00,0.00,500.00], \
-    [4.00,0.50,0.00,0.00,500.00], \
-    ]
 
-#simulation subprocess management:
-if '-sim' in sys.argv:
-    processes = set()
-    max_processes = 100
-    if 'p' in sys.argv:
-        for job in batch_pill_simulations:
-            processes.add(subprocess.Popen(['srun','./protein_microscopy','p','%.2f'%job[0],'%.2f'%job[1],'%.2f'%job[2],'%.2f'%job[3],'%.2f'%job[4],'-slice']))
-            if len(processes) >= max_processes:
-                os.wait()
-                processes.difference_update(p for p in processes if p.poll() is not None)
-    if 'triangle' in sys.argv:
-        for job in batch_triangle_simulations:
-            processes.add(subprocess.Popen(['srun','./protein_microscopy','triangle','%.2f'%job[0],'%.2f'%job[1],'%.2f'%job[2],'%.2f'%job[3],'%.2f'%job[4],'-slice']))
-            if len(processes) >= max_processes:
-                os.wait()
-                processes.difference_update(p for p in processes if p.poll() is not None)
-    if 'randst' in sys.argv:
-        for job in batch_randst_simulations:
-            processes.add(subprocess.Popen(['./protein_microscopy','randst','%.2f'%job[0],'%.2f'%job[1],'%.2f'%job[2],'%.2f'%job[3],'%.2f'%job[4]]))
-            if len(processes) >= max_processes:
-                os.wait()
[…]

### 2013-08-15 paper/paper.tex
udpate
added paragraph to paper

@@
 \fixme{I need a lot of references here!!!  (And the writing is just terrible)}
-It is vital that the process of bacterial cell division result in a single
+%It is vital that the process of bacterial cell division result in a single
 nucleiod in each daughter cell.  The cell must avoid minicelling, or
@@
 the MinD and MinE concentrations inside the cell.
+
+Modelled cells have a total cell volume that is roughly equivelent to
+that observed experimentally by Kubitschek.\cite{kubitschek1990cell}
+He observes mean cell volumes of 0.69$\mu m^3$ and 0.58$\mu m^3$ in
+different strains and shows as well that newborn cells have roughly half
+the volume of those on the brink of cell division.  Because we are
+interested in the protein system during the cell division process, we
+use cells that have cell volumes of roughly 1 $\mu m^3$
 
@@
 \subsection{Pill Shape}
+
 %% \begin{figure}

### 2013-08-15 batchloader.py
sync

@@ -15,6 +15,4 @@ def parseKwargs(stringList):
             stringDict[key]=value
     return stringDict
 
-
-
-
+print "foo"

### 2013-08-19 protein_microscopy.cpp
modified size of randst 97 and randst 96

@@ -510,6 +510,17 @@ int main (int argc, char *argv[]) {
                       3.8,3,.4,4.2,3,.4,4.6,3,.4,5,3,.4,5.4,3,.4,3.4,2.4,.6};
   double guass96[] = {1.3,1.3,.7,2.1,2,.7,3,2,.7,3.9,2,.7,4.7,1.3,.7,4,2.1,.7,4,3,.7,4,3.9,.7,
                       4.7,4.7,.7,3.9,4,.7,3,4,.7,2.3,4,.7,1.3,4.7,.7,2.1,3.9,.7,3,3.9,.7,2.1,3.9,.7};
+  for (int i=0;i<100;i++){
+    printf("guass96[%d] = %g\n",i,guass96[i]);
+    guass96[i] = guass96[i]/1.4;
+    printf("guass96[%d] = %g\n",i,guass96[i]);
+  }
+  for (int i=0;i<100;i++){
+    printf("guass97[%d] = %g\n",i,guass97[i]);
+    guass97[i] = 1.3*guass97[i];
+    printf("guass97[%d] = %g\n",i,guass97[i]);
+  }
+ printf("Those are all the guassians!\n");
   if (rand_seed == 99){
     for (int i=0;i<3*5;i++){
       guass[i]=guass99[i];
@@ -750,27 +761,29 @@ int main (int argc, char *argv[]) {
   fclose(out);
   printf("\nMembrane file printed.\n");
 
-  char* outfilename_sections = new char[1024];
-  sprintf(outfilename_sections, "data/shape-%s/membrane_files/sections-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),A,B,C,D,density_factor);
-  FILE *outfile_sections = fopen((const char*)outfilename_sections,"w");
-  for (int j=0;j<Ny;j++){
-    for (int i=0;i<Nz;i++) {
-      if (triangle_section(j*dx,i*dx)=="Right"){
-        marker = 1;
+  if (mem_f_shape=="triangle") {
+    char* outfilename_sections = new char[1024];
+    sprintf(outfilename_sections, "data/shape-%s/membrane_files/sections-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),A,B,C,D,density_factor);
+    FILE *outfile_sections = fopen((const char*)outfilename_sections,"w");
[…]

### 2013-08-19 paper/paper.tex

--- 2013-07-29 paper/paper.tex
@@
 
+Kubitschek\cite{kubitschek1990cell} \cite{kubitschek1968linear} has
+shown in multiple experiments that at the time of cell division cells
+have a volume that is within a range of roughly $1\mu m^3$ to $2\mu
+m^3$.  We follow Huang's simulations\cite{huang2003dynamic} and
+Mannik's experiments \cite{mannik2012robustness} and model cells that
+are slightly larger than this range.
+
+We mean to study cells that are parrallel to those lodged into
+crevices by Mannik so our flattened (non-pill shaped) cells have a
+hieght of 0.25 \cite{mannick2012robustness} and appropriate
+dimensions otherwise to yield the desired volume range.
+
 Our simulation used the same diffusion constants and reaction rates as
 Huang et al, which are
-
 \begin{gather*} %format better
@@
 \end{gather*}
-
 To test our computational model, we implemented a pill shaped cell, and

### 2013-08-23 paper/paper.tex
paper builds correctly with figures

@@
 %% \end{figure}
+
+ \begin{figure}
+   \includegraphics[width=\columnwidth]{../data/shape-p/plots/debug-box-plot_D--p-150-60-0-0-1500}
+   \caption{Protein density fluctuation with time against the polar
+     wall in a 4$\mu m$ by 2$\mu m$ pill shaped cell.  The wall-bound
+     proteins are shown at a point that is on the wall and the
+     cytoplasm densities are shown at a point immediately adjecent.
+     This plot is normalized so that every protein density peaks at 1}
+   \label{frequency-plot-40-20-0-0-150}
+ \end{figure}
 

### 2013-08-23 protein_microscopy.cpp
forgot to push a couple files

@@ -497,7 +497,7 @@ int main (int argc, char *argv[]) {
   //fixed simulation parameters
   tot_time = 2500; //sec
   if (debug_flag==1) {
-    tot_time = 250;
+    tot_time = 11;
   }
   time_step = .1*dx*dx/difD;//sec
   iter = int(tot_time/time_step);

### 2013-08-24 protein_microscopy.cpp
does better in valgrind

@@ -30,6 +30,7 @@ char* hires_flag_str = new char[1024];
 char* slice_flag_str = new char[1024];
 char* debug_flag_str = new char[1024];
 
+
 double dx; //grid spacing
 double tot_time; //total simulation time
 double time_step; //simulation time step
@@ -410,6 +411,10 @@ int main (int argc, char *argv[]) {
   density_factor = atof(argv[6]);
   dx=.05;
 
+  memset(hires_flag_str,0,1024*sizeof(char));
+  memset(slice_flag_str,0,1024*sizeof(char));
+  memset(debug_flag_str,0,1024*sizeof(char));
+
   //flag checking
   for (int i=0; i<argc; i++) {
     if (strcmp(argv[i],"-area")==0) {
@@ -510,6 +515,7 @@ int main (int argc, char *argv[]) {
   char * out_file_name = new char[1024];
   sprintf(out_file_name,"data/shape-%s/out_files/%s-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.out",mem_f_shape.c_str(),mem_f_shape.c_str(),A,B,C,D,density_factor);
   FILE * out_file = fopen((const char *)out_file_name,"w");
+  delete[] out_file_name;
 
   //random stuff that needs to be contained
   fprintf(out_file,"Nx=%d\nNy=%d\nNz=%d\nX=%f\nY=%f\nZ=%f\n",Nx,Ny,Nz,(Nx*dx),(Ny*dx),(Nz*dx));
@@ -615,6 +621,22 @@ int main (int argc, char *argv[]) {
     proteinList[pNum]->maxval = new double[iter];
     proteinList[pNum]->ymax = new int[iter];
     proteinList[pNum]->zmax = new int[iter];
+
+    memset(proteinList[pNum]->sum,0,Ny*Nz*sizeof(double));
+    memset(proteinList[pNum]->name,0,1024*sizeof(char));
+
+    memset(proteinList[pNum]->numLeft,0,iter*sizeof(double));
+    memset(proteinList[pNum]->numMid,0,iter*sizeof(double));
+    memset(proteinList[pNum]->numRight,0,iter*sizeof(double));
+
+    memset(proteinList[pNum]->numRightUp,0,iter*sizeof(double));
+    memset(proteinList[pNum]->numRightDown,0,iter*sizeof(double));
+    memset(proteinList[pNum]->numLeftUp,0,iter*sizeof(double));
+    memset(proteinList[pNum]->numLeftDown,0,iter*sizeof(double));
+
[…]

### 2013-08-24 protein_microscopy.cpp
correct initialization

@@ -623,7 +623,7 @@ int main (int argc, char *argv[]) {
     proteinList[pNum]->zmax = new int[iter];
 
     memset(proteinList[pNum]->sum,0,Ny*Nz*sizeof(double));
-    memset(proteinList[pNum]->name,0,1024*sizeof(char));
+    memset(proteinList[pNum]->name,'\0',1024*sizeof(char));
 
     memset(proteinList[pNum]->numLeft,0,iter*sizeof(double));
     memset(proteinList[pNum]->numMid,0,iter*sizeof(double));

### 2013-08-24 protein_microscopy.cpp
commented memsets

@@ -604,6 +604,9 @@ int main (int argc, char *argv[]) {
 
   int print_denominator = 1000;
 
+  printf("Ny*Nz*sizeof(double) = %lu",Ny*Nz*sizeof(double));
+  printf("iter*sizeof(double) = %lu",iter*sizeof(double));
+
   //initialize things
   for (int pNum=0; pNum<numProteins; pNum++) {
     proteinList[pNum]->sum = new double[Ny*Nz];
@@ -622,21 +625,23 @@ int main (int argc, char *argv[]) {
     proteinList[pNum]->ymax = new int[iter];
     proteinList[pNum]->zmax = new int[iter];
 
-    memset(proteinList[pNum]->sum,0,Ny*Nz*sizeof(double));
-    memset(proteinList[pNum]->name,'\0',1024*sizeof(char));
+    // crashes rene's computer
+    // :(
+    // memset(proteinList[pNum]->sum,0,Ny*Nz*sizeof(double));
+    // memset(proteinList[pNum]->name,'\0',1024*sizeof(char));
 
-    memset(proteinList[pNum]->numLeft,0,iter*sizeof(double));
-    memset(proteinList[pNum]->numMid,0,iter*sizeof(double));
-    memset(proteinList[pNum]->numRight,0,iter*sizeof(double));
+    // memset(proteinList[pNum]->numLeft,0,iter*sizeof(double));
+    // memset(proteinList[pNum]->numMid,0,iter*sizeof(double));
+    // memset(proteinList[pNum]->numRight,0,iter*sizeof(double));
 
-    memset(proteinList[pNum]->numRightUp,0,iter*sizeof(double));
-    memset(proteinList[pNum]->numRightDown,0,iter*sizeof(double));
-    memset(proteinList[pNum]->numLeftUp,0,iter*sizeof(double));
-    memset(proteinList[pNum]->numLeftDown,0,iter*sizeof(double));
+    // memset(proteinList[pNum]->numRightUp,0,iter*sizeof(double));
+    // memset(proteinList[pNum]->numRightDown,0,iter*sizeof(double));
+    // memset(proteinList[pNum]->numLeftUp,0,iter*sizeof(double));
+    // memset(proteinList[pNum]->numLeftDown,0,iter*sizeof(double));
 
-    memset(proteinList[pNum]->maxval,0,iter*sizeof(double));
-    memset(proteinList[pNum]->ymax,0,iter*sizeof(int));
[…]

### 2013-08-27 protein_microscopy.cpp
changed length of iter and also fixed small bug in randst 96 sections

@@ -505,13 +505,12 @@ int main (int argc, char *argv[]) {
 
 
   //fixed simulation parameters
-  tot_time = 2500; //sec
+  tot_time = 2500/2; //sec
   if (debug_flag==1) {
     tot_time = 11;
   }
   time_step = .1*dx*dx/difD;//sec
-  iter = int(tot_time/time_step);
-  //iter = int(tot_time/time_step);
+  iter = int(tot_time/time_step)/4.2;//this will give us triangle data in about a day and randst in two days
   printout_iterations = int(5.0/time_step);
   printf("%d\n",printout_iterations);//approximately 5 seconds between each printout
   double dV = dx*dx*dx;
@@ -943,10 +942,10 @@ int main (int argc, char *argv[]) {
             if (b < vert_div && a < hor_div) {
               marker = 1;
             }
-            else if (b < vert_div && a > hor_div) {
+            else if (b < vert_div && a >= hor_div) {
               marker = 2;
             }
-            else if (b > vert_div && a < hor_div) {
+            else if (b >= vert_div && a < hor_div) {
               marker = 3;
             }
             else {
@@ -1044,10 +1043,10 @@ int main (int argc, char *argv[]) {
                   if (b < vert_div && a < hor_div) {
                     proteinList[pNum]->numLeftDown[i_dat] += accessGlobals[pNum][c*Ny*Nz+a*Nz+b]*dV;
                   }
-                  else if (b < vert_div_two && a > hor_div) {
+                  else if (b < vert_div_two && a >= hor_div) {
                     proteinList[pNum]->numLeftUp[i_dat] += accessGlobals[pNum][c*Ny*Nz+a*Nz+b]*dV;
                   }
-                  else if (b > vert_div_two && a < hor_div) {
+                  else if (b >= vert_div_two && a < hor_div) {
                     proteinList[pNum]->numRightDown[i_dat] += accessGlobals[pNum][c*Ny*Nz+a*Nz+b]*dV;
                   }
                   else {

### 2013-08-27 paper/paper.tex
minor changes to plotting legend, movie scale, and paper adding figures, have not added these figs to makefile yet

--- 2013-08-19 paper/paper.tex
@@
 %% \end{figure}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-400-50-0-0-1500}
+  \caption{Total protein fluctuation in the right, middle, and
+    left parts of a 4$\mu m$ by 1$\mu m$ pill shaped cell.  The
+    different forms of protein changes while the total number of
+    proteins remains constant.}
+  \label{total-oscillation-plot-40-05-0-0-150}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-200-50-0-0-1500}
+  \caption{Total protein fluctuation in the right, middle, and
+    left parts of a 2$\mu m$ by 1$\mu m$ pill shaped cell.}
+  \label{total-oscillation-plot-20-05-0-0-150}
+\end{figure}
+
+Make sure to talk about length of periods as well
+
+Figure \ref{total-oscillation-plot-40-05-0-0-150} shows results for a
+pill shaped cell of length $4\mu$ and radius $.5\mu$.  The plot shows
+both the transerence between different protein compounds and movement
+within the cell.  Starting at the beginning of a period, we can see
+that first there is a spike
 

### 2013-08-27 pyplots/density_movie.py

@@ -76,7 +76,7 @@ def contourplt(protein):
         page = protein.dataset[k]
         plt.clf()
         plt.axes().set_aspect('equal', 'datalim')
-        CS = plt.contourf(Z, Y, page, cmap=plt.cm.jet,origin='lower',levels=np.arange(minval,maxval+10,5))
+        CS = plt.contourf(Z, Y, page, cmap=plt.cm.jet,origin='lower',levels=np.arange(minval,maxval+10,1))
         cbar = plt.colorbar(CS)
         plt.clim(minval,maxval)
         plt.title(str(protein.protein)+" volume density at time: "+str(k*5)+" sec")

### 2013-08-27 paper/paper.tex
wrote some paper

--- 2013-08-19 paper/paper.tex
@@
 \fixme{I need a lot of references here!!!  (And the writing is just terrible)}
-%It is vital that the process of bacterial cell division result in a single
+It is vital that the process of bacterial cell division result in a single
 nucleiod in each daughter cell.  The cell must avoid minicelling, or
@@
 \section{Methods and Initial Conditions}
-The model for the behavior of the MinD and MinE proteins inside the cell
-implemented the same set of 5 reaction-diffusion equations described in the paper
-by Huang et al (equations 1, 2, 3, 4, and 5). A 3d grid was constructed in
-cartesian coordinates with a grid spacing of .05 $\mu$m. From there, we
-were able to define a cell shape on the grid, and solve the
-reaction-diffusion equations numerically to observe the time evolution of
-the MinD and MinE concentrations inside the cell.
+The model for the behavior of the MinD and MinE proteins inside the
+cell implements the same set of 5 reaction-diffusion equations studied in
+the work of Huang et al (equations 1, 2, 3, 4, and
+5)\cite{huang2003dynamic}. A 3d grid is constructed in cartesian
+coordinates with a grid spacing of .05 $\mu$m. We define our cell
+shapes and solve the reaction-diffusion equations numerically to
+observe the time evolution of the MinD and MinE concentrations inside
+the cell.
+
+We start our cells with the MinD and MinE concentrations that are
+reported as wild type concentrations by Huang et al . We as well use the same reaction
+diffusion constants and and reaction rates,
+\begin{gather*} %format better
+  \mathcal{D}_D = \mathcal{D}_{E}  = 2.5 \mu \textrm{m$^2$ / sec}, \\
+  \sigma_D^{\textrm{ADP $\rightarrow$ ATP}}  = 1/\textrm{sec},  \sigma_D = 0.025 \mu \textrm{m/sec}, \\
+  \sigma_{dD}  = 0.0015 \mu \textrm{m$^3$/sec}, \\
+  \sigma_{de}  = 0.7/\textrm{sec}, \sigma_E = 0.093 \mu \textrm{m$^3$/sec}.
+\end{gather*}
+
+We study cell shapes that are similar to those studied by Huang and
+also new, flattened pancake-like shapes, inspired by the experimental work of
+Mannik \cite{mannick2012robustness}.  Our pill shapes differ from
+Huangs in that they are cylinders with hemisphere endcaps instead of
+pure cylindridrical shapes.  Our cylinderidrical radius is $0.50\mu$
+and the lengths of our cells (measured between the tips of the
+endcaps) are $5\mu$, $4\mu$, $3\mu$, and $2.5\mu$.
+
+With our flattened cell shapes we mean to study cells that are
+parrallel to those lodged into crevices by Mannik so we give them
+height of $0.25\mu$ \cite{mannick2012robustness}.  Viewed from the top
+down the cells will have the shapes described below and viewed from
+the side they have at their edges a semicircular protrusion (one may
+imagine the edges of a pancake).
+
+Our first group of (three) flattened cell shapes are triangular.  One
+of them is equilateral, one has a 3-4-5 right angle shape, and the
+last is iscoscolese.
+
+Our second group of (four) flattened cells are our own creations,
+designed to investigate different patterns of protein oscillation
+behavoir.
+
+The cell shapes and the sections that we split them into in our data
+analysis are shown in Figure \fixme{We need a big figure with all of this!!}.
 
@@
 Mannik's experiments \cite{mannik2012robustness} and model cells that
-are slightly larger than this range.
+are slightly larger than this range.  Amoung our flattened cells the
+two dimensional length scales are tuned so that every total cell
+volume is very close to $3\mu^3$.  \fixme{should we just leave it to
+  the reader to figure out for themselves what our pill shape volumes
+  are?}
 
-We mean to study cells that are parrallel to those lodged into
-crevices by Mannik so our flattened (non-pill shaped) cells have a
-hieght of 0.25 \cite{mannick2012robustness} and appropriate
-dimensions otherwise to yield the desired volume range.
-
-Our simulation used the same diffusion constants and reaction rates as
-Huang et al, which are
-\begin{gather*} %format better
-  \mathcal{D}_D = \mathcal{D}_{E}  = 2.5 \mu \textrm{m$^2$ / sec}, \\
-  \sigma_D^{\textrm{ADP $\rightarrow$ ATP}}  = 1/\textrm{sec},  \sigma_D = 0.025 \mu \textrm{m/sec}, \\
-  \sigma_{dD}  = 0.0015 \mu \textrm{m$^3$/sec}, \\
-  \sigma_{de}  = 0.7/\textrm{sec}, \sigma_E = 0.093 \mu \textrm{m$^3$/sec}.
-\end{gather*}
-To test our computational model, we implemented a pill shaped cell, and
-tested using the same cell parameters as Huang et al, which were a radius
-of 0.5 $\mu$m in the middle and at the spherical endcaps, and two different
-cell lengths of 4 $\mu$m and 10 $\mu$m. We found the same type of
-oscillations as in their paper using these initial conditions, verifying
-that our model works as intended. Below are snapshots of MinD and MinE
-concentrations at 5 second timestamps in the 4 $\mu$m cell:
-\newline
-\newline
-[insert 5 second time stamps of 4 $\mu$m sim]
-\newline
-\newline
-We then began to define other, non-traditional cell shapes for the purpose of
-modeling squished and perturbed E. coli cells, which were created
-experimentally in Mannick et al. To achieve this, we went with a
-cartesian lattice rather than the cylindrical lattice used in Huang et
-al's simulations, as it allows for more flexibility in defining the
-cell shape. Some of the cell shape models included a flattened pill
-(stadium shape), an ellipsoid, a spherical cell, and various randomly
-generated smooth shapes, such as those in the figures below.
-\newline
-\newline
-[insert memf print of 2-3 cell shapes]
-\newline
-\newline
 To interpret the results, we generated several different plot views of
@@
 
-\fixme{Be more exact about what exactly Nd is versus nATP, in terms of
-  the unit and dimensions.  The plotting may need to be changed}
-Figure %%\ref{frequency-plot-40-20-0-0-150} shows the protein density
-fluctuations at a point in space adjecent to a polar wall.  At each
-collection of peaks the proteins reach their zenith in an order that
-agrees with the qualitative picture described by
-Huang\cite{huang2003dynamic}, except for nADP peak.  The peaks start
-with a maxima of ATP-MinD accumulating at the walls \fixme{Need a
-  better way to refer to compounds}. This peak is followed by a peak
-in Nde, or ATP-MinD-MinE, as the cell is converted on the wall from
-the former to the latter compound.  As this compound splits apart and
-leaves the wall we see a peak in nE, or MinE in the cytoplasm.  This
-is then followed by a broader peak in nATP, or the MinD-ATP compound,
-as minD-ADP is (changed but I forgot the name for it) into minD-ATP in
-the cytoplasm.  The minD-ATP naturally diffuses away from the pole,
-which is shown by the broad nature of this peak.  All of these peaks
-fit the qualitative picture except for the sharp MinD-ADP peak.  One
-could except that it is a sharp peak, meaning that the MinD-ADP proteins
-do not last in the cytoplasm for very long before they are converted
-(once again forgot the name) into MinD-ATP.  The location of the peak
-in the time dimension is troubling, however, since that we would
-expect it to occur just after the peak in Nde, since the wall-bound
-MinD-ATP-MinE proteins are the ones that split up and leave the wall,
-creating both the MinE and the MinD-ADP.  One would expect to see the
-minD-ADP peak to coincide in time with the minE peak, but it instead
-coincides with the wall-bound MinD-ATP-MinE peak. (Although you can
-maybe sort of convince yourself otherwiase, really looking at it).
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-400-50-0-0-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-200-50-0-0-1500}
+  \caption{Total protein fluctuation in the right, middle, and left
+    parts of a 5$\mu m$ by 1$\mu m$ pill shaped cell (above) and a
+    3$\mu m$ by 1$\mu m$ pill shaped cell (below).  The vertical axis shows
+    stacked the total number of proteins that are of four different
+    compound stages and in the right section of the cell (bottom four
+    colors), in the middle of the cell (middle four colors) and in the
+    left section of the cell (top four colors). The different forms of
+    protein changes while the total number of MinD protein in the cell
+    remains constant, shown by the fact that the very top line is
+    horizontal.}
+  \label{total-oscillation-plot}
+\end{figure}
 
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-p/plots/frequency_plot_all_middle-p-40-20-0-0-150.pdf}
-%%   \caption{A comparison of protein density fluctuation with time
-%%     against the polar wall and at a point in the center of the
-%%     z-length and adjacent to the wall, in the cytoplasm.  The cell is
-%%     pill shaped and has dimensions of 4$\mu m$ by 2$\mu m$.  }
-%%   \label{frequency-plot-40-20-0-0-150}
-%% \end{figure}
+Figure \ref{total-oscillation-plot} shows total protein
+results for pill shaped cell of length $5\mu$ and radius $.5\mu$.  The
+plot shows both the transerence between different stages of protein
+compound and movement within the cell.  Starting at the beginning of a
+period, we can see that first there is a spike on the left of MinD-ATP
+attached to the wall that is accompanied by a growing number of
+cytoplasmic MinD-ATP and MinD-ADP that are entering the left section,
+followed by a high peak in MinD-MinE-ATP.  This peak gives way through
+the middle to peaks on the right side of the cell, the first being a
+small bump in cytoplasmic MinD-ATP that dissapears into a much larger
+spike in wall attached MinD-ATP, which is followed by a peak in wall
+attached MinD-MinE-ATP.  The pattern during each period clearly shows
+the cycle of proteins rections, as well as the very regular nature of
+the pole to pole protein oscillations.
 
-The theory states that the aversion of the FtsZ polymer to the MinC
-protein is responsible for the FtsZ polymer setting up in the center
-of the cell as opposed to at the cellular poles.  The MinC protein in
-turn natrually associates with the minD protein that is modelled in
-Huang's differential equations.  \fixme{look this up and write this
-  again} The theory is dependent on there being a significant
-difference in protein density between the center and polar regions. It
-is worthwhile examining this difference in detail.  Figure
-%%\ref{frequency-plot-40-20-0-0-150} shows a comparison of density
-fluctuation over time at a point adjacent to the polar cell wall and
-at a point adjacent to the cell wall in the center region of the cell.
-The different proteins show different relationships between their
-maxima and minima.  The MinD-ADP show sharp spikes at the poles and
-much smaller oscillations at in the middle.  The values at the poles
-are always greater than those in the middle, and the polar peaks
-exhibit densities that are roughly 2.5 times greater than the maxima
-in the center (\fixme{this factor and the following factors will be put
-  into a table of comparisons for each protein and for the different
-  cell sizes}).  The MinD-ATP densities show a very different trend.
-For these it is the center density that is almost always greater than
-the polar density.  The difference in density at the pole versus the
-middle is a factor of roughly .85 (once again we'll do this more
-officially in a table).  The MinE is similar to the MinD-ADP
-comparison.  It shows a difference in maxima by a factor of roughly 2.
-The MinC protein is associated with the minD protein, so perhaps the
-most important camparison is between the nfl-MinD (MinD protein in all
-its forms) at the ends and in the center of the pill.  This shows
-sharp spikes at the pills and a maxima difference factor of roughly
-1.25. \fixme{I'd like to analyze further what this means for the FtZ
-  polymer.  Would a difference like this really have a big effect?
-  What sort of effect should it have, looking at experimental data?
-  One thing is that Mannik (is it Mannik?) genetically deletes the
-  MinC protein and they get 73 percent proper cell division.  It
-  really would be good to do a more extensive analysis here,
-  referencing what other papers say about this.}
-
-It would be good here to add the time map plots and discuss the idea
-about the proteins spending most of their time in the center of the
-cell.
-
-Figure \ref{frequency-plot-40-20-0-0-150} also shows that the middle
-density oscillates at a frequency that is twice that of the polar
-regions, which is to be expected considering the symmetry of the
-center compared to the that of the polar regions.  Also, the
-difference between density maxima and minima each oscillation is
-smaller for the middle points than for the polar points.  This is
-evident from simply watching the simulation movies - the fluctulations
-are more extreme in the polar regions.
-
-Add a table here that shows the period of oscillations versus the cell
-dimensions.  Do the mathematical solution of the differential
-equations for an infinite long cylinder with different widths to see
-how fast the mxima move and compare (Dr. Roundy says that making the
-radial speed infinite would help.
+\fixme{our 5 length cells are labeled as 4 cells in the file labels,
+  since 4 is the length of the cylinder. In the text I'll refer to the
+  5 length cells (file says 4) as 5 length cells.  What huang's paper
+  calls 4 length cells will be labeled by our files as 3 length cells,
+  but will be refered in our text as 4 length cells}.  We can see a
+clear difference in period between the $5\mu$, $4\mu$, and $2\mu$
+length cells.  The oscillation periods for our $4\mu$ show excellent
+agreement with the simulations of Huang et all
+\cite{huang2003dynamic}.  This is to be expected since we begin our
+simulations with their reported wild type concentrations of MinD and
+MinE proteins. The periods for the different pill lengths are shown in
+the table below.  We can see a direct correltation between size and
+period, as the proteins must diffuse further in a longer cell before
+they accumulate on the opposite wall.
+\newline
+\newline
+Period According to Pill Length
+\begin{tabular}{|r|c|c|c|l|}
+  \hline
+  Length($\mu$) & 2.50 & 3.00 & 4.00 & 5.00\\
+  \hline
+  Period(sec) & sim & 33 & 38 & 48 \\ \cline{2-2}
+  \hline
+\end{tabular}
 
@@
 \section{Pill Shape}
+\fixme{Be more exact about what exactly Nd is versus nATP, in terms of
+  the unit and dimensions.  The plotting may need to be changed}
+Figure %%\ref{frequency-plot-40-20-0-0-150} shows the protein density
+fluctuations at a point in space adjecent to a polar wall.  At each
+collection of peaks the proteins reach their zenith in an order that
+agrees with the qualitative picture described by
+Huang\cite{huang2003dynamic}, except for nADP peak.  The peaks start
+with a maxima of ATP-MinD accumulating at the walls \fixme{Need a
+  better way to refer to compounds}. This peak is followed by a peak
+in Nde, or ATP-MinD-MinE, as the cell is converted on the wall from
+the former to the latter compound.  As this compound splits apart and
+leaves the wall we see a peak in nE, or MinE in the cytoplasm.  This
+is then followed by a broader peak in nATP, or the MinD-ATP compound,
+as minD-ADP is (changed but I forgot the name for it) into minD-ATP in
+the cytoplasm.  The minD-ATP naturally diffuses away from the pole,
+which is shown by the broad nature of this peak.  All of these peaks
+fit the qualitative picture except for the sharp MinD-ADP peak.  One
+could except that it is a sharp peak, meaning that the MinD-ADP proteins
+do not last in the cytoplasm for very long before they are converted
+(once again forgot the name) into MinD-ATP.  The location of the peak
+in the time dimension is troubling, however, since that we would
+expect it to occur just after the peak in Nde, since the wall-bound
+MinD-ATP-MinE proteins are the ones that split up and leave the wall,
+creating both the MinE and the MinD-ADP.  One would expect to see the
+minD-ADP peak to coincide in time with the minE peak, but it instead
+coincides with the wall-bound MinD-ATP-MinE peak. (Although you can
+maybe sort of convince yourself otherwiase, really looking at it).
+
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-p/plots/frequency_plot_all_middle-p-40-20-0-0-150.pdf}
+%%   \caption{A comparison of protein density fluctuation with time
+%%     against the polar wall and at a point in the center of the
+%%     z-length and adjacent to the wall, in the cytoplasm.  The cell is
+%%     pill shaped and has dimensions of 4$\mu m$ by 2$\mu m$.  }
+%%   \label{frequency-plot-40-20-0-0-150}
+%% \end{figure}
+
+The theory states that the aversion of the FtsZ polymer to the MinC
+protein is responsible for the FtsZ polymer setting up in the center
+of the cell as opposed to at the cellular poles.  The MinC protein in
+turn natrually associates with the minD protein that is modelled in
+Huang's differential equations.  \fixme{look this up and write this
+  again} The theory is dependent on there being a significant
+difference in protein density between the center and polar regions. It
+is worthwhile examining this difference in detail.  Figure
+%%\ref{frequency-plot-40-20-0-0-150} shows a comparison of density
+fluctuation over time at a point adjacent to the polar cell wall and
+at a point adjacent to the cell wall in the center region of the cell.
+The different proteins show different relationships between their
+maxima and minima.  The MinD-ADP show sharp spikes at the poles and
+much smaller oscillations at in the middle.  The values at the poles
+are always greater than those in the middle, and the polar peaks
+exhibit densities that are roughly 2.5 times greater than the maxima
+in the center (\fixme{this factor and the following factors will be put
+  into a table of comparisons for each protein and for the different
+  cell sizes}).  The MinD-ATP densities show a very different trend.
+For these it is the center density that is almost always greater than
+the polar density.  The difference in density at the pole versus the
+middle is a factor of roughly .85 (once again we'll do this more
+officially in a table).  The MinE is similar to the MinD-ADP
+comparison.  It shows a difference in maxima by a factor of roughly 2.
+The MinC protein is associated with the minD protein, so perhaps the
+most important camparison is between the nfl-MinD (MinD protein in all
+its forms) at the ends and in the center of the pill.  This shows
+sharp spikes at the pills and a maxima difference factor of roughly
+1.25. \fixme{I'd like to analyze further what this means for the FtZ
+  polymer.  Would a difference like this really have a big effect?
+  What sort of effect should it have, looking at experimental data?
+  One thing is that Mannik (is it Mannik?) genetically deletes the
+  MinC protein and they get 73 percent proper cell division.  It
+  really would be good to do a more extensive analysis here,
+  referencing what other papers say about this.}
+
+It would be good here to add the time map plots and discuss the idea
+about the proteins spending most of their time in the center of the
+cell.
+
+Figure \ref{frequency-plot-40-20-0-0-150} also shows that the middle
+density oscillates at a frequency that is twice that of the polar
+regions, which is to be expected considering the symmetry of the
+center compared to the that of the polar regions.  Also, the
+difference between density maxima and minima each oscillation is
+smaller for the middle points than for the polar points.  This is
+evident from simply watching the simulation movies - the fluctulations
+are more extreme in the polar regions.
+
+Add a table here that shows the period of oscillations versus the cell
+dimensions.  Do the mathematical solution of the differential
+equations for an infinite long cylinder with different widths to see
+how fast the mxima move and compare (Dr. Roundy says that making the
+radial speed infinite would help.
+
 Pill Normal section -

### 2013-08-28 pyplots/box_plot.py
lengthened the amount of data that goes into the box plots -warning - this may screw up the pill plots.  you may need to plot one of those using this file from the commend line, with a significantly smaller window of time over which you plot Tested everything on crystal.

@@ -34,7 +34,6 @@ def returnData(boxName,proteinType):
     proteinsOverTime = proteinsOverTime[0].split('\t')
     proteinsOverTime = proteinsOverTime[2:-1]
     proteinsOverTime = [float(i) for i in proteinsOverTime]
-
     return proteinsOverTime
 
 #takes input format: ["proteinType1-boxNum1","proteinType1-boxnum2",proteinType2-boxnum1"...]. will return a list of lists
@@ -100,7 +99,7 @@ def main():
     timeAxis = range(len(plotCurveList_D[0]))
 
     #begin messy code (to deal with matplotlib) - don't judge me
-    (start, end) = (6*int(len(timeAxis)/10),7*int(len(timeAxis)/10))
+    (start, end) = (0*int(len(timeAxis)/10),10*int(len(timeAxis)/10))
 
     #get num on each plot
     for proteinType in proteinTypeList:

### 2013-08-28 paper/paper.tex

@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-400-50-0-0-1500}
+  %%\includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-400-50-0-0-1500}
   \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-200-50-0-0-1500}
@@
 
+\subsection{Triangular Shapes}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-400-400-400-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-500-500-300-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-360-480-600-1500}
+  \caption{Total protein fluctuation in the right, middle, and left
+    parts of a equilateral (top), iscoscolese (middle), and 3-4-5
+    (bottom) triangle.  The vertical axis shows stacked the total
+    number of proteins that are of four different compound stages and
+    in the different sections of the cell.}
+  \label{total-oscillation-triangle-plot}
+\end{figure}
+
+Figure \ref{total-oscillation-triangle-plot} shows the equivalent
+motion and transference between compound states for the triangular
+states as Figure \ref{total-oscillation-plot} does for the pill shaped
+cells.  The equilateral triangular shows that in all three sections
+there is a spike in wall attached MinD-ATP directly followed by a
+spike in wall attached MinD-MinE-ATP.  The pill had shown a similar
+pattern except that the mid section exhibited no such pronounced
+spike.  Interestingly, the right and mid sections show spikes at
+similar times when compared to the left section spikes, which seem to
+oscillate in a manner shifted pi off from the other two.  This
+behavoir shows itself in the animations, which show a relaxation into
+a stable oscillation from a maxima in one corner to a double maxima in
+the other two corners, and back again.  The left section heights are
+roughly twice that of the right section heights.  The simulations are
+started with higher concentrations of proteins in primarily the right
+section, with some overlap into the middle section, so that perhpas
+this oscillation pattern seems reasonable.  However, it's interesting
+to note that the oscillations, started with assymmetric density, do
+not naturally rotate around the corners of the triangle in a circular
+pattern.
+
+It seems as well that there is a desired oscillation maxima for the
+particular shape and size of the cell, as can be seen by the
+relaxation, over the first four periods, to a regular maximal height
+of the right and left sections' total protein at the height of each spike.
+
+\fixme{Note to make sure I'm interpreting the iscosolese triangle data
+  correctly: the triangle sides are 5,5,3, and the higher density
+  starts in the corner that is opposite the short side.  This corner
+  is covered by the right section.  I've verified this by looking at
+  the protein_microscopy and drawing a little picture, which is on my
+  desk...if you dare look for something on my desk!!!}  The iscosolese
+triangle starts its simulation with a higher concentration of protein
+in the section that is opposite the shorter side.  It quickly relaxes
+into a stable oscillation pattern.  This pattern shows that right
+corner section regularly has higher spikes in total protein than the
+other sections, and that its spikes appear one pi removed from the
+spikes for the other two sections.  This a similar behavoir to that
+which is seen in the equilateral triangle, differening in that it
+converges more quickly towards this behavoir and that it shows a
+greater exageration in the height of protein buildup in the right most
+section.
+
+\fixme{Note on interpretation of 3-4-5 triangle: the higher density
+  starts to the right of a vertical line that is parrallel to the
+  second longest side in the triangle (the longer of the two
+  non-hypotonuse sides).  This means the higher concentration covers
+  the right angle and also the smaller angle in the triangle} The
+3-4-5 triangle exhibits behavoir that I need more data to properly
+observe.  I does not converge as quickly as that for the iscosolese or
+equilateral triangles.
+
 \subsection{Randst shape}
+\fixme{Cheat sheet for the shapes, need to put these into a big figure
+  from the sections output: 96=star shape, 97=sideways sideways
+  flying saucer pancake, 98=manniks squished cell, 99=an A}
+
+\begin{figure}
+
+\end{figure}
 \subsubsection{Randst-96-Star}
+The animations seem to relax into a pattern in which the oscillations
+go from the smallest corner, out to the other three, and then back to
+the smallest corner.  \fixme{There isn't enough data to see properly
+  though, need to run for longer.}
+
 \subsubsection{Randst-97-}
-\subsubsection{Randst-98-Actually Random}
-\subsubsection{Randst-99}
+The sideways flying saucer pancake shape shows a truly interesting
+breakdown of an unstable equilibrium oscillation.  For the first
+number of oscillations the maxima trade off right to left, from a high
+peak in the leftward compartment to vertically opposed peaks in the
+poles of the long axis of the cell.  This is perhaps due to the fact
+that the starting density is highly concentrated to the right of a
+dividing line that runs parrallel to the right vertical side.  After a
+few oscillations the back and forth oscillations tip toward the
+vertical direction and the system loses its initial oscillation
+pattern.
+
+\subsubsection{Randst-98-C-Reminiscent of Mannik's cell}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-800-9800-1500}
+  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
+  \caption{Total protein fluctuation in the manniks squished cell
+    shape.  The vertical axis shows stacked the total number of
+    proteins that are of four different compound stages and in the
+    different sections of the cell.}
+  \label{total-oscillation-randst-98-plot}
+\end{figure}
+
+Our animations and total protein fluctuation plots (Figure
+\ref{total-oscillation-randst-98-plot} for our C shape (reminiscent of
+the flattened cell shown in Mannik's work) shows a very regular,
+stable, simple oscillation pattern.  There are two clear ends of this
+cell that oppose one another, and the protein maximum travels to one
+end, where it reaches a peak, then travels through the cell to the
+other end, reaching another peak, and then repeats the process.  In a
+way it is similar to the simple pill shapes, in that there are two
+clear endcaps and a middle section (that is in this case bends and
+curves).  The protein fluctuation plots show our familiar pattern of
+high spikes in wall attached MinD-ATP immediately followed by spikes
+in wall attached MinD-MinE-ATP, followed by a drop in both as the
+proteins move towards the other side.
+
+\subsubsection{Randst-99 our A shape}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
+  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
+  \caption{Total protein fluctuation in the A shaped shape.  The vertical axis shows stacked the total number
+    of proteins that are of four different compound stages and in the
+    different sections of the cell.}
+  \label{total-oscillation-randst-96-plot}
+\end{figure}
+Our animations for this plot show a very interesting pattern.  The
+maxima oscillates from the right corner to the top corner, then
+\emph{back to the right corner} then to the top corner again, then to
+the left corner, then back to the top, then to the left, then to the
+top again, then back to the right side.  It's fascinating that there
+must be two back and forth motions before proceeding to the other side
+\fixme{would this happen over and over or would there be a chaos,
+  breakdown sort of thing at some point.  Need longer sim}.  The total
+fluctuation plot shows this double maxima corner pattern, with two
+spikes on the right, then two spikes on the left, then two back on the
+right.
+
 \section{Interpretation of Data}

### 2013-08-30 protein_microscopy.cpp
fixing bug

@@ -1,0 +1,2019 @@
+#include <iostream>
+using namespace std;
+#include <stdio.h>
+#include <time.h>
+#include <math.h>
+#include <stdlib.h>
+#include <string.h>
+#include "protein.h"
+#include "MersenneTwister.h"
+#include <cassert>
+
+const double difD = 2.5; // (um)^2 s^- 1
+const double difE = 2.5; // (um)^2 s^-1
+const double rate_ADP_ATP = 1; // s^-1
+const double rate_D = .025; // um s^-1
+const double rate_dD = .0015; // (um)^3 s^-1
+const double rate_de = .7; // s^-1
+const double rate_E = .093; // (um)^3 s^-1
+
+const double nATP_starting_density = 1000.0/(M_PI*0.5*0.5); //proteins per micrometer^3 (values from paper)
+const double nE_starting_density = 350.0/(M_PI*0.5*0.5); // proteins per micrometer
+double density_factor;
+
+int area_rating_flag = 0;
+int slice_flag = 0;
+int dump_flag = 0;
+int debug_flag = 0;
+
+char* hires_flag_str = new char[1024];
+char* slice_flag_str = new char[1024];
+char* debug_flag_str = new char[1024];
+
+
+double dx; //grid spacing
+double tot_time; //total simulation time
+double time_step; //simulation time step
+int iter; //total # of iterations
+int printout_iterations; //iterations between file printout
+
+int box_divider_left;
+int box_divider_right;
+
+double x, y, z;
+int Nx, Ny, Nz; //number of gridpoints in each direction
+
+string mem_f_shape; //cell shape argument
+double A, B, C, D; //specific shape parameters, set by command line args
+
+//N denotes protein number, n denotes protein number density
+double *nATP; //min D bound to an ATP
+double *nADP; //min D bound to an ADP
+double *nE; //loose min E in cytoplasm
+double *ND; //min D bound to ATP on the wall
+double *NDE; //min D bound to ATP and min E on the wall
+double *f_mem;
+
+const int starting_num_guassians=20;
[…]

### 2013-08-30 paper/paper.tex
merge with Rene and also moved wall summing loop in protein_microscopy.cpp Tested everything on crystal.

@@
 
+With arrow plots - have noticed that the wall attached proteins seem
+to climb along the walls with little arrows, so the maxima crawl
+along, in a way.
+
 \begin{figure}
@@
 pattern.
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_ND-randst-25-800-600-9700-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_E_NDE-randst-25-800-600-9700-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-E_nE-randst-25-800-600-9700-1500}
+  \caption{Arrows that connect maxima that are global in space and
+    local in time. The arrow heads touch spatial, time maxima and are
+    adjecent to the tails of arrows that show the very next spatial,
+    time maxima. The proteins shown are wall attached MinD-ATP (top),
+    wall attached MinD-MinE-ATP (middle), and cytoplasmic MinE (bottom).}
+  \label{arrow-plot-randst-97-plot}
+\end{figure}
+
+Figure \ref{arrow-plot-randst-97-plot} shows three arrow plots for
+this shape of cell.  It's interesting that wall attached MinD never
+have global maxima in the middle flat region of the cell while both
+forms of MinE, the cytoplasmic MinE and the wall attached
+MinD-MinE-ATP, have a number of maxima in this region of the cell.  It
+seems that the MinE never stray far from the middle of the cell - they
+approach the ends and react with the other proteins, sticking for a
+while on the walls.  In order for a cytoplasmic MinE to reach the very
+end, it must pass a large amount of opportunity to react with MinD.
+\fixme{I stopped writing this reasoning because I'm not sure it's
+  valid.  Interesting thoug.  Look at this more.}
 
@@
 
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_ND-randst-25-600-800-9800-1500}
+  \caption{Arrows that connect maxima that are global in space and
+    local in time. The arrow heads touch spatial, time maxima and are
+    adjecent to the tails of arrows that show the very next spatial,
+    time maxima. The protein that is shown is wall attached MinD-ATP.}
+  \label{arrow-plot-randst-98-plot}
+\end{figure}
+
+The arrow plot shown here is typical of mannik's squished adnormal
+shape.  It shows the protein maxima moving through the cell from one
+end to the other end, and back again.
+
 \subsubsection{Randst-99 our A shape}
@@
 right.
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_nATP-randst-25-600-600-9900-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_nADP-randst-25-600-600-9900-1500}
+  \caption{Arrows that connect maxima that are global in space and
+    local in time. The arrow heads touch spatial, time maxima and are
+    adjecent to the tails of arrows that show the very next spatial,
+    time maxima. The proteins shown are cytopasmic MinD-ATP (above) and MinD-ADP (below).}
+  \label{arrow-plot-randst-99-plot}
+\end{figure}
+Figure \ref{arrow-plot-randst-99-plot} shows maxima that are global in
+space and local in time.  It is interesting that the MinD-ATP, the
+stage that immediately proceeds attachement to the wall, show maxima
+in one base corner of the A shape and then immediate maxima in the
+other base corner, skipping any maxima steps in the middle (the top of
+the A), while the MinD-ADP, the stage that has just left the wall,
+shows no such behavoir.  Every base corner maxima is followed by a top
+corner maxima, with very obvious symmetry.
 

### 2013-08-30 protein_microscopy.cpp

@@ -846,7 +846,26 @@ int main (int argc, char *argv[]) {
   fflush(out_file);
   printf("density set.\n");
 
+  double left_area_total = 0;
+  double middle_area_total = 0;
+  double right_area_total = 0;
+
   if (mem_f_shape=="p"){
+    for (int a=0;a<Ny; a++) {
+      for (int b=0; b<Nz; b++) {
+        for (int c=0; c<Nx; c++) {
+          if (b < box_divider_left) {
+            left_area_total += mem_A[c*Ny*Nz+a*Nz+b];
+          }
+          else if (b > box_divider_right) {
+            right_area_total += mem_A[c*Ny*Nz+a*Nz+b];
+          }
+          else {
+            middle_area_total += mem_A[c*Ny*Nz+a*Nz+b];
+          }
+        }
+      }
+    }
     char* outfilename_sections = new char[1024];
     sprintf(outfilename_sections, "data/shape-%s/membrane_files/%s%s%ssections-%s-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),
             debug_flag_str,hires_flag_str,slice_flag_str,mem_f_shape.c_str(),A,B,C,D,density_factor);
@@ -1420,24 +1439,7 @@ int main (int argc, char *argv[]) {
         char *avename = new char[1024];
         sprintf(avename,"%s",print_filename("ave_plot",""));
         FILE* ave_plot = fopen(avename,"w");
-        double left_area_total = 0;
-        double middle_area_total = 0;
-        double right_area_total = 0;
-        for (int a=0;a<Ny; a++) {
-          for (int b=0; b<Nz; b++) {
-            for (int c=0; c<Nx; c++) {
-              if (b < box_divider_left) {
-                left_area_total += mem_A[c*Ny*Nz+a*Nz+b];
-              }
-              else if (b > box_divider_right) {
-                right_area_total += mem_A[c*Ny*Nz+a*Nz+b];
-              }
-              else {
-                middle_area_total += mem_A[c*Ny*Nz+a*Nz+b];
-              }
-            }
-          }
-        }
+
         printf("left area = %g middle area = %g right area = %g\n",left_area_total,middle_area_total,right_area_total);
         fflush(stdout);
         if (mem_f_shape == "p"){

### 2013-08-30 protein_microscopy.cpp
membrane and section files now print in data/shape-*

@@ -785,7 +785,7 @@ int main (int argc, char *argv[]) {
   //begin membrane printing - need to change this to mem_f instead of 1's and 0's
   printf("HELLLLOOOOOOO %s\n",mem_f_shape.c_str());
   char* outfilename = new char[1024];
-  sprintf(outfilename,"data/shape-%s/membrane_files/%s%s%smembrane-%s-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),debug_flag_str,hires_flag_str,slice_flag_str,mem_f_shape.c_str(),A,B,C,D,density_factor);
+  sprintf(outfilename,"data/shape-%s/%s%s%smembrane-%s-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),debug_flag_str,hires_flag_str,slice_flag_str,mem_f_shape.c_str(),A,B,C,D,density_factor);
   FILE *out = fopen((const char *)outfilename,"w");
   if (out==0){
     printf ("couldn't print outfile\n");
@@ -813,7 +813,7 @@ int main (int argc, char *argv[]) {
 
   if (mem_f_shape=="triangle") {
     char* outfilename_sections = new char[1024];
-    sprintf(outfilename_sections, "data/shape-%s/membrane_files/%s%s%ssections-%s-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),
+    sprintf(outfilename_sections, "data/shape-%s/%s%s%ssections-%s-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),
             debug_flag_str,hires_flag_str,slice_flag_str,mem_f_shape.c_str(),A,B,C,D,density_factor);
     FILE *outfile_sections = fopen((const char*)outfilename_sections,"w");
     for (int j=0;j<Ny;j++){
@@ -848,7 +848,7 @@ int main (int argc, char *argv[]) {
 
   if (mem_f_shape=="p"){
     char* outfilename_sections = new char[1024];
-    sprintf(outfilename_sections, "data/shape-%s/membrane_files/%s%s%ssections-%s-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),
[…]

### 2013-08-31 pyplots/ave_plot.py
created ave_plot.py Tested everything on crystal.

@@ -5,7 +5,7 @@ matplotlib.use("Agg")
 import matplotlib.pyplot as plt
 import sys
 import pylab
-import file_loader_dump as load
+import file_loader as load
 
 ## WIP!!
 
@@ -26,41 +26,22 @@ import file_loader_dump as load
 def returnData(boxName,proteinType):
 
     #open the data file, grab the line with the correct protein type and box partition, load it as a [string] (so we can use list comprehensions)
-    with open("./data/shape-%s/box-plot--%s-%s-%s-%s-%s-%s.dat"%(load.f_shape,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5),"r") as boxData:
+    with open("./data/shape-%s/%s%s%sbox-plot--%s-%s-%s-%s-%s-%s.dat"%(load.f_shape,load.debug_str,load.hires_str,load.slice_str,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5),"r") as boxData:
         proteinsOverTime = [line for line in boxData if (proteinType in line) and (boxName in line)]
-
 
     #format the string so that it is a list of numbers (split on tab, pop off keywords and newlines, convert str -> float)
     proteinsOverTime = proteinsOverTime[0].split('\t')
     proteinsOverTime = proteinsOverTime[2:-1]
     proteinsOverTime = [float(i) for i in proteinsOverTime]
+    output = np.array(proteinsOverTime)
+    return (output)
 
-    return proteinsOverTime
-
-#takes input format: ["proteinType1-boxNum1","proteinType1-boxnum2",proteinType2-boxnum1"...]. will return a list of lists
-#in the stacking order specified by the input (first entry is at the bottom).
-def stackData(plotList):
-    #parse the input
-    tempList = []
-    for proteinData in plotList:
-        splitString = proteinData.split('-')
-        (protein, boxName) = (splitString[0], splitString[1])
-        tempList += [returnData(boxName,protein)]
-        print proteinData 
-
-    #"stack" the lists
-    stackedPlotList = [tempList[0]]
-    for i in range(1,len(tempList)):
-        stackedPlotList += [[j+k for (j,k) in zip(stackedPlotList[i-1],tempList[i])]]
-
-    return stackedPlotList
 
 def main():
 
[…]

### 2013-08-31 pyplots/ave_plot.py
added integral output ot ave plot, still need to make bar charts for these Tested everything on crystal.

@@ -62,8 +62,8 @@ def main():
     #prune duplicates
     proteinTypeList = list(set(proteinTypeList))
     boxList = list(set(boxList))
- 
-    #generate list of proteinType and box combinations to feed into returnData
+
+    #generate list of proteinType and box combinations to feed into ckData
     plotNameList_D = []
     plotNameList_E = []
     numProteinTypes_D = 0
@@ -75,45 +75,43 @@ def main():
             if "D_" in proteinType and "n" not in proteinType:
                 plotNameList_D += ["%s-%s"%(box,proteinType)]
                 numPlots_D += 1
-            if "E_" in proteinType and "n" not in proteinType:
-                plotNameList_E += ["%s-%s"%(box,proteinType)]
-                numPlots_E += 1
 
     for proteinType in proteinTypeList:
         if "D_" in proteinType and "n" not in proteinType:
             numProteinTypes_D += 1
-        if "E_" in proteinType and "n" not in proteinType:
-            numProteinTypes_E +=1
 
     plotCurveList_D = []
-    plotCurveList_E = []
     for proteinData in plotNameList_D:
         splitString = proteinData.split('-')
         (protein, boxName) = (splitString[0], splitString[1])
         plotCurveList_D += [returnData(boxName,protein)]
-    for proteinData in plotNameList_E:
-        splitString = proteinData.split('-')
-        (protein, boxName) = (splitString[0], splitString[1])
-        plotCurveList_E += [returnData(boxName,protein)]
 
     print len(plotCurveList_D[:][0])
-#pass plotNameList through stackData to generate the list of line data to be plotted
-    #plotCurveList_D = stackData(plotNameList_D)
-    #plotCurveList_E = stackData(plotNameList_E)
 
     #get a time axis for the plot from the length of one of the data sets we have
     timeAxis = range(len(plotCurveList_D[0]))
     #print len(plotCurveList_D[:,0])
 
     #begin messy code (to deal with matplotlib) - don't judge me
-    (start, end) = (int(5.2*int(len(timeAxis)/10)),int(6*int(len(timeAxis)/10)))
+    (start, end) = (int(5.3*int(len(timeAxis)/10)),int(5.7*int(len(timeAxis)/10)))
+
+
+    #integral of proteins over time
+    for i in range(numPlots_D):
+        integral = 0
[…]

### 2013-08-31 paper/paper.tex
added stuff to paper Tested everything on node23.

@@
 \end{tabular}
+\newline
+\newline
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-p/plots/ave-plot_D--p-400-50-0-0-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-p/plots/ave-plot_D--p-200-50-0-0-1500}
+  \caption{Average protein density per unit area of wall for the wall
+    attached stages of the protein cycle.  Shown in the right, middle,
+    and left parts of a 5$\mu m$ by 1$\mu m$ pill shaped cell (above)
+    and a 3$\mu m$ by 1$\mu m$ pill shaped cell (below).}
+  \label{ave-per-area-plot-pill}
+\end{figure}
+
+Figure \ref{ave-per-area-plot-pill} shows the ave protein per unit
+area that is wall attached in the middle, right, and left sections of
+the pill shaped cell.  This is an important test of the central idea
+behind the utility of the Min protein system.  The system is meant to
+place Min proteins on the walls in heavier concentrations in the caps
+of the cell and lower concentrations in the middle section, so that
+the FtZ polymer may build up along the center walls.  We can see from
+the plot of the 3$\mu m$ by 1$\mu m$ cell that the MinD proteins reach
+concentration peaks in the caps that are roughly three times higher
+(for the MinD-ATP proteins) and roughly 1.5 times higher (for the
+MinD-MinE-ATP) than peaks in the center.  Integrals of these plotted
+values show that the time averaged concentrations are likewise higher
+in the caps than in the center.  \fixme{am computing these integrals
+  now in ave_plot.py but need to print out into maybe a bar chart}
 
@@
 \subsubsection{Randst-96-Star}
-The animations seem to relax into a pattern in which the oscillations
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
+  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
+  \caption{Total protein fluctuation in the star cell shape.  The vertical axis shows stacked the total
+    number of proteins that are of four different compound stages and
+    in the different sections of the cell.}
+  \label{total-oscillation-randst-96-plot}
+\end{figure}
+
+We haven't simulated long enough yet, so no real pattern has shown
+itself.  There's certainly oscillations, and it's almost as if there's
+competing modes - top to bottom, left to right, corner to corner, etc.
+Interesting.
+
+\fixme{maybe?}The animations seem to relax into a pattern in which the oscillations
 go from the smallest corner, out to the other three, and then back to
-the smallest corner.  \fixme{There isn't enough data to see properly
+the smallest corner?  \fixme{There isn't enough data to see properly
   though, need to run for longer.}
@@
 \subsubsection{Randst-97-}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-600-9700-1500}
+  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
+  \caption{Total protein fluctuation in the sideways flying saucer
+    pancake cell shape.  The vertical axis shows stacked the total
+    number of proteins that are of four different compound stages and
+    in the different sections of the cell.}
+  \label{total-oscillation-randst-97-plot}
+\end{figure}
+
 The sideways flying saucer pancake shape shows a truly interesting
@@
 vertical direction and the system loses its initial oscillation
-pattern.
+pattern.  The total MinD animation shows that it falls quickly instead into a
+back and forth pattern between the two opposing endcaps, skipping
+right over the middle indentation.  The oscillation at this point is
+reminiscent of the pills shape oscillation, showing the robust nature
+of the back and forth pattern.
+
+Figure \ref{total-oscillation-randst-97-plot} shows between the top
+right and top left sections a pattern very close to the pattern seen
+in the pill shaped oscillations, with sharp spikes in wall attached
+MinD-ATP followed by lesser spikes in wall attached MinD-MinE-ATP,
+follwed by the other end showing a similar behavoir pi radius later.
+It is interesting to observe the middle section and the middle
+leftward indentation as well.  It can be seen that the MinD-ATP shows
+moderate spikes in between the spikes on the top and the bottom,
+showing that the proteins are traveling through this section, but
+interestingly the left middle indentation shows this spike
+consistently later than the right middle section. As the protein
+travels back and forth through the cell, there is a certain amount of
+lag in the middle indentation.  The system gets caught there for a
+little bit before moving on.
 
@@
   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_ND-randst-25-600-800-9800-1500}
-  \caption{Arrows that connect maxima that are global in space and
-    local in time. The arrow heads touch spatial, time maxima and are
-    adjecent to the tails of arrows that show the very next spatial,
-    time maxima. The protein that is shown is wall attached MinD-ATP.}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-D_ND-randst-25-600-800-9800-1500}
+  \caption{(above) Arrows that connect maxima that are global in space
+    and local in time. The arrow heads touch spatial, time maxima and
+    are adjecent to the tails of arrows that show the very next
+    spatial, time maxima. (below) An time averaged plot of the same
+    proteins in the same cells shape.  The protein that is shown is
+    wall attached MinD-ATP.}
   \label{arrow-plot-randst-98-plot}
@@
 shape.  It shows the protein maxima moving through the cell from one
-end to the other end, and back again.
+end to the other end, and back again.  The effect of this movement can
+be seen in the time averaged plot directly below the arrow plot.  The
+proteins spend a majority of time at the very ends of the cell.
 

### 2013-08-31 protein_microscopy.cpp
changed protein_microscopy so it prints out accurate membrane section files for p, changed so prints out these files for all shapes in membrane_files Tested everything on node23.

@@ -813,7 +813,7 @@ int main (int argc, char *argv[]) {
 
   if (mem_f_shape=="triangle") {
     char* outfilename_sections = new char[1024];
-    sprintf(outfilename_sections, "data/shape-%s/%s%s%ssections-%s-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),
+    sprintf(outfilename_sections, "data/shape-%s/membrane_files/%s%s%ssections-%s-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),
             debug_flag_str,hires_flag_str,slice_flag_str,mem_f_shape.c_str(),A,B,C,D,density_factor);
     FILE *outfile_sections = fopen((const char*)outfilename_sections,"w");
     for (int j=0;j<Ny;j++){
@@ -867,21 +867,22 @@ int main (int argc, char *argv[]) {
       }
     }
     char* outfilename_sections = new char[1024];
-    sprintf(outfilename_sections, "data/shape-%s/%s%s%ssections-%s-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),
+    sprintf(outfilename_sections, "data/shape-%s/membrane_files/%s%s%ssections-%s-%4.02f-%4.02f-%4.02f-%4.02f-%4.02f.dat",mem_f_shape.c_str(),
             debug_flag_str,hires_flag_str,slice_flag_str,mem_f_shape.c_str(),A,B,C,D,density_factor);
     FILE *outfile_sections = fopen((const char*)outfilename_sections,"w");
     for (int a=0; a<Ny; a++) {
       for (int b=0; b<Nz; b++) {
-        if (mem_f_shape == "p") {
-          if (b < box_divider_left) {
-            marker = 1;
-          }
-          if (b > box_divider_right) {
-            marker = 2;
-          }
-          if ((b <= box_divider_right) && (b >= box_divider_left)) {
-            marker = 3;
-          }
+        if (b < box_divider_left) {
+          marker = 1;
+        }
+        if (b > box_divider_right) {
+          marker = 2;
+        }
+        if ((b <= box_divider_right) && (b >= box_divider_left)) {
+          marker = 3;
+        }
+        if (inside(int(Nx/2),a,b)==false) {
+          marker = 0;
         }
[…]

### 2013-08-31 pyplots/box_plot.py
altered file loader and box plot so picks up extra 2 arguments from command line that give the start and finish of each plot. changed jobs to give an example of what I have in mind, although the make papers doesnt want to incorporate changes into paper Tested everything on node23.

@@ -58,7 +58,7 @@ def main():
 
     with open("./data/shape-%s/%s%s%sbox-plot--%s-%s-%s-%s-%s-%s.dat"%(load.f_shape,load.debug_str,load.hires_str,load.slice_str,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5),"r") as boxData:
         fileLines = boxData.readlines()
-
+    
     #get number of boxes and protein types. little hokey but it works. in boxData.readlines(), there is exactly one '\n' newline string
     #for each protein type block. therefor, the number of protein types is equal to the number of times "\n" appears by itself in the list.
     numProteinTypes = len([line for line in fileLines if line=="\n"])
@@ -100,7 +100,13 @@ def main():
     timeAxis = range(len(plotCurveList_D[0]))
 
     #begin messy code (to deal with matplotlib) - don't judge me
-    (start, end) = (0*int(len(timeAxis)/10),10*int(len(timeAxis)/10))
+
+    start_time_as_frac_of_ten = float(load.f_param6)
+    end_time_as_frac_of_ten = float(load.f_param7)
+    print load.f_shape
+    print start_time_as_frac_of_ten
+    print end_time_as_frac_of_ten
+    (start, end) = (int(start_time_as_frac_of_ten*len(timeAxis)/10),int(end_time_as_frac_of_ten*len(timeAxis)/10))
 
     #get num on each plot
     for proteinType in proteinTypeList:

### 2013-08-31 pyplots/file_loader.py

@@ -21,13 +21,23 @@ slice_str=""
 debug_str=""
 
 #change them to print the correct file names if arguments present
+expected_arg_number = 6
 if "-hires" in sys.argv:
     dx=.05
     hires_str="hires-"
+    expected_arg_number += 1
 if "-slice" in sys.argv:
     slice_str="slice-"
+    expected_arg_number += 1
 if "-debug" in sys.argv:
     debug_str="debug-"
+    expected_arg_number += 1
+if "-paper" in sys.argv:
+    expected_arg_number += 1
+
+#if len(sys.argv)>expected_arg_number:
+f_param6 = sys.argv[7]
+f_param7 = sys.argv[8]
 
 filename_tuple = (f_shape,hires_str,slice_str,f_shape,f_param1,f_param2,f_param3,f_param4,f_param5)
 

### 2013-09-01 pyplots/file_loader.py
altered file loader and box plot so picks up extra 2 arguments from command line that give the start and finish of each plot. changed jobs to give an example of what I have in mind, although the make papers doesnt want to incorporate changes into paper Tested everything on node23.

@@ -35,9 +35,9 @@ if "-debug" in sys.argv:
 if "-paper" in sys.argv:
     expected_arg_number += 1
 
-#if len(sys.argv)>expected_arg_number:
-f_param6 = sys.argv[7]
-f_param7 = sys.argv[8]
+if len(sys.argv)>expected_arg_number:
+    f_param6 = sys.argv[7]
+    f_param7 = sys.argv[8]
 
 filename_tuple = (f_shape,hires_str,slice_str,f_shape,f_param1,f_param2,f_param3,f_param4,f_param5)
 

### 2013-09-01 pyplots/file_loader.py
committing the latest thing Ive tried with this but still dont see why the make is not working Tested everything on node23.

@@ -21,23 +21,30 @@ slice_str=""
 debug_str=""
 
 #change them to print the correct file names if arguments present
-expected_arg_number = 6
 if "-hires" in sys.argv:
     dx=.05
     hires_str="hires-"
-    expected_arg_number += 1
 if "-slice" in sys.argv:
     slice_str="slice-"
-    expected_arg_number += 1
 if "-debug" in sys.argv:
     debug_str="debug-"
-    expected_arg_number += 1
-if "-paper" in sys.argv:
-    expected_arg_number += 1
+
+expected_arg_number = 7
+for arg in sys.argv:
+    if "-" in arg:
+        expected_arg_number+=1
+        print "hello"
+        print f_shape, f_param1, f_param2, f_param3, f_param4, f_param5, sys.argv[7], sys.argv[8]
+        print arg
+        print expected_arg_number
+
 
 if len(sys.argv)>expected_arg_number:
     f_param6 = sys.argv[7]
     f_param7 = sys.argv[8]
+    print f_param6
+    print f_param7
+    print "  "
 
 filename_tuple = (f_shape,hires_str,slice_str,f_shape,f_param1,f_param2,f_param3,f_param4,f_param5)
 

### 2013-09-01 paper/paper.tex
added writing to paper, although most of it is in note form, Im adding a lot of references Tested everything on crystal.

@@
 MinC, which naturally associates with MinD.
+
+A significant amount of work has been done in simulating and studying
+the dynamics of the Min protein system and cells. A number of
+different models have been simulated and studied.  They divide into
+two natural groups - stochastic (specific protein positions are
+tracked at all times) and deterministic (protein averages are used
+along with rate constants to simulate interaction). They also split up
+into other groups - cooperative attachement (MinD on the cytoplasm is
+attracted to other MinD on cytoplasm, shown by non-linear attachement
+on walls experimentally).  Huangs' 2003 and Meinhardt and De Boer 2001
+are of this type.  Huang's seuccessfully predicts that breakdown of
+striped oscillation pattern occurs when exchange of ATP for ADP bound
+to cytosolic MinD is not too fast.  There is as well aggregation
+current models, characterized by the proteins moving along the
+membranes in a way so that they're attracted to other proteins on the
+walls.  We are simulating Huang's model, so a further test of the
+robustness of the oscillations with wild type values, and as well
+compare against exprimental evidence given by mannik.  We use Huang's
+becuase of the success so far, and then also the other type
+(aggregation current models) depend on there being limited binding
+spots on the membrane for minD.  This author also states that the
+deterministic models have largely varified stochastic model
+results.\cite{kruse2007experimentalist}
+
+\cite{howard2005cellular}\cite{kruse2002dynamic}
+
+Huang has also made simulation studies of round cell shapes and shown
+that oscillations occur in these cell shapes, and that their behavior
+depends on the radius of the shape. They show that the Min proteins can
+select the long axis of the nearly round shapes based soley on the
+geometry of the cell.\cite{huang2004min} \fixme{definately want to get
+  this paper and read it}
+
+Previous experimental studies have shown that MinC, known to inhibit
+the FtZ polymer, exhibits an oscilatory, pole to pole behavoir in conjunction with
+MinD and MinE. \cite{hu1999topological}
+
+The function of the Min system might not be restricted to proper cell
+division.  There is evidence that it is instrumental in the
+dissasembly of the cytokinetic ring directly after cell division,
+insuring that cell division takes place only once per cell
+cycle. \cite{van2010mincdj}
+
+Other simulations have been shown to exhibit oscillations in the
+cylinder shaped cell.  While Huangs' 2003 study involves stages of
+protein compounds (attached proteins), the differential equations
+governing protein mobility in this study are designed with free
+unattached proteins who interact with eachother.  Huang does cite this
+paper so we can say that he followed and improved upon these
+simulations.\cite{meinhardt2001pattern}
+
+The MinE has been observed in the center of the cell and it's ability
+to counteract what's refered to as MinCD cell division inhibitor has
+been known.  It's been found that its not stationary but undergoes
+repetitive movement back and forth. \cite{fu2001mine}
+
+Previous studies have been made of the Min system's associtation with
+the cell membrane
+\cite{hsieh2010direct}\cite{mileykovskaya2003effects}. Previous
+studies have shown that phospho lipids on the cell wall attract
+MinD/MinE proteins and reduce ATPase activity.  It's further been
+shown that the proteins interact preferebly with anionic lipids that
+are localized at the poles of the cell.\cite{renner2012mind}
+
+Expreiemntal studies have been made of the process of septum formation
+in the middle of the pill shaped cell and its effect on MinD
+oscillations, leading to the conclusion that it is geometry of septum
+formation that allows for the creation of two MinD oscillation systems, one
+in each daughter cell. \cite{juarez2010changes}
 

### 2013-09-01 pyplots/box_plot.py

@@ -103,9 +103,9 @@ def main():
 
     start_time_as_frac_of_ten = float(load.f_param6)
     end_time_as_frac_of_ten = float(load.f_param7)
-    print load.f_shape
-    print start_time_as_frac_of_ten
-    print end_time_as_frac_of_ten
+    # print load.f_shape
+    # print start_time_as_frac_of_ten
+    # print end_time_as_frac_of_ten
     (start, end) = (int(start_time_as_frac_of_ten*len(timeAxis)/10),int(end_time_as_frac_of_ten*len(timeAxis)/10))
 
     #get num on each plot

### 2013-09-02 paper/paper.tex
put tabular in a table in paper.tex Tests skipped!

--- 2013-08-30 paper/paper.tex
@@
 they accumulate on the opposite wall.
-\newline
-\newline
-Period According to Pill Length
+
+\begin{table}
   \begin{tabular}{|r|c|c|c|l|}
@@
   \end{tabular}
+  \caption{Period According to Pill Length}
+\end{table}
 
@@
 
-With arrow plots - have noticed that the wall attached proteins seem
-to climb along the walls with little arrows, so the maxima crawl
-along, in a way.
-
 \begin{figure}
@@
 pattern.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_ND-randst-25-800-600-9700-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_E_NDE-randst-25-800-600-9700-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-E_nE-randst-25-800-600-9700-1500}
-  \caption{Arrows that connect maxima that are global in space and
-    local in time. The arrow heads touch spatial, time maxima and are
-    adjecent to the tails of arrows that show the very next spatial,
-    time maxima. The proteins shown are wall attached MinD-ATP (top),
-    wall attached MinD-MinE-ATP (middle), and cytoplasmic MinE (bottom).}
-  \label{arrow-plot-randst-97-plot}
-\end{figure}
-
-Figure \ref{arrow-plot-randst-97-plot} shows three arrow plots for
-this shape of cell.  It's interesting that wall attached MinD never
-have global maxima in the middle flat region of the cell while both
-forms of MinE, the cytoplasmic MinE and the wall attached
-MinD-MinE-ATP, have a number of maxima in this region of the cell.  It
-seems that the MinE never stray far from the middle of the cell - they
-approach the ends and react with the other proteins, sticking for a
-while on the walls.  In order for a cytoplasmic MinE to reach the very
-end, it must pass a large amount of opportunity to react with MinD.
-\fixme{I stopped writing this reasoning because I'm not sure it's
-  valid.  Interesting thoug.  Look at this more.}
 
@@
 
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_ND-randst-25-600-800-9800-1500}
-  \caption{Arrows that connect maxima that are global in space and
-    local in time. The arrow heads touch spatial, time maxima and are
-    adjecent to the tails of arrows that show the very next spatial,
-    time maxima. The protein that is shown is wall attached MinD-ATP.}
-  \label{arrow-plot-randst-98-plot}
-\end{figure}
-
-The arrow plot shown here is typical of mannik's squished adnormal
-shape.  It shows the protein maxima moving through the cell from one
-end to the other end, and back again.
-
 \subsubsection{Randst-99 our A shape}
@@
 right.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_nATP-randst-25-600-600-9900-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_nADP-randst-25-600-600-9900-1500}
-  \caption{Arrows that connect maxima that are global in space and
-    local in time. The arrow heads touch spatial, time maxima and are
-    adjecent to the tails of arrows that show the very next spatial,
-    time maxima. The proteins shown are cytopasmic MinD-ATP (above) and MinD-ADP (below).}
-  \label{arrow-plot-randst-99-plot}
-\end{figure}
-Figure \ref{arrow-plot-randst-99-plot} shows maxima that are global in
-space and local in time.  It is interesting that the MinD-ATP, the
-stage that immediately proceeds attachement to the wall, show maxima
-in one base corner of the A shape and then immediate maxima in the
-other base corner, skipping any maxima steps in the middle (the top of
-the A), while the MinD-ADP, the stage that has just left the wall,
-shows no such behavoir.  Every base corner maxima is followed by a top
-corner maxima, with very obvious symmetry.
 

### 2013-09-03 paper/paper.tex
Worked on Introduction and added a lot of references to paper Tested everything on node26.

--- 2013-09-01 paper/paper.tex
@@
 \section{Introduction}
-\fixme{I need a lot of references here!!!  (And the writing is just terrible)}
-It is vital that the process of bacterial cell division result in a single
-nucleiod in each daughter cell.  The cell must avoid minicelling, or
-splitting into daughter cells with lopsided volumes.  One of the mechanisms
-the cell employs in order to avoid this is to allow a long FtsZ polymer
-chain to develop on the cell wall in the center of the cell.  This chain
-acts as a guide for the cell splitting process.  Huang et all have shown in
-simulation that a system of Min protein interaction within the cell will
-lead to a natural oscillation of the MinC protein, which exhibits an
-aversion to the FtsZ polymer, from one cell end to the other that will
-leave the center free of any build up of MinC.  This will allow for the
-PtsZ chain to develop in the center and not at the ends, where the two
-nucleiods are housed.  The interaction takes place between MinE,MinD, and
-MinC, which naturally associates with MinD.
+It is vital that during the process of bacterial cell division a
+cell avoid minicelling, or splitting into daughter cells with lopsided
+volumes.  During this process a long FtsZ polymer chain develops on
+the cell wall in the center region of the cell which acts as a guide
+for the division. Previous experimental studies have shown
+that the MinC protein, known to inhibit the FtZ polymer, exhibits a
+pole to pole oscillatory behavoir in conjunction with the MinD and
+MinE proteins, while the oscillating MinE tends to be more localized
+in the center of the cell \cite{hu1999topological} \cite{fu2001mine}
+The MinC protein will then have a higher time averaged
+concentration in the cell poles as opposed to the center region of the
+cell, prohibiting the FtZ from building in the wrong region.
 
-A significant amount of work has been done in simulating and studying
-the dynamics of the Min protein system and cells. A number of
-different models have been simulated and studied.  They divide into
-two natural groups - stochastic (specific protein positions are
-tracked at all times) and deterministic (protein averages are used
-along with rate constants to simulate interaction). They also split up
-into other groups - cooperative attachement (MinD on the cytoplasm is
-attracted to other MinD on cytoplasm, shown by non-linear attachement
-on walls experimentally).  Huangs' 2003 and Meinhardt and De Boer 2001
-are of this type.  Huang's seuccessfully predicts that breakdown of
-striped oscillation pattern occurs when exchange of ATP for ADP bound
-to cytosolic MinD is not too fast.  There is as well aggregation
-current models, characterized by the proteins moving along the
-membranes in a way so that they're attracted to other proteins on the
-walls.  We are simulating Huang's model, so a further test of the
-robustness of the oscillations with wild type values, and as well
-compare against exprimental evidence given by mannik.  We use Huang's
-becuase of the success so far, and then also the other type
-(aggregation current models) depend on there being limited binding
-spots on the membrane for minD.  This author also states that the
-deterministic models have largely varified stochastic model
-results.\cite{kruse2007experimentalist}
-
-\cite{howard2005cellular}\cite{kruse2002dynamic}
-
-Huang has also made simulation studies of round cell shapes and shown
-that oscillations occur in these cell shapes, and that their behavior
-depends on the radius of the shape. They show that the Min proteins can
-select the long axis of the nearly round shapes based soley on the
-geometry of the cell.\cite{huang2004min} \fixme{definately want to get
-  this paper and read it}
-
-Previous experimental studies have shown that MinC, known to inhibit
-the FtZ polymer, exhibits an oscilatory, pole to pole behavoir in conjunction with
-MinD and MinE. \cite{hu1999topological}
-
-The function of the Min system might not be restricted to proper cell
-division.  There is evidence that it is instrumental in the
-dissasembly of the cytokinetic ring directly after cell division,
-insuring that cell division takes place only once per cell
-cycle. \cite{van2010mincdj}
-
-Other simulations have been shown to exhibit oscillations in the
-cylinder shaped cell.  While Huangs' 2003 study involves stages of
-protein compounds (attached proteins), the differential equations
-governing protein mobility in this study are designed with free
-unattached proteins who interact with eachother.  Huang does cite this
-paper so we can say that he followed and improved upon these
-simulations.\cite{meinhardt2001pattern}
-
-The MinE has been observed in the center of the cell and it's ability
-to counteract what's refered to as MinCD cell division inhibitor has
-been known.  It's been found that its not stationary but undergoes
-repetitive movement back and forth. \cite{fu2001mine}
+A significant amount of work has been done to develop protein reaction
+and diffusion models that exhibit accurate macroscopic dynamics of the
+MinD protein system. Early models involved free proteins that affect
+eachothers' rates of diffusion and membrane attachement but do not
+combine into compound states\cite{meinhardt2001pattern} .  In 2003
+Huang \cite{huang2003dynamic} improved upon this work with a simple
+model based on MinD-MinE combination, ATPase hydrolysis, and MinD
+membrane attechent that when simulated exhibits accurate MinD
+oscillations in cylindrical cells\cite{huang2003dynamic}. In this
+model cytoplasmic MinD is more likely to attach to the membrane when
+MinD is already clustered there (following observed non-linear
+attachement of minD on the cell membrane), and is stationary once
+attached.  A number of studies have used an approach similar in that
+they do not rely on the ability of MinD to move along the walls and
+cluster ~\cite{kruse2007experimentalist} \cite{meinhardt2001pattern}
+\cite{drew2005polymerization} \cite{fange2006noise}, while studies
+have been made as well of models which rely on MinD mobility and
+attraction on the cell
+membrane\cite{kruse2002dynamic}\cite{howard2005cellular}.  Variations
+of the Huang 2003 model that attempt to stochasticly account for
+variations of molecular interaction confirm the major results obtained
+by Huang's model and more successfully predict experimentally observed
+oscillations in round cell phenotypes.\cite{drew2005polymerization}
+\cite{fange2006noise} \cite{huang2004min} Biochemical models of
+broader scope have also been used to study the MinD system and show
+consistent results.\cite{arjunan2010new}
 
@@
 the cell membrane
-\cite{hsieh2010direct}\cite{mileykovskaya2003effects}. Previous
-studies have shown that phospho lipids on the cell wall attract
-MinD/MinE proteins and reduce ATPase activity.  It's further been
-shown that the proteins interact preferebly with anionic lipids that
-are localized at the poles of the cell.\cite{renner2012mind}
+\cite{hsieh2010direct}\cite{mileykovskaya2003effects}.  Studies have
+shown as well that MinD binds preferentially to regions enriched with
+cadiolipin, an anionic phospholipid that collects on regions of high
+negative curvature. This mechanism has been incorporated into other
+models.\cite{drew2005polymerization}
+\cite{cytrynbaum2007multistranded} \cite{renner2012mind}
+\cite{renner2012mind} However, this mechanism of combined clustering,
+phospholipids and MinD has not been observed in real
+cells. \cite{halatek2012highly}
 
-Expreiemntal studies have been made of the process of septum formation
-in the middle of the pill shaped cell and its effect on MinD
-oscillations, leading to the conclusion that it is geometry of septum
-formation that allows for the creation of two MinD oscillation systems, one
-in each daughter cell. \cite{juarez2010changes}
-
-Mannik et all have shown that the formation of irregular cell shapes
-adversly effects the Min system's ability to maintain their regular
-oscillatory behavior (cramming into spaces).
+It is vital for the mechanism by which the cell accurately divides to
+be robust and indeed it has been shown to
+be\cite{touhami2006temperature}.  Studies have shown that the
+oscillations can effectively find poles in abberent cell
+shapes\cite{varma2008min}\cite{juarez2010changes}.  However, Mannik et
+al. have shown that there are limits to this robustness. Forcing cells
+into flattened, irregular cell shapes adversly effects the Min
+system's ability to maintain their regular oscillatory
+behavior\cite{mannik2012robustness}\cite{mannik2009bacterial}.  We
+follow the experimental work of Mannik et and use Huang's mean field
+differential equation reaction model to explore the model's ability to
+find regular oscillatory behavoir in a series of abberent shapes.
 
@@
 \fixme{I need a lot of references here!!!}
+ need a lot of references here!!!  (And the writing is just
+terrible) It is vital that during the process of bacterial cell
+division that the cell avoid minicelling, or splitting into daughter
+cells with lopsided volumes.  During this process a long FtsZ polymer
+chain develops on the cell wall in the center region of the cell
+acting as a guide for the cell splitting process.  in simulation that a system of Min protein interaction within
+the cell will lead to a natural oscillation of the MinC protein, which
+exhibits an aversion to the FtsZ polymer, from one cell end to the
+other that will leave the center free of any build up of MinC.  This
+will allow for the PtsZ chain to develop in the center and not at the
+ends, where the two nucleiods are housed.  The interaction takes place
+between MinE,MinD, and MinC, which naturally associates with MinD.
+
+A significant amount of work has been done in simulating and studying
+the dynamics of the Min protein system and cells. A number of
+different models have been simulated and studied.  They divide into
+two natural groups - stochastic (specific protein positions are
+tracked at all times) and deterministic (protein averages are used
+along with rate constants to simulate interaction). They also split up
+into other groups - cooperative attachement (MinD on the cytoplasm is
+attracted to other MinD on cytoplasm, shown by non-linear attachement
+on walls experimentally).  Huangs' 2003 and Meinhardt and De Boer 2001
+are of this type.  Huang's seuccessfully predicts that breakdown of
+striped oscillation pattern occurs when exchange of ATP for ADP bound
+to cytosolic MinD is not too fast.  There is as well aggregation
+current models, characterized by the proteins moving along the
+membranes in a way so that they're attracted to other proteins on the
+walls.  We are simulating Huang's model, so a further test of the
+robustness of the oscillations with wild type values, and as well
+compare against exprimental evidence given by mannik.  We use Huang's
+becuase of the success so far, and then also the other type
+(aggregation current models) depend on there being limited binding
+spots on the membrane for minD.  This author also states that the
+deterministic models have largely varified stochastic model
+results.\cite{kruse2007experimentalist}
+
+It has also been observed that the spatial characteristics of
+oscillation is not effected by broad ranges of tempurature changes
+(although the frequency does vary) allowing for very robust cell
+division that is not dettered by environmental tempurature
+fluctuations. \cite{touhami2006temperature}
+
+We wish to subject Huang's seminal model to more harsh geometrical
+tests of robustness and compare results to the new experimental
+results of Mannik.\cite{mannik2012robustness}
+
+Models also introduce the affect of cardiolipin, an anionic
+phospholipid that collects on regions of high negative curvature (the
+membrane of the cell poles) and attracs MinD, since it had been
+observed that minD binds preferetntially in regions enriched with
+these phospholipids \cite{drew2005polymerization}\cite{cytrynbaum2007multistranded}. However, this
+mechanism of combined clustering, phospholipids and MinD has not been
+observed in real cells.  \cite{halatek2012highly}
+
+A mathematical model that describes the building of the FtZ polymer
+along the midsection cell membrane.  Solved numerically using a finite
+volume method. \cite{zhang2013mathematical}
+
+Variations of the Huang 2003 model that attempt to more accurately
+account for the details of molecular interaction, focusing on the
+mechanism of MinD binding to other MinD on the cell membrane.  These
+models confirm the major results obtained by Huang's model, while
+showing some interesting additional features.
+.\cite{drew2005polymerization}\cite{fange2006noise}\fixme{this last
+  reference sounds like maybe the stochastic changes they made to the
+  model cause the simulations to be more accurate in certain, odd
+  cases.  Should we have used this model?}
+
+More general biochemical models have also been used to study the MinD
+system and show consistent results.\cite{arjunan2010new}
+
+Stochastic models that area based on Huangs mean-field model but take
+chemical fluctuations into account in a discrete fashion show the same
+results as Huang's simulations in ordinary cell shapes, and better
+predict experimentally observed oscillations in round cell
+shapes.\cite{fange2006noise}
+
+Purely theoretical models have been constructed that rely on min
+protein's mobility on the membranes and tendency to cluster
+together.\cite{kruse2002dynamic}\cite{howard2005cellular} \fixme{read
+  and write about these}
+
+Huang has also made simulation studies of round cell shapes and shown
+that oscillations occur in these cell shapes, and that their behavior
+depends on the radius of the shape. They show that the Min proteins can
+select the long axis of the nearly round shapes based soley on the
+geometry of the cell.\cite{huang2004min} \fixme{definately want to get
+  this paper and read it}
+
+Previous experimental studies have shown that MinC, known to inhibit
+the FtZ polymer, exhibits an oscilatory, pole to pole behavoir in conjunction with
+MinD and MinE. \cite{hu1999topological}
+
+The function of the Min system might not be restricted to proper cell
+division.  There is evidence that it is instrumental in the
+dissasembly of the cytokinetic ring directly after cell division,
+insuring that cell division takes place only once per cell
+cycle. \cite{van2010mincdj}
+
+Other simulations have been shown to exhibit oscillations in the
+cylinder shaped cell.  While Huangs' 2003 study involves stages of
+protein compounds (attached proteins), the differential equations
+governing protein mobility in this study are designed with free
+unattached proteins who interact with eachother.  Huang does cite this
+paper so we can say that he followed and improved upon these
+simulations.\cite{meinhardt2001pattern}
+
+The MinE has been observed in the center of the cell and it's ability
+to counteract what's refered to as MinCD cell division inhibitor has
+been known.  It's been found that its not stationary but undergoes
+repetitive movement back and forth. \cite{fu2001mine}
+
+Previous studies have been made of the Min system's associtation with
+the cell membrane
+\cite{hsieh2010direct}\cite{mileykovskaya2003effects}. Previous
+studies have shown that phospho lipids on the cell wall attract
+MinD/MinE proteins and reduce ATPase activity.  It's further been
+shown that the proteins interact preferebly with anionic lipids that
+are localized at the poles of the cell.\cite{renner2012mind}
+
+Expreiemntal studies have been made of the process of septum formation
+in the middle of the pill shaped cell and its effect on MinD
+oscillations, leading to the conclusion that it is geometry of septum
+formation that allows for the creation of two MinD oscillation systems, one
+in each daughter cell. \cite{juarez2010changes}
+
 It is vital that the process of bacterial cell division result in a single

### 2013-09-03 protein_microscopy.cpp
markers change

@@ -873,13 +873,13 @@ int main (int argc, char *argv[]) {
     for (int a=0; a<Ny; a++) {
       for (int b=0; b<Nz; b++) {
         if (b < box_divider_left) {
-          marker = 1;
+          marker = 3;
         }
         if (b > box_divider_right) {
-          marker = 2;
+          marker = 1;
         }
         if ((b <= box_divider_right) && (b >= box_divider_left)) {
-          marker = 3;
+          marker = 2;
         }
         if (inside(int(Nx/2),a,b)==false) {
           marker = 0;
@@ -937,41 +937,41 @@ int main (int argc, char *argv[]) {
       for (int b=0; b<Nz; b++) {
         if (rand_seed == 99 || rand_seed == 98) {
             if (b < vert_div) {
-              marker = 1;
+              marker = 3;
             }
             else if (b > vert_div_two) {
-              marker = 2;
+              marker = 1;
             }
             else {
-              marker = 3;
+              marker = 2;
             }
           }
           if (rand_seed == 97) {
             if (b < vert_div) {
-              marker = 1;
+              marker = 4;
             }
             else if (a > hor_div_two) {
-              marker = 2;
+              marker = 1;
             }
             else if (a < hor_div) {
               marker = 3;
             }
             else {
-              marker = 4;
+              marker = 2;
             }
           }
           if (rand_seed == 96) {
             if (b < vert_div && a < hor_div) {
-              marker = 1;
-            }
-            else if (b < vert_div && a >= hor_div) {
-              marker = 2;
-            }
-            else if (b >= vert_div && a < hor_div) {
               marker = 3;
             }
-            else {
+            else if (b < vert_div && a >= hor_div) {
               marker = 4;
+            }
+            else if (b >= vert_div && a < hor_div) {
+              marker = 1;
+            }
+            else {
+              marker = 2;
             }
           }
           if (inside(int(Nx/2),a,b)==false) {

### 2013-09-03 protein_microscopy.cpp
changed marker output in cpp and added section files Tested everything on node26.

@@ -46,7 +46,7 @@ int Nx, Ny, Nz; //number of gridpoints in each direction
 string mem_f_shape; //cell shape argument
 double A, B, C, D; //specific shape parameters, set by command line args
 
-//N denotes protein number, n denotes protein number density
+//N denotes protein number, n denotes protein number density 
 double *nATP; //min D bound to an ATP
 double *nADP; //min D bound to an ADP
 double *nE; //loose min E in cytoplasm

### 2013-09-03 pyplots/box_plot.py
add some sections plots to boxplots Tested everything on bingley.

@@ -121,7 +121,38 @@ def main():
     alphaScale_E = [n/numProteinTypes for n in range(1,numProteinTypes_E+1)]
 
     #generate the plot
-    plt.figure()
+    f, (bax,sectionax) = plt.subplots(1, 2)
+
+    # first plot the section data...
+    sectiondata = np.loadtxt("data/shape-%s/membrane_files/%s%s%ssections-%s-%s-%s-%s-%s-%s.dat"
+                             % (load.f_shape,load.debug_str,load.hires_str,load.slice_str,load.f_shape,
+                                load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5))
+    def plot_sections(sectionax, sectiondata):
+        dx = 0.1 # FIXME
+        x = np.arange(sectiondata.shape[1]*1.0)*dx
+        y = np.arange(sectiondata.shape[0]*1.0)*dx
+        X,Y = np.meshgrid(x,y)
+        xmax = X[sectiondata>0].max()
+        xmin = X[sectiondata>0].min()
+        ymax = Y[sectiondata>0].max()
+        ymin = Y[sectiondata>0].min()
+        levels = [0.5, 1.5, 2.5, 3.5, 4.5]
+        mycolors = ["w","g","r","c","m","y"]
+        for i in xrange(min(4, len(boxList))):
+            if boxList[i] == 'Right':
+                mycolors[1] = colorScale[i]
+            if boxList[i] == 'Mid':
+                mycolors[2] = colorScale[i]
+            if boxList[i] == 'Left':
+                mycolors[3] = colorScale[i]
+            # FIXME: fix this
+        mycolors = colorScale[1:]
+        sectionax.contourf(X, Y, sectiondata, levels=levels, colors=mycolors)
+        sectionax.set_aspect('equal')
+        sectionax.set_xlim(xmin, xmax)
+        sectionax.set_ylim(ymin, ymax)
+    plot_sections(sectionax, sectiondata)
+
     j=0
     k=0
     for i in range(len(plotCurveList_D[:,0])):
@@ -129,32 +160,38 @@ def main():
             j+=1
             k=0
         if i==0:
-            plt.plot(timeAxis[start:end],
-                     plotCurveList_D[i, start:end],
-                     color=colorScale[j],alpha=alphaScale_D[k])
-            plt.fill_between(timeAxis[start:end],
+            bax.plot(timeAxis[start:end],
+                       plotCurveList_D[i, start:end],
[…]

### 2013-09-03 pyplots/box_plot.py
do section coloring more nicely Tested everything on bingley.

@@ -145,7 +145,14 @@ def main():
                 mycolors[2] = colorScale[i]
             if boxList[i] == 'Left':
                 mycolors[3] = colorScale[i]
-            # FIXME: fix this
+            if boxList[i] == 'UpperLeft':
+                mycolors[1] = colorScale[i]
+            if boxList[i] == 'UpperRight':
+                mycolors[2] = colorScale[i]
+            if boxList[i] == 'LowerLeft':
+                mycolors[3] = colorScale[i]
+            if boxList[i] == 'LowerRight':
+                mycolors[4] = colorScale[i]
         mycolors = colorScale[1:]
         sectionax.contourf(X, Y, sectiondata, levels=levels, colors=mycolors)
         sectionax.set_aspect('equal')

### 2013-09-04 pyplots/box_plot.py
rotate section plots slightly cleverly for boxplots Tested everything on bingley.

@@ -132,10 +132,16 @@ def main():
         x = np.arange(sectiondata.shape[1]*1.0)*dx
         y = np.arange(sectiondata.shape[0]*1.0)*dx
         X,Y = np.meshgrid(x,y)
+        inmembrane = np.zeros_like(sectiondata)
+        inmembrane[sectiondata>0] = 1.0
         xmax = X[sectiondata>0].max()
         xmin = X[sectiondata>0].min()
         ymax = Y[sectiondata>0].max()
         ymin = Y[sectiondata>0].min()
+        ymean = (Y*inmembrane).sum()/inmembrane.sum()
+        xmean = (X*inmembrane).sum()/inmembrane.sum()
+        yweighted = (Y*sectiondata).sum()/sectiondata.sum()
+        xweighted = (X*sectiondata).sum()/sectiondata.sum()
         levels = [0.5, 1.5, 2.5, 3.5, 4.5]
         mycolors = ["w","g","r","c","m","y"]
         for i in xrange(min(4, len(boxList))):
@@ -154,10 +160,25 @@ def main():
             if boxList[i] == 'LowerRight':
                 mycolors[4] = colorScale[i]
         mycolors = colorScale[1:]
-        sectionax.contourf(X, Y, sectiondata, levels=levels, colors=mycolors)
+        # here we rotate and flip so that the order of sections will
+        # match the box plot as well as we can manage.
+        if yweighted - ymean > abs(xweighted - xmean):
+            sectionax.contourf(X, Y, sectiondata, levels=levels, colors=mycolors)
+            sectionax.set_xlim(xmin, xmax)
+            sectionax.set_ylim(ymin, ymax)
+        elif ymean - yweighted > abs(xweighted - xmean):
+            sectionax.contourf(X, ymax - (Y - ymin), sectiondata, levels=levels, colors=mycolors)
+            sectionax.set_xlim(xmin, xmax)
+            sectionax.set_ylim(ymin, ymax)
+        elif xweighted > xmean:
+            sectionax.contourf(Y, X, sectiondata, levels=levels, colors=mycolors)
+            sectionax.set_xlim(ymin, ymax)
+            sectionax.set_ylim(xmin, xmax)
+        else:
+            sectionax.contourf(Y, xmax - (X - xmin), sectiondata, levels=levels, colors=mycolors)
+            sectionax.set_xlim(ymin, ymax)
+            sectionax.set_ylim(xmin, xmax)
[…]

### 2013-09-04 paper/paper.tex
changes to paper and bib Tested everything on node26.

@@
 \section{Introduction}
-It is vital that during the process of bacterial cell division a
-cell avoid minicelling, or splitting into daughter cells with lopsided
+It is vital that during the process of bacterial cell division a cell
+avoid minicelling, or splitting into daughter cells with lopsided
 volumes.  During this process a long FtsZ polymer chain develops on
-the cell wall in the center region of the cell which acts as a guide
-for the division. Previous experimental studies have shown
-that the MinC protein, known to inhibit the FtZ polymer, exhibits a
-pole to pole oscillatory behavoir in conjunction with the MinD and
-MinE proteins, while the oscillating MinE tends to be more localized
-in the center of the cell \cite{hu1999topological} \cite{fu2001mine}
-The MinC protein will then have a higher time averaged
-concentration in the cell poles as opposed to the center region of the
-cell, prohibiting the FtZ from building in the wrong region.
+the cell wall in the center region of the cell that dictates the plane
+of division\cite{adams2009bacterial}
+\cite{lutkenhaus2007assembly}. Previous experimental studies have
+shown that the MinC protein, known to inhibit the FtZ
+polymer\cite{shen2010examination}, exhibits a pole to pole oscillatory
+behavoir in conjunction with the MinD and MinE proteins, while the
+oscillating MinE tends to be more localized in the center of the cell
+\cite{hu1999topological} \cite{fu2001mine} \cite{shapiro2009and}
+\cite{yu1999ftsz} \cite{raskin1999rapid}The MinC protein will then have a higher time
+averaged concentration in the cell poles as opposed to the center
+region of the cell, aiding in prohibiting the FtZ from developing in the wrong
+region.
 
@@
 
+\fixme{should read following citation more carefully, worried -
+  abstract says that simple models don't explain certain experimental
+  findings.} \cite{ivanov2010multiple}
+
 Previous studies have been made of the Min system's associtation with
@@
 system's ability to maintain their regular oscillatory
-behavior\cite{mannik2012robustness}\cite{mannik2009bacterial}.  We
+behavior\cite{mannik2012robustness} \cite{mannik2010bacteria} \cite{mannik2009bacterial}.  We
 follow the experimental work of Mannik et and use Huang's mean field

### 2013-09-04 paper/paper.tex
very small paper change Tested everything on node26.

@@
   abstract says that simple models don't explain certain experimental
-  findings.} \cite{ivanov2010multiple}
+  findings.} \cite{ivanov2010multiple} \fixme{should read following
+  more carefully this is Huang doing much the same as what were doing}
+\cite{varma2008min}
 

### 2013-09-17 pyplots/box_plot.py
reformat long lines of code Tested everything on bingley.

@@ -22,11 +22,15 @@ import file_loader as load
 # --------
 #where n(t) is the number of proteins of one type at time t
 
-#opens the file and grabs a particular line matching proteinType and boxName. returns list of protein counts at each time.
+#opens the file and grabs a particular line matching proteinType and
+#boxName. returns list of protein counts at each time.
 def returnData(boxName,proteinType):
 
     #open the data file, grab the line with the correct protein type and box partition, load it as a [string] (so we can use list comprehensions)
-    with open("./data/shape-%s/%s%s%sbox-plot--%s-%s-%s-%s-%s-%s.dat"%(load.f_shape,load.debug_str,load.hires_str,load.slice_str,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5),"r") as boxData:
+    with open("./data/shape-%s/%s%s%sbox-plot--%s-%s-%s-%s-%s-%s.dat"%
+              (load.f_shape,load.debug_str,load.hires_str,load.slice_str,
+               load.f_shape,load.f_param1,load.f_param2,load.f_param3,
+               load.f_param4,load.f_param5),"r") as boxData:
         proteinsOverTime = [line for line in boxData if (proteinType in line) and (boxName in line)]
 
 
@@ -36,8 +40,10 @@ def returnData(boxName,proteinType):
     proteinsOverTime = [float(i) for i in proteinsOverTime]
     return proteinsOverTime
 
-#takes input format: ["proteinType1-boxNum1","proteinType1-boxnum2",proteinType2-boxnum1"...]. will return a list of lists
-#in the stacking order specified by the input (first entry is at the bottom).
+#takes input format:
+#["proteinType1-boxNum1","proteinType1-boxnum2",proteinType2-boxnum1"...]. will
+#return a list of lists in the stacking order specified by the input
+#(first entry is at the bottom).
 def stackData(plotList):
     #parse the input
     tempList = []

### 2013-09-17 paper/paper.tex
add abstract Tested everything on bingley.

--- 2013-09-04 paper/paper.tex
@@
 \documentclass[letterpaper,twocolumn,amsmath,amssymb,pre]{revtex4-1}
+
 \usepackage{graphicx}% Include figure files
-\usepackage{animate}
-\usepackage{dcolumn}% Align table columns on decimal point
-\usepackage{bm}% bold math
 \usepackage{color}
-\usepackage{breqn}
 
@@
 \newcommand{\green}[1]{{\bf \color{green} #1}}
-\newcommand{\rr}{\textbf{r}}
-\newcommand{\refnote}{\red{[ref]}}
 
 \newcommand{\fixme}[1]{\red{[#1]}}
-
-%\newcommand{\derivation}[1]{#1} % Use this to show all derivations in detail
-\newcommand{\derivation}[1]{} % Use this for nice pegagogical paper...
-
-% needsworklater is used to annotate bits that need work, but that we
-% can postpone for a while.
-\newcommand{\needsworklater}[1]{\emph{[#1]}}
-% needsworknow is intended to prioritize stuff that needs fixing.
-\newcommand{\needsworknow}[1]{\textcolor{red}{[\emph{#1}]}}
 
@@
 
-%\pacs{61.20.Ne, 61.20.Gy, 61.20.Ja}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\author{Jeff B. Schulte}
+\affiliation{Department of Physics, Oregon State University}
+\author{Rene WHAT. Zeto}
+\affiliation{Department of Physics, Oregon State University}
+\author{David Roundy}
+\affiliation{Department of Physics, Oregon State University}
+
 \begin{abstract}
-  This paper is about science.
+  The dynamics of the Min-protein system help Escherichia coli
+  bacteria regulate the process of cell division by identifying the
+  center of the cell.  We model the Min-protein system in bacteria
+  that have been forced into unusual flattened shapes, as have
+  recently been experimentally observed.  We find that although the
+  presence of Min oscillations is robust in a wide variety of cellular
+  configurations, the location of the peaks is strongly affected by
+  the cellular shape.  In some cases no periodic oscillations are
+  observed.  In particular, we find that cellular shapes observed
+  experimentally to present irregular oscillations do so in the
+  theoretical model, consistently \fixme{or inconsistently?} with
+  experiment.  \fixme{In agreement with previous theoretical and
+    experimental results, we observe ``rotating'' behavior in certain
+    shapes having three corners.}
 \end{abstract}
+
+\maketitle
+
 \section{Introduction}
@@
 cluster ~\cite{kruse2007experimentalist} \cite{meinhardt2001pattern}
-\cite{drew2005polymerization} \cite{fange2006noise}, while studies
-have been made as well of models which rely on MinD mobility and
-attraction on the cell
+\cite{drew2005polymerization} \cite{fange2006noise}
+\cite{kerr2006division}, while studies have been made as well of
+models which rely on MinD mobility and attraction on the cell
 membrane\cite{kruse2002dynamic}\cite{howard2005cellular}.  Variations
-of the Huang 2003 model that attempt to stochasticly account for
-variations of molecular interaction confirm the major results obtained
-by Huang's model and more successfully predict experimentally observed
-oscillations in round cell phenotypes.\cite{drew2005polymerization}
+of the Huang 2003 model that stochasticly account for variations of
+molecular interaction \cite{fange2006noise} and as well monte-carlo
+simulations that implement stochastic version of Huang's mean filed
+reaction rates confirm the major results obtained by Huang's model and
+more successfully predict experimentally observed oscillations in
+round cell phenotypes.\cite{drew2005polymerization}
 \cite{fange2006noise} \cite{huang2004min} Biochemical models of
 broader scope have also been used to study the MinD system and show
-consistent results.\cite{arjunan2010new}
-
-\fixme{should read following citation more carefully, worried -
-  abstract says that simple models don't explain certain experimental
-  findings.} \cite{ivanov2010multiple}
+consistent results.\cite{arjunan2010new}.  However, in general the
+results of the stochastic and monte-carlo simulations are similar to
+those given by Huang's mean field results.  They both show the
+characteristic oscillations in the pill shaped cells.  We do not see
+any compelling reason to avoid using this simple and successful model.
 
@@
 negative curvature. This mechanism has been incorporated into other
-models.\cite{drew2005polymerization}
-\cite{cytrynbaum2007multistranded} \cite{renner2012mind}
-\cite{renner2012mind} However, this mechanism of combined clustering,
-phospholipids and MinD has not been observed in real
-cells. \cite{halatek2012highly}
+models.\cite{drew2005polymerization,cytrynbaum2007multistranded,renner2012mind,renner2012mind}
+However, this mechanism of combined clustering, phospholipids and MinD
+has not been observed in real cells. \cite{halatek2012highly}
 
@@
 oscillations can effectively find poles in abberent cell
-shapes\cite{varma2008min}\cite{juarez2010changes}.  However, Mannik et
-al. have shown that there are limits to this robustness. Forcing cells
-into flattened, irregular cell shapes adversly effects the Min
-system's ability to maintain their regular oscillatory
-behavior\cite{mannik2012robustness} \cite{mannik2010bacteria} \cite{mannik2009bacterial}.  We
-follow the experimental work of Mannik et and use Huang's mean field
-differential equation reaction model to explore the model's ability to
-find regular oscillatory behavoir in a series of abberent shapes.
+shapes~\cite{corbin2002exploring} \cite{juarez2010changes}.  Varma et
+al. have studied three pronged connected tube shapes, both
+experimentally and in simulation\cite{varma2008min} and have shown
+that even in these oscillations develop in regular patterns. However,
+Mannik et al. have shown that there are limits to this
+robustness. Forcing cells into flattened, irregular cell shapes
+adversly effects the Min system's ability to maintain their regular
+oscillatory behavior \fixme{this link doesn't work = cite{mannik2012robustness}}
+\cite{mannik2010bacteria} \cite{mannik2009bacterial}.  We follow the
+experimental work of Mannik et and use Huang's mean field differential
+equation reaction model to explore the model's ability to find regular
+oscillatory behavoir in a series of abberent shapes.
 
@@
 m^3$.  We follow Huang's simulations\cite{huang2003dynamic} and
-Mannik's experiments \cite{mannik2012robustness} and model cells that
+Mannik's experiments \fixme{this link doesn't work = cite{mannik2012robustness}} and model cells that
 are slightly larger than this range.  Amoung our flattened cells the
@@
   \end{tabular}
-\newline
-\newline
+  \caption{Period According to Pill Length}
+\end{table}
 
@@
 in the caps than in the center.  \fixme{am computing these integrals
-  now in ave_plot.py but need to print out into maybe a bar chart}
+  now in ave\_plot.py but need to print out into maybe a bar chart}
 
@@
   is covered by the right section.  I've verified this by looking at
-  the protein_microscopy and drawing a little picture, which is on my
+  the protein\_microscopy and drawing a little picture, which is on my
   desk...if you dare look for something on my desk!!!}  The iscosolese
@@
 \end{figure}
+
+Looking at at few periods in detail.  We find that there is a small
+increase in cytoplasmic MinE always directly before the the beggining
+of climb in the membrane bound MinE peak.  Also, there is at any one
+time a very large amount more of minE that is membrane bound then
+cytoplasmic in any ones section.  A difference of a factor of roughly
+20 when membrane MinE is at its peak, and roughly 12 when membrane
+MinE is at it's minimum.  There seem to be two modes of oscillation,
+each exhibiting a density peak maxima that moves back and forth
+diagonaly from one corner to the opposite, as if there were two
+overlapping, criss-crossed cells oscillating.  In the box plot this is
+seen as roughly coinciding membrane minD peaks in the lower left and
+right corners, followed one pi later in peaks in the upper right and
+upper left corners.  Interesting that this did not exhibit
+counterclockwise motion that Huangs 2008 paper might suggest.  Should
+run sims that start in the wacky way that just started running with
+triangles.
+\newline
 
@@
 \fixme{would this happen over and over or would there be a chaos,
-  breakdown sort of thing at some point.  Need longer sim}.  The total
+  breakdown sort of thing at some point.  Need longer sim}.  The
+animations show that when there is a maxima in the center, if it is a
+maxima that is on the right side of the center upper cup then this
+maxima will be followed by a maxima in the lower left corner.  This
+maxima in the lower left corner (immediately following the one on the
+right side of the upper cup) will reside for a bit longer than the
+left corner maxima preceding it.  These longer residing maxima will
+then be followed by a switch, to the right corner, with a short less
+intensive maxima traveling through the center.  The MinE shows the
+same pattern. So what does this say, keeping in mind our model of MinD
+diffusing and MinE comming in to eat it away?  MinD starts in the
+lower left, diffuses up and maximizes on the right side of upper cup.
+Why right side of upper cup?  Because there is more MinE on the left
+side then on the right side of that upper cup, because MinE has just
+spent time coagulating on left corner wall because there was more MinD
+there.  The MinE attaches to the MinD on the membrane and begins to
+release it.  Why at that point does the MinD go back to the left
+corner?  When the MinE eats away at the wall bound MinD it starts at
+te edges and moves in.  There's one frame where the MinE has maxima on
+either side of the MinD maxima on the right side cup.  The center of
+the cup is a little further away so it attaches to these out ridges
+first and then moves in.  After it eats at the corners and starts
+moving in why does the MinD go back to the left corner?  Watching the
+cytoplasmic MinE, something very interesting: It as well maximizes
+twice in one corner, but in between the two maximizations it has a
+smaller maxima in the other corner.  So when the MinD is getting eaten
+away from the top cup, the minE is moving over to maximize in the
+opposite corner.  Why does it maximize there? there are more minD on
+the membrane to attach to on the left, so it can diffuse further down
+into the corner.  Want to be able to construct a full frame by frame
+picture, with all the proteins layed out top to bottom, each frame
+ontop of its likewise frame.  Actually, you can see this effect very
+slightly watching the 98 shape, between the center cap and the right
+corner.
+
+Also - as to why the proteins like poles and corners.  It's a
+diffusion model, so there's no momentum.  When they are at an end or
+corner, they will go in all directions, and if there's a small hole
+way out, only a small percentage will go down it.  As the others
+attach to the wall, there is a higher chance that diffusing particles
+will attach to that wall instead.
+
+The total
 fluctuation plot shows this double maxima corner pattern, with two
@@
 tests of robustness and compare results to the new experimental
-results of Mannik.\cite{mannik2012robustness}
+results of Mannik.\fixme{this link doesn't work = cite{mannik2012robustness}}
 

### 2013-09-17 pyplots/box_plot.py
find period and display just one period in box plot Tested everything on bingley.

@@ -60,6 +60,44 @@ def stackData(plotList):
     output = np.array(stackedPlotList)
     return output/output[len(output[:,0])-1, 0] # normalize output as a fraction of total
 
+def find_period(f):
+    """
+      Find the period of a function that is described by the input
+      array f, and return indices for a start and end range for one
+      period.  If we cannot find the period accurately, just return
+      the entire range.
+    """
+    # first we look at the fft to get a guess at the period (probably
+    # not *too* accurate or too bad).
+    fk = np.fft.fft(f)
+    fk[0] = 0
+    kmax = 1
+    fkmax = np.abs(fk[:int(len(fk)/2)]).max()
+    for i in xrange(1,int(len(fk)/2)):
+        if np.abs(fk[i]) == fkmax:
+            kmax = i
+            break
+    #print 'kmax is', kmax
+    period_estimate = len(f)/kmax
+    plt.plot(fk)
+    plt.figure()
+    if kmax < 5:
+        return (0, len(f))
+    # now we locate the final minimum of the function.
+    lastmin = len(f)-2
+    while f[lastmin] > f[lastmin+1] or f[lastmin] > f[lastmin-1]:
+        lastmin -= 1
+    # and last (but not least), we locate the second-to-last
+    # (penultimate) minimum, which should have a very similar value to
+    # the final minimum.
+    penultimate_min = lastmin - int(period_estimate*.7)
+    while f[penultimate_min] > f[penultimate_min+1] or f[penultimate_min] > f[penultimate_min-1] or np.abs(f[penultimate_min]/f[lastmin]-1) > 0.01:
+        penultimate_min -= 1
+    #return (0, len(f) - 1)
+    if penultimate_min < 0:
+        return (0, len(f))
+    return (penultimate_min, lastmin)
+
 def main():
 
     with open("./data/shape-%s/%s%s%sbox-plot--%s-%s-%s-%s-%s-%s.dat"%(load.f_shape,load.debug_str,load.hires_str,load.slice_str,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5),"r") as boxData:
@@ -113,6 +151,7 @@ def main():
     # print start_time_as_frac_of_ten
     # print end_time_as_frac_of_ten
[…]

### 2013-09-17 image_shell.sh
pulled from dr roundy, add some things Tested everything on crystal.

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+srun python pyplots/image_plot.py randst 0.25 8.00 6.00 97.00 15.00 701.00 861.00
+srun python pyplots/image_plot.py randst 0.25 6.00 6.00 96.00 15.00 701.00 861.00
+srun python pyplots/image_plot.py randst 0.25 6.00 8.00 98.00 15.00 701.00 861.00
+srun python pyplots/image_plot.py triangle 0.25 4.00 4.00 4.00 15.00 701.00 861.00
+srun python pyplots/image_plot.py triangle 0.25 5.00 5.00 3.00 15.00 701.00 861.00
+srun python pyplots/image_plot.py triangle 0.25 3.60 4.80 6.00 15.00 701.00 861.00

### 2013-09-17 pyplots/ave_plot.py
various plotting cleanups
* removed autogenerated pdf files
* remove excessive useless print statements from plotting programs
* cleaned up batch plot code:
  - batch now fails if any of the plots fail
  - batch will never run more than 4 plots simultaneously (unless
    using srun)

Tested everything on bingley.

@@ -86,11 +86,8 @@ def main():
         (protein, boxName) = (splitString[0], splitString[1])
         plotCurveList_D += [returnData(boxName,protein)]
 
-    print len(plotCurveList_D[:][0])
-
     #get a time axis for the plot from the length of one of the data sets we have
     timeAxis = range(len(plotCurveList_D[0]))
-    #print len(plotCurveList_D[:,0])
 
     #begin messy code (to deal with matplotlib) - don't judge me
     (start, end) = (int(5.3*int(len(timeAxis)/10)),int(5.7*int(len(timeAxis)/10)))
@@ -101,17 +98,13 @@ def main():
         integral = 0
         for j in range(len(plotCurveList_D[0])):
             integral += plotCurveList_D[i][j]
-        print plotNameList_D[i]
-        print integral/1000
-
 
     #plot scales. colors limited for now.
     colorScale = ["b","g","r","c","m","y"]
     alphaScale_D = [n/numProteinTypes_D for n in range(1,numProteinTypes_D+1)]
 
     # yLimit = max(plotCurveList_D[0][start:end])
-    # print yLimit
-    # print "hello"
+
                  #generate the plot
     plt.figure()
     j=0
@@ -120,8 +113,6 @@ def main():
         if i%(numProteinTypes_D)==0:
             j+=1
             k=0
-        print i
-        print len(plotCurveList_D[0])
         plt.plot(timeAxis[start:end],
                  plotCurveList_D[i][start:end],
                  color=colorScale[j],alpha=alphaScale_D[k])

### 2013-09-29 paper/paper.tex
pulled from dr roundy, add some things Tested everything on crystal.
Fixed wall bug in arrow plots and paper Tested everything on node37.

@@
   \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-400-400-400-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-500-500-300-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-360-480-600-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-500-300-500-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-480-360-1500}
   \caption{Total protein fluctuation in the right, middle, and left
@@
 \end{figure}
+\subsubsection{Randst-94-mannik shape}
+\begin{figure}
+  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1100-1100-9500-1500.pdf}
+  \includegraphics[width=2.8cm]{../mannik-1.png}
+  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1300-2000-9400-1500.pdf}
+  \includegraphics[width=2.8cm]{../mannik-2.png}
+  \caption{Arrow plots for our simulation and mannik's experimental}
+  \label{arrow-randst-94}
+\end{figure}
+
 \subsubsection{Randst-96-Star}

### 2013-09-29 pyplots/arrow_plot.py

@@ -9,9 +9,34 @@ import file_loader as load
 
 
 #membrane.dat or arrow.dat printed transposed, gotta align them:
-cell_membrane = np.transpose(np.loadtxt("./data/shape-%s/membrane_files/%s%s%ssections-%s-%s-%s-%s-%s-%s.dat"%
+cell_membrane_initial = np.loadtxt("./data/shape-%s/membrane_files/%s%s%ssections-%s-%s-%s-%s-%s-%s.dat"%
                                         (load.f_shape,load.debug_str,load.hires_str,load.slice_str,
-                                         load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5)))
+                                         load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5))
+
+#http://stackoverflow.com/questions/8486294/how-to-add-an-extra-column-to-an-numpy-array
+#this is algorithm want
+Ny = len(cell_membrane_initial[:,0])
+Nz = len(cell_membrane_initial[0,:])
+
+temp_array = np.zeros((Ny+1,Nz+1))
+temp_array[:-1,:-1] = cell_membrane_initial
+cell_membrane = temp_array
+
+
+row_of_zeros = np.zeros(len(cell_membrane[:,0]))
+np.vstack((cell_membrane[:,0],row_of_zeros))
+np.vstack((row_of_zeros,cell_membrane[:,0]))
+
+row_of_zeros = np.zeros(len(cell_membrane[0,:]))
+np.vstack((cell_membrane[0,:],row_of_zeros))
+np.vstack((row_of_zeros,cell_membrane[0,:]))
+
+
+cell_membrane
+if load.f_param4 != "94.00":
+    np.transpose(cell_membrane)
+
+
 
 for protein in load.proteinList:
     tails = np.loadtxt('./data/shape-%s/%s%s%sarrow-plot-%s-%s-%s-%s-%s-%s-%s.dat'%(load.f_shape,load.debug_str,load.hires_str,load.slice_str,protein,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5))
@@ -48,18 +73,18 @@ for protein in load.proteinList:
     if len(tails)==0:
         print "The tails in this file has no tails!!"
         exit(0)
[…]

### 2013-09-29 pyplots/box_plot.py

@@ -155,25 +155,21 @@ def main():
 
     start_time_as_frac_of_ten = float(load.f_param6)
     end_time_as_frac_of_ten = float(load.f_param7)
-    # print load.f_shape
-    # print start_time_as_frac_of_ten
-    # print end_time_as_frac_of_ten
-    #(start, end) = (int(start_time_as_frac_of_ten*len(timeAxis)/10),int(end_time_as_frac_of_ten*len(timeAxis)/10))
     (start, end) = find_period(plotCurveList_D[3])
 
     #print set(plotCurveList_D[1]).union(set(plotCurveList_D[2]))
-    print start
 
-    arrow_start = start+10
+    arrow_start = start+int(0.05*(end-start))
     arrow_x = [arrow_start]*len(plotCurveList_D)
-    print len(plotCurveList_D)
+    for i in range(arrow_start,arrow_start + int((end-start)/5)):
+            if ((plotCurveList_D[0][arrow_x[0]]-0) < (plotCurveList_D[0][i]-0)):
+                arrow_x[0] = i
     for type in range(1,len(plotCurveList_D)):
         for i in range(arrow_start,arrow_start + int((end-start)/5)):
             if ((plotCurveList_D[type][arrow_x[type]]-plotCurveList_D[type-1][arrow_x[type]]) < (plotCurveList_D[type][i]-plotCurveList_D[type-1][i])):
                 arrow_x[type] = i
-                print type,i
-    print arrow_x
 
+    
     # arrow_x = [100]*len(plotCurveList_D)
     # print len(plotCurveList_D)
     # for type in range(len(plotCurveList_D)):
@@ -275,6 +271,7 @@ def main():
 
     j=0
     k=0
+    text_adjust = -.2*box_time_step*(end-start)
     for i in range(len(plotCurveList_D[:,0])):
         if i%(numProteinTypes_D)==0:
             j+=1
@@ -283,6 +280,10 @@ def main():
             bax.plot(timeAxis[start:end],
                        plotCurveList_D[i, start:end],
                        color=colorScale[j],alpha=alphaScale_D[k])
+            y_label = (plotCurveList_D[i, arrow_x[i]])/2.0
+            bax.annotate('%s'%plotNameList_D[i],xy=(arrow_x[i]*box_time_step,y_label),xytext=(start*box_time_step+text_adjust,y_label),
+                         fontsize=7,
[…]

### 2013-09-30 paper/paper.tex

--- 2013-09-17 paper/paper.tex
@@
 \documentclass[letterpaper,twocolumn,amsmath,amssymb,pre]{revtex4-1}
-
 \usepackage{graphicx}% Include figure files
+\usepackage{animate}
+\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
 \usepackage{color}
+\usepackage{breqn}
 
@@
 \newcommand{\green}[1]{{\bf \color{green} #1}}
+\newcommand{\rr}{\textbf{r}}
+\newcommand{\refnote}{\red{[ref]}}
 
 \newcommand{\fixme}[1]{\red{[#1]}}
+
+%\newcommand{\derivation}[1]{#1} % Use this to show all derivations in detail
+\newcommand{\derivation}[1]{} % Use this for nice pegagogical paper...
+
+% needsworklater is used to annotate bits that need work, but that we
+% can postpone for a while.
+\newcommand{\needsworklater}[1]{\emph{[#1]}}
+% needsworknow is intended to prioritize stuff that needs fixing.
+\newcommand{\needsworknow}[1]{\textcolor{red}{[\emph{#1}]}}
 
@@
 
-\author{Jeff B. Schulte}
-\affiliation{Department of Physics, Oregon State University}
-\author{Rene WHAT. Zeto}
-\affiliation{Department of Physics, Oregon State University}
-\author{David Roundy}
-\affiliation{Department of Physics, Oregon State University}
-
+%\pacs{61.20.Ne, 61.20.Gy, 61.20.Ja}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}
-  The dynamics of the Min-protein system help Escherichia coli
-  bacteria regulate the process of cell division by identifying the
-  center of the cell.  We model the Min-protein system in bacteria
-  that have been forced into unusual flattened shapes, as have
-  recently been experimentally observed.  We find that although the
-  presence of Min oscillations is robust in a wide variety of cellular
-  configurations, the location of the peaks is strongly affected by
-  the cellular shape.  In some cases no periodic oscillations are
-  observed.  In particular, we find that cellular shapes observed
-  experimentally to present irregular oscillations do so in the
-  theoretical model, consistently \fixme{or inconsistently?} with
-  experiment.  \fixme{In agreement with previous theoretical and
-    experimental results, we observe ``rotating'' behavior in certain
-    shapes having three corners.}
+  This paper is about science.
 \end{abstract}
-
-\maketitle
-
 \section{Introduction}
@@
 in the caps than in the center.  \fixme{am computing these integrals
-  now in ave\_plot.py but need to print out into maybe a bar chart}
+  now in ave_plot.py but need to print out into maybe a bar chart}
 
@@
   is covered by the right section.  I've verified this by looking at
-  the protein\_microscopy and drawing a little picture, which is on my
+  the protein_microscopy and drawing a little picture, which is on my
   desk...if you dare look for something on my desk!!!}  The iscosolese

### 2013-09-30 pyplots/ave_plot.py
changed ave and box plots Tested everything on node26.

@@ -36,9 +36,46 @@ def returnData(boxName,proteinType):
     output = np.array(proteinsOverTime)
     return (output)
 
+def find_period(f):
+    """
+      Find the period of a function that is described by the input
+      array f, and return indices for a start and end range for one
+      period.  If we cannot find the period accurately, just return
+      the entire range.
+    """
+    # first we look at the fft to get a guess at the period (probably
+    # not *too* accurate or too bad).
+    fk = np.fft.fft(f)
+    fk[0] = 0
+    kmax = 1
+    fkmax = np.abs(fk[:int(len(fk)/2)]).max()
+    for i in xrange(1,int(len(fk)/2)):
+        if np.abs(fk[i]) == fkmax:
+            kmax = i
+            break
+    #print 'kmax is', kmax
+    period_estimate = len(f)/kmax
+    #plt.plot(np.abs(fk))
+    #plt.figure()
+    if kmax < 5:
+        return (0, len(f))
+    # now we locate the final minimum of the function.
+    lastmin = len(f)-2
+    while f[lastmin] > f[lastmin+1] or f[lastmin] > f[lastmin-1]:
+        lastmin -= 1
+    # and last (but not least), we locate the second-to-last
+    # (penultimate) minimum, which should have a very similar value to
+    # the final minimum.
+    penultimate_min = lastmin - int(period_estimate*.7)
+    while f[penultimate_min] > f[penultimate_min+1] or f[penultimate_min] > f[penultimate_min-1] or np.abs(f[penultimate_min]/f[lastmin]-1) > 0.01:
+        penultimate_min -= 1
+    #return (0, len(f) - 1)
+    if penultimate_min < 0:
+        return (0, len(f))
+    return (penultimate_min, lastmin)
+
 
 def main():
-
     with open("./data/shape-%s/%s%s%sbox-plot--%s-%s-%s-%s-%s-%s.dat"%(load.f_shape,load.debug_str,load.hires_str,load.slice_str,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5),"r") as boxData:
         fileLines = boxData.readlines()
 
@@ -87,11 +124,17 @@ def main():
         plotCurveList_D += [returnData(boxName,protein)]
 
     #get a time axis for the plot from the length of one of the data sets we have
[…]

### 2013-09-30 pyplots/box_plot.py

@@ -7,8 +7,9 @@ import sys
 import pylab
 import file_loader as load
 import matplotlib.patheffects
+from matplotlib.font_manager import FontProperties
 
-print matplotlib.__version__
+
 from mpl_toolkits.axes_grid.anchored_artists import AnchoredSizeBar
 
 ## WIP!!
@@ -103,7 +104,6 @@ def find_period(f):
     return (penultimate_min, lastmin)
 
 def main():
-
     with open("./data/shape-%s/%s%s%sbox-plot--%s-%s-%s-%s-%s-%s.dat"%(load.f_shape,load.debug_str,load.hires_str,load.slice_str,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5),"r") as boxData:
         fileLines = boxData.readlines()
 
@@ -161,15 +161,14 @@ def main():
 
     arrow_start = start+int(0.05*(end-start))
     arrow_x = [arrow_start]*len(plotCurveList_D)
-    for i in range(arrow_start,arrow_start + int((end-start)/5)):
+    for i in range(arrow_start,arrow_start + int((end-start)/100)):
             if ((plotCurveList_D[0][arrow_x[0]]-0) < (plotCurveList_D[0][i]-0)):
                 arrow_x[0] = i
     for type in range(1,len(plotCurveList_D)):
-        for i in range(arrow_start,arrow_start + int((end-start)/5)):
+        for i in range(arrow_start,arrow_start + int((end-start)/100)):
             if ((plotCurveList_D[type][arrow_x[type]]-plotCurveList_D[type-1][arrow_x[type]]) < (plotCurveList_D[type][i]-plotCurveList_D[type-1][i])):
                 arrow_x[type] = i
 
-    
     # arrow_x = [100]*len(plotCurveList_D)
     # print len(plotCurveList_D)
     # for type in range(len(plotCurveList_D)):
@@ -244,7 +243,8 @@ def main():
         # box plot.
         xdir, ydir = xweighted - xmean, yweighted - ymean
         xdir, ydir = xdir/np.sqrt(xdir**2+ydir**2), ydir/np.sqrt(xdir**2+ydir**2)
-        extrayspace = 3
+        extraxspace = .5
+        extrayspace = 0
         Yrotated = X*xdir + Y*ydir
         Xrotated = X*ydir - Y*xdir
[…]

### 2013-10-07 paper/paper.tex

--- 2013-09-29 paper/paper.tex
@@
 results of the stochastic and monte-carlo simulations are similar to
-those given by Huang's mean field results.  They both show the
-characteristic oscillations in the pill shaped cells.  We do not see
-any compelling reason to avoid using this simple and successful model.
+those given by Huang's mean field results.
 
@@
 
+Our simplest shape is the naturally occuring pill shape.  We peice this shape
+together as two hemispherical endcaps attached on either end of a
+cylinder.  This shape follows the early simulations of Huang et al but
+differs in that we have added the end caps for a more natural shape,
+expecting similar results.  We test cells of radius $.5\mu$ and of
+lengths $2\mu$, $3\mu$, and $5\mu$ between both tips of the end
+caps. In all these models we observe quick establishement (within a
+few periods) of extremely regular oscillatory behavoir that lasts for
+any length of time, with periods that closely agree with the results
+of Huang et al.  The following table shows the periods of oscillations
+at different cell lengths.
+
+\begin{table}
+  \begin{tabular}{|r|c|c|c|l|}
+    \hline
+    Length($\mu$) & 2.50 & 3.00 & 4.00 & 5.00\\
+    \hline
+    Period(sec) & sim & 33 & 38 & 48 \\ \cline{2-2}
+    \hline
+  \end{tabular}
+  \caption{Period According to Pill Length}
+\end{table}
+
+%% \begin{figure*}
+%%   \includegraphics[width=\textwidth]{../data/shape-p/plots/image-plot_E--p-200-50-0-0-1500}
+%%   \caption{Frames from an animation showing a series of contour plots
+%%     of the concentration of proteins in different stages over time.
+%%     The density of proteins are integrated along the axis
+%%     normal to the page. The frames occur 2.5 seconds apart.}
+%%   \label{total-oscillation-plot}
+%% \end{figure*}
+
+This simple model is a good starting point for observing in
+detail the dynamic interaction between the different stages of protein
+that lead to their qualitatively distinct behavoir. Figure (Figure
+image) shows the process in a series of frames taken from simulation
+animations.  The causal chain is cyclical so we can begin our
+observations at any stage in the cycle.  We look first at MinD:ATP
+floating freely in the cytoplasm.  The protein will not react with any
+other floating protein, and it will not spontenously shift back into
+the MinD:ADP stage of the cycle.  It will diffuse until it attaches to
+a cell membrane.  When compared to a protein that is in the middle
+cylindrical section of the cell, a protein that is in an end cap
+section is more likely to bump into a wall in a given number of
+diffusive steps, since there is a greater cross section of possible
+movement that is covered by a nearby wall.  All else being equal,
+proteins will collect with a higher rate on the caps.  This effect is
+made more pronounced by the MinD:ATP tendency to attract and cluster.
+When adjacent to the membrane, the rate of binding to the membrane is
+porportional to the amount of MinD already bound there.  Initially,
+then, there is a strong tendency of MinD to cluster in the polar
+regions of the cell.
+
+The next observed mechanism is the formation of MinE 'rings' on the
+membranes of the polar caps.  As the freely
+diffusing MinE enters the cap portion it begins to encounter
+concentrated membrane bound MinD.  As it bumps into the walls here it
+binds to this MinD and remians for a time on the walls in compound
+form.  When it is released, it can diffuse naturally outward or inward
+towards the cell.  If it diffuses inward, there is less cross
+sectional wall for it to bump into and also less concentrated MinD:ATP
+to react with.  If it diffuses outward, the curvature of the cell wall
+cuases there to be a greater chance that it will bump into the cell
+membrane (for the same reason outlined for the MinD:ATP above) and if
+there is MinD:ATP bound there, there is a chance that it will bind to
+that protein and react again.  If it does diffuse in this directin, it
+will likely react with MinD:ATP before getting very far into the
+encap.  Thus after dettaching from the membrane at the edge of the
+MinD:ATP encap cluster, the MinE is most likely to travel a small
+distance further into the polar region and then attach and react again
+with MinD:ATP protein there.  This process results in the observed
+qualitative 'encroaching MinE ring' behavoir that released MinD:ADP
+back into the cytoplasm.  This MinD:ADP will diffuse for a time before
+spontanosly uindergowing hydrolysis \fixme{is this right?} and
+reaching the MinD:ATP state that can bind to the membrane again.
+There is a strong chance that it has by this time diffused out of the
+polar region and is on its way to the opposite polar region of the
+cell.  If it hasn't then it will reattach to the MinD:ATP on the cell
+wall deeper into the endcap and will eventually be converged upon by
+the MinE ring, only to be released again in MinD:ADP form.
+
+Overall this process results in an extremely robust oscillatory
+behavoir of polar selection and oscillation in a wide variety of cell
+shapes.
+
 \begin{figure}
@@
 
-Figure \ref{total-oscillation-plot} shows total protein
-results for pill shaped cell of length $5\mu$ and radius $.5\mu$.  The
-plot shows both the transerence between different stages of protein
-compound and movement within the cell.  Starting at the beginning of a
-period, we can see that first there is a spike on the left of MinD-ATP
-attached to the wall that is accompanied by a growing number of
-cytoplasmic MinD-ATP and MinD-ADP that are entering the left section,
-followed by a high peak in MinD-MinE-ATP.  This peak gives way through
-the middle to peaks on the right side of the cell, the first being a
-small bump in cytoplasmic MinD-ATP that dissapears into a much larger
-spike in wall attached MinD-ATP, which is followed by a peak in wall
-attached MinD-MinE-ATP.  The pattern during each period clearly shows
-the cycle of proteins rections, as well as the very regular nature of
-the pole to pole protein oscillations.
+Figure \ref{total-oscillation-plot} is a plot of the total fraction of
+MinD found in each stage of the cycle in each of three sections of the
+cell (we have split the pill into two polar sections and one center
+section) over time.  One complete oscillation period is shown, in
+which one of the poles begins and ends at a maximum density
+concentration and the other a minimum denisty concentration.  Looking
+at the evolution of the latter, we see an initial high concentration
+of cytoplasmic MinD:ATP, as the this protein diffuses into the polar
+region, followed by a dip in this and large spike in membrane bound
+MinD:ATP, as the protein clusters onto the polar cell wall, followed
+by a spike in the memebrane bound MinE:MinD:ATP stage of protein,
+together with a slight rise in cytoplasmic MinD:ADP as the MinD
+dettaches from the wall.
+
+results for pill shaped cell of length
+$5\mu$ and radius $.5\mu$.  The plot shows both the transerence
+between different stages of protein compound and movement within the
+cell.  Starting at the beginning of a period, we can see that first
+there is a spike on the left of MinD-ATP attached to the wall that is
+accompanied by a growing number of cytoplasmic MinD-ATP and MinD-ADP
+that are entering the left section, followed by a high peak in
+MinD-MinE-ATP.  This peak gives way through the middle to peaks on the
+right side of the cell, the first being a small bump in cytoplasmic
+MinD-ATP that dissapears into a much larger spike in wall attached
+MinD-ATP, which is followed by a peak in wall attached MinD-MinE-ATP.
+The pattern during each period clearly shows the cycle of proteins
+rections, as well as the very regular nature of the pole to pole
+protein oscillations.
 
@@
 corner maxima, with very obvious symmetry.
+
+%% \begin{center}
+%%   \begin{figure}
+%%     {\includegraphics[width=\paperwidth]{../data/shape-randst/plots/image-plot_E--randst-25-602-602-9900-1500}}
+%%     \caption{Attempt at adding image plot to paper.}
+%%     \label{image-plot}
+%%   \end{figure}
+%% \end{center}
 

### 2013-10-09 paper/paper.tex
added writing and plot Tested everything on node22.

@@
 
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-p/plots/frequency-plot-all-NflD-p-40-20-0-0-150.pdf}
-%%   \caption{Protein density fluctuation with time against the polar
-%%     wall in a 4$\mu m$ by 2$\mu m$ pill shaped cell.  The wall-bound
-%%     proteins are shown at a point that is on the wall and the
-%%     cytoplasm densities are shown at a point immediately adjecent.
-%%     This plot is normalized so that every protein density peaks at 1}
-%%   \label{frequency-plot-40-20-0-0-150}
-%% \end{figure}
-
 Our simplest shape is the naturally occuring pill shape.  We peice this shape
@@
   \caption{Period According to Pill Length}
+  \label{table-p}
 \end{table}
 
-%% \begin{figure*}
-%%   \includegraphics[width=\textwidth]{../data/shape-p/plots/image-plot_E--p-200-50-0-0-1500}
-%%   \caption{Frames from an animation showing a series of contour plots
-%%     of the concentration of proteins in different stages over time.
-%%     The density of proteins are integrated along the axis
-%%     normal to the page. The frames occur 2.5 seconds apart.}
-%%   \label{total-oscillation-plot}
-%% \end{figure*}
-
-This simple model is a good starting point for observing in
-detail the dynamic interaction between the different stages of protein
-that lead to their qualitatively distinct behavoir. Figure (Figure
-image) shows the process in a series of frames taken from simulation
-animations.  The causal chain is cyclical so we can begin our
-observations at any stage in the cycle.  We look first at MinD:ATP
-floating freely in the cytoplasm.  The protein will not react with any
-other floating protein, and it will not spontenously shift back into
-the MinD:ADP stage of the cycle.  It will diffuse until it attaches to
-a cell membrane.  When compared to a protein that is in the middle
-cylindrical section of the cell, a protein that is in an end cap
-section is more likely to bump into a wall in a given number of
-diffusive steps, since there is a greater cross section of possible
-movement that is covered by a nearby wall.  All else being equal,
-proteins will collect with a higher rate on the caps.  This effect is
-made more pronounced by the MinD:ATP tendency to attract and cluster.
-When adjacent to the membrane, the rate of binding to the membrane is
-porportional to the amount of MinD already bound there.  Initially,
-then, there is a strong tendency of MinD to cluster in the polar
-regions of the cell.
+This simple model is a good starting point for observing in detail the
+dynamic interaction between the different stages of protein that lead
+to their qualitatively distinct behavoir. Figure \ref{image-p} shows
+the process in a series of frames taken from simulation animations.
+Each frame is 2.5 seconds ahead of the last.  The causal chain is
+cyclical so we can begin our observations at any stage in the cycle.
+We consider first MinD:ATP floating freely in the cytoplasm.  The
+protein will not react with any other floating protein, and it will
+not spontenously shift back into the MinD:ADP stage of the cycle.  It
+will diffuse until it attaches to a cell membrane.  When compared to a
+protein that is in the middle cylindrical section of the cell, a
+protein that is in an end cap section is more likely to bump into a
+wall in a given number of diffusive steps, since there is a greater
+cross section of possible movement that is covered by a nearby wall.
+All else being equal, proteins will collect with a higher rate on the
+caps.  This effect is made more pronounced by the MinD:ATP tendency to
+attract and cluster.  When adjacent to the membrane, the rate of
+binding to the membrane is porportional to the amount of MinD already
+bound there.  Initially, then, there is a strong tendency of MinD to
+cluster in the polar regions of the cell.
 
@@
 with MinD:ATP protein there.  This process results in the observed
-qualitative 'encroaching MinE ring' behavoir that released MinD:ADP
+qualitative 'encroaching MinE ring' behavoir that releases MinD:ADP
 back into the cytoplasm.  This MinD:ADP will diffuse for a time before
@@
 shapes.
+
+\begin{figure*}
+  \includegraphics[width=\textwidth]{../data/shape-p/plots/image-plot--p-400-50-0-0-1500.pdf}
+  \caption{Frames from an animation showing a series of contour plots
+    of the concentration of proteins in different stages over time.
+    The density of proteins are integrated along the axis
+    normal to the page. The frames occur 2.5 seconds apart.}
+  \label{image-p}
+\end{figure*}
+
+Consider Figure \ref{image-p}.  At 0 seconds we can see cytoplasmic
+nATP roughly evenly distributed throughout the cell.  There is nADP
+concentrated in the left pole and it will transform into nATP.  At 2.5
+seconds we see membrane bound MinD:ATP form on the right side of the
+cell.  It avoids the left side because there is a concentration of
+cytoplasmic MinE on the left side and compared to the right side,
+which is empty of MinE, MinD:ATP attaching to the wall on the left has
+no time to collect and cluster before reacting.  One can see how as
+the MinE spreads out rightward, the the clustered membrane bound
+MinD:ATP stays just at the edge of it, always to the right.  Where the
+two meet there is at every time step a spike in membrane bound
+MinD-MinE:ATP, resulting from the MinE reaction with the MinD on the
+wall.  One can see from roughly 5 seconds to 17.5 seconds the
+cytoplasmic MinE chases in a way the MinD towards the right, reacting
+with it as it clusters on the wall.  Upon reaching the right side, the
+MinD is in a way trapped, and the MinE now concentrated in that pole
+will react until the MinD has diffused back towards the other side and
+there is no more membrane bound MinD:ATP to react with.  The cycle
+then begins again.
 
@@
     horizontal.}
-  \label{total-oscillation-plot}
+  \label{box-p}
 \end{figure}
 
-Figure \ref{total-oscillation-plot} is a plot of the total fraction of
+Figure \ref{box-p} is a plot of the total fraction of
 MinD found in each stage of the cycle in each of three sections of the
@@
 which one of the poles begins and ends at a maximum density
-concentration and the other a minimum denisty concentration.  Looking
+concentration and the other a minimum density concentration.  Looking
 at the evolution of the latter, we see an initial high concentration
@@
 
-Figure \ref{frequency-plot-40-20-0-0-150} also shows that the middle
+Figure also shows that the middle
 density oscillates at a frequency that is twice that of the polar

### 2013-10-09 pyplots/file_loader.py
changed back file_loader because I still havent implemented the definition overloading properly Tested everything on node22.

@@ -49,13 +49,13 @@ class data(object):
         self.dataset = np.array([np.loadtxt(file) for file in self.filenames])
         self.datashape = self.dataset[0].shape
         self.axes = [[i*dx for i in range(self.datashape[1])],[j*dx for j in range(self.datashape[0])]]
-    def __init__(self,protein,start_time,end_time):
-        self.protein = protein
-        self.filenames = self.get_filenames(protein,start_time,end_time)
-        self.tsteps = len(self.filenames)
-        self.dataset = np.array([np.loadtxt(file) for file in self.filenames])
-        self.datashape = self.dataset[0].shape
-        self.axes = [[i*dx for i in range(self.datashape[1])],[j*dx for j in range(self.datashape[0])]]
+    # def __init__(self,protein,start_time,end_time):
+    #     self.protein = protein
+    #     self.filenames = self.get_filenames(protein,start_time,end_time)
+    #     self.tsteps = len(self.filenames)
+    #     self.dataset = np.array([np.loadtxt(file) for file in self.filenames])
+    #     self.datashape = self.dataset[0].shape
+    #     self.axes = [[i*dx for i in range(self.datashape[1])],[j*dx for j in range(self.datashape[0])]]
 
 #loads the files for creating the data object.
     @staticmethod

### 2013-10-12 paper/paper.tex
added to paper and added new 97 shape data Tested everything on node32.

@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-p/plots/ave-plot_D--p-400-50-0-0-1500}
   \includegraphics[width=\columnwidth]{../data/shape-p/plots/ave-plot_D--p-200-50-0-0-1500}
@@
 the plot of the 3$\mu m$ by 1$\mu m$ cell that the MinD proteins reach
-concentration peaks in the caps that are roughly three times higher
-(for the MinD-ATP proteins) and roughly 1.5 times higher (for the
-MinD-MinE-ATP) than peaks in the center.  Integrals of these plotted
-values show that the time averaged concentrations are likewise higher
-in the caps than in the center.  \fixme{am computing these integrals
-  now in ave\_plot.py but need to print out into maybe a bar chart}
+concentration peaks in the caps that are higher than peaks in the
+center.  \fixme{is the next part true?} Integrals of these plotted values show that the time averaged
+concentrations are likewise higher in the caps than in the center.
 
@@
     in the different sections of the cell.}
-  \label{total-oscillation-triangle-plot}
+  \label{box-triangle}
 \end{figure}
+
+The double pole oscillation pattern, where one pole is located in a
+single corner of the triangle and the other pole is spread out between
+the opposite two, can be seen in Figure \ref{box-triangle}.  The
+equilateral triangle shows a spike in both the Center and Left
+sections at the same time, both showing the familiar sequence of peaks
+amoungst the different states of the protein seen in the poles of the
+pill shaped bacteria.  A spike in the other corner, showing the common
+sequence, occurs during the minima of the former two, wth a higher
+concentration at the peak.  A similar pattern is seen in the
+iscosolese triangular shape, where interestingly the onset of the
+maxima in the single maxima corner (the Left section) builds more
+quickly than it fades.  This is presumably becuase as the cytoplasmic
+minD:ATP diffuses down a more accute corner, it is sourrounded by
+closer cell walls than it would be in a less acute corner, so that the
+it is more apt at any diffusive step to make contact and cluster on
+the walls.  That particular part of the process is therefore
+accelerated, driving the build up of the maxima forward.  The right
+triangle shows a similar pattern.
 
@@
 
-With arrow plots - have noticed that the wall attached proteins seem
-to climb along the walls with little arrows, so the maxima crawl
-along, in a way.
-
+\subsubsection{Randst-mannik shape}
 \begin{figure}
-
-\end{figure}
-\subsubsection{Randst-94-mannik shape}
-\begin{figure}
-  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1100-1100-9500-1500.pdf}
+  \includegraphics[width=2.8cm]{../mannik-2.png}
   \includegraphics[width=2.8cm]{../mannik-1.png}
   \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1300-2000-9400-1500.pdf}
-  \includegraphics[width=2.8cm]{../mannik-2.png}
+  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1101-1101-9500-1500.pdf}
+  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-600-800-9800-1500}
+  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1102-1102-9500-1500}
   \caption{Arrow plots for our simulation and mannik's experimental}
-  \label{arrow-randst-94}
+  \label{arrow-compare-mannik}
 \end{figure}
 
+Figure \ref{arrow-compare-mannik} shows a comparison of time maxima
+plots with similar plots published by mannik et al.  The sequence of
+arrows show a series of global maxima in space and local maxima in
+time at their heads, numbered by the sequence in which they occur.
+They function as a trace of the path that the traveling maxima take.
+We have created for each of the two shapes published by Mannik a
+closely resembling shape (shown directly below Mannik's) and a
+variation on this shape (shown below that) in order to test the effect
+of variations on basic shapes.  The plots of the left shape show that
+much of the preffered locations for the proteins to maximize are
+similar between this experimental and simulated shape.  The maxima in
+the top center of the cell does not seem to appear in the experimental
+version.  Also in both of the simulations on the left there don't seem
+to be maxima at membrane regions with negative radii of curvature
+while the experimental shows a maxima in the bottom center region
+right at one of these regions.  The shape on the right compares less
+successfully.  Here the simulation shows a limited number of maxima
+locations that appear to be quite regular, where mannik's experimental
+results show a much more chaotic system.  In particular, the maxima
+location on the right wall seems to be very robust.  It acts as one of
+the poles do in the pill shapes.  \fixme{I'm now running a sim with a
+  slightly different shape to see result} The simulated version has
+found a robust two pole pattern, similar to that seen in other shapes.
+
+\subsubsection{Randst-99 our lambda shape}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
+  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}arrow-plot-NflD-randst-25-600-800-9800-1500.pdf
+
+  \caption{Total protein fluctuation in the A shaped shape.  The vertical axis shows stacked the total number
+    of proteins that are of four different compound stages and in the
+    different sections of the cell.}
+  \label{total-oscillation-randst-96-plot}
+\end{figure}
+
+Our animations for this cell shape show a very interesting pattern.
+The maxima oscillates from the right corner to the top corner, then
+\emph{back to the right corner} then to the top corner again, then to
+the left corner, then back to the top, then to the left, then to the
+top again, then back to the right side.
+
+\fixme{running larger and smaller.  Guessing the larger will do pole
+  and pole, so talk about in terms of you have huge, pole and pole,
+  then once get small enough double oscillations develop.  Why do they
+  do that?  And hen you can do image plot for the one with consistent
+  double oscillations.  Can right now explain reason for double
+  oscillations.  Look at todo.txt.  The slightly varied guassian shape,
+  so a little assymetric, doesn't change double oscillation pattern.}
+
+Contour plot frames from the animations show the second maxima in the
+lower left corner (immediately following the one in the upper middle
+corner) will reside for a bit longer than the left corner maxima
+preceding it.  These longer residing maxima will then be followed by a
+switch, to the right corner, with a short, less intensive maxima
+traveling through the center.  The MinE shows the same pattern. The
+MinE that was just concentrated on the left corner during the first
+maxima, after releasing the MinD from the membrane there, diffuses up
+and attaches to the MinD on the upper corner membrane and begins to
+release it.  During this process the MinE starts at the edges and
+moves in towards the center of the maxima.  The center of the cup is a
+little further away so it attaches to these outer ridges first and
+then moves in.  After it eats at the corners and starts moving in the
+MinD eventually travels back to set up a maxima in the left corner.
+Watching the cytoplasmic MinE, something very interesting: It as well
+maximizes twice in the left corner, but during the MinD's first maxima
+in the left corner, the MinD has a maxima in the upper corner, and
+during the MinD's second left maxima, the MinE travels to the right
+corner and has a maxima there.  At the same time (during the second
+MinD left corner maxima), there is a large amount of cytoplasmic
+MinD:ATP on the right side.  The MinE does this becuase during the
+first MinD left corner maxima, the MinE has just come off a maxima in
+the right corner.  So it diffuses up to the upper corner and sets up
+there.  During the second MinD left corner maxima, the MinE has just
+come off the upper corner maxima.  It will diffuse into the right
+corner and left corner.  In the left corner it interacts with the MinD
+bound to the membrane there.  In the right corner it sits and
+eventually diffuses away, but at a somewhat slow pace.  \fixme{An idea
+  is that once the MinD travels back from the left corner after its
+  second maxima there, it is not able tot set up a maxima in the upper
+  corner as easily, since there is left over MinE there, which has
+  just traveled from the right corner.  The problem with this is that
+  the MinE doesn't seem to be maximized in the upper corner when the
+  MinD is traveling back up from the left.}  The other idea is simply
+that because the minE is traveling all the way from the right corner,
+the longer time it takes to get there simply means that it all
+concentrates on the left, leaving the upp and right side completely
+open for the build up of MinD.  \fixme{Still dont quite get it but
+  take a look at the other simulations and come back.} Actually, you
+can see this effect very slightly watching the 98 shape, between the
+center cap and the right corner.
+
+%% \begin{center}
+%%   \begin{figure}
+%%     {\includegraphics[width=\paperwidth]{../data/shape-randst/plots/image-plot_E--randst-25-602-602-9900-1500}}
+%%     \caption{Attempt at adding image plot to paper.}
+%%     \label{image-plot}
+%%   \end{figure}
+%% \end{center}
 \subsubsection{Randst-96-Star}
@@
 proteins spend a majority of time at the very ends of the cell.
-
-\subsubsection{Randst-99 our A shape}
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
-  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
-  \caption{Total protein fluctuation in the A shaped shape.  The vertical axis shows stacked the total number
-    of proteins that are of four different compound stages and in the
-    different sections of the cell.}
-  \label{total-oscillation-randst-96-plot}
-\end{figure}
-Our animations for this plot show a very interesting pattern.  The
-maxima oscillates from the right corner to the top corner, then
-\emph{back to the right corner} then to the top corner again, then to
-the left corner, then back to the top, then to the left, then to the
-top again, then back to the right side.  It's fascinating that there
-must be two back and forth motions before proceeding to the other side
-\fixme{would this happen over and over or would there be a chaos,
-  breakdown sort of thing at some point.  Need longer sim}.  The
-animations show that when there is a maxima in the center, if it is a
-maxima that is on the right side of the center upper cup then this
-maxima will be followed by a maxima in the lower left corner.  This
-maxima in the lower left corner (immediately following the one on the
-right side of the upper cup) will reside for a bit longer than the
-left corner maxima preceding it.  These longer residing maxima will
-then be followed by a switch, to the right corner, with a short less
-intensive maxima traveling through the center.  The MinE shows the
-same pattern. So what does this say, keeping in mind our model of MinD
-diffusing and MinE comming in to eat it away?  MinD starts in the
-lower left, diffuses up and maximizes on the right side of upper cup.
-Why right side of upper cup?  Because there is more MinE on the left
-side then on the right side of that upper cup, because MinE has just
-spent time coagulating on left corner wall because there was more MinD
-there.  The MinE attaches to the MinD on the membrane and begins to
-release it.  Why at that point does the MinD go back to the left
-corner?  When the MinE eats away at the wall bound MinD it starts at
-te edges and moves in.  There's one frame where the MinE has maxima on
-either side of the MinD maxima on the right side cup.  The center of
-the cup is a little further away so it attaches to these out ridges
-first and then moves in.  After it eats at the corners and starts
-moving in why does the MinD go back to the left corner?  Watching the
-cytoplasmic MinE, something very interesting: It as well maximizes
-twice in one corner, but in between the two maximizations it has a
-smaller maxima in the other corner.  So when the MinD is getting eaten
-away from the top cup, the minE is moving over to maximize in the
-opposite corner.  Why does it maximize there? there are more minD on
-the membrane to attach to on the left, so it can diffuse further down
-into the corner.  Want to be able to construct a full frame by frame
-picture, with all the proteins layed out top to bottom, each frame
-ontop of its likewise frame.  Actually, you can see this effect very
-slightly watching the 98 shape, between the center cap and the right
-corner.
-
-Also - as to why the proteins like poles and corners.  It's a
-diffusion model, so there's no momentum.  When they are at an end or
-corner, they will go in all directions, and if there's a small hole
-way out, only a small percentage will go down it.  As the others
-attach to the wall, there is a higher chance that diffusing particles
-will attach to that wall instead.
-
-The total
-fluctuation plot shows this double maxima corner pattern, with two
-spikes on the right, then two spikes on the left, then two back on the
-right.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_nATP-randst-25-600-600-9900-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_nADP-randst-25-600-600-9900-1500}
-  \caption{Arrows that connect maxima that are global in space and
-    local in time. The arrow heads touch spatial, time maxima and are
-    adjecent to the tails of arrows that show the very next spatial,
-    time maxima. The proteins shown are cytopasmic MinD-ATP (above) and MinD-ADP (below).}
-  \label{arrow-plot-randst-99-plot}
-\end{figure}
-Figure \ref{arrow-plot-randst-99-plot} shows maxima that are global in
-space and local in time.  It is interesting that the MinD-ATP, the
-stage that immediately proceeds attachement to the wall, show maxima
-in one base corner of the A shape and then immediate maxima in the
-other base corner, skipping any maxima steps in the middle (the top of
-the A), while the MinD-ADP, the stage that has just left the wall,
-shows no such behavoir.  Every base corner maxima is followed by a top
-corner maxima, with very obvious symmetry.
-
-%% \begin{center}
-%%   \begin{figure}
-%%     {\includegraphics[width=\paperwidth]{../data/shape-randst/plots/image-plot_E--randst-25-602-602-9900-1500}}
-%%     \caption{Attempt at adding image plot to paper.}
-%%     \label{image-plot}
-%%   \end{figure}
-%% \end{center}
 

### 2013-10-13 paper/paper.tex
Updating paper and data and plotting Tested everything on node32.

@@
 
-\begin{table}
-  \begin{tabular}{|r|c|c|c|l|}
-    \hline
-    Length($\mu$) & 2.50 & 3.00 & 4.00 & 5.00\\
-    \hline
-    Period(sec) & sim & 33 & 38 & 48 \\ \cline{2-2}
-    \hline
-  \end{tabular}
-  \caption{Period According to Pill Length}
-  \label{table-p}
-\end{table}
-
 This simple model is a good starting point for observing in detail the
@@
     of the concentration of proteins in different stages over time.
-    The density of proteins are integrated along the axis
-    normal to the page. The frames occur 2.5 seconds apart.}
+    The density of proteins are integrated along the axis normal to
+    the page. The frames occur 2.5 seconds apart. \fixme{this looks
+      assymetric! That's a big problem.}}
   \label{image-p}
@@
 %% \end{center}
+
+\subsubsection{Randst-97-}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-600-9700-1500}
+  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
+  \caption{Total protein fluctuation in the sideways flying saucer
+    pancake cell shape.  The vertical axis shows stacked the total
+    number of proteins that are of four different compound stages and
+    in the different sections of the cell.}
+  \label{box-97}
+\end{figure}
+
+Early on in its simulation the sideways flying saucer pancake shape
+shows a clear breakdown of an unstable equilibrium oscillation.  We
+have set the intial conditions so that MinD density is highly
+concentrated to the left of a dividing line that runs parrallel to the
+left vertical side.  For the first number of oscillations the maxima
+trade off right to left, from a high peak in the rightward middle
+compartment to vertically opposed peaks in the poles of the long axis
+of the cell.  This is seen in the first part of Figure~\ref{box-97},
+where the lower and upper sections peak in unison, and the middle
+right section peaks $\pi$ radians removed from these.  After a few
+oscillations the back and forth oscillations tip toward the vertical
+direction and the system loses its initial oscillation pattern.  It
+falls quickly instead into a back and forth pattern between the two
+opposing endcaps.  The oscillation at this point is reminiscent of the
+pills shape oscillation, once again showing the robust nature of the
+back and forth, two pole pattern.
+
+During each period, directly after one of the polar maxima has
+subsided, there is a small spike with the regular maxima pattern (a
+spike in membrane bound MinD:ATP immediately followed by a spike in
+membrane bound MinD:MinE:ATP) seen in the small middle right
+compartment section.  The animations show that the MinD, oscillating
+back and forth between the upper and lower poles, seems to catch and
+lag in the indentation for a bit before moving on.  Once again the
+positive radius of curvature acts as an attractive place for MinD to
+cluster on the walls, and it is not released to move on through the
+cytoplasm again until MinE has formed its ring and completely reacted
+it away.
+
 \subsubsection{Randst-96-Star}
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-700-700-9600-1500}
   %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
@@
     in the different sections of the cell.}
-  \label{total-oscillation-randst-96-plot}
+  \label{box-96}
 \end{figure}
+
+This clover shape finds a regular oscillatory behavoir after about
+seven periods that consists of two maxima that peak regularly in the
+corners accross from each other at the same times (Figure
+\ref{box-96}) and then again opposing maxima that peak at the same
+time in the other two corners.\fixme{should try some different
+  starting conditions with this to see if there's another patter.}
 
@@
 
-\subsubsection{Randst-97-}
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-600-9700-1500}
-  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
-  \caption{Total protein fluctuation in the sideways flying saucer
-    pancake cell shape.  The vertical axis shows stacked the total
-    number of proteins that are of four different compound stages and
-    in the different sections of the cell.}
-  \label{total-oscillation-randst-97-plot}
-\end{figure}
-
-The sideways flying saucer pancake shape shows a truly interesting
-breakdown of an unstable equilibrium oscillation.  For the first
-number of oscillations the maxima trade off right to left, from a high
-peak in the leftward compartment to vertically opposed peaks in the
-poles of the long axis of the cell.  This is perhaps due to the fact
-that the starting density is highly concentrated to the right of a
-dividing line that runs parrallel to the right vertical side.  After a
-few oscillations the back and forth oscillations tip toward the
-vertical direction and the system loses its initial oscillation
-pattern.  The total MinD animation shows that it falls quickly instead into a
-back and forth pattern between the two opposing endcaps, skipping
-right over the middle indentation.  The oscillation at this point is
-reminiscent of the pills shape oscillation, showing the robust nature
-of the back and forth pattern.
-
-Figure \ref{total-oscillation-randst-97-plot} shows between the top
-right and top left sections a pattern very close to the pattern seen
-in the pill shaped oscillations, with sharp spikes in wall attached
-MinD-ATP followed by lesser spikes in wall attached MinD-MinE-ATP,
-follwed by the other end showing a similar behavoir pi radius later.
-It is interesting to observe the middle section and the middle
-leftward indentation as well.  It can be seen that the MinD-ATP shows
-moderate spikes in between the spikes on the top and the bottom,
-showing that the proteins are traveling through this section, but
-interestingly the left middle indentation shows this spike
-consistently later than the right middle section. As the protein
-travels back and forth through the cell, there is a certain amount of
-lag in the middle indentation.  The system gets caught there for a
-little bit before moving on.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_ND-randst-25-800-600-9700-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_E_NDE-randst-25-800-600-9700-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-E_nE-randst-25-800-600-9700-1500}
-  \caption{Arrows that connect maxima that are global in space and
-    local in time. The arrow heads touch spatial, time maxima and are
-    adjecent to the tails of arrows that show the very next spatial,
-    time maxima. The proteins shown are wall attached MinD-ATP (top),
-    wall attached MinD-MinE-ATP (middle), and cytoplasmic MinE (bottom).}
-  \label{arrow-plot-randst-97-plot}
-\end{figure}
-
-Figure \ref{arrow-plot-randst-97-plot} shows three arrow plots for
-this shape of cell.  It's interesting that wall attached MinD never
-have global maxima in the middle flat region of the cell while both
-forms of MinE, the cytoplasmic MinE and the wall attached
-MinD-MinE-ATP, have a number of maxima in this region of the cell.  It
-seems that the MinE never stray far from the middle of the cell - they
-approach the ends and react with the other proteins, sticking for a
-while on the walls.  In order for a cytoplasmic MinE to reach the very
-end, it must pass a large amount of opportunity to react with MinD.
-\fixme{I stopped writing this reasoning because I'm not sure it's
-  valid.  Interesting thoug.  Look at this more.}
-
-\subsubsection{Randst-98-C-Reminiscent of Mannik's cell}
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-800-9800-1500}
-  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
-  \caption{Total protein fluctuation in the manniks squished cell
-    shape.  The vertical axis shows stacked the total number of
-    proteins that are of four different compound stages and in the
-    different sections of the cell.}
-  \label{total-oscillation-randst-98-plot}
-\end{figure}
-
-Our animations and total protein fluctuation plots (Figure
-\ref{total-oscillation-randst-98-plot} for our C shape (reminiscent of
-the flattened cell shown in Mannik's work) shows a very regular,
-stable, simple oscillation pattern.  There are two clear ends of this
-cell that oppose one another, and the protein maximum travels to one
-end, where it reaches a peak, then travels through the cell to the
-other end, reaching another peak, and then repeats the process.  In a
-way it is similar to the simple pill shapes, in that there are two
-clear endcaps and a middle section (that is in this case bends and
-curves).  The protein fluctuation plots show our familiar pattern of
-high spikes in wall attached MinD-ATP immediately followed by spikes
-in wall attached MinD-MinE-ATP, followed by a drop in both as the
-proteins move towards the other side.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_ND-randst-25-600-800-9800-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-D_ND-randst-25-600-800-9800-1500}
-  \caption{(above) Arrows that connect maxima that are global in space
-    and local in time. The arrow heads touch spatial, time maxima and
-    are adjecent to the tails of arrows that show the very next
-    spatial, time maxima. (below) An time averaged plot of the same
-    proteins in the same cells shape.  The protein that is shown is
-    wall attached MinD-ATP.}
-  \label{arrow-plot-randst-98-plot}
-\end{figure}
-
-The arrow plot shown here is typical of mannik's squished adnormal
-shape.  It shows the protein maxima moving through the cell from one
-end to the other end, and back again.  The effect of this movement can
-be seen in the time averaged plot directly below the arrow plot.  The
-proteins spend a majority of time at the very ends of the cell.
-
 \section{Interpretation of Data}
@@
 
-\section{Introduction}
-\fixme{I need a lot of references here!!!}
- need a lot of references here!!!  (And the writing is just
-terrible) It is vital that during the process of bacterial cell
-division that the cell avoid minicelling, or splitting into daughter
-cells with lopsided volumes.  During this process a long FtsZ polymer
-chain develops on the cell wall in the center region of the cell
-acting as a guide for the cell splitting process.  in simulation that a system of Min protein interaction within
-the cell will lead to a natural oscillation of the MinC protein, which
-exhibits an aversion to the FtsZ polymer, from one cell end to the
-other that will leave the center free of any build up of MinC.  This
-will allow for the PtsZ chain to develop in the center and not at the
-ends, where the two nucleiods are housed.  The interaction takes place
-between MinE,MinD, and MinC, which naturally associates with MinD.
-
-A significant amount of work has been done in simulating and studying
-the dynamics of the Min protein system and cells. A number of
-different models have been simulated and studied.  They divide into
-two natural groups - stochastic (specific protein positions are
-tracked at all times) and deterministic (protein averages are used
-along with rate constants to simulate interaction). They also split up
-into other groups - cooperative attachement (MinD on the cytoplasm is
-attracted to other MinD on cytoplasm, shown by non-linear attachement
-on walls experimentally).  Huangs' 2003 and Meinhardt and De Boer 2001
-are of this type.  Huang's seuccessfully predicts that breakdown of
-striped oscillation pattern occurs when exchange of ATP for ADP bound
-to cytosolic MinD is not too fast.  There is as well aggregation
-current models, characterized by the proteins moving along the
-membranes in a way so that they're attracted to other proteins on the
-walls.  We are simulating Huang's model, so a further test of the
-robustness of the oscillations with wild type values, and as well
-compare against exprimental evidence given by mannik.  We use Huang's
-becuase of the success so far, and then also the other type
-(aggregation current models) depend on there being limited binding
-spots on the membrane for minD.  This author also states that the
-deterministic models have largely varified stochastic model
-results.\cite{kruse2007experimentalist}
-
-It has also been observed that the spatial characteristics of
-oscillation is not effected by broad ranges of tempurature changes
-(although the frequency does vary) allowing for very robust cell
-division that is not dettered by environmental tempurature
-fluctuations. \cite{touhami2006temperature}
-
-We wish to subject Huang's seminal model to more harsh geometrical
-tests of robustness and compare results to the new experimental
-results of Mannik.\fixme{this link doesn't work = cite{mannik2012robustness}}
-
-Models also introduce the affect of cardiolipin, an anionic
-phospholipid that collects on regions of high negative curvature (the
-membrane of the cell poles) and attracs MinD, since it had been
-observed that minD binds preferetntially in regions enriched with
-these phospholipids \cite{drew2005polymerization}\cite{cytrynbaum2007multistranded}. However, this
-mechanism of combined clustering, phospholipids and MinD has not been
-observed in real cells.  \cite{halatek2012highly}
-
-A mathematical model that describes the building of the FtZ polymer
-along the midsection cell membrane.  Solved numerically using a finite
-volume method. \cite{zhang2013mathematical}
-
-Variations of the Huang 2003 model that attempt to more accurately
-account for the details of molecular interaction, focusing on the
-mechanism of MinD binding to other MinD on the cell membrane.  These
-models confirm the major results obtained by Huang's model, while
-showing some interesting additional features.
-.\cite{drew2005polymerization}\cite{fange2006noise}\fixme{this last
-  reference sounds like maybe the stochastic changes they made to the
-  model cause the simulations to be more accurate in certain, odd
-  cases.  Should we have used this model?}
-
-More general biochemical models have also been used to study the MinD
-system and show consistent results.\cite{arjunan2010new}
-
-Stochastic models that area based on Huangs mean-field model but take
-chemical fluctuations into account in a discrete fashion show the same
-results as Huang's simulations in ordinary cell shapes, and better
-predict experimentally observed oscillations in round cell
-shapes.\cite{fange2006noise}
-
-Purely theoretical models have been constructed that rely on min
-protein's mobility on the membranes and tendency to cluster
-together.\cite{kruse2002dynamic}\cite{howard2005cellular} \fixme{read
-  and write about these}
-
-Huang has also made simulation studies of round cell shapes and shown
-that oscillations occur in these cell shapes, and that their behavior
-depends on the radius of the shape. They show that the Min proteins can
-select the long axis of the nearly round shapes based soley on the
-geometry of the cell.\cite{huang2004min} \fixme{definately want to get
-  this paper and read it}
-
-Previous experimental studies have shown that MinC, known to inhibit
-the FtZ polymer, exhibits an oscilatory, pole to pole behavoir in conjunction with
-MinD and MinE. \cite{hu1999topological}
-
-The function of the Min system might not be restricted to proper cell
-division.  There is evidence that it is instrumental in the
-dissasembly of the cytokinetic ring directly after cell division,
-insuring that cell division takes place only once per cell
-cycle. \cite{van2010mincdj}
-
-Other simulations have been shown to exhibit oscillations in the
-cylinder shaped cell.  While Huangs' 2003 study involves stages of
-protein compounds (attached proteins), the differential equations
-governing protein mobility in this study are designed with free
-unattached proteins who interact with eachother.  Huang does cite this
-paper so we can say that he followed and improved upon these
-simulations.\cite{meinhardt2001pattern}
-
-The MinE has been observed in the center of the cell and it's ability
-to counteract what's refered to as MinCD cell division inhibitor has
-been known.  It's been found that its not stationary but undergoes
-repetitive movement back and forth. \cite{fu2001mine}
-
-Previous studies have been made of the Min system's associtation with
-the cell membrane
-\cite{hsieh2010direct}\cite{mileykovskaya2003effects}. Previous
-studies have shown that phospho lipids on the cell wall attract
-MinD/MinE proteins and reduce ATPase activity.  It's further been
-shown that the proteins interact preferebly with anionic lipids that
-are localized at the poles of the cell.\cite{renner2012mind}
-
-Expreiemntal studies have been made of the process of septum formation
-in the middle of the pill shaped cell and its effect on MinD
-oscillations, leading to the conclusion that it is geometry of septum
-formation that allows for the creation of two MinD oscillation systems, one
-in each daughter cell. \cite{juarez2010changes}
-
-It is vital that the process of bacterial cell division result in a single
-nucleiod in each daughter cell.  The cell must avoid minicelling, or
-splitting into daughter cells with lopsided volumes.  One of the mechanisms
-the cell employs in order to avoid this is to allow a long FtsZ polymer
-chain to develop on the cell wall in the center of the cell.  This chain
-acts as a guide for the cell splitting process.  Huang et all have shown in
-simulation that a system of Min protein interaction within the cell will
-lead to a natural oscillation of the MinC protein, which exhibits an
-aversion to the FtsZ polymer, from one cell end to the other that will
-leave the center free of any build up of MinC.  This will allow for the
-PtsZ chain to develop in the center and not at the ends, where the two
-nucleiods are housed.  The interaction takes place between MinE,MinD, and
-MinC, which naturally associates with MinD.
-
-Mannik et all have shown that the formation of irregular cell shapes
-adversly effects the Min system's ability to maintain their regular
-oscillatory behavior (cramming into spaces).
-
-\subsection{What is the MinD system and why is it important?}
-
--Systm of proteins in E.Coli and other cells.
--Theorized to be instrumental in cell citokenisis. Reference experiments
-\subsection{How proteins move in cell}
--Reference experimental showing proteins oscillating
--Reference theory showing difEQ model shows oscillations
--Reference Mannik shoving into crevices.
--Worthwhile studying effect of walls shape on the movement of cells
-(Sign post of what to expect from this paper)
-
-\section{Methods and Initial Conditions}
-\subsection{Mathematical Model} %shouldn't be a scripty mu
-The model for the behavior of the MinD and MinE proteins inside the cell
-implemented the same set of 5 reaction-diffusion equations described in the paper
-by Huang et al (equations 1, 2, 3, 4, and 5). A 3d grid was constructed in
-cartesian coordinates with a grid spacing of .05 $\mu$m. From there, we
-were able to define a cell shape on the grid, and solve the
-reaction-diffusion equations numerically to observe the time evolution of
-the MinD and MinE concentrations inside the cell.
-
-Our simulation used the same diffusion constants and reaction rates as
-Huang et al, which are
-
-\begin{gather*} %format better
-  \mathcal{D}_D = \mathcal{D}_{E}  = 2.5 \mu \textrm{m$^2$ / sec}, \\
-  \sigma_D^{\textrm{ADP $\rightarrow$ ATP}}  = 1/\textrm{sec},  \sigma_D = 0.025 \mu \textrm{m/sec}, \\
-  \sigma_{dD}  = 0.0015 \mu \textrm{m$^3$/sec}, \\
-  \sigma_{de}  = 0.7/\textrm{sec}, \sigma_E = 0.093 \mu \textrm{m$^3$/sec}.
-\end{gather*}
-
-To test our computational model, we implemented a pill shaped cell, and
-tested using the same cell parameters as Huang et al, which were a radius
-of 0.5 $\mu$m in the middle and at the spherical endcaps, and two different
-cell lengths of 4 $\mu$m and 10 $\mu$m. We found the same type of
-oscillations as in their paper using these initial conditions, verifying
-that our model works as intended. Below are snapshots of MinD and MinE
-concentrations at 5 second timestamps in the 4 $\mu$m cell:
-\newline
-\newline
-[insert 5 second time stamps of 4 $\mu$m sim]
-\newline
-\newline
-We then began to define other, non-traditional cell shapes for the purpose of
-modeling squished and perturbed E. coli cells, which were created
-experimentally in Mannick et al. To achieve this, we went with a
-cartesian lattice rather than the cylindrical lattice used in Huang et
-al's simulations, as it allows for more flexibility in defining the
-cell shape. Some of the cell shape models included a flattened pill
-(stadium shape), an ellipsoid, a spherical cell, and various randomly
-generated smooth shapes, such as those in the figures below.
-\newline
-\newline
-[insert memf print of 2-3 cell shapes]
-\newline
-\newline
-To interpret the results, we generated several different plot views of
-the printed simulation data. These plots included a time averaged view
-of the protein densities in the cell; a plot tracking the location of
-protein concentrations that were global maxima in space and local maxima in
-time; and an animated view that showed the actual dispersion of
-protein concentrations in the cell over time.
-\section{Specific Results}
-%-Datahjhuj and plots that show concrete results. Pill normal is for the establishing that we have what works, reference  other paper, then modify, is the idea.
-\section{Pill Shape}
-\fixme{Be more exact about what exactly Nd is versus nATP, in terms of
-  the unit and dimensions.  The plotting may need to be changed}
-Figure %%\ref{frequency-plot-40-20-0-0-150} shows the protein density
-fluctuations at a point in space adjecent to a polar wall.  At each
-collection of peaks the proteins reach their zenith in an order that
-agrees with the qualitative picture described by
-Huang\cite{huang2003dynamic}, except for nADP peak.  The peaks start
-with a maxima of ATP-MinD accumulating at the walls \fixme{Need a
-  better way to refer to compounds}. This peak is followed by a peak
-in Nde, or ATP-MinD-MinE, as the cell is converted on the wall from
-the former to the latter compound.  As this compound splits apart and
-leaves the wall we see a peak in nE, or MinE in the cytoplasm.  This
-is then followed by a broader peak in nATP, or the MinD-ATP compound,
-as minD-ADP is (changed but I forgot the name for it) into minD-ATP in
-the cytoplasm.  The minD-ATP naturally diffuses away from the pole,
-which is shown by the broad nature of this peak.  All of these peaks
-fit the qualitative picture except for the sharp MinD-ADP peak.  One
-could except that it is a sharp peak, meaning that the MinD-ADP proteins
-do not last in the cytoplasm for very long before they are converted
-(once again forgot the name) into MinD-ATP.  The location of the peak
-in the time dimension is troubling, however, since that we would
-expect it to occur just after the peak in Nde, since the wall-bound
-MinD-ATP-MinE proteins are the ones that split up and leave the wall,
-creating both the MinE and the MinD-ADP.  One would expect to see the
-minD-ADP peak to coincide in time with the minE peak, but it instead
-coincides with the wall-bound MinD-ATP-MinE peak. (Although you can
-maybe sort of convince yourself otherwiase, really looking at it).
-
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-p/plots/frequency_plot_all_middle-p-40-20-0-0-150.pdf}
-%%   \caption{A comparison of protein density fluctuation with time
-%%     against the polar wall and at a point in the center of the
-%%     z-length and adjacent to the wall, in the cytoplasm.  The cell is
-%%     pill shaped and has dimensions of 4$\mu m$ by 2$\mu m$.  }
-%%   \label{frequency-plot-40-20-0-0-150}
-%% \end{figure}
-
-The theory states that the aversion of the FtsZ polymer to the MinC
-protein is responsible for the FtsZ polymer setting up in the center
-of the cell as opposed to at the cellular poles.  The MinC protein in
-turn natrually associates with the minD protein that is modelled in
-Huang's differential equations.  \fixme{look this up and write this
-  again} The theory is dependent on there being a significant
-difference in protein density between the center and polar regions. It
-is worthwhile examining this difference in detail.  Figure
-%%\ref{frequency-plot-40-20-0-0-150} shows a comparison of density
-fluctuation over time at a point adjacent to the polar cell wall and
-at a point adjacent to the cell wall in the center region of the cell.
-The different proteins show different relationships between their
-maxima and minima.  The MinD-ADP show sharp spikes at the poles and
-much smaller oscillations at in the middle.  The values at the poles
-are always greater than those in the middle, and the polar peaks
-exhibit densities that are roughly 2.5 times greater than the maxima
-in the center (\fixme{this factor and the following factors will be put
-  into a table of comparisons for each protein and for the different
-  cell sizes}).  The MinD-ATP densities show a very different trend.
-For these it is the center density that is almost always greater than
-the polar density.  The difference in density at the pole versus the
-middle is a factor of roughly .85 (once again we'll do this more
-officially in a table).  The MinE is similar to the MinD-ADP
-comparison.  It shows a difference in maxima by a factor of roughly 2.
-The MinC protein is associated with the minD protein, so perhaps the
-most important camparison is between the nfl-MinD (MinD protein in all
-its forms) at the ends and in the center of the pill.  This shows
-sharp spikes at the pills and a maxima difference factor of roughly
-1.25. \fixme{I'd like to analyze further what this means for the FtZ
-  polymer.  Would a difference like this really have a big effect?
-  What sort of effect should it have, looking at experimental data?
-  One thing is that Mannik (is it Mannik?) genetically deletes the
-  MinC protein and they get 73 percent proper cell division.  It
-  really would be good to do a more extensive analysis here,
-  referencing what other papers say about this.}
-
-It would be good here to add the time map plots and discuss the idea
-about the proteins spending most of their time in the center of the
-cell.
-
-Figure also shows that the middle
-density oscillates at a frequency that is twice that of the polar
-regions, which is to be expected considering the symmetry of the
-center compared to the that of the polar regions.  Also, the
-difference between density maxima and minima each oscillation is
-smaller for the middle points than for the polar points.  This is
-evident from simply watching the simulation movies - the fluctulations
-are more extreme in the polar regions.
-
-Add a table here that shows the period of oscillations versus the cell
-dimensions.  Do the mathematical solution of the differential
-equations for an infinite long cylinder with different widths to see
-how fast the mxima move and compare (Dr. Roundy says that making the
-radial speed infinite would help.
-
-Pill Normal section -
-Our goal with this project was to test whether or not the computational
-model developed by Huang et al was consistent with the newer experimental
-results (squishing E Coli) produced by Mannick et al. We generally see
-that:
-
-- Protein concentrations bounce around to areas with high curvature.
-- - example: nflD randst 1 6 6 99 tri-polar zones with tri-polar concentrations
-- - nflE the same
-- There is some time delay between where different protein types appear.
-
-The pills with larger cylindrical widths, 4.00 3.00 (the wider pill shapes)
-exhibit oscillations with maxima reached on either side (half period
-times) 30s, 70s, 110s, so first half oscillation occured in 30s, the
-next two in 40s
-
-The 4.00 2.00 pills exhibit a similar pattern, but max out at times
-25s,55s,85s,115s, so thirty seconds each half period.  Seemed once again that
-the first oscillation had a higher max density, then settled down.  I
-wonder if extremely increasing the starting condition density
-lopsidedness will still yield a settle down pattern with the same max
-densities?  Is this dependent on shape/size?
-
-The 4.00 0.50 pill seemed to show oscillations of 20 second half
-periods very consistently.  Density maximum did not seem to lose
-intensity.  Seemed to be the same each oscillation.
-
- Also with this, when look at the periods and max
-denisty/min density ratio, consider the size dimensions of the pill
-shape and see if can see a mathematical relation.
-
-The nflE 4.00 0.50 shows a very large difference in center highest density
-versus pole highest density (during a maxima).  Is this perhaps the
-protein that's more important.
-
-Looking at the extrema plots - one very interesting thing is the 4.00
-2.00 ATP extrema, which shows the extrema only in the center of the
-cell.  The other proteins for this shape show the extrema to be at the
-ends.  Also, it seems the 4.00 3.00 cell shapes for these plots are
-missing.  Very interesting to see if there is a certain protein that
-has its maxima in the center of the cell, while the others have maxima
-elsewhere.  Tells a story that could maybe relate to the other shapes.
-
-Also, try starting the cells with density only in the corner.  Now the
-extrema go down the center of the cell, see if there would remain a
-lopsided nature of the oscillations if you started it like this instead.
-
-The very long cells have very long periods
-
-The time map plots seem inconsistent in that some show the highest
-densities on the poles, some in the centers, some on just one pole.
-For these want to run starting from a time when the proteins are
-evenly spread out (so between two maxima) and stop at a similar pointe
-at the end.
-
-The time map plots that I believe though sometimes show that the max
-density time-wise is actually in the middle of the cell!  Make sure we
-have a good, longer view of this being true.
-
-Important
-
-Pill Short -
-     -Know how short is too short
-
-Randst 99 -
-
-\section{Randst shape}
-whats the difference between the extremes in density at different
-places (like the density max at the poles and at the rims in the
-center).  Still need to do this.
-
-There are sudden bursts in the nflE protein plots, at the poles. Their
-density maxima build very quickly then diffuse more slowly.
-
-\subsection{randst-96}
-The star shape (randst-96) Shows oscillations in nflD horizontally,
-two poles to two poles.  There is sometimes a small amount of lag
-between the upper maxima moving horizontally and the lower.  Half
-periods take roughly 25s. Dimensions are roughly 5.00 by 5.00?  Check
-this.  The nflE short bursts do develop lag between when the top and
-the bottom go off.  Should coordinate this with the nflD lag.
-
-Tried to see if there is a time correlation between nflE and nflD but
-the maxima seem to appear in the poles at roughly the same time.
-
-Watched Nd and nE simulations next to each other at same time.  Both
-have maxima that build up right at the walls (in the corners) and then
-subside.  It's clear that the nE density bursts appear directly after
-the Nd bursts.  The Nd bursts are subsiding as the nE bursts are
-rising up.  The Nd reaches a time maxima just before the nE.  This is
-true in each corner, so that when the maxima are lopsided top to
-bottom - when the top right corner maximizes first, say, the interplay
-between nE and Nd remains very clear in those corners where and when
-maxima occur.
-
-Watched nATP and nADP together.  nATP maxima seem to follow slightly
-after nADP maxima.  This is not surprising since in rotation nATP
-follows after nADP.  nATP maxima is more spread out - inbetween pole
-maxima there is more spread out maxima in the center.  This should
-show itself in the time map plotting.  About this - the percentage
-difference seem to be the same between the non-max places and max
-places, roughly, its just that the nATP seems to have a max region
-that covers a wider area throughout the oscillation (or at least in
-between the maxima points in the oscillation).
-
-Also watched the Nd next to the nATP.  The Nd maximize more extreme in
-the corners up against the walls.  The nATP density follows the Nd
-maxima, it looks like the nATP maxima follows the Nd.  So if the Nd
-appears somewhere (in a corner) then the nATP will travel there to
-follow.
-
-\subsection{randst-97}
-Randst 97 nflE starts with small maxima, not much difference at all,
-then actually builds to high maxima at the poles.
-\subsection{randst-99}
-Randst 99 (sort of triangle) is roughly dimensions of 3.5 by 3.5?
-nflD oscillations appear to be half periods of 25s as well.  Maxima appear
-at the poles and in the interim there are weak maxima in center pole.
-\subsection{randst-98}
-Funny randst shape 98 shows nflD oscillations of about 30s or so.
-
-nADP and nATP side by side.  nADP maximizes in the corners right
-before the nATP maxima follows.  Makes sense looking at equations.
-Once again the nATP maxima is more spread out, where maxima in nADP
-appear more just at walls.
-
-Nd and nATP side by side.  Nd maximizes at walls and the nATP moves in
-to follow it
-
-Nd and nE side by side.  Nd maximizes in corners and then the nE also
-maximizes in the corners.  The nE maxima appear in these sort of quick
-bursts in the corners, along with a slower broader movements away from
-that corner after the burst and into the next, where another sharp
-burst occurs.  The Nd bursts occurs after the Nd as subsided in that
-corner, and really by the time the burst maximizes, the Nd is already
-on its way over and starting to build on the otehr side.
-
-Randst nflD doesn't show much oscillation at all, but we start it so
-that the density is not max at the pole.
-
-%%\begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-80-60-980-150.pdf}
-%%   \caption{randst 98}
-%%   %\label{fig:pair-distribution-3}
-%% \end{figure}
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-970-150.pdf}
-%%   \caption{randst 97}
-%%   %\label{fig:pair-distribution-3}
-%% \end{figure}
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-960-150.pdf}
-%%   \caption{randst 96}
-%%   %\label{fig:pair-distribution-3}
-%% \end{figure}
-
-Randst 98 -
-
-Randst 97 -
-
-Randst 96 -
-
-Triangle -
-
-\section{Interpretation of Data}
--Discussion of conceptual reasons of why we see what we see
--Plots that are more interpretive (area-rating)
--Some sort of predictive claim?
-
-\section{animate?}
-%%\animategraphics[height=2.8in,autoplay,controls]{12}{../data/shape-randst/plots/movie-density-Nd-96/animate_}{0}{120}
-
-\section{Conclusion}
-
 \end{document}

### 2013-10-13 pyplots/arrow_plot.py

@@ -41,7 +41,7 @@ if load.f_param4 != "94.00":
 for protein in load.proteinList:
     tails = np.loadtxt('./data/shape-%s/%s%s%sarrow-plot-%s-%s-%s-%s-%s-%s-%s.dat'%(load.f_shape,load.debug_str,load.hires_str,load.slice_str,protein,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5))
     tails = [list(element) for element in tails]
-    cut = len(tails)-10
+    cut = len(tails)-15
     tails = [tail for tail in tails[cut:][:]]
     # z_max = max(tails[:][2])
     # z_min = min(tails[:][2])
@@ -90,7 +90,7 @@ for protein in load.proteinList:
         number_ypos = tails[i][1]+.18*dir_y
         plt.ax.annotate('',xy=(tails[i+1][0],tails[i+1][1]),xytext=(tails[i][0],tails[i][1]),
                         fontsize=7,
-                        arrowprops=dict(facecolor='red',shrink=0.01, width=.3, headwidth=5.))
+                        arrowprops=dict(color='red',shrink=0.01, width=.3, headwidth=5.))
         plt.ax.text(number_zpos,number_ypos,"%d"%(i+1),fontsize=30,fontproperties=font,color='red')
     cell_membrane[cell_membrane>0] = 1
     cell_x = np.linspace(0,load.dx*len(cell_membrane[0,:]),len(cell_membrane[0,:]))
@@ -103,7 +103,7 @@ for protein in load.proteinList:
     plt.ylim((0,load.dx*cell_membrane.shape[0]))
     plt.xlabel("Z grid position")
     plt.ylabel("Y grid position")
-    plt.title("Local temporal maxima, global spatial maxima view of %s"%(protein))
+    #plt.title("Local temporal maxima, global spatial maxima view of %s"%(protein))
     plt.savefig(load.print_string("arrow-plot",protein))
 
 plt.show()

### 2013-10-13 pyplots/box_plot.py

@@ -140,18 +140,21 @@ def main():
             if "E_" in proteinType:
                 plotNameList_E += ["%s-%s"%(box,proteinType)]
 
-    print plotNameList_D
+    print ""
+    print "plotNameList before ", plotNameList_D, "\n"
     new_plotNameList_D = [0]*len(plotNameList_D)
     P_Ord = [3,0,2,1,7,4,6,5,11,8,10,9]
-    if load.f_param4 == '97.00' or load.f_param4 == '96.00':
-        P_Ord = [3,0,2,1,7,4,6,5,11,8,10,9,15,12,14,13]
+    if load.f_param4 == '97.00':
+        P_Ord = [3,0,2,1,11,8,10,9,15,12,14,13,7,4,6,5]
+    if load.f_param4 == '96.00':
+        P_Ord = [15,12,14,13,3,0,2,1,7,4,6,5,11,8,10,9]
     for i in range(len(P_Ord)):
         new_plotNameList_D[i] = plotNameList_D[P_Ord[i]]
     for i in range(len(plotNameList_D)):
         plotNameList_D[i] = new_plotNameList_D[i]
-    print plotNameList_D
+    print "plotNameList after ",plotNameList_D,"\n"
     plotProteinLabels = ['MinD:ATP (cyto)','MinD:ATP (mem)','MinE:MinD:ATP','MinD:ADP (cyto)']
-    print plotProteinLabels
+
 
 
     #pass plotNameList through stackData to generate the list of line data to be plotted
@@ -173,6 +176,12 @@ def main():
     start = int(tot_time*start_time_as_frac_of_ten/10.0/box_time_step)
     end = int(tot_time*end_time_as_frac_of_ten/10.0/box_time_step)
     (start, end) = find_period(plotCurveList_D[3])
+    if load.f_param4 == '97.00':
+        start_time_as_frac_of_ten = 0
+        end_time_as_frac_of_ten = 2.3
+        start = int(tot_time*start_time_as_frac_of_ten/10.0/box_time_step)
+        end = int(tot_time*end_time_as_frac_of_ten/10.0/box_time_step)
+
 
     #print set(plotCurveList_D[1]).union(set(plotCurveList_D[2]))
 
@@ -239,7 +248,7 @@ def main():
         yweighted = (Y*sectiondata).sum()/sectiondata.sum()
         xweighted = (X*sectiondata).sum()/sectiondata.sum()
         levels = [0.5, 1.5, 2.5, 3.5, 4.5]
[…]

### 2013-10-13 pyplots/density_movie.py

@@ -79,14 +79,14 @@ def contourplt(protein):
         CS = plt.contourf(Z, Y, page, cmap=plt.cm.jet,origin='lower',levels=np.arange(minval,maxval+10,1))
         cbar = plt.colorbar(CS)
         plt.clim(minval,maxval)
-        plt.title(str(protein.protein)+" volume density at time: "+str(k*5)+" sec")
+        plt.title(str(protein.protein)+" volume density at time: "+str(k*2.5)+" sec")
         plt.xlabel("Z position")
         plt.ylabel("Y position")
         plt.savefig('./data/shape-'+f_shape+'/plots/'+load.debug_str+load.hires_str+load.slice_str+'-tmp_%03d'%k+'-'+str(protein.protein)+ \
                         '-'+f_shape+'-'+f_param1+'-'+f_param2+'-'+f_param3+'-'+f_param4+'-'+f_param5+'.png',dpi=50)
 
     #shell command to convert all of the recently generated .png's to a single .gif using convert utility
-    os.system("convert -delay 20 ./data/shape-"+f_shape+"/plots/"+load.debug_str+load.hires_str+load.slice_str+"-tmp_*" \
+    os.system("convert -delay 10 ./data/shape-"+f_shape+"/plots/"+load.debug_str+load.hires_str+load.slice_str+"-tmp_*" \
     +"-"+str(protein.protein)+"-"+f_shape+"-"+f_param1+"-"+f_param2 \
     +"-"+f_param3+"-"+f_param4+"-"+f_param5+".png ./data/shape-"+f_shape \
     +"/plots/"+load.debug_str+load.hires_str+load.slice_str+"density_movie-"+str(protein.protein)+"-"+f_shape \

### 2013-10-13 pyplots/file_loader.py

@@ -71,9 +71,9 @@ class data(object):
                                      (f_shape,debug_str,hires_str,slice_str,protein,f_shape,f_param1,f_param2,f_param3,f_param4,f_param5,file_num))
         dat_filenames = sorted(dat_filenames)
         i=0 #pop the first 10% of file names to let things equillibriate a bit
-        while i<round(len(dat_filenames)/10):
-            dat_filenames.pop(0)
-            i+=1
+        # while i<round(len(dat_filenames)/10):
+        #     dat_filenames.pop(0)
+        #     i+=1
         if (dat_filenames == []):
             print "File loading error: filename list is empty."
             print "./data/shape-%s/%s%s%s%s-%s-%s-%s-%s-%s-%s-*.dat"%(f_shape,debug_str,hires_str,slice_str,protein,f_shape,f_param1,f_param2,f_param3,f_param4,f_param5)

### 2013-10-13 pyplots/image_plot.py

@@ -61,7 +61,7 @@ def build(proteins,proteinList):
     spread = Image.new("RGB", (120+(400-2*cut)*total_length, 300*len(proteins)), "white")
     for i in range(len(proteins)):
         if (proteinList[i]=="ND" or proteinList[i]=="NDE"):
-            maxval = timemax(proteins[i])
+            maxval = timemax(proteins[i])/4
         else:
             maxval = timemax(proteins[i])
         sys.stdout.flush()
@@ -78,7 +78,7 @@ def build(proteins,proteinList):
         #plt.axis('off')
             plt.axes().get_xaxis().set_ticks([])
             plt.axes().get_yaxis().set_ticks([])
-            plt.xlabel('%s  %gs' %  (proteinList[i], float(k*dump_time_step)) )
+            plt.xlabel('%s  %gs' %  (proteinList[i], float(k*dump_time_step)),fontsize=40)
             if (k == int(start_time/dump_time_step)):
                 plt.ylabel('%s' % proteinList[i])
             plt.savefig('./data/shape-'+f_shape+'/pngs/'+load.debug_str+load.hires_str+load.slice_str+'tmp_%03d'%k+'-'+str(proteins[i].protein)+ \
@@ -98,9 +98,6 @@ def build(proteins,proteinList):
                 spread.paste(cropped, (cut+(init_box[2]-2*cut)*k,box[3]*i))
         plt.close()
     spread.save(load.print_string("image-plot",""))
-    #spread.save("data/shape-"+f_shape +"/plots/"+load.debug_str+load.hires_str+load.slice_str+"image-" \
-    #                        +f_shape+"-"+f_param1+"-"+f_param2 \
-    #                        +"-"+f_param3+"-"+f_param4+"-"+f_param5+".pdf")
 
 proteinList = ["nADP","nATP","ND","nE","NDE"]#["nE","nATP","nADP","ND"]#,"NDE"]
 proteins = [0]*len(proteinList)

### 2013-10-16 paper/paper.tex
wrote more paper Tested everything on node31.

@@
   \caption{Total protein fluctuation in the right, middle, and left
-    parts of a equilateral (top), iscoscolese (middle), and 3-4-5
+    parts of an equilateral (top), iscoscolese (middle), and 3-4-5
     (bottom) triangle.  The vertical axis shows stacked the total
@@
 
-The double pole oscillation pattern, where one pole is located in a
+The double pole oscillation pattern, in which one pole is located in a
 single corner of the triangle and the other pole is spread out between
@@
 the walls.  That particular part of the process is therefore
-accelerated, driving the build up of the maxima forward.  The right
-triangle shows a similar pattern.
+accelerated, driving the build up of the maxima forward.
 
-Figure \ref{total-oscillation-triangle-plot} shows the equivalent
-motion and transference between compound states for the triangular
-states as Figure \ref{total-oscillation-plot} does for the pill shaped
-cells.  The equilateral triangular shows that in all three sections
-there is a spike in wall attached MinD-ATP directly followed by a
-spike in wall attached MinD-MinE-ATP.  The pill had shown a similar
-pattern except that the mid section exhibited no such pronounced
-spike.  Interestingly, the right and mid sections show spikes at
-similar times when compared to the left section spikes, which seem to
-oscillate in a manner shifted pi off from the other two.  This
-behavoir shows itself in the animations, which show a relaxation into
-a stable oscillation from a maxima in one corner to a double maxima in
-the other two corners, and back again.  The left section heights are
-roughly twice that of the right section heights.  The simulations are
-started with higher concentrations of proteins in primarily the right
-section, with some overlap into the middle section, so that perhpas
-this oscillation pattern seems reasonable.  However, it's interesting
-to note that the oscillations, started with assymmetric density, do
-not naturally rotate around the corners of the triangle in a circular
-pattern.
+The right triangle shows a similar pattern except that here there is
+an assymetry between the two corners that maximize at roughly the same
+time.  One corner is further from the single maximizing corner and it
+consisitently peaks later.  The MinD simply have further to travel
+before they maximize there.
 
-It seems as well that there is a desired oscillation maxima for the
-particular shape and size of the cell, as can be seen by the
-relaxation, over the first four periods, to a regular maximal height
-of the right and left sections' total protein at the height of each spike.
+For these three sizess and shapes there is not sign that the
+oscillation patterns once they are set will break down.
 
-\fixme{Note to make sure I'm interpreting the iscosolese triangle data
-  correctly: the triangle sides are 5,5,3, and the higher density
-  starts in the corner that is opposite the short side.  This corner
-  is covered by the right section.  I've verified this by looking at
-  the protein\_microscopy and drawing a little picture, which is on my
-  desk...if you dare look for something on my desk!!!}  The iscosolese
-triangle starts its simulation with a higher concentration of protein
-in the section that is opposite the shorter side.  It quickly relaxes
-into a stable oscillation pattern.  This pattern shows that right
-corner section regularly has higher spikes in total protein than the
-other sections, and that its spikes appear one pi removed from the
-spikes for the other two sections.  This a similar behavoir to that
-which is seen in the equilateral triangle, differening in that it
-converges more quickly towards this behavoir and that it shows a
-greater exageration in the height of protein buildup in the right most
-section.
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-601-601-601-1500}
+  \caption{Total protein fluctuation of an equilateral triangle with
+    larger dimensions (each side is roughly $6\mu m$.  The vertical
+    axis shows stacked the total number of proteins that are of four
+    different compound stages and in the different sections of the
+    cell. The time limits have been set to show the broken down
+    section of the simulation.}
+  \label{box-triangle}
 
-\fixme{Note on interpretation of 3-4-5 triangle: the higher density
-  starts to the right of a vertical line that is parrallel to the
-  second longest side in the triangle (the longer of the two
-  non-hypotonuse sides).  This means the higher concentration covers
-  the right angle and also the smaller angle in the triangle} The
-3-4-5 triangle exhibits behavoir that I need more data to properly
-observe.  I does not converge as quickly as that for the iscosolese or
-equilateral triangles.
+The larger equilateral shape shows the same pattern as the smaller
+version does only until fifteen periods, at which point there is a
+breakdown of the oscillation pattern.  During the last three stable
+periods, the single maximizing corner, the lower left section in the
+figure, has a lower peak each period as the membrane bound MinD:ATP in
+the other corners lag more and more before being eaten away by the
+MinE.  Finally these maxima lag so much that they break down the
+regular pattern.  There then occurs about five periods of semi chaotic
+behavoir, until it settles back into another stable oscillation that
+is similar to the original one, except that a different corner has
+been chosen to be the singlular maxima (the right section in the
+figure), while the other two corners maximize at the same time.  This
+interesting breakdown and recovery shows both the robustness of the
+double pole oscilatory tendency and the importance of required
+distance of travel for the different proteins.
+
+\end{figure}
+
+Fifteen
 
@@
 
+Simulations of this shape that has the same height and dimensions .6
+times the size do not exhibit the same pattern.  In these the MinD
+maxima oscillate quickly back and forth between the two lower corner
+poles.
+
+Simulations in which the two planar dimensions are 2 and then 3 times
+the size (cells roughly $6\mu m$ and $9\mu m$, respectively, from top
+to bottom) show no stable regular periodic pattern \fixme{although
+  they haven't really run long enough to exhibit much.  They certainly
+  won't show the double oscillation pattern, however.}  The animations
+of $6\mu m$ cells show that the MinD acts as a sort of traveling
+cluster that is constantly being eaten away be MinE behind it.  When
+this cluster enters a region of high curvature that ends in a dead end
+corner it performs the polar maxima behavoir seen in the other
+simulations, regrouping out away from the corner where it travels in
+the opposite direction while being ``chased'' away by the MinE that
+has itself maximized in the corner.  If it has just maximized in the
+top corner, it regroups traveling downward and then naturally splits
+into two groups that travel out and form maxima in the two opposite
+bottom corners.  After maximizing in these two corners the two groups
+recombine again in the center and travel in some direction together as
+one cluster.  Simulations of the $9\mu m$ cells show a similar roaming
+cluster.  Although here, the maxima occur on non-polar walls often,
+and will often split into two roaming clusters that interact less
+quickly and are less correlated than those seen in the $6\mu m$ cell.
+
+It seems that there is an approximate critical cell size for which the
+MinD will act in these ``wandering cluster'' formations.  The cell is
+large enough so that there is a loss of MinD correlation between the
+opposite sides (the protein in the right corner at any time is too far
+away from the left to immediately affect the protein there).
+
 %% \begin{center}
@@
 
+Figure \ref{total-oscillation-triangle-plot} shows the equivalent
+motion and transference between compound states for the triangular
+states as Figure \ref{total-oscillation-plot} does for the pill shaped
+cells.  The equilateral triangular shows that in all three sections
+there is a spike in wall attached MinD-ATP directly followed by a
+spike in wall attached MinD-MinE-ATP.  The pill had shown a similar
+pattern except that the mid section exhibited no such pronounced
+spike.  Interestingly, the right and mid sections show spikes at
+similar times when compared to the left section spikes, which seem to
+oscillate in a manner shifted pi off from the other two.  This
+behavoir shows itself in the animations, which show a relaxation into
+a stable oscillation from a maxima in one corner to a double maxima in
+the other two corners, and back again.  The left section heights are
+roughly twice that of the right section heights.  The simulations are
+started with higher concentrations of proteins in primarily the right
+section, with some overlap into the middle section, so that perhpas
+this oscillation pattern seems reasonable.  However, it's interesting
+to note that the oscillations, started with assymmetric density, do
+not naturally rotate around the corners of the triangle in a circular
+pattern.
+
+It seems as well that there is a desired oscillation maxima for the
+particular shape and size of the cell, as can be seen by the
+relaxation, over the first four periods, to a regular maximal height
+of the right and left sections' total protein at the height of each spike.
+
+\fixme{Note to make sure I'm interpreting the iscosolese triangle data
+  correctly: the triangle sides are 5,5,3, and the higher density
+  starts in the corner that is opposite the short side.  This corner
+  is covered by the right section.  I've verified this by looking at
+  the protein\_microscopy and drawing a little picture, which is on my
+  desk...if you dare look for something on my desk!!!}  The iscosolese
+triangle starts its simulation with a higher concentration of protein
+in the section that is opposite the shorter side.  It quickly relaxes
+into a stable oscillation pattern.  This pattern shows that right
+corner section regularly has higher spikes in total protein than the
+other sections, and that its spikes appear one pi removed from the
+spikes for the other two sections.  This a similar behavoir to that
+which is seen in the equilateral triangle, differening in that it
+converges more quickly towards this behavoir and that it shows a
+greater exageration in the height of protein buildup in the right most
+section.
+
+\fixme{Note on interpretation of 3-4-5 triangle: the higher density
+  starts to the right of a vertical line that is parrallel to the
+  second longest side in the triangle (the longer of the two
+  non-hypotonuse sides).  This means the higher concentration covers
+  the right angle and also the smaller angle in the triangle} The
+3-4-5 triangle exhibits behavoir that I need more data to properly
+observe.  I does not converge as quickly as that for the iscosolese or
+equilateral triangles.
+
 \end{document}

### 2013-10-16 pyplots/box_plot.py
changed box plot time limits for a couple specific shapes in the paper Tested everything on node26.

@@ -176,9 +176,13 @@ def main():
     start = int(tot_time*start_time_as_frac_of_ten/10.0/box_time_step)
     end = int(tot_time*end_time_as_frac_of_ten/10.0/box_time_step)
     (start, end) = find_period(plotCurveList_D[3])
-    if load.f_param4 == '97.00':
-        start_time_as_frac_of_ten = 0
-        end_time_as_frac_of_ten = 2.3
+    if load.f_param4 == '97.00' or (load.f_shape == 'triangle' and load.f_param3 == '6.01'):
+        if load.f_param4 == '97.00':
+            start_time_as_frac_of_ten = 0
+            end_time_as_frac_of_ten = 2.3
+        if load.f_shape == 'triangle' and load.f_param3 == '6.01':
+            start_time_as_frac_of_ten = 5.00
+            end_time_as_frac_of_ten = 9.00
         start = int(tot_time*start_time_as_frac_of_ten/10.0/box_time_step)
         end = int(tot_time*end_time_as_frac_of_ten/10.0/box_time_step)
 

### 2013-11-09 protein_microscopy.cpp
uncommented things in protein mic that otherwise would make things seg fault Tested everything on node33.

@@ -646,7 +646,7 @@ int main (int argc, char *argv[]) {
    }
    if (rand_seed == 99) {
      for (int i=0;i<100;i++){
-       guass99[i] = 1.3*guass99[i];
+       guass99[i] = 3.0*guass99[i];
      }
    }
    printf("Those are all the guassians!\n");
@@ -684,50 +684,42 @@ int main (int argc, char *argv[]) {
    //end random stuff
 
    //   double x = .32999;//dx*Nx/2.0;
-   double x = dx*8;//0.10;
-   double y = dx*34;//dx*Ny/2.0;
-   double z = dx*Nz/2.0;
-   printf("mem_f(%g,%g,%g) = %g\nA = %g  B = %g\n",x,y,z,mem_f(x,y,z),A,B);
-   double xi = x/dx;
-   double yi = y/dx;
-   double zi = z/dx;
-   double fXYZ = mem_f((xi+0.5)*dx, (yi+0.5)*dx, (zi+0.5)*dx);
-   double fxYZ = mem_f((xi-0.5)*dx, (yi+0.5)*dx, (zi+0.5)*dx);
-   double f = mem_f(xi*dx, yi*dx, zi*dx);
-   printf("f = %g fX = %g fx = %g\n",f,fXYZ,fxYZ);
+   // double x = dx*8;//0.10;
+   // double y = dx*34;//dx*Ny/2.0;
+   // double z = dx*Nz/2.0;
+   // double xi = x/dx;
+   // double yi = y/dx;
+   // double zi = z/dx;
+   // double fXYZ = mem_f((xi+0.5)*dx, (yi+0.5)*dx, (zi+0.5)*dx);
+   // double fxYZ = mem_f((xi-0.5)*dx, (yi+0.5)*dx, (zi+0.5)*dx);
+   // double f = mem_f(xi*dx, yi*dx, zi*dx);
+   // printf("f = %g fX = %g fx = %g\n",f,fXYZ,fxYZ);
 
-   fflush(stdout);
 
-   double *mem_A = new double[Nx*Ny*Nz];
-   set_membrane(out_file, mem_f, mem_A);
-
-   bool *insideArr = new bool[Nx*Ny*Nz];
-   set_insideArr(insideArr);
-
-   double total_cell_volume = 0;
-   double total_cell_area = 0;
-   for (int i=0;i<Nx*Ny*Nz;i++){
-    total_cell_area += mem_A[i];
-    if (insideArr[i]==true) {
[…]

### 2013-11-09 paper/paper.tex
a few edits of paper Tested everything on collins.

@@
 \newcommand{\fixme}[1]{\red{[#1]}}
+\newcommand{\davidsays}[1]{{\color{red} [\green{David:} \emph{#1}]}}
+
+\newcommand\micron{\ensuremath{\mu\text{m}}}
 
@@
 the cell wall in the center region of the cell that dictates the plane
-of division\cite{adams2009bacterial}
-\cite{lutkenhaus2007assembly}. Previous experimental studies have
-shown that the MinC protein, known to inhibit the FtZ
+of division~\cite{adams2009bacterial,
+  lutkenhaus2007assembly}. Previous experimental studies have shown
+that the MinC protein, known to inhibit the FtZ
 polymer\cite{shen2010examination}, exhibits a pole to pole oscillatory
 behavoir in conjunction with the MinD and MinE proteins, while the
-oscillating MinE tends to be more localized in the center of the cell
-\cite{hu1999topological} \cite{fu2001mine} \cite{shapiro2009and}
-\cite{yu1999ftsz} \cite{raskin1999rapid}The MinC protein will then have a higher time
+oscillating MinE tends to be more localized in the center of the
+cell~\cite{hu1999topological, fu2001mine, shapiro2009and, yu1999ftsz,
+  raskin1999rapid}. The MinC protein will then have a higher time
 averaged concentration in the cell poles as opposed to the center
-region of the cell, aiding in prohibiting the FtZ from developing in the wrong
-region.
-
-A significant amount of work has been done to develop protein reaction
-and diffusion models that exhibit accurate macroscopic dynamics of the
-MinD protein system. Early models involved free proteins that affect
-eachothers' rates of diffusion and membrane attachement but do not
-combine into compound states\cite{meinhardt2001pattern} .  In 2003
-Huang \cite{huang2003dynamic} improved upon this work with a simple
-model based on MinD-MinE combination, ATPase hydrolysis, and MinD
-membrane attechent that when simulated exhibits accurate MinD
-oscillations in cylindrical cells\cite{huang2003dynamic}. In this
-model cytoplasmic MinD is more likely to attach to the membrane when
-MinD is already clustered there (following observed non-linear
-attachement of minD on the cell membrane), and is stationary once
-attached.  A number of studies have used an approach similar in that
-they do not rely on the ability of MinD to move along the walls and
-cluster ~\cite{kruse2007experimentalist} \cite{meinhardt2001pattern}
-\cite{drew2005polymerization} \cite{fange2006noise}
-\cite{kerr2006division}, while studies have been made as well of
-models which rely on MinD mobility and attraction on the cell
-membrane\cite{kruse2002dynamic}\cite{howard2005cellular}.  Variations
-of the Huang 2003 model that stochasticly account for variations of
-molecular interaction \cite{fange2006noise} and as well monte-carlo
-simulations that implement stochastic version of Huang's mean filed
-reaction rates confirm the major results obtained by Huang's model and
-more successfully predict experimentally observed oscillations in
-round cell phenotypes.\cite{drew2005polymerization}
-\cite{fange2006noise} \cite{huang2004min} Biochemical models of
-broader scope have also been used to study the MinD system and show
-consistent results.\cite{arjunan2010new}.  However, in general the
-results of the stochastic and monte-carlo simulations are similar to
-those given by Huang's mean field results.
-
-Previous studies have been made of the Min system's associtation with
-the cell membrane
-\cite{hsieh2010direct}\cite{mileykovskaya2003effects}.  Studies have
-shown as well that MinD binds preferentially to regions enriched with
-cadiolipin, an anionic phospholipid that collects on regions of high
-negative curvature. This mechanism has been incorporated into other
-models.\cite{drew2005polymerization,cytrynbaum2007multistranded,renner2012mind,renner2012mind}
-However, this mechanism of combined clustering, phospholipids and MinD
-has not been observed in real cells. \cite{halatek2012highly}
+region of the cell, aiding in prohibiting the FtZ from developing in
+the wrong region.
 
@@
 adversly effects the Min system's ability to maintain their regular
-oscillatory behavior \fixme{this link doesn't work = cite{mannik2012robustness}}
-\cite{mannik2010bacteria} \cite{mannik2009bacterial}.  We follow the
-experimental work of Mannik et and use Huang's mean field differential
-equation reaction model to explore the model's ability to find regular
-oscillatory behavoir in a series of abberent shapes.
+oscillatory behavior \fixme{this link doesn't work =
+  cite{mannik2012robustness}} \cite{mannik2010bacteria}
+\cite{mannik2009bacterial}.  We follow the experimental work of Mannik
+et and use Huang's mean field differential equation reaction model to
+explore the model's ability to find regular oscillatory behavoir in a
+series of abberent shapes.  \davidsays{This paragraph could use some
+  work, and should reference Mannik early, and emphasize his research.
+  First paragraph sets the stage for why our work is important by
+  introducing the MinD system.  Second paragraph should explain why we
+  are studying the Min system in funny cell shapes.}
 
-\subsection{What is the MinD system and why is it important?}
-\subsection{How proteins move in cell}
-\section{Methods and Initial Conditions}
-The model for the behavior of the MinD and MinE proteins inside the
-cell implements the same set of 5 reaction-diffusion equations studied in
-the work of Huang et al (equations 1, 2, 3, 4, and
-5)\cite{huang2003dynamic}. A 3d grid is constructed in cartesian
-coordinates with a grid spacing of .05 $\mu$m. We define our cell
-shapes and solve the reaction-diffusion equations numerically to
-observe the time evolution of the MinD and MinE concentrations inside
-the cell.
+A significant amount of work has been done to develop protein reaction
+and diffusion models that exhibit accurate macroscopic dynamics of the
+MinD protein system. Early models involved free proteins that affect
+eachothers' rates of diffusion and membrane attachement but do not
+combine into compound states~\cite{meinhardt2001pattern}.  In 2003
+Huang improved upon this work with a simple model based on MinD-MinE
+combination, ATPase hydrolysis, and MinD membrane attechent that when
+simulated exhibits accurate MinD oscillations in cylindrical
+cells~\cite{huang2003dynamic}. In this model cytoplasmic MinD is more
+likely to attach to the membrane when MinD is already clustered there
+(following observed non-linear attachement of minD on the cell
+membrane), and is stationary once attached.  A number of studies have
+used an approach similar in that they do not rely on the ability of
+MinD to move along the walls and
+cluster~\cite{kruse2007experimentalist, meinhardt2001pattern,
+  drew2005polymerization, fange2006noise, kerr2006division}, while
+studies have been made as well of models which rely on MinD mobility
+and attraction on the cell membrane~\cite{kruse2002dynamic,
+  howard2005cellular}.  Variations of the Huang 2003 model that
+stochasticly account for variations of molecular interaction
+\cite{fange2006noise} and as well monte-carlo simulations that
+implement stochastic version of Huang's mean filed reaction rates
+confirm the major results obtained by Huang's model and more
+successfully predict experimentally observed oscillations in round
+cell phenotypes~\cite{drew2005polymerization, fange2006noise,
+  huang2004min}. Biochemical models of broader scope have also been
+used to study the MinD system and show consistent
+results.\cite{arjunan2010new}.  However, in general the results of the
+stochastic and monte-carlo simulations are similar to those given by
+Huang's mean field results.
 
-We start our cells with the MinD and MinE concentrations that are
-reported as wild type concentrations by Huang et al . We as well use the same reaction
-diffusion constants and and reaction rates,
-\begin{gather*} %format better
-  \mathcal{D}_D = \mathcal{D}_{E}  = 2.5 \mu \textrm{m$^2$ / sec}, \\
-  \sigma_D^{\textrm{ADP $\rightarrow$ ATP}}  = 1/\textrm{sec},  \sigma_D = 0.025 \mu \textrm{m/sec}, \\
-  \sigma_{dD}  = 0.0015 \mu \textrm{m$^3$/sec}, \\
-  \sigma_{de}  = 0.7/\textrm{sec}, \sigma_E = 0.093 \mu \textrm{m$^3$/sec}.
-\end{gather*}
+Previous studies have been made of the Min system's associtation with
+the cell membrane
+\cite{hsieh2010direct}\cite{mileykovskaya2003effects}.  Studies have
+shown as well that MinD binds preferentially to regions enriched with
+cadiolipin, an anionic phospholipid that collects on regions of high
+negative curvature. This mechanism has been incorporated into other
+models.\cite{drew2005polymerization,cytrynbaum2007multistranded,renner2012mind,renner2012mind}
+However, this mechanism of combined clustering, phospholipids and MinD
+has not been observed in real cells. \cite{halatek2012highly}
 
-We study cell shapes that are similar to those studied by Huang and
-also new, flattened pancake-like shapes, inspired by the experimental work of
-Mannik \cite{mannick2012robustness}.  Our pill shapes differ from
-Huangs in that they are cylinders with hemisphere endcaps instead of
-pure cylindridrical shapes.  Our cylinderidrical radius is $0.50\mu$
-and the lengths of our cells (measured between the tips of the
-endcaps) are $5\mu$, $4\mu$, $3\mu$, and $2.5\mu$.
+\begin{figure}
+  \includegraphics[width=\columnwidth]{reactions}
+  \caption{Reactions included in the model of Huang \emph{et
+      al.}~\cite{huang2003dynamic}.}\label{fig:reactions}
+\end{figure}
 
-With our flattened cell shapes we mean to study cells that are
-parrallel to those lodged into crevices by Mannik so we give them
-height of $0.25\mu$ \cite{mannick2012robustness}.  Viewed from the top
-down the cells will have the shapes described below and viewed from
-the side they have at their edges a semicircular protrusion (one may
-imagine the edges of a pancake).
+\section{Model and Methods}
+We implement the model of Huang \emph{et al.}  for the behavior of the
+MinD and MinE proteins inside the cell~\cite{huang2003dynamic}.  This
+model is defined by a set of five reaction-diffusion equations:
+\begin{align}
+  \frac{\partial n_{?}}{\partial t} &= \text{\davidsays{Actual differential equations here.}}
+\end{align}
+These equations define the rates of diffusion and reaction shown in
+Figure~\ref{fig:reactions}.  \davidsays{Add more text here, describing
+  the system and the reactants.  In particular, we want to state that
+  MinD:ADP binds ATP (or is hydrolyzed?... check!) to form MinD:ATP,
+  which then gets stuck to the cell membrane, which is more likely
+  when there is already MinD:ATP bound to the membrane.  The MinE then
+  binds to the membrane-bound MinD:ATP.  Finally the whole complex can
+  fall off the membrane, at which stage you end up with MinD:ADP and
+  are ready to start over.  This is also where we define our
+  terminology for the volume and surface densities.}
 
-Our first group of (three) flattened cell shapes are triangular.  One
-of them is equilateral, one has a 3-4-5 right angle shape, and the
-last is iscoscolese.
+The reaction shown in Figure~\ref{fig:reactions} is cyclical so we can
+begin our observations at any stage in the cycle (which is presented
+for the natural cell shape in Fig.~\ref{image-p} below).  We consider
+first MinD:ATP floating freely in the cytoplasm.  The protein will not
+react with any other floating protein, and it will not spontenously
+shift back into the MinD:ADP stage of the cycle.  It will diffuse
+until it attaches to a cell membrane.  This is will happen most
+rapidly in regions of high curvature, where diffusion is more likely
+to lead to an encounter with a wall.  This effect is made more
+pronounced by the MinD:ATP tendency to attract and cluster on the
+membrane, as reflected in Equation~\ref{eq:d-on-wall}, which shows
+that when adjacent to the membrane, the rate of binding to the
+membrane is porportional to the amount of MinD already bound to the
+wall.  Initially, then, there is a strong tendency of MinD to cluster
+on the polar regions of the cell, where the curvature is highest.
 
-Our second group of (four) flattened cells are our own creations,
-designed to investigate different patterns of protein oscillation
-behavoir.
-
-The cell shapes and the sections that we split them into in our data
-analysis are shown in Figure \fixme{We need a big figure with all of this!!}.
-
-Kubitschek\cite{kubitschek1990cell} \cite{kubitschek1968linear} has
-shown in multiple experiments that at the time of cell division cells
-have a volume that is within a range of roughly $1\mu m^3$ to $2\mu
-m^3$.  We follow Huang's simulations\cite{huang2003dynamic} and
-Mannik's experiments \fixme{this link doesn't work = cite{mannik2012robustness}} and model cells that
-are slightly larger than this range.  Amoung our flattened cells the
-two dimensional length scales are tuned so that every total cell
-volume is very close to $3\mu^3$.  \fixme{should we just leave it to
-  the reader to figure out for themselves what our pill shape volumes
-  are?}
-
-To interpret the results, we generated several different plot views of
-the printed simulation data. These plots included a time averaged view
-of the protein densities in the cell; a plot tracking the location of
-protein concentrations that were global maxima in space and local maxima in
-time; and an animated view that showed the actual dispersion of
-protein concentrations in the cell over time.
-\subsection{Mathematical Model}
-\section{Specific Results}
-\subsection{Pill Shape}
-
-Our simplest shape is the naturally occuring pill shape.  We peice this shape
-together as two hemispherical endcaps attached on either end of a
-cylinder.  This shape follows the early simulations of Huang et al but
-differs in that we have added the end caps for a more natural shape,
-expecting similar results.  We test cells of radius $.5\mu$ and of
-lengths $2\mu$, $3\mu$, and $5\mu$ between both tips of the end
-caps. In all these models we observe quick establishement (within a
-few periods) of extremely regular oscillatory behavoir that lasts for
-any length of time, with periods that closely agree with the results
-of Huang et al.  The following table shows the periods of oscillations
-at different cell lengths.
-
-This simple model is a good starting point for observing in detail the
-dynamic interaction between the different stages of protein that lead
-to their qualitatively distinct behavoir. Figure \ref{image-p} shows
-the process in a series of frames taken from simulation animations.
-Each frame is 2.5 seconds ahead of the last.  The causal chain is
-cyclical so we can begin our observations at any stage in the cycle.
-We consider first MinD:ATP floating freely in the cytoplasm.  The
-protein will not react with any other floating protein, and it will
-not spontenously shift back into the MinD:ADP stage of the cycle.  It
-will diffuse until it attaches to a cell membrane.  When compared to a
-protein that is in the middle cylindrical section of the cell, a
-protein that is in an end cap section is more likely to bump into a
-wall in a given number of diffusive steps, since there is a greater
-cross section of possible movement that is covered by a nearby wall.
-All else being equal, proteins will collect with a higher rate on the
-caps.  This effect is made more pronounced by the MinD:ATP tendency to
-attract and cluster.  When adjacent to the membrane, the rate of
-binding to the membrane is porportional to the amount of MinD already
-bound there.  Initially, then, there is a strong tendency of MinD to
-cluster in the polar regions of the cell.
-
-The next observed mechanism is the formation of MinE 'rings' on the
-membranes of the polar caps.  As the freely
-diffusing MinE enters the cap portion it begins to encounter
-concentrated membrane bound MinD.  As it bumps into the walls here it
-binds to this MinD and remians for a time on the walls in compound
-form.  When it is released, it can diffuse naturally outward or inward
+We next see the formation of MinE `rings' on the membranes of the
+polar caps.  As the freely diffusing MinE enters the cap portion it
+begins to encounter concentrated membrane bound MinD.  The MinE binds
+to this MinD and remians for a time on the walls in compound form.
+When it is released, it can diffuse naturally outward or inward
 towards the cell.  If it diffuses inward, there is less cross
@@
 to react with.  If it diffuses outward, the curvature of the cell wall
-cuases there to be a greater chance that it will bump into the cell
+cuases there to be a greater chance that it will encounter the cell
 membrane (for the same reason outlined for the MinD:ATP above) and if
@@
 
+ A 3d grid is constructed in cartesian
+coordinates with a grid spacing of .05\micron. We define our cell
+shapes and solve the reaction-diffusion equations numerically to
+observe the time evolution of the MinD and MinE concentrations inside
+the cell.
+
+We start our cells with the MinD and MinE concentrations that are
+reported as wild type concentrations by Huang et al . We as well use the same reaction
+diffusion constants and and reaction rates,
+\begin{gather*} %format better
+  \mathcal{D}_D = \mathcal{D}_{E}  = 2.5 \micron^2/\text{sec}, \\
+  \sigma_D^{\textrm{ADP $\rightarrow$ ATP}}  = 1/\textrm{sec},  \sigma_D = 0.025 \micron /\textrm{sec}, \\
+  \sigma_{dD}  = 0.0015 \micron^3/ \textrm{sec}, \\
+  \sigma_{de}  = 0.7/\textrm{sec}, \sigma_E = 0.093 \micron^3 /\textrm{sec}.
+\end{gather*}
+
+\section{Cell shapes}
+
+In order to address the limits at which the stability of the
+oscillations of the Min system break down, as observed by Mannik
+\emph{et al.}~\cite{mannik2012robustness}, we model the Min system in
+a variety of cell shapes.  We begin with natural pill-shaped cells,
+and the proceed to examine a number of flattened pancake-like shapes,
+which reflect the experiment of Mannik \emph{et al.}, in which
+bacteria were confined within a thin slit~\cite{mannik2012robustness}.
+Our pill shapes differ from those of Huang \emph{et al.} in that they
+are cylinders with hemisphere endcaps instead of pure cylindridrical
+shapes. \davidsays{Double-check the Huang paper on their shapes.}  Our
+cylinderidrical radius is $0.50\micron$ and the lengths of our cells
+(measured between the tips of the endcaps) are $5\micron$, $4\micron$, $3\micron$,
+and $2.5\micron$.
+
+With our flattened cell shapes we mean to study cells that are
+parrallel to those lodged into crevices by Mannik so we give them
+height of $0.25\micron$ \cite{mannik2012robustness}.  Viewed from the top
+down the cells will have the shapes described below and viewed from
+the side they have at their edges a semicircular protrusion (one may
+imagine the edges of a pancake).
+
+Our first group of (three) flattened cell shapes are triangular.  One
+of them is equilateral, one has a 3-4-5 right angle shape, and the
+last is iscoscolese.
+
+Our second group of (four) flattened cells are our own creations,
+designed to investigate different patterns of protein oscillation
+behavoir.
+
+The cell shapes and the sections that we split them into in our data
+analysis are shown in Figure \fixme{We need a big figure with all of this!!}.
+
+Kubitschek has shown in multiple experiments that at the time of cell
+division cells have a volume that is within a range of roughly
+$1\micron^3$ to $2\micron^3$~\cite{kubitschek1990cell,
+  kubitschek1968linear}.  We follow Huang's
+simulations\cite{huang2003dynamic} and Mannik's experiments
+\fixme{this link doesn't work = cite{mannik2012robustness}} and model
+cells that are slightly larger than this range.  Amoung our flattened
+cells the two dimensional length scales are tuned so that every total
+cell volume is very close to $3\micron^3$.  \fixme{should we just
+  leave it to the reader to figure out for themselves what our pill
+  shape volumes are?}
+
+To interpret the results, we generated several different plot views of
+the printed simulation data. These plots included a time averaged view
+of the protein densities in the cell; a plot tracking the location of
+protein concentrations that were global maxima in space and local maxima in
+time; and an animated view that showed the actual dispersion of
+protein concentrations in the cell over time.
+\section{Specific Results}
+
+\subsection{Pill Shape}
+
 \begin{figure*}
@@
     the page. The frames occur 2.5 seconds apart. \fixme{this looks
-      assymetric! That's a big problem.}}
+      assymetric! That's a big problem.} \davidsays{I like this plot,
+      but would rather see it improved in a few ways.  I noticed the
+      implementation combines together bitmaps.  Nicer would be to use
+      subplots within matplotlib, so we output the plot directly as a
+      pdf.  Then we could also arrange things so there is much less
+      vertical white space.  It'd be nicer to have labels at the left
+      and a time axis at the bottom, with no labels by each image.  I
+      know this will take a while, so it's not yet a high priority.}}
   \label{image-p}
@@
 
-Consider Figure \ref{image-p}.  At 0 seconds we can see cytoplasmic
-nATP roughly evenly distributed throughout the cell.  There is nADP
+We begin with the naturally occuring pill shape.  We peice this shape
+together as two hemispherical endcaps attached on either end of a
+cylinder.  This shape follows the early simulations of Huang \emph{et
+  al.} but differs in that we have added the end caps for a more
+natural shape, expecting similar results.  We test cells of radius
+$.5\micron$ and of lengths $2\micron$, $3\micron$, and $5\micron$
+between both tips of the end caps. In all these models we observe
+quick establishement (within a few periods) of extremely regular
+oscillatory behavoir that lasts indefinitely, with periods that
+closely agree with the results of Huang \emph{et al.}
+Table~\ref{tab:pill-periods} shows the periods of oscillations
+at different cell lengths.
+
+\begin{table}
+  \begin{tabular}{|r|c|c|c|l|}
+    \hline
+    Length($\mu$) & 2.50 & 3.00 & 4.00 & 5.00\\
+    \hline
+    Period(sec) & sim & 33 & 38 & 48 \\ \cline{2-2}
+    \hline
+  \end{tabular}
+  \caption{Period According to Pill Length}\label{tab:pill-period}
+\end{table}
+
+This simple model is a good starting point for observing in detail the
+dynamic interaction between the different stages of protein that lead
+to their qualitatively distinct behavoir. Figure \ref{image-p} shows
+the process in a series of frames taken from simulation animations.
+Each frame is 2.5 seconds ahead of the last.
+
+Consider Figure \ref{image-p}.  In the beginning, the cytoplasmic
+nATP is roughly evenly distributed throughout the cell.  There is nADP
 concentrated in the left pole and it will transform into nATP.  At 2.5
@@
   \caption{Total protein fluctuation in the right, middle, and left
-    parts of a 5$\mu m$ by 1$\mu m$ pill shaped cell (above) and a
-    3$\mu m$ by 1$\mu m$ pill shaped cell (below).  The vertical axis shows
+    parts of a 5$\micron$ by 1$\micron$ pill shaped cell (above) and a
+    3$\micron$ by 1$\micron$ pill shaped cell (below).  The vertical axis shows
     stacked the total number of proteins that are of four different
@@
 
-\begin{table}
-  \begin{tabular}{|r|c|c|c|l|}
-    \hline
-    Length($\mu$) & 2.50 & 3.00 & 4.00 & 5.00\\
-    \hline
-    Period(sec) & sim & 33 & 38 & 48 \\ \cline{2-2}
-    \hline
-  \end{tabular}
-  \caption{Period According to Pill Length}
-\end{table}
-
 \begin{figure}
@@
     attached stages of the protein cycle.  Shown in the right, middle,
-    and left parts of a 5$\mu m$ by 1$\mu m$ pill shaped cell (above)
-    and a 3$\mu m$ by 1$\mu m$ pill shaped cell (below).}
+    and left parts of a 5$\micron$ by 1$\micron$ pill shaped cell (above)
+    and a 3$\micron$ by 1$\micron$ pill shaped cell (below).}
   \label{ave-per-area-plot-pill}
@@
 the FtZ polymer may build up along the center walls.  We can see from
-the plot of the 3$\mu m$ by 1$\mu m$ cell that the MinD proteins reach
+the plot of the 3$\micron$ by 1$\micron$ cell that the MinD proteins reach
 concentration peaks in the caps that are higher than peaks in the
@@
   \caption{Total protein fluctuation of an equilateral triangle with
-    larger dimensions (each side is roughly $6\mu m$.  The vertical
+    larger dimensions (each side is roughly $6\micron$.  The vertical
     axis shows stacked the total number of proteins that are of four
@@
 Simulations in which the two planar dimensions are 2 and then 3 times
-the size (cells roughly $6\mu m$ and $9\mu m$, respectively, from top
+the size (cells roughly $6\micron$ and $9\micron$, respectively, from top
 to bottom) show no stable regular periodic pattern \fixme{although
@@
   won't show the double oscillation pattern, however.}  The animations
-of $6\mu m$ cells show that the MinD acts as a sort of traveling
+of $6\micron$ cells show that the MinD acts as a sort of traveling
 cluster that is constantly being eaten away be MinE behind it.  When
@@
 recombine again in the center and travel in some direction together as
-one cluster.  Simulations of the $9\mu m$ cells show a similar roaming
+one cluster.  Simulations of the $9\micron$ cells show a similar roaming
 cluster.  Although here, the maxima occur on non-polar walls often,
 and will often split into two roaming clusters that interact less
-quickly and are less correlated than those seen in the $6\mu m$ cell.
+quickly and are less correlated than those seen in the $6\micron$ cell.
 

### 2013-11-11 pyplots/box_plot.py
fix Min D -> MinD in box plot Tested everything on collins.

@@ -350,7 +350,7 @@ def main():
     bax.set_xlim(box_time_step*start,box_time_step*end)
     bax.get_yaxis().set_visible(False)
     bax.set_ylim(0, 1)
-    bax.set_title("Min D protein counts over time")
+    bax.set_title("MinD protein counts over time")
     bax.set_xlabel("Time (s)")
     rax = bax.twinx()
     rax.set_ylabel('Fraction of proteins in each stage and section',labelpad=-15)
@@ -392,7 +392,7 @@ def main():
         k+=1
     bax.set_xlim(box_time_step*start,box_time_step*end)
     bax.set_ylim(0, 1)
-    bax.set_title("Min E protein counts over time")
+    bax.set_title("MinE protein counts over time")
     bax.set_xlabel("Time (s)")
     bax.set_ylabel("Fraction of proteins")
     bax.legend(plotNameList_E,bbox_to_anchor=(0.3,-0.05,1.0,1.0),loc="lower right",prop={'size':8}).draw_frame(False)

### 2013-11-11 pyplots/file_loader.py
small cahnges to python files, cleaned up file_loader a bit Tested everything on node33.

@@ -40,46 +40,40 @@ if len(sys.argv)>expected_arg_number:
 
 filename_tuple = (f_shape,hires_str,slice_str,f_shape,f_param1,f_param2,f_param3,f_param4,f_param5)
 
+
+
 #data object, to create in another plot: proteinname=data(protein="proteinname")
 class data(object):
-    def __init__(self,protein):
+    def __init__(self,protein,start_time=0,end_time=0):
         self.protein = protein
-        self.filenames = self.get_filenames(protein,0,0)
+        self.filenames = get_filenames(protein,start_time,end_time)
         self.tsteps = len(self.filenames)
         self.dataset = np.array([np.loadtxt(file) for file in self.filenames])
         self.datashape = self.dataset[0].shape
         self.axes = [[i*dx for i in range(self.datashape[1])],[j*dx for j in range(self.datashape[0])]]
-    # def __init__(self,protein,start_time,end_time):
-    #     self.protein = protein
-    #     self.filenames = self.get_filenames(protein,start_time,end_time)
-    #     self.tsteps = len(self.filenames)
-    #     self.dataset = np.array([np.loadtxt(file) for file in self.filenames])
-    #     self.datashape = self.dataset[0].shape
-    #     self.axes = [[i*dx for i in range(self.datashape[1])],[j*dx for j in range(self.datashape[0])]]
 
 #loads the files for creating the data object.
-    @staticmethod
-    def get_filenames(protein,start_time,end_time):
-        dat_filenames = []
-        if end_time == 0:
-            for fn in glob.iglob("./data/shape-%s/%s%s%s%s-%s-%s-%s-%s-%s-%s-*.dat"%(f_shape,debug_str,hires_str,slice_str,protein,f_shape,f_param1,f_param2,f_param3,f_param4,f_param5)):
-                dat_filenames.append(fn)
-        if end_time != 0:
-            for i in np.arange(start_time,end_time,2.5):
-                file_num = round(i/2.5)
-                dat_filenames.append("./data/shape-%s/%s%s%s%s-%s-%s-%s-%s-%s-%s-%d.dat"%
-                                     (f_shape,debug_str,hires_str,slice_str,protein,f_shape,f_param1,f_param2,f_param3,f_param4,f_param5,file_num))
-        dat_filenames = sorted(dat_filenames)
[…]

### 2013-11-11 pyplots/image_plot.py

@@ -61,7 +61,7 @@ def build(proteins,proteinList):
     spread = Image.new("RGB", (120+(400-2*cut)*total_length, 300*len(proteins)), "white")
     for i in range(len(proteins)):
         if (proteinList[i]=="ND" or proteinList[i]=="NDE"):
-            maxval = timemax(proteins[i])/4
+            maxval = timemax(proteins[i])/1
         else:
             maxval = timemax(proteins[i])
         sys.stdout.flush()

### 2013-11-11 pyplots/file_loader.py
add nicer image plot with data, plus put in Makefile Tested everything on collins.

@@ -1,6 +1,7 @@
 import numpy as np
 import sys
 import glob
+import os
 
 #get the shape an physical parameters of the cell (last argument is density lopsidedness)
 f_shape = sys.argv[1]
@@ -9,6 +10,9 @@ f_param2 = sys.argv[3]
 f_param3 = sys.argv[4]
 f_param4 = sys.argv[5]
 f_param5 = sys.argv[6]
+
+git_add_files = False # set this to True to automagically git add dat
+                      # files that we need to do the plots
 
 dx=.05
 
@@ -68,6 +72,9 @@ def get_filenames(protein,start_time,end_time):
     # while i<round(len(dat_filenames)/10):
     #     dat_filenames.pop(0)
     #     i+=1
+    if git_add_files:
+        for filename in dat_filenames:
+            os.system('git add -f %s' % filename)
     if (dat_filenames == []):
         print "File loading error: filename list is empty."
         print "./data/shape-%s/%s%s%s%s-%s-%s-%s-%s-%s-%s-*.dat"%(f_shape,debug_str,hires_str,slice_str,protein,f_shape,f_param1,f_param2,f_param3,f_param4,f_param5)

### 2013-11-11 pyplots/image_plot.py

@@ -20,100 +20,55 @@ end_time = float(sys.argv[8])
 
 
 dump_time_step = 2.5
-#computes the maximum of a two dimensional array - REPLACE with method
-def maxnum(page):
-    Z = [0. for i in range(page.shape[0])]
-    for i in range(page.shape[0]):
-        Z[i] = max(page[i])
-    maxval = max(Z)
-    return maxval
-
-#computes the minimum of a two dimensional array - REPLACE with method
-def minnum(page):
-    Z = [0. for i in range(page.shape[0])]
-    for i in range(page.shape[0]):
-        for j in range(len(page[i])):
-            if page[i][j] == 0:
-             page[i][j] = 50000000 #eh
-        Z[i] = min(page[i])
-    minval = min(Z)
-    return minval
 
 #computes the global maximum over a set of two dimensional arrays (stored as files)
 def timemax(protein):
-    Z = [0. for i in range(protein.tsteps)]
-    for i in (range(int(end_time/dump_time_step)-int(start_time/dump_time_step))):
-        Z[i] = maxnum(protein.dataset[i])
-    maxval = max(Z)
-    return maxval
+    return max([v.max() for v in protein])
 
 #computes the global minimum over a set of two dimensional arrays (stored as files)
 def timemin(protein):
-    Z = [0. for i in range(protein.tsteps)]
-    for i in (range(int(end_time/dump_time_step)-int(start_time/dump_time_step))):
-        Z[i] = minnum(protein.dataset[i])
-    minval = min(Z)
-    return minval
+    return min([v.min() for v in protein])
 
-def build(proteins,proteinList):
-    total_length = int(end_time/dump_time_step)- int(start_time/dump_time_step)
-    cut = 40
-    spread = Image.new("RGB", (120+(400-2*cut)*total_length, 300*len(proteins)), "white")
-    for i in range(len(proteins)):
-        if (proteinList[i]=="ND" or proteinList[i]=="NDE"):
-            maxval = timemax(proteins[i])/4
-        else:
-            maxval = timemax(proteins[i])
-        sys.stdout.flush()
-        minval = timemin(proteins[i])
-        plt.figure()
-        Z, Y = np.meshgrid(np.arange(0,proteins[i].datashape[1],1), np.arange(0,proteins[i].datashape[0],1))
[…]

### 2013-11-12 paper/paper.tex
nicer title Tested everything on collins.
small cahnges to python files, cleaned up file_loader a bit Tested everything on node33.

@@
 \begin{document}
-\title{E Coli Project Paper Incredibly Rough Draft}
+\title{Robustness of MinD oscillation in \emph{Escherichia coli} with
+  diverse cell shapes}
 
@@
 Simulations of this shape that has the same height and dimensions .6
-times the size do not exhibit the same pattern.  In these the MinD
-maxima oscillate quickly back and forth between the two lower corner
-poles.
+times the size (cells roughly $1.6\mu m$ from top to bottom) do not
+exhibit the same pattern.  In these the MinD maxima oscillate quickly
+back and forth between the two lower corner poles.
 

### 2013-11-12 protein_microscopy.cpp
fixed bug in trimming Tested everything on node33.

@@ -800,14 +800,14 @@ int main (int argc, char *argv[]) {
      }
    }
    printf("max xi=%d\tyi=%d\tzi=%d\t min xi=%d\tyi=%d\tzi=%d\t\n",max_xi,max_yi,max_zi,min_xi,min_yi,min_zi);
-   int new_Nx = max_xi-min_xi+2;
-   int new_Ny = max_yi-min_yi+2;
-   int new_Nz = max_zi-min_zi+2;
+   int new_Nx = max_xi-min_xi+3;
+   int new_Ny = max_yi-min_yi+3;
+   int new_Nz = max_zi-min_zi+3;
    double *mem_A = new double[new_Ny*new_Nz*new_Nz];
-   for(int xi=min_xi;xi<Nx;xi++){
-     for(int yi=min_yi;yi<Ny;yi++){
-       for(int zi=min_zi;zi<Nz;zi++){
-         mem_A[(xi-min_xi+1)*new_Ny*new_Nz+(yi-min_yi+1)*new_Nz+(zi-min_zi+1)] = first_mem_A[xi*Ny*Nz+yi*Nz+zi];
+   for(int xi=0;xi<new_Nx;xi++){
+     for(int yi=0;yi<new_Ny;yi++){
+       for(int zi=0;zi<new_Nz;zi++){
+         mem_A[xi*new_Ny*new_Nz+yi*new_Nz+zi] = first_mem_A[(xi+min_xi-1)*Ny*Nz+(yi+min_yi-1)*Nz+(zi+min_zi-1)];
        }
      }
    }

### 2013-11-12 protein_microscopy.cpp
shortened memory initialized in print list arrays Tested everything on crystal.

@@ -601,6 +601,7 @@ int main (int argc, char *argv[]) {
    time_step = .1*dx*dx/difD;//sec
    iter = int(tot_time/time_step);//this will give us triangle data in about two days and randst in four days?
    printout_iterations = int(0.5/time_step);
+   int print_denominator = 1000; //This dictates how often (in iterations) you add a line to the box, time, and ave plots
    printf("printout iterations = %d\n",printout_iterations);//approximately 5 seconds between each printout
    double dV = dx*dx*dx;
 
@@ -914,8 +915,6 @@ int main (int argc, char *argv[]) {
   protein* proteinList[numProteins] = { nATP_plot, nADP_plot, nE_plot, ND_plot, NDE_plot, NflD_plot, NflE_plot };
   double* accessGlobals[numProteins] = { nATP, nADP, nE, ND, NDE, NflD, NflE };
 
-  int print_denominator = 1000;
-
   printf("Ny*Nz*sizeof(double) = %lu",Ny*Nz*sizeof(double));
   printf("iter*sizeof(double) = %lu",iter*sizeof(double));
 
@@ -924,39 +923,38 @@ int main (int argc, char *argv[]) {
 
   //initialize things
   for (int pNum=0; pNum<numProteins; pNum++) {
+    int total_print_iter = iter/print_denominator+2;
     proteinList[pNum]->sum = new double[Ny*Nz];
     proteinList[pNum]->name = new char[1024];
 
-    proteinList[pNum]->numLeft = new double[iter];
-    proteinList[pNum]->numMid = new double[iter];
-    proteinList[pNum]->numRight = new double[iter];
+    proteinList[pNum]->numLeft = new double[total_print_iter];
+    proteinList[pNum]->numMid = new double[total_print_iter];
+    proteinList[pNum]->numRight = new double[total_print_iter];
 
-    proteinList[pNum]->numRightUp = new double[iter];
-    proteinList[pNum]->numRightDown = new double[iter];
-    proteinList[pNum]->numLeftUp = new double[iter];
-    proteinList[pNum]->numLeftDown = new double[iter];
+    proteinList[pNum]->numRightUp = new double[total_print_iter];
+    proteinList[pNum]->numRightDown = new double[total_print_iter];
+    proteinList[pNum]->numLeftUp = new double[total_print_iter];
[…]

### 2013-11-13 paper/paper.tex
added equations in Model and Methods Tested everything on node23.

@@
 \documentclass[letterpaper,twocolumn,amsmath,amssymb,pre]{revtex4-1}
-
 \usepackage{graphicx}% Include figure files
@@
 model is defined by a set of five reaction-diffusion equations:
-\begin{align}
-  \frac{\partial n_{?}}{\partial t} &= \text{\davidsays{Actual differential equations here.}}
-\end{align}
+
+\begin{multline}
+  \frac{\partial n_{D:ADP}}{\partial t} = D_D\nabla^2n_{D:ADP}-\sigma_D^{ADP\rightarrow ATP}n_{D:ADP}\\
+  +\delta(r-R)\sigma_{de}n_{de}\hspace{3.4cm}
+\end{multline}
+\begin{multline}
+  \frac{\partial n_{D:ATP}}{\partial t} = D_D\nabla^2n_{D:ATP}+\sigma_D^{ADP\rightarrow ATP}n_{D:ADP}\\
+  -\sigma(r-R)[\sigma_D+\sigma_{dD}(n_d+n_{de})]n_{D:ATP}
+\end{multline}
+\begin{multline}
+  \frac{\partial n_E}{\partial t} = D_E\nabla^2n_E+\delta(r-R)\sigma_{de}n_{de}\\
+  -\delta(r-R)\sigma_E n_d n_E\hspace{3.3cm}
+\end{multline}
+\begin{multline}
+  \frac{\partial n_d}{\partial t} = -\sigma_En_dn_E(R)\\
+  +[\sigma_D+\sigma_{dD}(n_d+n_{de})]n_{D:ATP}(R)\hspace{.9cm}
+\end{multline}
+\begin{multline}
+  \frac{\partial n_{de}}{\partial t} = -\sigma_{de}n_{de}+\sigma_En_dn_E(R)\hspace{3cm}
+\end{multline}
+
 These equations define the rates of diffusion and reaction shown in
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-601-601-601-1500}
+%%  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-600-600-1500}
   \caption{Total protein fluctuation of an equilateral triangle with

### 2013-11-13 paper/paper.tex
rewrote equation and other things in Model and Methods, moved some of what was there to the pill section Tested everything on node23.

--- 2013-11-12 paper/paper.tex
@@
 We implement the model of Huang \emph{et al.}  for the behavior of the
-MinD and MinE proteins inside the cell~\cite{huang2003dynamic}.  This
-model is defined by a set of five reaction-diffusion equations:
-\begin{align}
-  \frac{\partial n_{?}}{\partial t} &= \text{\davidsays{Actual differential equations here.}}
-\end{align}
-These equations define the rates of diffusion and reaction shown in
-Figure~\ref{fig:reactions}.  \davidsays{Add more text here, describing
-  the system and the reactants.  In particular, we want to state that
-  MinD:ADP binds ATP (or is hydrolyzed?... check!) to form MinD:ATP,
-  which then gets stuck to the cell membrane, which is more likely
-  when there is already MinD:ATP bound to the membrane.  The MinE then
-  binds to the membrane-bound MinD:ATP.  Finally the whole complex can
-  fall off the membrane, at which stage you end up with MinD:ADP and
-  are ready to start over.  This is also where we define our
-  terminology for the volume and surface densities.}
+MinD and MinE proteins inside the cell~\cite{huang2003dynamic}.
+Figure~\ref{fig:reactions} shows the reaction process.  The
+cytoplasmic MinD:ADP complex undergoes nucleotide exchange and is
+changed into the MinD:ATP complex.  This will naturally diffuse
+towards and attach to the cell membrane.  A cytoplasmic MinE will
+attach to the wall bound MinD:ATP complex and after a time will
+activate ATP hydrolosis.  This breaks up the complex, releasing MinE,
+phosphate, and MinD:ADP back into the cell.  The MinD:ADP will undergo
+nucleotide exchange and begin again the cyclic process.  There is a
+mechanism for MinD:ATP clustering that is shown in
+Equation~\ref{fig:FourthPDE}.  When brushing up against the cell
+membrane, the MinD:ATP attachement rate increases linearly with the
+density of MinD:ATP already attached.  This model is defined by a set of
+five reaction-diffusion equations:
 
-The reaction shown in Figure~\ref{fig:reactions} is cyclical so we can
-begin our observations at any stage in the cycle (which is presented
-for the natural cell shape in Fig.~\ref{image-p} below).  We consider
-first MinD:ATP floating freely in the cytoplasm.  The protein will not
-react with any other floating protein, and it will not spontenously
-shift back into the MinD:ADP stage of the cycle.  It will diffuse
-until it attaches to a cell membrane.  This is will happen most
-rapidly in regions of high curvature, where diffusion is more likely
-to lead to an encounter with a wall.  This effect is made more
-pronounced by the MinD:ATP tendency to attract and cluster on the
-membrane, as reflected in Equation~\ref{eq:d-on-wall}, which shows
-that when adjacent to the membrane, the rate of binding to the
-membrane is porportional to the amount of MinD already bound to the
-wall.  Initially, then, there is a strong tendency of MinD to cluster
-on the polar regions of the cell, where the curvature is highest.
+\begin{multline}
+  \frac{\partial \rho_{D:ADP}}{\partial t} = \mathcal{D}_D\nabla^2\rho_{D:ADP}-k_D^{ADP\rightarrow ATP}\rho_{D:ADP}\\
+  +\delta(d_w)k_{de}\sigma_{DE}\hspace{3.4cm}
+\end{multline}
+\begin{multline}
+  \frac{\partial \rho_{D:ATP}}{\partial t} = \mathcal{D}_D\nabla^2\rho_{D:ATP}+k_D^{ADP\rightarrow ATP}\rho_{D:ADP}\\
+  -\delta(d_w)[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP}
+\end{multline}
+\begin{multline}
+  \frac{\partial \rho_E}{\partial t} = \mathcal{D}_E\nabla^2\rho_E+\delta(d_w)k_{de}\sigma_{DE}
+  -\delta(d_w)k_E \sigma_D \rho_E
+\end{multline}
+\begin{multline}
+  \frac{\partial \sigma_d}{\partial t} = -k_E\rho_d\rho_E
+  +[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP}
+  \label{fig:FourthPDE}
+\end{multline}
+\begin{multline}
+  \frac{\partial \sigma_{DE}}{\partial t} = -k_{de}\sigma_{DE}+k_E\sigma_D\rho_E\hspace{3cm}
+  \label{fig:FifthPDE}
+\end{multline}
 
-We next see the formation of MinE `rings' on the membranes of the
-polar caps.  As the freely diffusing MinE enters the cap portion it
-begins to encounter concentrated membrane bound MinD.  The MinE binds
-to this MinD and remians for a time on the walls in compound form.
-When it is released, it can diffuse naturally outward or inward
-towards the cell.  If it diffuses inward, there is less cross
-sectional wall for it to bump into and also less concentrated MinD:ATP
-to react with.  If it diffuses outward, the curvature of the cell wall
-cuases there to be a greater chance that it will encounter the cell
-membrane (for the same reason outlined for the MinD:ATP above) and if
-there is MinD:ATP bound there, there is a chance that it will bind to
-that protein and react again.  If it does diffuse in this directin, it
-will likely react with MinD:ATP before getting very far into the
-encap.  Thus after dettaching from the membrane at the edge of the
-MinD:ATP encap cluster, the MinE is most likely to travel a small
-distance further into the polar region and then attach and react again
-with MinD:ATP protein there.  This process results in the observed
-qualitative 'encroaching MinE ring' behavoir that releases MinD:ADP
-back into the cytoplasm.  This MinD:ADP will diffuse for a time before
-spontanosly uindergowing hydrolysis \fixme{is this right?} and
-reaching the MinD:ATP state that can bind to the membrane again.
-There is a strong chance that it has by this time diffused out of the
-polar region and is on its way to the opposite polar region of the
-cell.  If it hasn't then it will reattach to the MinD:ATP on the cell
-wall deeper into the endcap and will eventually be converged upon by
-the MinE ring, only to be released again in MinD:ADP form.
+Where $\rho$ is cytoplasmic protein density ($\mu m^{-3}$), $\sigma$
+is membrane bound density ($\mu m^{-2}$), $\mathcal{D}_D$ and
+$\mathcal{D}_{E}$ th diffusions constants for MinD and MinE,
+respectively, $k_D^{\textrm{ADP $\rightarrow$ ATP}}$ the rate of
+conversion from MinD:ADP to the MinD:ATP complex, $k_D$ the rate of
+MinD:ATP attachement to the membrane when no protein is already
+attached there, $k_{dD}$ the increase of this rate when MinD:ATP is
+present on the membrane, $k_{de}$ the rate of hydrolisis of the
+MinD:MinE:ATP complex, $k_E$ the rate of cytoplasmic MinE binding to
+membrane bound MinD:ATP complex, and $d_w$ is the distance from the
+point in space to the closest wall (which will always be
+perpendicular to this distance).  $\delta(d_w)$ has units of
+$\mu m^{-1}$ and will be zero everywhere except at the wall.
+Equations \ref{fig:FourthPDE} and \ref{fig:FifthPDE} will only be
+relevent at the membrane because the membrane bound density values
+will have no meaning in the cytoplasm where there is no membrane.
 
-Overall this process results in an extremely robust oscillatory
-behavoir of polar selection and oscillation in a wide variety of cell
-shapes.
+Our diffusion and reaction rates are shown below.  We are interested
+primarily with the effect of cellular shape on the protein
+oscillations, so we follow Huang's work\cite{huang2003dynamic} and do
+not deviate from these values.  Huang's simulations use total MinD and
+MinE concentrations of $1,000/\mu m$ and $350/\mu m$, respectively, in
+a cylindrical cell of radius $0.5\mu m$, and in our (non-cylindrical)
+cells we use the same number of proteins per unit volume.
 
- A 3d grid is constructed in cartesian
-coordinates with a grid spacing of .05\micron. We define our cell
-shapes and solve the reaction-diffusion equations numerically to
-observe the time evolution of the MinD and MinE concentrations inside
-the cell.
+\begin{gather*}
+  \mathcal{D}_D = \mathcal{D}_{E} = 2.5\micron^2/\text{sec}\\
+  k_D^{\textrm{ADP $\rightarrow$ ATP}} = 1/\textrm{sec,  }
+  k_D = 0.025 \micron /\textrm{sec}\\
+  k_{dD} = 0.0015 \micron^3/ \textrm{sec,  }
+  k_{de} = 0.7/\textrm{sec}\\
+  k_E = 0.093 \micron^3 /\textrm{sec}.
+\end{gather*}
+
+A 3d grid is constructed in cartesian coordinates with a grid spacing
+of .05\micron. We define our cell shapes and solve the
+reaction-diffusion equations numerically to observe the time evolution
+of the MinD and MinE concentrations inside the cell.
 
@@
 diffusion constants and and reaction rates,
-\begin{gather*} %format better
-  \mathcal{D}_D = \mathcal{D}_{E}  = 2.5 \micron^2/\text{sec}, \\
-  \sigma_D^{\textrm{ADP $\rightarrow$ ATP}}  = 1/\textrm{sec},  \sigma_D = 0.025 \micron /\textrm{sec}, \\
-  \sigma_{dD}  = 0.0015 \micron^3/ \textrm{sec}, \\
-  \sigma_{de}  = 0.7/\textrm{sec}, \sigma_E = 0.093 \micron^3 /\textrm{sec}.
-\end{gather*}
 
@@
 \subsection{Pill Shape}
+
+The reaction shown in Figure~\ref{fig:reactions} is cyclical so we can
+begin our observations at any stage in the cycle (which is presented
+for the natural cell shape in Fig.~\ref{image-p} below).  We consider
+first MinD:ATP floating freely in the cytoplasm.  The protein will not
+react with any other floating protein, and it will not spontenously
+shift back into the MinD:ADP stage of the cycle.  It will diffuse
+until it attaches to a cell membrane.  This is will happen most
+rapidly in regions of high curvature, where diffusion is more likely
+to lead to an encounter with a wall.  This effect is made more
+pronounced by the MinD:ATP tendency to attract and cluster on the
+membrane, as reflected in Equation~\ref{eq:d-on-wall}, which shows
+that when adjacent to the membrane, the rate of binding to the
+membrane is porportional to the amount of MinD already bound to the
+wall.  Initially, then, there is a strong tendency of MinD to cluster
+on the polar regions of the cell, where the curvature is highest.
+
+We next see the formation of MinE `rings' on the membranes of the
+polar caps.  As the freely diffusing MinE enters the cap portion it
+begins to encounter concentrated membrane bound MinD.  The MinE binds
+to this MinD and remians for a time on the walls in compound form.
+When it is released, it can diffuse naturally outward or inward
+towards the cell.  If it diffuses inward, there is less cross
+sectional wall for it to bump into and also less concentrated MinD:ATP
+to react with.  If it diffuses outward, the curvature of the cell wall
+cuases there to be a greater chance that it will encounter the cell
+membrane (for the same reason outlined for the MinD:ATP above) and if
+there is MinD:ATP bound there, there is a chance that it will bind to
+that protein and react again.  If it does diffuse in this directin, it
+will likely react with MinD:ATP before getting very far into the
+encap.  Thus after dettaching from the membrane at the edge of the
+MinD:ATP encap cluster, the MinE is most likely to travel a small
+distance further into the polar region and then attach and react again
+with MinD:ATP protein there.  This process results in the observed
+qualitative 'encroaching MinE ring' behavoir that releases MinD:ADP
+back into the cytoplasm.  This MinD:ADP will diffuse for a time before
+spontanosly uindergowing hydrolysis \fixme{is this right?} and
+reaching the MinD:ATP state that can bind to the membrane again.
+There is a strong chance that it has by this time diffused out of the
+polar region and is on its way to the opposite polar region of the
+cell.  If it hasn't then it will reattach to the MinD:ATP on the cell
+wall deeper into the endcap and will eventually be converged upon by
+the MinE ring, only to be released again in MinD:ADP form.
+
+Overall this process results in an extremely robust oscillatory
+behavoir of polar selection and oscillation in a wide variety of cell
+shapes.
 

### 2013-11-15 paper/paper.tex
updates to paper and pretty figure Tested everything on collins.

@@
 mechanism for MinD:ATP clustering that is shown in
-Equation~\ref{fig:FourthPDE}.  When brushing up against the cell
+Equation~\ref{eq:d-on-wall}.  When brushing up against the cell
 membrane, the MinD:ATP attachement rate increases linearly with the
@@
   +[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP}
-  \label{fig:FourthPDE}
+  \label{eq:d-on-wall}
 \end{multline}
@@
   \frac{\partial \sigma_{DE}}{\partial t} = -k_{de}\sigma_{DE}+k_E\sigma_D\rho_E\hspace{3cm}
-  \label{fig:FifthPDE}
+  \label{eq:FifthPDE}
 \end{multline}
@@
 $\mu m^{-1}$ and will be zero everywhere except at the wall.
-Equations \ref{fig:FourthPDE} and \ref{fig:FifthPDE} will only be
+Equations \ref{eq:d-on-wall} and \ref{eq:FifthPDE} will only be
 relevent at the membrane because the membrane bound density values
@@
   \includegraphics[width=\textwidth]{../data/shape-p/plots/image-plot--p-400-50-0-0-1500.pdf}
-  \caption{Frames from an animation showing a series of contour plots
-    of the concentration of proteins in different stages over time.
-    The density of proteins are integrated along the axis normal to
-    the page. The frames occur 2.5 seconds apart. \fixme{this looks
-      assymetric! That's a big problem.} \davidsays{I like this plot,
-      but would rather see it improved in a few ways.  I noticed the
-      implementation combines together bitmaps.  Nicer would be to use
-      subplots within matplotlib, so we output the plot directly as a
-      pdf.  Then we could also arrange things so there is much less
-      vertical white space.  It'd be nicer to have labels at the left
-      and a time axis at the bottom, with no labels by each image.  I
-      know this will take a while, so it's not yet a high priority.}}
+  \caption{Images of the concentration of each species in a natural
+    pill-shaped bacterium as a function of time, with darker regions
+    indicating higher concentration.  Frames from an animation showing
+    a series of contour plots of the concentration of proteins in
+    different stages over time.  The order of frames is such that
+    individual MinD proteins begin at the bottom of the plot (in the
+    MinD:ATP state in the cytoplasm), and progress upward until they
+    reach the MinE:MinD:ATP membrane-bound complex.  At that point,
+    they will spontaneously dissociate into cytoplasmic MinE (the top
+    row) and the starting state of cytoplasmic MinD:ADP.  The
+    densities plotted are integrated along the axis orthogonal to the
+    page, and the color scale is chosen separately for each species
+    with black as the maximum value over space and time.}
   \label{image-p}

### 2013-11-15 pyplots/image_plot.py

@@ -33,7 +33,7 @@ proteinList = ["nADP","nATP","ND","NDE","nE"]
 proteinLabels = ["MinD:ADP (ctyo)",
                  "MinD:ATP (cyto)",
                  "MinD:ATP (mem)",
-                 "MinE:MinD:ATP",
+                 "MinE:MinD:ATP (mem)",
                  "MinE (cyto)"]
 
 proteins = [0]*len(proteinList)
@@ -41,12 +41,13 @@ proteins = [0]*len(proteinList)
 for i in range(len(proteinList)):
     proteins[i] = load.data(proteinList[i],start_time,end_time)
 
-plt.figure(figsize=(10,4))
+plt.figure(figsize=(9,3.5))
 numtimes = int(end_time/dump_time_step)- int(start_time/dump_time_step)
 numproteins = len(proteins)
+skip_times = 2 # only plot every skip_times of the snapshots
 dZ = proteins[0].datashape[1]*1.05
-dY = proteins[0].datashape[0]*1.1
-kvals = range(int(end_time/dump_time_step)-int(start_time/dump_time_step))
+dY = proteins[0].datashape[0]*1.1/skip_times
+kvals = range(0, int(end_time/dump_time_step)-int(start_time/dump_time_step), skip_times)
 
 #axes = plt.subplot(1, 1, 1, axisbg='black')
 
@@ -55,10 +56,11 @@ for i in range(len(proteins)):
         maxval = timemax(proteins[i].dataset)/4
     else:
         maxval = timemax(proteins[i].dataset)
-    minval = timemin(proteins[i].dataset[int(start_time/dump_time_step):])
-    nlevels = 10
-    mylevels = np.linspace(minval,(1+1.0/nlevels)*maxval,nlevels)
-    Z, Y = np.meshgrid(np.arange(0,proteins[i].datashape[1],1), np.arange(0,proteins[i].datashape[0],1))
+    #minval = timemin(proteins[i].dataset[int(start_time/dump_time_step):])
+    nlevels = 20
+    mylevels = np.linspace(0,(1+1.0/nlevels)*maxval,nlevels)
+    Z, Y = np.meshgrid(np.arange(0,proteins[i].dataset[0].shape[1],1),
+                       np.arange(0,proteins[i].dataset[0].shape[0],1))
 #generate a sequence of .png's for each file (printed time step). these will be used to create a gif.
     for k in kvals:
[…]

### 2013-11-19 paper/paper.tex
Rewrote the second paragraph, which is hopefully more focused now. Fixed some grammar issues and edited a paragraph in methods.

@@
 \newcommand{\davidsays}[1]{{\color{red} [\green{David:} \emph{#1}]}}
+\newcommand{\renesays}[1]{{\color{red} [\green{Rene:} \emph{#1}]}}
 
@@
 \affiliation{Department of Physics, Oregon State University}
-\author{Rene WHAT. Zeto}
+\author{Rene W. Zeto}
 \affiliation{Department of Physics, Oregon State University}
@@
 \section{Introduction}
-It is vital that during the process of bacterial cell division a cell
+It is vital that during the process of bacterial cell division, a cell
 avoid minicelling, or splitting into daughter cells with lopsided
-volumes.  During this process a long FtsZ polymer chain develops on
-the cell wall in the center region of the cell that dictates the plane
-of division~\cite{adams2009bacterial,
-  lutkenhaus2007assembly}. Previous experimental studies have shown
-that the MinC protein, known to inhibit the FtZ
-polymer\cite{shen2010examination}, exhibits a pole to pole oscillatory
-behavoir in conjunction with the MinD and MinE proteins, while the
-oscillating MinE tends to be more localized in the center of the
-cell~\cite{hu1999topological, fu2001mine, shapiro2009and, yu1999ftsz,
-  raskin1999rapid}. The MinC protein will then have a higher time
-averaged concentration in the cell poles as opposed to the center
-region of the cell, aiding in prohibiting the FtZ from developing in
-the wrong region.
+volumes.  A long FtsZ polymer chain develops on the cell wall, in the
+center region of the cell, the region which dictates the plane of
+division~\cite{adams2009bacterial, lutkenhaus2007assembly}. Previous
+experimental studies have shown that the MinC protein, known to
+inhibit the FtZ polymer\cite{shen2010examination}, exhibits pole to
+pole oscillatory behavior in conjunction with the MinD and MinE
+proteins, while the oscillating MinE tends to be more localized in the
+center of the cell~\cite{hu1999topological, fu2001mine,
+  shapiro2009and, yu1999ftsz, raskin1999rapid}. The MinC protein will
+then have a higher time averaged concentration in the cell poles, as
+opposed to the center region of the cell, aiding in prohibiting the
+FtZ from developing in the wrong region.
 
-It is vital for the mechanism by which the cell accurately divides to
-be robust and indeed it has been shown to
-be\cite{touhami2006temperature}.  Studies have shown that the
-oscillations can effectively find poles in abberent cell
-shapes~\cite{corbin2002exploring} \cite{juarez2010changes}.  Varma et
-al. have studied three pronged connected tube shapes, both
-experimentally and in simulation\cite{varma2008min} and have shown
-that even in these oscillations develop in regular patterns. However,
-Mannik et al. have shown that there are limits to this
-robustness. Forcing cells into flattened, irregular cell shapes
-adversly effects the Min system's ability to maintain their regular
-oscillatory behavior \fixme{this link doesn't work =
-  cite{mannik2012robustness}} \cite{mannik2010bacteria}
-\cite{mannik2009bacterial}.  We follow the experimental work of Mannik
-et and use Huang's mean field differential equation reaction model to
-explore the model's ability to find regular oscillatory behavoir in a
-series of abberent shapes.  \davidsays{This paragraph could use some
-  work, and should reference Mannik early, and emphasize his research.
-  First paragraph sets the stage for why our work is important by
-  introducing the MinD system.  Second paragraph should explain why we
-  are studying the Min system in funny cell shapes.}
+The cell division process must be able to prevent minicelling, even
+under irregular conditions. Studies have shown that it is capable of
+performing this task for fairly perturbed cell
+shapes\cite{touhami2006temperature}. Mannik et al. have done some
+early experimental work showing regular oscillations of cell division
+systems in bacteria that were physically forced into unusual
+shapes. Varma et al. studied one particular example of a perturbed
+shape, a three-pronged tube, and found both experimental and
+simulation results\cite{varma2008min} supporting the idea that certain
+systems inside the cell begin to undergo oscillations inside the
+cell. These oscillations seem to seek out the extreme poles in the
+cell shape\cite{corbin2002exploring} \cite{juarez2010changes}, and
+effectively prevent minicelling in most cases. However, Mannik et
+al. have also shown that there are limitations to this
+mechanism\cite{mannik2010bacteria} \cite{mannik2009bacterial}. One
+instance of this behavior is observable when the cell has been forced
+into a flattened, irregular shape. Oscillations in this sort of cell
+shape are far from the regular sorts of oscillations seen in the
+computational work done by Huang et al\cite{huang2003dynamic}. We seek
+to apply a computational model to explore the more extreme or
+irregular cell shapes, in order to determine the limits of the steady
+cell oscillations seen by Mannik et al.
+
+%is this necessary? was in old paragraph.
+%\fixme{this link doesn't work =
+%  cite{mannik2012robustness}} \cite{mannik2010bacteria}
+%\cite{mannik2009bacterial}
 
@@
 MinD protein system. Early models involved free proteins that affect
-eachothers' rates of diffusion and membrane attachement but do not
+each others' rates of diffusion and membrane attachment, but do not
 combine into compound states~\cite{meinhardt2001pattern}.  In 2003
 Huang improved upon this work with a simple model based on MinD-MinE
-combination, ATPase hydrolysis, and MinD membrane attechent that when
-simulated exhibits accurate MinD oscillations in cylindrical
+combination, ATPase hydrolysis, and MinD membrane attachment that when
+simulated, exhibits accurate MinD oscillations in cylindrical
 cells~\cite{huang2003dynamic}. In this model cytoplasmic MinD is more
@@
 stochasticly account for variations of molecular interaction
-\cite{fange2006noise} and as well monte-carlo simulations that
-implement stochastic version of Huang's mean filed reaction rates
-confirm the major results obtained by Huang's model and more
-successfully predict experimentally observed oscillations in round
-cell phenotypes~\cite{drew2005polymerization, fange2006noise,
+\cite{fange2006noise} and monte-carlo simulations that implement this
+stochastic version of Huang's mean field reaction rates confirm the
+major results obtained by Huang's model, and more successfully predict
+experimentally observed oscillations in round cell
+phenotypes~\cite{drew2005polymerization, fange2006noise,
   huang2004min}. Biochemical models of broader scope have also been
 used to study the MinD system and show consistent
-results.\cite{arjunan2010new}.  However, in general the results of the
+results.\cite{arjunan2010new}.  However, in general, the results of the
 stochastic and monte-carlo simulations are similar to those given by
@@
   \frac{\partial \rho_{D:ADP}}{\partial t} = \mathcal{D}_D\nabla^2\rho_{D:ADP}-k_D^{ADP\rightarrow ATP}\rho_{D:ADP}\\
-  +\delta(d_w)k_{de}\sigma_{DE}\hspace{3.4cm}
+  +\delta(d_w)k_{de}\sigma_{DE},\hspace{3.4cm}
 \end{multline}
@@
   \frac{\partial \rho_{D:ATP}}{\partial t} = \mathcal{D}_D\nabla^2\rho_{D:ATP}+k_D^{ADP\rightarrow ATP}\rho_{D:ADP}\\
-  -\delta(d_w)[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP}
+  -\delta(d_w)[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP},
 \end{multline}
@@
   \frac{\partial \rho_E}{\partial t} = \mathcal{D}_E\nabla^2\rho_E+\delta(d_w)k_{de}\sigma_{DE}
-  -\delta(d_w)k_E \sigma_D \rho_E
+  -\delta(d_w)k_E \sigma_D \rho_E,
 \end{multline}
@@
   \frac{\partial \sigma_d}{\partial t} = -k_E\rho_d\rho_E
-  +[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP}
+  +[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP},
   \label{eq:d-on-wall}
@@
   \frac{\partial \sigma_{DE}}{\partial t} = -k_{de}\sigma_{DE}+k_E\sigma_D\rho_E\hspace{3cm}
-  \label{eq:FifthPDE}
+  \label{eq:FifthPDE},
 \end{multline}
 
-Where $\rho$ is cytoplasmic protein density ($\mu m^{-3}$), $\sigma$
+where $\rho$ is cytoplasmic protein density ($\mu m^{-3}$), $\sigma$
 is membrane bound density ($\mu m^{-2}$), $\mathcal{D}_D$ and
@@
 
-A 3d grid is constructed in cartesian coordinates with a grid spacing
-of .05\micron. We define our cell shapes and solve the
-reaction-diffusion equations numerically to observe the time evolution
-of the MinD and MinE concentrations inside the cell.
-
 We start our cells with the MinD and MinE concentrations that are
-reported as wild type concentrations by Huang et al . We as well use the same reaction
-diffusion constants and and reaction rates,
+reported as wild type concentrations by Huang et al. These
+concentration values are 1273 $\mu m^{-3}$ and 445 $\mu m^{-3}$,
+respectively. A 3d grid is then constructed in cartesian coordinates,
+with a grid spacing of .05\micron. We define our cell shapes and solve
+the reaction-diffusion equations numerically to observe the time
+evolution of the MinD and MinE concentrations inside the
+cell. \renesays{This last sentence sweeps a lot under the rug. How
+  much more detail should be given to the computational method?}
 

### 2013-11-19 paper/paper.tex
remove answered davidsays and recolor Rene blue Tested everything on collins.

@@
 \newcommand{\davidsays}[1]{{\color{red} [\green{David:} \emph{#1}]}}
-\newcommand{\renesays}[1]{{\color{red} [\green{Rene:} \emph{#1}]}}
+\newcommand{\renesays}[1]{{\color{red} [\blue{Rene:} \emph{#1}]}}
 
@@
 are cylinders with hemisphere endcaps instead of pure cylindridrical
-shapes. \davidsays{Double-check the Huang paper on their shapes.}  Our
+shapes.  Our
 cylinderidrical radius is $0.50\micron$ and the lengths of our cells

### 2013-11-21 paper/paper.tex
modified the model section and the shapes section in the paper Tested everything on node37.

@@
 \newcommand{\renesays}[1]{{\color{red} [\blue{Rene:} \emph{#1}]}}
+\newcommand{\jeffsays}[1]{{\color{red} [\blue{Jeff:} \emph{#1}]}}
 
@@
 phosphate, and MinD:ADP back into the cell.  The MinD:ADP will undergo
-nucleotide exchange and begin again the cyclic process.  There is a
-mechanism for MinD:ATP clustering that is shown in
-Equation~\ref{eq:d-on-wall}.  When brushing up against the cell
-membrane, the MinD:ATP attachement rate increases linearly with the
-density of MinD:ATP already attached.  This model is defined by a set of
-five reaction-diffusion equations:
+nucleotide exchange and begin again the cyclic process.  This model is
+defined by a set of five reaction-diffusion equations:
 
@@
   \frac{\partial \rho_{D:ATP}}{\partial t} = \mathcal{D}_D\nabla^2\rho_{D:ATP}+k_D^{ADP\rightarrow ATP}\rho_{D:ADP}\\
-  -\delta(d_w)[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP},
+  -\delta(d_w)[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP}
 \end{multline}
@@
   \frac{\partial \rho_E}{\partial t} = \mathcal{D}_E\nabla^2\rho_E+\delta(d_w)k_{de}\sigma_{DE}
-  -\delta(d_w)k_E \sigma_D \rho_E,
+  -\delta(d_w)k_E \sigma_D \rho_E
 \end{multline}
@@
   \frac{\partial \sigma_d}{\partial t} = -k_E\rho_d\rho_E
-  +[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP},
+  +[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP}
   \label{eq:d-on-wall}
@@
   \frac{\partial \sigma_{DE}}{\partial t} = -k_{de}\sigma_{DE}+k_E\sigma_D\rho_E\hspace{3cm}
-  \label{eq:FifthPDE},
+  \label{eq:FifthPDE}
 \end{multline}
@@
 Our diffusion and reaction rates are shown below.  We are interested
-primarily with the effect of cellular shape on the protein
+primarily in the effect of cellular shape on the protein
 oscillations, so we follow Huang's work\cite{huang2003dynamic} and do
-not deviate from these values.  Huang's simulations use total MinD and
-MinE concentrations of $1,000/\mu m$ and $350/\mu m$, respectively, in
-a cylindrical cell of radius $0.5\mu m$, and in our (non-cylindrical)
-cells we use the same number of proteins per unit volume.
+not deviate from the wild type values used in that work.  Huang's
+simulations use total MinD and MinE concentrations of $1,000/\mu m$
+and $350/\mu m$, respectively, in a cylindrical cell of radius $0.5\mu
+m$, and in our (non-cylindrical) cells we use the same number of
+proteins per unit volume.  These concentration values are 1273 $\mu
+m^{-3}$ and 445 $\mu m^{-3}$, respectively.
 
@@
 
-We start our cells with the MinD and MinE concentrations that are
-reported as wild type concentrations by Huang et al. These
-concentration values are 1273 $\mu m^{-3}$ and 445 $\mu m^{-3}$,
-respectively. A 3d grid is then constructed in cartesian coordinates,
-with a grid spacing of .05\micron. We define our cell shapes and solve
-the reaction-diffusion equations numerically to observe the time
-evolution of the MinD and MinE concentrations inside the
-cell. \renesays{This last sentence sweeps a lot under the rug. How
-  much more detail should be given to the computational method?}
+A 3d grid is then constructed in cartesian coordinates, with a grid
+spacing of .05\micron. We define our cell shapes and solve the
+reaction-diffusion equations numerically to observe the time evolution
+of the MinD and MinE concentrations inside the cell. \renesays{This
+  last sentence sweeps a lot under the rug. How much more detail
+  should be given to the computational method?}
 
-\section{Cell shapes}
-
-In order to address the limits at which the stability of the
-oscillations of the Min system break down, as observed by Mannik
-\emph{et al.}~\cite{mannik2012robustness}, we model the Min system in
-a variety of cell shapes.  We begin with natural pill-shaped cells,
-and the proceed to examine a number of flattened pancake-like shapes,
-which reflect the experiment of Mannik \emph{et al.}, in which
-bacteria were confined within a thin slit~\cite{mannik2012robustness}.
-Our pill shapes differ from those of Huang \emph{et al.} in that they
-are cylinders with hemisphere endcaps instead of pure cylindridrical
-shapes.  Our
-cylinderidrical radius is $0.50\micron$ and the lengths of our cells
-(measured between the tips of the endcaps) are $5\micron$, $4\micron$, $3\micron$,
-and $2.5\micron$.
-
-With our flattened cell shapes we mean to study cells that are
-parrallel to those lodged into crevices by Mannik so we give them
-height of $0.25\micron$ \cite{mannik2012robustness}.  Viewed from the top
-down the cells will have the shapes described below and viewed from
-the side they have at their edges a semicircular protrusion (one may
-imagine the edges of a pancake).
-
-Our first group of (three) flattened cell shapes are triangular.  One
-of them is equilateral, one has a 3-4-5 right angle shape, and the
-last is iscoscolese.
-
-Our second group of (four) flattened cells are our own creations,
-designed to investigate different patterns of protein oscillation
-behavoir.
-
-The cell shapes and the sections that we split them into in our data
-analysis are shown in Figure \fixme{We need a big figure with all of this!!}.
-
-Kubitschek has shown in multiple experiments that at the time of cell
-division cells have a volume that is within a range of roughly
-$1\micron^3$ to $2\micron^3$~\cite{kubitschek1990cell,
-  kubitschek1968linear}.  We follow Huang's
-simulations\cite{huang2003dynamic} and Mannik's experiments
-\fixme{this link doesn't work = cite{mannik2012robustness}} and model
-cells that are slightly larger than this range.  Amoung our flattened
-cells the two dimensional length scales are tuned so that every total
-cell volume is very close to $3\micron^3$.  \fixme{should we just
-  leave it to the reader to figure out for themselves what our pill
-  shape volumes are?}
-
-To interpret the results, we generated several different plot views of
-the printed simulation data. These plots included a time averaged view
-of the protein densities in the cell; a plot tracking the location of
-protein concentrations that were global maxima in space and local maxima in
-time; and an animated view that showed the actual dispersion of
-protein concentrations in the cell over time.
-\section{Specific Results}
-
-\subsection{Pill Shape}
-
-The reaction shown in Figure~\ref{fig:reactions} is cyclical so we can
-begin our observations at any stage in the cycle (which is presented
-for the natural cell shape in Fig.~\ref{image-p} below).  We consider
-first MinD:ATP floating freely in the cytoplasm.  The protein will not
-react with any other floating protein, and it will not spontenously
-shift back into the MinD:ADP stage of the cycle.  It will diffuse
-until it attaches to a cell membrane.  This is will happen most
-rapidly in regions of high curvature, where diffusion is more likely
-to lead to an encounter with a wall.  This effect is made more
-pronounced by the MinD:ATP tendency to attract and cluster on the
+The reactions shown in Figure~\ref{fig:reactions} are cyclical so we
+can begin our observations at any stage in the cycle (which is
+presented for the natural, pill shapes cell in Fig.~\ref{image-p}
+below).  We consider first MinD:ATP floating freely in the cytoplasm.
+The protein will not react with any other floating protein, and it
+will not spontenously shift back into the MinD:ADP stage of the cycle.
+It will diffuse until it attaches to a cell membrane.  This will
+happen most rapidly in cytoplasmic regions that are close to membrane
+regions of high curvature, where diffusion in a random direction is
+more likely to lead to an encounter with a wall.  This effect is made
+more pronounced by the MinD:ATP tendency to attract and cluster on the
 membrane, as reflected in Equation~\ref{eq:d-on-wall}, which shows
@@
 begins to encounter concentrated membrane bound MinD.  The MinE binds
-to this MinD and remians for a time on the walls in compound form.
-When it is released, it can diffuse naturally outward or inward
-towards the cell.  If it diffuses inward, there is less cross
-sectional wall for it to bump into and also less concentrated MinD:ATP
-to react with.  If it diffuses outward, the curvature of the cell wall
-cuases there to be a greater chance that it will encounter the cell
-membrane (for the same reason outlined for the MinD:ATP above) and if
-there is MinD:ATP bound there, there is a chance that it will bind to
-that protein and react again.  If it does diffuse in this directin, it
-will likely react with MinD:ATP before getting very far into the
-encap.  Thus after dettaching from the membrane at the edge of the
-MinD:ATP encap cluster, the MinE is most likely to travel a small
-distance further into the polar region and then attach and react again
-with MinD:ATP protein there.  This process results in the observed
-qualitative 'encroaching MinE ring' behavoir that releases MinD:ADP
-back into the cytoplasm.  This MinD:ADP will diffuse for a time before
-spontanosly uindergowing hydrolysis \fixme{is this right?} and
-reaching the MinD:ATP state that can bind to the membrane again.
-There is a strong chance that it has by this time diffused out of the
-polar region and is on its way to the opposite polar region of the
-cell.  If it hasn't then it will reattach to the MinD:ATP on the cell
-wall deeper into the endcap and will eventually be converged upon by
-the MinE ring, only to be released again in MinD:ADP form.
+to this MinD and remains for a time on the walls in compound form.
+When it is released, it has the two options of diffusing naturally
+outward or inward towards the cell.  If it diffuses inward, there is
+less cross sectional wall for it to bump into and also less
+concentrated MinD:ATP to react with.  If it diffuses outward, the
+curvature of the cell wall cuases there to be a greater probability
+per unit time that it will encounter the cell membrane (for the same
+reason outlined for the MinD:ATP above) where there is more membrane
+bound MinD:ATP. If it does diffuse in this directin, it will likely
+react with MinD:ATP before getting very far into the encap.  This
+process results in the observed qualitative 'encroaching MinE ring'
+behavoir that releases MinD:ADP back into the cytoplasm.  This
+MinD:ADP will diffuse for a time before spontanosly undergowing
+nucleotide exchange and reaching the MinD:ATP state that
+can bind to the membrane again.  There is a strong chance that it has
+by this time diffused out of the polar region and is on its way to the
+opposite polar region of the cell.  If it hasn't then it will reattach
+to the MinD:ATP on the cell wall deeper into the endcap and will
+eventually be converged upon by the MinE ring, only to be released
+again in MinD:ADP form.
 
-Overall this process results in an extremely robust oscillatory
+Overall this process results in extremely robust oscillatory
 behavoir of polar selection and oscillation in a wide variety of cell
 shapes.
+
+\section{Cell shapes}
+
+We mean to investigate the geometric limits of the Min system
+oscillations, as observed by Mannik \emph{et
+  al.}~\cite{mannik2012robustness}, so we model the Min system in a
+variety of cell shapes.  We begin with naturally occuring pill-shaped
+cells and then proceed to examine a number of flattened pancake-like
+shapes, which reflect the experiment of Mannik \emph{et al.}, in which
+bacteria were confined within a thin slit~\cite{mannik2012robustness}.
+Our pill shapes differ from those of Huang \emph{et al.} in that they
+are cylinders with hemisphere endcaps instead of pure cylindrical
+shapes.  Our cylinderidrical radius is $0.5\micron$ and the lengths
+of our cells (measured between the tips of the endcaps) are
+$5\micron$, $4\micron$, $3\micron$, and $2.5\micron$.
+
+With our flattened cell shapes we mean to study cells that are
+parrallel to those lodged into crevices by Mannik so we give them
+height of $0.25\micron$ \cite{mannik2012robustness}.  Viewed from the top
+down the cells will have the shapes described below and viewed from
+the side they have at their edges a semicircular protrusion (one may
+imagine the edges of a pancake).
+
+Our first group of (three) flattened cell shapes are triangular when
+viewed from above.  One of them is equilateral, one has a 3-4-5 right
+angle shape, and the last is iscoscolese.
+
+Our second group of (two) flattened cells are designed to replicate
+those published by Mannik, in order to compare the results of the
+simulation model with the experimental results in that work.
+
+Our third group of (three) flattened cells are our own creations,
+designed to investigate different patterns of protein oscillation
+behavoir.
+
+Kubitschek has shown in multiple experiments that at the time of cell
+division cells have a volume that is within a range of roughly
+$1\micron^3$ to $2\micron^3$~\cite{kubitschek1990cell,
+  kubitschek1968linear}.  We follow Huang's
+simulations\cite{huang2003dynamic} and Mannik's experiments and model
+cells that are slightly larger than this range.  Amoung our flattened
+cells the two dimensional length scales are tuned so that total cell
+volumes are very close to $3\micron^3$. \jeffsays{I'm not sure how
+  true this is.  We should go through and check.  There've been a few
+  implementations of printouts reporting volume in the cpp}
+\section{Specific Results}
+
+\subsection{Pill Shape}
 

### 2013-11-21 paper/paper.tex
mostly rewrite pill section, and start synchronizing box plot with image plot Tested everything on collins.

@@
 m^{-3}$ and 445 $\mu m^{-3}$, respectively.
-
 \begin{gather*}
@@
 \end{gather*}
-
-A 3d grid is then constructed in cartesian coordinates, with a grid
+A 3D grid is then constructed in cartesian coordinates, with a grid
 spacing of .05\micron. We define our cell shapes and solve the
-reaction-diffusion equations numerically to observe the time evolution
-of the MinD and MinE concentrations inside the cell. \renesays{This
-  last sentence sweeps a lot under the rug. How much more detail
-  should be given to the computational method?}
+reaction-diffusion partial differential equations numerically to
+observe the time evolution of the MinD and MinE concentrations inside
+the cell.
 
@@
 
-We begin with the naturally occuring pill shape.  We peice this shape
-together as two hemispherical endcaps attached on either end of a
-cylinder.  This shape follows the early simulations of Huang \emph{et
-  al.} but differs in that we have added the end caps for a more
-natural shape, expecting similar results.  We test cells of radius
-$.5\micron$ and of lengths $2\micron$, $3\micron$, and $5\micron$
-between both tips of the end caps. In all these models we observe
-quick establishement (within a few periods) of extremely regular
-oscillatory behavoir that lasts indefinitely, with periods that
-closely agree with the results of Huang \emph{et al.}
-Table~\ref{tab:pill-periods} shows the periods of oscillations
-at different cell lengths.
+We begin with the naturally occuring pill cell shape.  We peice this
+shape together as two hemispherical endcaps attached on either end of
+a cylinder.  This shape follows the early simulations of Huang
+\emph{et al.} but differs in that we have added the end caps for a
+more natural shape, expecting similar results.  We test cells of
+radius $.5\micron$ and of lengths $2\micron$, $3\micron$, and
+$5\micron$ measured from the tip of one end cap to the top of the
+other. In each case, we observe quick establishement (within a few
+periods) of extremely regular oscillatory behavoir that lasts
+indefinitely.  The period increases with cell length, as shown in
+Table~\ref{tab:pill-periods}, in agreement with the results of Huang
+\emph{et al.}.
 
@@
   \end{tabular}
-  \caption{Period According to Pill Length}\label{tab:pill-period}
+  \caption{Period of oscillation according to length of cell for
+    pill-shaped cells.}\label{tab:pill-periods}
 \end{table}
@@
 the process in a series of frames taken from simulation animations.
-Each frame is 2.5 seconds ahead of the last.
+Each frame is 2.5 seconds ahead of the last, and each image shows a
+the concentration of a given state of protein summed over the
+coordinate orthogonal to the page.  The color scale for each protein
+state is set according to the maximum density observed.
 
-Consider Figure \ref{image-p}.  In the beginning, the cytoplasmic
-nATP is roughly evenly distributed throughout the cell.  There is nADP
-concentrated in the left pole and it will transform into nATP.  At 2.5
-seconds we see membrane bound MinD:ATP form on the right side of the
-cell.  It avoids the left side because there is a concentration of
-cytoplasmic MinE on the left side and compared to the right side,
-which is empty of MinE, MinD:ATP attaching to the wall on the left has
-no time to collect and cluster before reacting.  One can see how as
-the MinE spreads out rightward, the the clustered membrane bound
-MinD:ATP stays just at the edge of it, always to the right.  Where the
-two meet there is at every time step a spike in membrane bound
-MinD-MinE:ATP, resulting from the MinE reaction with the MinD on the
-wall.  One can see from roughly 5 seconds to 17.5 seconds the
-cytoplasmic MinE chases in a way the MinD towards the right, reacting
-with it as it clusters on the wall.  Upon reaching the right side, the
-MinD is in a way trapped, and the MinE now concentrated in that pole
-will react until the MinD has diffused back towards the other side and
-there is no more membrane bound MinD:ATP to react with.  The cycle
-then begins again.
+In the beginning, the cytoplasmic MinD:ATP is roughly evenly
+distributed throughout the cell with close to its peak density.  There
+is a high concentration of MinD on the membrane (in both its
+membrane-bound states) at the lower end of the cell, and there is also
+cytoplasmic MinD:ADP concentrated in the lower end, which has recently
+left the cell membrane.   There is relatively little cytoplasimic
+MinE, as it is primarily bound to the lower end of the membrane.
+
+After ??? seconds, very little MinD remains bound to the membrane, and
+there is a high concentration of cytoplasmic MinE in the lower half of
+the cell.  In the mean time MinD has begun binding in significant
+quantities to the upper half of the cell membrane, resulting in a
+diminishing of the concentration of cytoplasmic MinD:ATP in the upper
+half of the cell.  At this stage, we begin to see the formation of the
+``MinE ring'' in the center of the cell---visible here in the plot of
+the concentration of membrane-bound MinE:MinD:ATP as two lines
+representing a cross section of the ring.  This ring forms as the
+cytoplasmic MinE reacts with the membrane-bound MinD:ATP, and leads to
+the removal of MinD from the membrane.
+
+From ??? seconds to ??? seconds, we see the MinE ring progress
+upwards, as the cytoplasmic MinE diffuses in that direction,
+progressively removing the membrane-bound MinD from eventually all but
+the very top of the cell membrane.  During this process, the MinD:ATP
+bound to the top of the cell membrane is attracting increasing
+quantities of MinD:ATP from the cytoplasm.  At ??? seconds, the cell
+is in the mirror image state from which it started, and the period is
+half-complete.  The second half of the period is a mirror image of the
+process just observed, as MinD is driven from the membrane at the top
+of the cell, begins binding to the lower half of the cell and a MinE
+ring pushes it back down to lower end of the cell.
 
 \begin{figure}
-  %%\includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-400-50-0-0-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-200-50-0-0-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-400-50-0-0-1500}
+  %\includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-200-50-0-0-1500}
   \caption{Total protein fluctuation in the right, middle, and left
@@
 
-Figure \ref{box-p} is a plot of the total fraction of
-MinD found in each stage of the cycle in each of three sections of the
-cell (we have split the pill into two polar sections and one center
-section) over time.  One complete oscillation period is shown, in
-which one of the poles begins and ends at a maximum density
-concentration and the other a minimum density concentration.  Looking
-at the evolution of the latter, we see an initial high concentration
-of cytoplasmic MinD:ATP, as the this protein diffuses into the polar
-region, followed by a dip in this and large spike in membrane bound
-MinD:ATP, as the protein clusters onto the polar cell wall, followed
-by a spike in the memebrane bound MinE:MinD:ATP stage of protein,
-together with a slight rise in cytoplasmic MinD:ADP as the MinD
-dettaches from the wall.
+\davidsays{We should make Fig. \ref{box-p} and Fig. \ref{image-p} plot
+  for precisely the same times, that will make it way easier to read
+  the two plots.}  While Fig.~\ref{image-p} is helpful for visualizing
+the process occuring in the Min system, it is does not show the
+relative number of proteins in each state.  To visualize this
+information, we plot in Fig.~\ref{box-p} the fraction of MinD found in
+each stage of the cycle in each of three sections of the cell---top,
+middle and bottom---as a function of time over one period.  The time
+axis is the same as in Fig.~\ref{image-p}.  Looking at the evolution
+of the latter, we see an initial high concentration of cytoplasmic
+MinD:ATP, as the this protein diffuses into the polar region, followed
+by a dip in this and large spike in membrane bound MinD:ATP, as the
+protein clusters onto the polar cell wall, followed by a spike in the
+memebrane bound MinE:MinD:ATP stage of protein, together with a slight
+rise in cytoplasmic MinD:ADP as the MinD dettaches from the wall.
 
@@
 \section{Conclusion}
+\bibliography{paper}
+
+\end{document}
+
 \section*{Appendix}
-\bibliography{paper}
 

### 2013-11-21 pyplots/box_plot.py

@@ -140,8 +140,8 @@ def main():
             if "E_" in proteinType:
                 plotNameList_E += ["%s-%s"%(box,proteinType)]
 
-    print ""
-    print "plotNameList before ", plotNameList_D, "\n"
+    #print ""
+    #print "plotNameList before ", plotNameList_D, "\n"
     new_plotNameList_D = [0]*len(plotNameList_D)
     P_Ord = [3,0,2,1,7,4,6,5,11,8,10,9]
     if load.f_param4 == '97.00':
@@ -152,7 +152,7 @@ def main():
         new_plotNameList_D[i] = plotNameList_D[P_Ord[i]]
     for i in range(len(plotNameList_D)):
         plotNameList_D[i] = new_plotNameList_D[i]
-    print "plotNameList after ",plotNameList_D,"\n"
+    #print "plotNameList after ",plotNameList_D,"\n"
     plotProteinLabels = ['MinD:ATP (cyto)','MinD:ATP (mem)','MinE:MinD:ATP','MinD:ADP (cyto)']
 
 
@@ -176,6 +176,17 @@ def main():
     start = int(tot_time*start_time_as_frac_of_ten/10.0/box_time_step)
     end = int(tot_time*end_time_as_frac_of_ten/10.0/box_time_step)
     (start, end) = find_period(plotCurveList_D[3])
+
+    # print useful coordination data
+    period = timeAxis[end-1] - timeAxis[start]
+    print 'period is', period
+    firsttime = timeAxis[start]
+    while firsttime > period:
+        firsttime -= period
+    print 'early start time is', firsttime
+    # now offset time so it starts at zero
+    timeAxis = timeAxis - timeAxis[start]
+
     if load.f_param4 == '97.00' or (load.f_shape == 'triangle' and load.f_param3 == '6.01'):
         if load.f_param4 == '97.00':
             start_time_as_frac_of_ten = 0
@@ -185,7 +196,6 @@ def main():
             end_time_as_frac_of_ten = 9.00
         start = int(tot_time*start_time_as_frac_of_ten/10.0/box_time_step)
         end = int(tot_time*end_time_as_frac_of_ten/10.0/box_time_step)
-
 
     #print set(plotCurveList_D[1]).union(set(plotCurveList_D[2]))
 
@@ -266,7 +276,7 @@ def main():
         if load.f_param4 == '96.00':
             #rightup = 2, rightdown = 1, leftup = 4, leftdown = 3
             mycolors = ['g','r','c','m']
-        print mycolors
+        #print mycolors
[…]

### 2013-11-21 pyplots/file_loader.py

@@ -58,13 +58,14 @@ class data(object):
 
 #loads the files for creating the data object.
 def get_filenames(protein,start_time,end_time):
+    dump_time_step = 0.5 # seconds
     dat_filenames = []
     if end_time == 0:
         for fn in glob.iglob("./data/shape-%s/%s%s%s%s-%s-%s-%s-%s-%s-%s-*.dat"%(f_shape,debug_str,hires_str,slice_str,protein,f_shape,f_param1,f_param2,f_param3,f_param4,f_param5)):
             dat_filenames.append(fn)
     if end_time != 0:
-        for i in np.arange(start_time,end_time,2.5):
-            file_num = round(i/2.5)
+        for i in np.arange(start_time,end_time,dump_time_step):
+            file_num = round(i/dump_time_step)
             dat_filenames.append("./data/shape-%s/%s%s%s%s-%s-%s-%s-%s-%s-%s-%03d.dat"%
                                  (f_shape,debug_str,hires_str,slice_str,protein,f_shape,f_param1,f_param2,f_param3,f_param4,f_param5,file_num))
     dat_filenames = sorted(dat_filenames)

### 2013-11-21 pyplots/image_plot.py

@@ -19,7 +19,7 @@ start_time = float(sys.argv[7])
 end_time = float(sys.argv[8])
 
 
-dump_time_step = 2.5
+dump_time_step = 0.5
 
 #computes the global maximum over a set of two dimensional arrays (stored as files)
 def timemax(protein):

### 2013-11-25 paper/paper.tex
Switch to shorter pill shape in paper and synchronize image and box plot Tested everything on node32.

@@
 \begin{figure*}
-  \includegraphics[width=\textwidth]{../data/shape-p/plots/image-plot--p-400-50-0-0-1500.pdf}
+  \includegraphics[width=\textwidth]{../data/shape-p/plots/image-plot--p-300-50-0-0-1500.pdf}
   \caption{Images of the concentration of each species in a natural
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-400-50-0-0-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-300-50-0-0-1500}
   %\includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-200-50-0-0-1500}
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-p/plots/ave-plot_D--p-200-50-0-0-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-p/plots/ave-plot_D--p-300-50-0-0-1500}
   \caption{Average protein density per unit area of wall for the wall
@@
 
-%% \begin{center}
-%%   \begin{figure}
-%%     {\includegraphics[width=\paperwidth]{../data/shape-randst/plots/image-plot_E--randst-25-602-602-9900-1500}}
-%%     \caption{Attempt at adding image plot to paper.}
-%%     \label{image-plot}
-%%   \end{figure}
-%% \end{center}
-
 \subsubsection{Randst-97-}

### 2013-11-25 pyplots/box_plot.py

@@ -53,8 +53,7 @@ def stackData(plotList):
     #parse the input
     tempList = []
     for proteinData in plotList:
-        splitString = proteinData.split('-')
-        (protein, boxName) = (splitString[0], splitString[1])
+        protein, boxName = proteinData.split('-')
         tempList += [returnData(boxName,protein)]
 
     #"stack" the lists
@@ -72,6 +71,7 @@ def find_period(f):
       period.  If we cannot find the period accurately, just return
       the entire range.
     """
+    f = -f
     # first we look at the fft to get a guess at the period (probably
     # not *too* accurate or too bad).
     fk = np.fft.fft(f)
@@ -175,15 +175,18 @@ def main():
     tot_time = len(plotCurveList_D[0])*box_time_step
     start = int(tot_time*start_time_as_frac_of_ten/10.0/box_time_step)
     end = int(tot_time*end_time_as_frac_of_ten/10.0/box_time_step)
-    (start, end) = find_period(plotCurveList_D[3])
+    (start, end) = find_period(plotCurveList_D[len(plotCurveList_D)-2])
+    (start, end) = find_period(np.array(returnData(boxList[len(boxList)-1], 'D_ND')))
 
     # print useful coordination data
     period = timeAxis[end-1] - timeAxis[start]
     print 'period is', period
     firsttime = timeAxis[start]
-    while firsttime > period:
+    while firsttime > 9*period:
         firsttime -= period
     print 'early start time is', firsttime
+    print 'and end time is ',firsttime+period
+    print 'and file numbers are', firsttime*2, 'and', (firsttime+period)*2
     # now offset time so it starts at zero
     timeAxis = timeAxis - timeAxis[start]
 
@@ -199,32 +202,7 @@ def main():
 
     #print set(plotCurveList_D[1]).union(set(plotCurveList_D[2]))
 
-    arrow_start = start+int(0.05*(end-start))
-    arrow_x = [arrow_start]*len(plotCurveList_D)
-    for i in range(arrow_start,arrow_start + int((end-start)/100)):
-            if ((plotCurveList_D[0][arrow_x[0]]-0) < (plotCurveList_D[0][i]-0)):
-                arrow_x[0] = i
-    for type in range(1,len(plotCurveList_D)):
-        for i in range(arrow_start,arrow_start + int((end-start)/100)):
[…]

### 2013-11-25 pyplots/image_plot.py

@@ -65,11 +65,11 @@ for i in range(len(proteins)):
     for k in kvals:
         page = proteins[i].dataset[k]
         page[page>maxval] = maxval
-        plt.contourf(Y+k*dY, Z+i*dZ, page, cmap=plt.cm.hot_r, levels=mylevels)
+        plt.contourf(Y+k*dY, proteins[0].datashape[1]-Z+i*dZ, page, cmap=plt.cm.hot_r, levels=mylevels)
 plt.axes().get_yaxis().set_ticks([(i+0.5)*dZ for i in range(len(proteinList))])
 plt.axes().get_yaxis().set_ticklabels(proteinLabels)
-plt.axes().get_xaxis().set_ticks([(0.5+k)*dY for k in kvals[::5*skip_times]])
-plt.axes().get_xaxis().set_ticklabels([int(k*dump_time_step) for k in kvals[::5*skip_times]])
+plt.axes().get_xaxis().set_ticks([(0.5+k)*dY for k in kvals[::int(2.5*skip_times)]])
+plt.axes().get_xaxis().set_ticklabels([int(k*dump_time_step) for k in kvals[::int(2.5*skip_times)]])
 plt.axes().set_aspect('equal')
 plt.axes().get_yaxis().set_ticks_position('none')
 plt.axes().get_xaxis().set_ticks_position('none')

### 2013-11-27 paper/paper.tex
a few pill edits Tested everything on collins.

@@
     pill-shaped bacterium as a function of time, with darker regions
-    indicating higher concentration.  Frames from an animation showing
+    indicating higher concentration.  The cells pictured are
+    $4\micron$ in length, measured from end to end.  Frames from an animation showing
     a series of contour plots of the concentration of proteins in
@@
 
-In the beginning, the cytoplasmic MinD:ATP is roughly evenly
-distributed throughout the cell with close to its peak density.  There
-is a high concentration of MinD on the membrane (in both its
-membrane-bound states) at the lower end of the cell, and there is also
-cytoplasmic MinD:ADP concentrated in the lower end, which has recently
-left the cell membrane.   There is relatively little cytoplasimic
-MinE, as it is primarily bound to the lower end of the membrane.
+At $t=0$ in Figs.~\ref{image-p}~and~\ref{box-p}, the cytoplasmic MinE
+is concentrated in the lower portion of the cell, and is diffusing
+upward.  The MinD protein is initially concentrated on the membrane in
+the upper portion of the cell.  At the boundary between the
+cytoplasmic MinE and the membrane-bound MinD, there is a ring of the
+membrane-bound MinE:MinD complex, which is moving towards the upper
+end of the cell, removing the MinD from the membrane as it goes.  The
+MinD is removed from the membrane in its MinD:ADP form, which begins
+to accumulate at the upper end of the cell, peaking peaking at around
+10 seconds.
 
-After ??? seconds, very little MinD remains bound to the membrane, and
-there is a high concentration of cytoplasmic MinE in the lower half of
-the cell.  In the mean time MinD has begun binding in significant
-quantities to the upper half of the cell membrane, resulting in a
-diminishing of the concentration of cytoplasmic MinD:ATP in the upper
-half of the cell.  At this stage, we begin to see the formation of the
-``MinE ring'' in the center of the cell---visible here in the plot of
-the concentration of membrane-bound MinE:MinD:ATP as two lines
-representing a cross section of the ring.  This ring forms as the
-cytoplasmic MinE reacts with the membrane-bound MinD:ATP, and leads to
-the removal of MinD from the membrane.
-
-From ??? seconds to ??? seconds, we see the MinE ring progress
-upwards, as the cytoplasmic MinE diffuses in that direction,
-progressively removing the membrane-bound MinD from eventually all but
-the very top of the cell membrane.  During this process, the MinD:ATP
-bound to the top of the cell membrane is attracting increasing
-quantities of MinD:ATP from the cytoplasm.  At ??? seconds, the cell
-is in the mirror image state from which it started, and the period is
-half-complete.  The second half of the period is a mirror image of the
-process just observed, as MinD is driven from the membrane at the top
-of the cell, begins binding to the lower half of the cell and a MinE
-ring pushes it back down to lower end of the cell.
+At 15 seconds, the membrane-bound MinD:ATP has been essentially
+removed from the top end of the cell, and MinD:ATP has begun to bind
+to the membrane in the the lower half of the cell.  At this stage,
+there is a high concentration of cytoplasmic MinE at the top of the
+cell, and by 16 seconds we begin to see the formation of a MinE ring
+just below the center of the cell.  At 18 seconds, the cell has
+reached its original state, with MinD:ATP bound to the membrane on the
+lower third of the cell, a high concentration of cytoplasmic MinE in
+the upper half of the cell, and a MinE ring pushing on the
+membrane-bound MinD:ATP.
 
@@
   \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-300-50-0-0-1500}
-  %\includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-200-50-0-0-1500}
   \caption{Total protein fluctuation in the right, middle, and left
-    parts of a 5$\micron$ by 1$\micron$ pill shaped cell (above) and a
-    3$\micron$ by 1$\micron$ pill shaped cell (below).  The vertical axis shows
-    stacked the total number of proteins that are of four different
-    compound stages and in the right section of the cell (bottom four
-    colors), in the middle of the cell (middle four colors) and in the
-    left section of the cell (top four colors). The different forms of
-    protein changes while the total number of MinD protein in the cell
-    remains constant, shown by the fact that the very top line is
-    horizontal.}
+    parts of a natural pill shaped cell.  The cell is the same as is
+    shown in Fig.~\ref{image-p}.  The time axis is also identical to
+    that shown in Fig.~\ref{image-p}, and shows one period of the
+    oscillation after the system has settled down.  The vertical axis
+    shows stacked the total number of proteins that are of four
+    different compound stages and in the right section of the cell
+    (bottom four colors), in the middle of the cell (middle four
+    colors) and in the left section of the cell (top four colors). The
+    different forms of protein changes while the total number of MinD
+    protein in the cell remains constant, shown by the fact that the
+    very top line is horizontal.}
   \label{box-p}
@@
 
-\davidsays{We should make Fig. \ref{box-p} and Fig. \ref{image-p} plot
-  for precisely the same times, that will make it way easier to read
-  the two plots.}  While Fig.~\ref{image-p} is helpful for visualizing
+While Fig.~\ref{image-p} is helpful for visualizing
 the process occuring in the Min system, it is does not show the
@@
 
-\fixme{our 5 length cells are labeled as 4 cells in the file labels,
-  since 4 is the length of the cylinder. In the text I'll refer to the
-  5 length cells (file says 4) as 5 length cells.  What huang's paper
-  calls 4 length cells will be labeled by our files as 3 length cells,
-  but will be refered in our text as 4 length cells}.  We can see a
+We can see a
 clear difference in period between the $5\mu$, $4\mu$, and $2\mu$

### 2013-11-27 pyplots/image_plot.py

@@ -30,7 +30,7 @@ def timemin(protein):
     return min([v.min() for v in protein])
 
 proteinList = ["nADP","nATP","ND","NDE","nE"]
-proteinLabels = ["MinD:ADP (ctyo)",
+proteinLabels = ["MinD:ADP (cyto)",
                  "MinD:ATP (cyto)",
                  "MinD:ATP (mem)",
                  "MinE:MinD:ATP (mem)",
